### 2017-04-17 bCFT_notes.tex
[init] establish repository

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[compact]{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\usepackage{todonotes}

\graphicspath{{./}{./images/}}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\tr}[0]{\text{tr}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\tikzset{
    partial ellipse/.style args={#1:#2:#3}{
        insert path={+ (#1:#3) arc (#1:#2:#3)}
    }
}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

% configure hyperref to remove ugly boxes from links
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}

\title{Boundary Conformal Field Theory}
\author{Tianci Zhou}

\begin{document}
\maketitle
\large

\section{Conformal Interface of Free Boson}
% flatex input: [boson_interface.tex]
\label{sec:var-boson}
[Section 2.1-2.2 of \cite{bachas_permeable_2002}.]

Let's consider the conformal interface connecting two possibly different free boson CFTs. Suppose the interface is located at $x = 0$ that glues the two theories in such a way that 
\begin{equation}
\begin{bmatrix}
\partial_t \phi\\
\partial_x \phi\\ 
\end{bmatrix}_{x = 0^-} 
 = M \begin{bmatrix}
\partial_t \phi\\
\partial_x \phi\\ 
\end{bmatrix}_{x = 0^+} 
\end{equation}
One may write the field on the left/right as $\phi^1$($\phi^2$), and then the gluing condition is
\begin{equation}
\partial_{\mu} \phi^1 = M_{\mu\nu} \partial_{\nu} \phi^2 
\end{equation}
The interface is now penetrable, and condition \eqref{eq:stress-cond} is weakened that only requires continuity of the momentum across the interface. From the explicit expression
\begin{equation}
T^{xt} = - g \partial_x \phi \partial_t \phi  = -g(\partial_{\mu} \phi \sigma^x_{\mu\nu}  \partial_{\nu} \phi ) 
\end{equation}
we have the relation
\begin{equation}
\partial_{\mu} \phi^2 \sigma^x_{\mu\nu}  \partial^2_{\nu} \phi -  \partial_{\mu} \phi^1 \sigma^x_{\mu\nu}  \partial^1_{\nu} \phi = 
\partial_{\mu} \phi^2 [\sigma^x_{\mu\nu} - M^T  \sigma^x M)_{\mu\nu} ]  \partial_{\nu} \phi^2 = 0
\end{equation}
For generic field configuration $\phi^2$, the condition is satisfied only when
\begin{equation}
\sigma^x = M^T \sigma^x M 
\end{equation}
By diagonalizing $\sigma^x$ and doing corresponding orthogonal transformation on $M$, 
\begin{equation}
\sigma^z = ( OMO^T  )^T \sigma^z ( OMO^T )  \quad 
O = \frac{1}{\sqrt{2}} 
\begin{bmatrix}
1 & 1 \\
1 & -1 \\                       
\end{bmatrix}
\end{equation}
we realize $O M O^T$ is in the Lorentz group $O( 1, 1 )$, whose 4 disconnected components that are determined by the sign of determinants and the $00$ element. A natural boost parameterization are 
\begin{equation} 
\Lambda = O M O^T = \pm 
\begin{bmatrix}
\cosh \beta & \sinh \beta \\
\sinh \beta & \cosh \beta \\  
\end{bmatrix}
\quad \pm 
\begin{bmatrix}
\cosh \beta & -\sinh \beta \\
\sinh \beta & -\cosh \beta \\  
\end{bmatrix}
\end{equation}
Reverting back to $M$, we have $\lambda = e^{-\beta}$
\begin{equation}
M_1 = \pm 
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda \\
\end{bmatrix}
\quad 
M_2 = \pm 
\begin{bmatrix}
0 & \lambda\\
\lambda^{-1} & 0 \\
\end{bmatrix}
\end{equation}
The $\pm$ branches in each $M$ can be combined if we set $\lambda = \text{tan} \theta$ for $\theta \in [- \frac{\pi}{2}, \frac{\pi}{2} ] $.

The physical significance of $\theta$ can be seen in the following scattering picture. The solutions of equation of motion are the left and right moving waves. The derivative $\partial_{-} = \partial_t - \partial_x$ removes the left moving component($x+t$) and hence can generate right moving fields $\partial_{-} \phi$. The process of right moving $\phi^1$ combined with left moving $\phi^2$ to generate a left moving $\phi^1$ and right moving $\phi^2$
\begin{equation}
\partial_{-} \phi^1 + \partial_{+} \phi^2 \rightarrow \partial_{+} \phi^1 + \partial_{-} \phi^2
\end{equation}
can be described by the scattering matrix
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
\end{equation}
After some linear algebra, we find that $2\theta$ is the angle that parameterize the scattering matrix\footnote{I adopt several different conventions from \cite{bachas_permeable_2002}. 1. I put $\partial_t$ as the first entry of the vector. 2. The matrices $M(\lambda)$ is actually $M(\lambda^{-1} )$ in \cite{bachas_permeable_2002}. These two cancel out and the resulting gluing conditions are the same. 3. I take $\partial_{-} \phi^1, \partial_{+} \phi^2$ as incoming wave, so that the $S$ matrix maps it to the outgoing waves, while \cite{bachas_permeable_2002} use the opposite: they obtain $S^{-1}$. Incidentally, $S = S^{-1}$. 4. I take $\partial_{-} = \partial_t - \partial_x $, while \cite{bachas_permeable_2002} seems to take $\partial_{-} = \partial_x - \partial_t$. Interchanging $x$ and $t$ amounts to change $\lambda$ to $\lambda^{-1}$, or $\theta$ to $\frac{\pi}{2}- \theta$, which indeed converts $S$ here to the $S$ in \cite{bachas_permeable_2002}. }
\begin{equation}
\label{eq:S1-S2}
S_1 =
\begin{bmatrix}
\cos 2 \theta & \sin 2 \theta \\
\sin 2 \theta & - \cos 2 \theta     
\end{bmatrix}
\qquad
S_2 = 
\begin{bmatrix}
-\cos 2 \theta & \sin 2 \theta \\
-\sin 2 \theta & - \cos 2 \theta   
\end{bmatrix}
\end{equation}

\subsection{Example: Free Boson with Different Compactification Radii}

[Section 2.2 of \cite{bachas_permeable_2002}.]

Suppose $\phi^1$ and $\phi^2$ are compact Bosons with compactification radii $2\pi R_1$ and $2\pi R_2$. We can rescale them to a single field 
\begin{equation}
\phi = \left\lbrace
       \begin{aligned}
         R_1^{-1} \phi^2  & \quad  x < 0 \\
         R_2^{-1} \phi^2  & \quad x > 0  \\
       \end{aligned} \right. 
\end{equation}
such that $\phi$ is a compact boson on the whole plane with radius $2\pi$, whose action(in Euclidean time) reads
\begin{equation}
S = \frac{g}{2} R_1^2 \int_{x \le 0 } \left(  \nabla \phi \right)^2 d\tau dt  + \frac{g}{2} R_2^2 \int_{x > 0 } \left(  \nabla \phi  \right)^2 d\tau dt 
\end{equation}
Both the bulk action as well as the interface should be invariant under the conformal transformation. We do such a conformal transformation, which induces a change on the field $\phi \rightarrow \delta \phi $, and since the bulk is invariant, we only need to check the boundary term
\begin{equation}
S = \frac{g}{2} \int_{x = 0 } ( R_1^2 \partial_x \phi\big|_{x = 0^{-}}   - R_2 ^2 \partial_x \phi \big|_{x = 0^{+}} ) \delta \phi  d\tau = 0
\end{equation}
The boundary condition
\begin{equation}
R_1^2 \partial_x \phi\big|_{x = 0^{-}}  = R_2 ^2 \partial_x \phi \big|_{x = 0^{+}}
\end{equation}
which makes any variation vanish must be conformal invariant. In terms of the $\phi^1$, $\phi^2$ fields
\begin{equation}
\partial_x \phi^1 = \frac{R_2}{R_1} \partial_x \phi^2 
\end{equation}
According to our previous analysis, it corresponds to $M_1$ with $\lambda = \frac{R_2}{R_1} = \tan \theta$, namely
\begin{equation}
\label{eq:cpt_boson_bd}
\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  - \cos \theta \phi^2 ) = 0
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:

% flatex input end: [boson_interface.tex]

% configure hyperref to remove ugly boxes from links

\subsection{Folding Trick and Boundary State}
% flatex input: [folding.tex]

[Section 2.3-2.4 of \cite{bachas_permeable_2002}]

We can fold the field $\phi^2$ to the left half plane on top of $\phi^1$, then the boundary at $x = 0$ is impenetrable for the tensor theory and therefore is a boundary state of Boson.

The folding takes $x$ to $-x$ in $\phi^2$, so its $x$ derivative in the boundary condition \eqref{eq:cpt_boson_bd} will change sign and becomes\footnote{Change $\theta$ to $\frac{\pi}{2} - \theta$ to compare relevant result with in \cite{bachas_permeable_2002}. I believe the \cite{bachas_permeable_2002} made a mistake here. Nevertheless the Casimir energy is insensitive to this change.},
\begin{equation}
\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  + \cos \theta \phi^2 ) = 0
\end{equation}
It looks like the rotated field within $\partial_t$ takes Dirichlet boundary condition and the other orthogonal field within $\partial_x $ takes Neumann boundary condition, so we have\footnote{We will deal with the winding sector in Sec.~\ref{sec:winding}}
\begin{equation}
\label{eq:rot-D-N}
\begin{aligned}
\cos  \theta a^1_n - \sin \theta a^2_n  &= + \left( \cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} \right)\\
\sin  \theta a^1_n + \cos \theta a^2_n  &= - \left( \sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} \right) 
\end{aligned}
\end{equation}
The left and right sides can be regarded as two new sets of $a^1$ and $a^2$ whose commutation relation is preserved by the orthogonal rotation. Consequently, the boundary state is
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle &= \exp\Big\{ \sum_{n > 0 } \frac{1}{n} (\cos  \theta a^1_{-n} - \sin \theta a ^2_{-n} )(\cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} ) \\
& \,\,  \qquad \qquad -\frac{1}{n} (\sin  \theta a^1_{-n} + \cos \theta a ^2_{-n} )(\sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} )
\Big\} | 0 \rangle \\
& = \exp\Big\{ \sum_{n > 0 } \frac{1}{n} \left( \cos 2\theta a^1_{-n} \bar{a}^1_{-n}  - \cos 2\theta a ^2_{-n} \bar{a}^2_{-n}   
- \sin 2 \theta a ^2_{-n}\bar{a}^1_{-n}  - \sin 2 \theta a ^1_{-n}\bar{a}^2_{-n}  \right ) \Big\}| 0 \rangle \\
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{bmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{bmatrix}
S_1
\begin{bmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{bmatrix} \Big\}
\end{aligned}
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [folding.tex]

% configure hyperref to remove ugly boxes from links

\section{Compact Boson Winding Modes}
\label{sec:winding}
% flatex input: [D_and_N.tex]

\subsection{Dirichlet and Neumann Boundary Conditions}

[Section 2 of \cite{bachas_fusion_2008}, Section 6.3.5 of \cite{di_francesco_conformal_1997}]

The winding modes of compact boson determines the conformal dimensions of the primary fields. It therefore restrict possible bcc operators on the boundary. In this section we work the simple Dirichlet and Neumann conditions for the winding modes.

{\bf Mode Expansion:} 
Suppose the boson is compactified as $\phi \rightarrow \phi + 2\pi R$, then mode expansion in Eq.~\ref{eq:boson-mode-exp} will have a different zero mode\footnote{The sign of the $x$ term is different from Eq. (6.91) in \cite{di_francesco_conformal_1997}, but calculation later shows that the $-$ sign is correct to give the $(\frac{n}{4\pi gR} + \frac{1}{2} \frac{m}{R})$ combination for $z$. }  
\begin{equation}
\begin{aligned}
\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \text{oscillator part}  \\
&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  + \text{oscillator part}  \\
\end{aligned}
\end{equation}
where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. A particle living on unit circle $[0, 2\pi]$ have integer($m \hbar$) angular momentum(conjugate momentum), and so momentum of Boson living on $[0, 2\pi R]$ will have $\frac{n}{R}$ as its eigenvalues.

The left and right mode decomposition is again done by complex variables
\begin{equation}
z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
\end{equation}
which leads to
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
\end{aligned}
\end{equation}
From the holomorphic derivative 
\begin{equation}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1}  \qquad a_0 = \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)
\end{equation}
we make up the zero mode term in $L_0$ is absent for free boson, 
\begin{equation}
L_0 = \sum_{n> 0 } a_{-n} a_n + \frac{1}{2} a_0^2 =   2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2 + \sum_{n> 0 } a_{-n} a_n
\end{equation}
The ground state now has dimension $h = 2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2$.

{\bf Dirichlet and Neumann}:

Now that we have a legitimate $a_0$ that behaves similar with other oscillator modes, we can then impose the same Dirichlet condition in Eq.~\ref{eq:D-mode-cond}, on the unit circle, the logarithmic term gives 
\begin{equation}
 -i \frac{1}{\sqrt{ 4\pi g}}  ( a_0 \ln z  + \bar{a}_0 \ln \bar{z} )\Big|_{\text{unit circle }} = 0 \quad \implies \quad a_0 - \bar{a}_0 = 0  \quad \implies \quad m = 0
\end{equation}
The boundary states satisfying this boundary condition can be a linear superposition of the zero winding states. Since it's Dirichlet, it is an eigenstate of $\hat{\phi}_0$\footnote{We have quantized the theory such that $[\phi_0, \frac{n}{R}] = i $. },
\begin{equation}
|{\rm D} \rangle  = g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle  
\end{equation}
With this one can show
\begin{equation}
\phi( x, t = 0 ) | {\rm D} \rangle = \phi_0 | {\rm D} \rangle
\end{equation}

Similarly, the Neumann boundary condition now has the $n = 0$ term in Eq.~\ref{eq:N-mode-cond}
\begin{equation}
 a_0 + \bar{a}_0 = 0  \quad \implies \quad n = 0 
\end{equation}
the resulting boundary state is a linear superposition over the winding sector
\begin{equation}
| {\rm N} \rangle = g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle 
\end{equation}
In fact, Neumann becomes Dirichlet in the dual field, so $\bar{\phi}_0$ is related to the boundary value of the dual field.

One can check that this indeed satisfies the Neumann boundary condition
\begin{equation}
\partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [D_and_N.tex]

% configure hyperref to remove ugly boxes from links
\subsection{Gluing Condition for Winding Modes}
% flatex input: [glue_zero.tex]
[Appendix A of Oshikawa\cite{oshikawa_boundary_2010}]

In Sec.~\ref{sec:var-boson}, we use variational approach to find conformal invariant boundary conditions, but the resulting equation \eqref{eq:cpt_boson_bd} do not provide information about the winding sector. The variational method fails because winding is a global properties of the Boson configuration, meaning insensitive to the local perturbation.

Here we present a general treatment about the winding modes. From the discussion of the Dirichlet and Neumann boundary condition in previous subsection, it seems that the constraints on the oscillator modes can be naturally extended to the zero mode for $n = 0$. We can show that this is in compliance with the conformal invariance.

Suppose in the junction we have a boundary condition that result in the following scattering relation
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
\end{equation}
the conformal invariance constraint gives two solutions $S_1$ and $S_2$ in Eq.~\eqref{eq:S1-S2}. Imagining that we fold $\phi^2$ on top of $\phi^1$, the $x$ derivative on $\phi^2$ then changes sign, we therefore have
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
\end{equation}
It it convenient to work in the holomorphic mode expansion \eqref{eq:boson-mode-exp} for the left and right separation. Specifically
\begin{equation}
\partial_{+} = \frac{4\pi i }{L} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = \frac{4\pi i }{L} z\partial_{z}
\end{equation}
and
\begin{equation}
\sum_{n \in \mathbb{Z}}  
\begin{bmatrix}
\bar{a}^1_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n}\\ 
\bar{a}^2_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n} 
\end{bmatrix}
 = S
\sum_{n \in \mathbb{Z}}
\begin{bmatrix}
a^1_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
a^2_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
\end{bmatrix}
\end{equation}
We impose boundary condition at $t = 0$\footnote{In Sec.~\ref{subsec:free-boson}, we interchange $x$ and $t$, and impose boundary condition at $x = 0$. For whatever convention, the boundary is on the unit circle $|z| = 1$. }, so $z$  is on the unit circle and $\bar{z} = \frac{1}{z}$. By comparing the modes(Fourier series on circle), we have
\begin{equation}
\label{eq:mode-eq}
a_n^i - (S^{\scalebox{0.5}[0.8]{\( - \)}1})_{ij} \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^j = 0
\end{equation}
This is clearly a generalization of the Dirichlet and Neumann boundary conditions, where the orthogonal matrix $S$ is replaced by $\pm \mathbb{I}$. In fact, the rotation does not change the quadratic relation
\begin{equation}
\sum_i a^i_n a^i_m =  \sum_i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}m}^i
\end{equation}
Hence for the quadratics in the Virasolo generators
\begin{equation}
\begin{aligned}
L_n &= \frac{1}{2} \sum_i  \sum_{m > -1 } (a^i_{n-m} a^i_m  + a^i_{-m} a^i_{n+m } ) - \frac{1}{2} a^i_0 a^i_n 
\end{aligned}
\end{equation}
the cancellation works the same way,
\begin{equation}
\begin{aligned}
L_n - \bar{L}_{-n} &= \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m + a^i_{-m} a^i_{n+m} - \bar{a}^i_{-n-m} \bar{a}^i_{-m} - \bar{a}^i_{m} \bar{a}^i_{-n+m }  )  - \frac{1}{2}( a_0^i a_n^i - \bar{a}_0^i \bar{a}^i _{-n})\\
& = \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m  - \bar{a}^i_{-n+m}\bar{a}^i_{-m})+ (a^i_{-m} a^i_{n+m} - \bar{a}^i_{m} \bar{a}^i_{-n -m }  )\\
& = 0 
\end{aligned}
\end{equation}
We now specialize to the two cases $S = S_1$ and $S_2$.

{\bf Boson $\lambda$ Junction: $S = S_1$}

We need to solve the $n = 0$ of \eqref{eq:mode-eq} for $S^{-1} = S_1^{-1} = S_1$\footnote{Recall that the solution of Eq.~\eqref{eq:mode-eq} for the nonzero mode is $\exp(\frac{1}{n} a_{-n}^{i} S^{-1}_{ij} a_{-n}^j |0\rangle)$. In Eq.~\eqref{eq:R-bs} we do have $R = S_1$. } and
\begin{equation}
a^i_0 = \sqrt{4\pi g}  \frac{1}{4\pi} (2\pi m_i R_i + \frac{1}{g} \frac{n_i}{R_i})
\end{equation}
For notational simplicity, we introduce the compactification lattice and its dual\cite{oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
\end{equation}
the constraint then becomes 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
which is basically the two dimensional case of the multi-component Boson constraints in Eq.~(86) of \cite{oshikawa_boundary_2010}.

Given the $S_1$ matrix in Eq.~\eqref{eq:S1-S2}, we have
\begin{equation}
1 + S_1 = 2  
\begin{bmatrix}
\cos^2 \theta & \sin \theta \cos\theta \\
\sin \theta \cos \theta  & \sin^2 \theta \\
\end{bmatrix}
\quad 
1 - S_1 = 2
\begin{bmatrix}
\sin^2 \theta & -\sin \theta \cos\theta \\
-\sin \theta \cos \theta  & \cos^2 \theta \\
\end{bmatrix}
\end{equation}
both have determinant zero. So the solution of the two lattice vectors in 
\begin{equation}
( 1 + S_1) \vec{M} = -( 1 - S_1 ) \frac{1}{g} \vec{M}^*
\end{equation}
must be the null vectors of the corresponding matrices, i.e. 
\begin{equation}
\vec{M} = ( \cos \theta, -\sin \theta )^\top \qquad \vec{M}^{*} = ( \sin \theta, \cos \theta )^\top 
\end{equation}
In terms of the winding numbers
\begin{equation}
  \tan \theta =  \frac{n_1 R_2}{n_2 R_1 } = -\frac{m_2 R_2}{ m_1 R_1}
\end{equation}
One can take a pair of coprime integers $k_1$ and $k_2$($k_1>0$), such that $-\frac{m_1}{m_2} = \frac{k_1}{k_2}$. That determines all the possible winding numbers of the basis\footnote{\cite{bachas_fusion_2008} takes $-S_1$ as the S matrix, so they have $\vec{M} = ( \cos \theta, \sin \theta)^\top $ and $\tan \theta = -\frac{n_1 R_2}{n_2 R_1 } = \frac{m_2 R_2}{ m_1 R_1} = \frac{k_2 R_2}{k_1 R_1}$ for $\frac{m_1}{m_2} = \frac{k_1}{k_2}$. And this is consistent with their parameterization  $ \left\lbrace
  \begin{aligned}
    m_1 = k_1 M  & \quad n_1 = k_2 N  \\
    m_2 = k_2 M &  \quad n_2 = -k_1 N \\
  \end{aligned} \right. $ }. The linear superposition is beyond conformal invariance, which should be determined by Cardy's consistency condition.

This set of boundary conditions can be viewed as Dirichlet and Neumann on the rotated basis, hence a reasonable conjecture is also the Fourier sum of the basis(constrained by $S_1$)
\begin{equation}
g_{\,\!_{S_1}} \sum_{S_1} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
\end{equation}

{\bf The T-dual Boundary State $S = S_2$}

Now we take $S = S_2$, the zero mode condition becomes
\begin{equation}
( \vec{M} + \frac{1}{g}\vec{M}^* ) =  S_2^{-1}  ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
the solution is
\begin{equation}
\vec{M} =  \frac{1}{g} \frac{1 - S_2}{1 + S_2} \vec{M}^{*} = \frac{1}{g}  \frac{1}{ 1 - \cos 2\theta}
\begin{bmatrix}
  0 & - \sin 2 \theta \\
\sin 2\theta & 0 \\
\end{bmatrix} \vec{M}^*
 = \frac{\cot \theta}{g} \begin{bmatrix}
  0 & - 1 \\
1 & 0 \\
\end{bmatrix}\vec{M}^*
\end{equation}
Using the basis vectors in Eq.~\ref{eq:lattice}, we have
\begin{equation}
\begin{bmatrix}
m_1\\
m_2\\
\end{bmatrix}
 = \frac{2 \cot \theta}{ 4\pi g  R_1 R_2 }
\begin{bmatrix}
-n_2 \\
n_1 
\end{bmatrix}
\end{equation}
Taking the same coprime interger $\frac{m_2}{n_1} = \frac{k_2}{k_1}$, we have the angle\footnote{It takes some effort to match the results with \cite{bachas_fusion_2008}. We both use $\frac{k_2}{k_1}$ the same way, so the parameterization is the same. They use $-S_2$ as oppose to $S_2$ to be the S matrix, so $\vec{M} = \frac{1}{g} \frac{1 + S_2}{1 - S_2} = \frac{\tan \theta}{g}\begin{bmatrix}
  0 & - 1 \\
1 & 0 \\
\end{bmatrix} \vec{M}^*$, their $\tan \theta$ is my $\cot \theta = \frac{k_2}{2k_1 } 4\pi g R_1 R_2$. They use $R \rightarrow \frac{1}{2R}$ as T-duality transformation. If they were to use $R \rightarrow \frac{1}{2R}$(this point corresponds to $g = \frac{1}{4\pi}$), then their $\tan \theta = \frac{k_2}{2 k_1} R_1 R_2$ which will be the same as our $\cot \theta$. So we agree.},
\begin{equation}
  \tan \theta = \frac{2 k_1}{k_2} \frac{1}{4 \pi g R_1 R_2}
\end{equation}
This state can be obtained by taking T duality for one of the bosons, hence it is a Dirichlet/Neumann boundary conditions for these two Bosons. It is then reasonable to use Fourier sum as the physical boundary state
\begin{equation}
g_{_{\,\!_{S_2}}}\sum_{S_2} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
\end{equation}

{\bf The $g$ Factor}:

The $g$ factor can only be determined by Cardy condition, which means that the occurrence $n^h_{ab}$ for each irreducible representation
\begin{equation}
Z_{ab} = \langle a | e^{- \beta  H }  | b \rangle  = \sum_{h} n_{ab}^h \chi_h 
\end{equation}
is an non-negative integer.

Since the character for the compact boson theory is known, we can just compute the amplitude, say $Z_{\lambda_1, \lambda_2}$ adjust the coefficient such the occurrence is an integer. \cite{bachas_fusion_2008} contains a calculation for Dirichlet case. I will not repeat it here.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [glue_zero.tex]

% configure hyperref to remove ugly boxes from links
\subsection{Winding Modes Contribution to Partition Function}
% flatex input: [Z-winding.tex]

In this section, we address the concern about how the winding mode will affect the partition function.
\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 1]
\draw (0,0)--(2,0);
\draw (0,1.5)--++(2,0);
\node () at (1,-0.5) {$\lambda_1$};
\node () at (1,2) {$\lambda_2$};
\draw[-stealth] (1,0.5)--++(0,0.5);
\end{tikzpicture}
\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
\end{figure}

Let the cylinder to have width $\beta$ and the length of in time direction is $\pi$(after folding), we have
\begin{equation}
Z = \langle \lambda_2 | e^{-\pi H} | \lambda_1 \rangle   \qquad H = \frac{4\pi}{ \beta} L_0 
\end{equation}
For the winding mode part, we just replace $L_0$ to be $a_0$. When the two boundary states are identical, the result will be a theta-function
\begin{equation}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{equation}
In the $\beta \rightarrow \infty$ limit, it will be proportional to $\beta$ by Poisson's resummation formula\footnote{One can also approximate the sum by integral in this limit: it will be a two dimensional Gaussian integral and the result is proportional to $\beta$}. So the winding mode part will at most contribute a $\ln \beta$ term in the free energy, which can be neglected in our leading $\beta$ scaling analysis.

The conclusion still holds for different $\lambda$ boundary states, in which case the only change is the possible values of $n_1$ and $m_1$(the lattice). The overlap $\langle \lambda_1 | \lambda_2 \rangle $ will not be zero even if the two sets of coprime integers are different for the two boundary states: they can meet in their least common divisor.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [Z-winding.tex]

% configure hyperref to remove ugly boxes from links

\section{Loschmidt Echo of Connecting Free Bosons}
\subsection{Corrections to Casimir Energy}
% flatex input: [free_boson_echo.tex]

To test our boundary state formalism, we consider the Loschmidt echo of connecting two (non-chiral) non-compact Bosons on the two half planes. 
% flatex input: [fig_H_tau.tex]

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 2]
\draw (0,0) --(0.9,0);
\draw (2.1,0)--++(.9,0);
\node[below] () at (1,-0.15) {$0$};
\fill (1,0) circle (0.02);
\node[below] () at (2,-0.13) {$\tau$};
\fill (2,0) circle (0.02);
\draw[blue] [domain=0:360] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[blue] [domain=0:360] plot ({2+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[red] [-stealth,domain=10:170] plot ({1+0.4*cos(\x)}, {0.4*sin(\x)});
\draw[red] [-stealth,domain=170:10] plot ({2+0.4*cos(\x)}, {0.4*sin(\x)});
\begin{scope}[shift={(2.6,0.6)}]
\node () at (0.08,0.08) {$z$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\begin{scope}[shift={(3.5,0)}]
\draw (1.1,0)--++(0.9,0);
\node[below] () at (1,0.1) {$0$};
\draw[blue] [domain=0:360] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[blue] (1,0) circle (1);
\draw[red] [-stealth,domain=10:170] plot ({1+0.5*cos(\x)}, {0.5*sin(\x)});
\end{scope}
\begin{scope}[shift={(5.6,0.6)}]
\node () at (0.08,0.1) {$\xi$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\begin{scope}[shift={(6.5,0)}]
\draw[dashed] (0,0)--(1.5,0);
\draw[blue] (0,0)--(0,1);
\draw (0,1)--(1.5,1);
\draw[blue] (1.5,1)--(1.5,0);
\draw[-stealth,red] (0.75,0.3)--++(0,0.5);
\end{scope}
\begin{scope}[shift={(7.7,0.6)}]
\node () at (0.09,0.08) {$w$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\end{tikzpicture}
\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction. The solid lines are cuts on the plane, where the upper and lower surfaces are boundary states. Red arrows are the directions of Hamiltonian flow that propagates one boundary state(lower surface) to another(upper surface). The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice). Middle: image of the map $\xi = \frac{z}{\tau - z}$. Right: image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and standard radial quantization can be applied. }
\label{fig:H-tau}
\end{figure}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [fig_H_tau.tex]

After doing the conformal map shown in \label{fig:fig_H}, we can relate the Loschmidt echo we are interested to the Casimir energy of a cylinder subject to different boundary conditions on the top and bottom
\begin{equation}
\mathcal{F} = - \ln |\langle a | e^{- 2\pi H} | b \rangle |^2 = 2 E_c 
\end{equation}
The width of the cylinder $\beta$ contains information of the scale $\tau$ as well as the regulator. Specifically, we set the radii of both blue the semi-circles on the left panel as $\epsilon$, so that the two end points of the dashed line are $(\frac{\tau - \epsilon}{\epsilon}, 0 )$ and $ (\frac{\epsilon}{ \tau - \epsilon}, 0 )$. The resulting width on the right panel is then
\begin{equation}
\beta  = \ln  \frac{\tau - \epsilon}{\epsilon} -  \ln \frac{\epsilon}{ \tau - \epsilon}  = 2 \ln \frac{\tau - \epsilon}{ \epsilon} 
= 2 \ln \frac{\tau}{\epsilon} + \mathcal{O}(\frac{\epsilon}{\tau})
\end{equation}
We calculate the Casimir energy by canonical quantization, zeta function regularized path integral and boundary states in App.~\ref{app:casimir_energy_DD_DN}. All these methods give the following table
\begin{table}[h]
\begin{center}
\begin{tabular}{ |c|c|c|c|c| } 
 \hline
  & P & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
  $E_c $ & $ {\color{red} - \dfrac{1}{12}\beta } $ & ${\color{blue}- \dfrac{1}{48} \beta }$ & ${\color{blue} \dfrac{1}{96} \beta }$ &  ${\color{blue}- \dfrac{1}{48} \beta }$ \\[2ex]
 \hline
\end{tabular}
\end{center}
\caption{Boson Casimir energy subject to different boundary conditions.}
\label{tab:casimir}
\end{table}

{\bf Tom's Argument: } It does not make sense to have positive power for the echo. We must have missed some contributions from the Schwartzian etc.

A simple argument is that by doing periodic boundary conditions, the groundstate energy (Casimir energy) on the original $z$ plane must be zero. So for all these results we should compensate ${\color{red}\frac{1}{12}\beta}$. With this recipe, we have

\begin{table}[h]
\begin{center}
\begin{tabular}{ |c|c|c|c| } 
 \hline
   & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
  $E_c $ &  ${\color{purple} \dfrac{1}{16} \beta }$ & ${\color{purple} \dfrac{3}{32} \beta }$ &  ${\color{purple} \dfrac{1}{16} \beta} $ \\[2ex] \hline   \rule[4ex]{0pt}{1pt}
  $\mathcal{F} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} }$ & ${\color{purple} \dfrac{3}{8}\ln \frac{\tau}{\epsilon}} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} } $ \\[2ex] 
 \hline
\end{tabular}
\end{center}
\caption{Logarithm of Loschmidt echo of different boundary conditions.}
\label{tab:log_echo}
\end{table}

{\bf Cardy-Peschel Formula:}

One can also apply the Cardy-Peschel formula for the two corners of angle $2\pi$
\begin{equation}
F =  \left\{ \frac{\pi}{\theta} h + \frac{c}{24} \Big(  \frac{\theta}{\pi} - \frac{\pi}{\theta}  \Big)   \right\} \ln \tau 
= \left( \frac{1}{2} h + \frac{c}{16}  \right) \ln \tau 
\end{equation}
Since there are two corners, and the echo corresponds to twice the free energy, we have 
\begin{equation}
  \mathcal{F} = ( 2h + \frac{c}{4} ) \ln \tau 
= \left\lbrace
  \begin{aligned}
    {\color{purple}\frac{1}{4} \ln \tau}  &\quad   h = 0 \text{ for DD, NN } \\
    {\color{purple}\frac{3}{8} \ln \tau}  &\quad   h = \frac{1}{16} \text{ for DN, ND}  \\
  \end{aligned} \right. 
\end{equation}

{\bf Various Corrections}

We identify the various corrections needed in the $z \rightarrow \xi \rightarrow w$ transformation.

On the $z$ plane of Fig.~\ref{fig:H-tau}, the blue lines are short distance regulators for the two corners. As discussed in the corner case of App.~\ref{app:cardy-peschel}, the inner circle regulator only contribute $\frac{c}{6}\ln \frac{\epsilon}{a} $, which is negligible when $\epsilon$ is the of cutoff order. However, after mapping to the $\xi$ plane, the outer circle will contribute $-\frac{c}{6} \beta$, which should not be there. So
\begin{equation}
F_{\xi } = F_{z} + \frac{c}{6} \beta 
\end{equation}

In App.~\ref{app:H_in_r}, we showed that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian
\begin{equation}
H_{z} = H_{\xi} - \frac{c}{24\pi} \beta 
\end{equation}
After the evolution for $2\pi$, the difference in the free energy is
\begin{equation}
F_w = F_{\xi} - \frac{c}{12} \beta 
\end{equation}
Gathering the two together, we obtain the missing $\frac{c}{12} \beta$ between the echo diagram and the Casimir energy, 
\begin{equation}
F_{w} = F_z + {\color{red} \frac{c}{12}\beta }
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [free_boson_echo.tex]

% configure hyperref to remove ugly boxes from links
\subsection{Folding Trick}
% flatex input: [echo_folding.tex]

We use the folding trick to compute it again but using gluing condition(dashed line in Fig.~\ref{fig:H-tau_fold}) in place of trivial boundary condition after connecting the two bosons. These will corresponds to connecting boundary condition for bosons of different radii.
% flatex input: [fig_H_tau_fold.tex]

\begin{figure}[htb]
\centering
\begin{tikzpicture}[scale = 2]
\draw (0,0) --(0.9,0);
\draw[dashed] (1.1,0)--++(0.8,0);
\draw (2.1,0)--++(.9,0);
\node[below] () at (1,0) {$0$};
\fill (1,0) circle (0.02);
\node[below] () at (2,0) {$\tau$};
\fill (2,0) circle (0.02);
\draw[blue] [domain=0:180] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[blue] [domain=0:180] plot ({2+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[red] [-stealth,domain=10:170] plot ({1+0.4*cos(\x)}, {0.4*sin(\x)});
\draw[red] [-stealth,domain=170:10] plot ({2+0.4*cos(\x)}, {0.4*sin(\x)});
\begin{scope}[shift={(2.6,0.6)}]
\node () at (0.08,0.08) {$z$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\begin{scope}[shift={(3.5,0)}]
\draw (0,0) --(0.9,0);
\draw[dashed] (1.1,0)--++(0.9,0);
\node[below] () at (1,0) {$0$};
\draw[blue] [domain=0:180] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[blue] [domain=0:180] plot ({1+1*cos(\x)}, {1*sin(\x)});
\draw[red] [-stealth,domain=10:170] plot ({1+0.5*cos(\x)}, {0.5*sin(\x)});
\end{scope}
\begin{scope}[shift={(5.6,0.6)}]
\node () at (0.08,0.1) {$\xi$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\begin{scope}[shift={(6.5,0)}]
\draw[dashed] (0,0)--(1.5,0);
\draw[blue] (0,0)--(0,1);
\draw (0,1)--(1.5,1);
\draw[blue] (1.5,1)--(1.5,0);
\draw[-stealth,red] (0.75,0.3)--++(0,0.5);
\end{scope}
\begin{scope}[shift={(7.7,0.6)}]
\node () at (0.09,0.08) {$w$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\end{tikzpicture}
\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice). Middle: image of the map $\xi = \frac{z}{\tau - z}$. Right: image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and standard radial quantization can be applied. }
\label{fig:H-tau_fold}
\end{figure}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [fig_H_tau_fold.tex]

Set aside the corrections from the various Schwartzian, we check the dilation part the Hamiltonian with App.~\ref{app:casimir_energy_DD_DN}, 
\begin{equation}
H =  \frac{2\pi }{\beta} ( L_0 + \bar{L}_0 )
\end{equation}
Acting on the boundary state, it is effectively
\begin{equation}
H = \frac{4\pi}{\beta} L_0 
\end{equation}
We use the matrix notation to represent the 4 sets of bosons in this problem: $\vec{b}_1, \vec{b}_2, \bar{\vec{b}}_1, \bar{\vec{b}}_2$. The Hamiltonian(without shifting) is
\begin{equation}
H = ( \vec{b}_1^{\dagger}, \vec{b}_2^{\dagger}) 
\begin{bmatrix}
M & 0 \\
0& M \\                                                
\end{bmatrix} 
\begin{pmatrix}
\vec{b }_1\\
\vec{b }_2 \\
\end{pmatrix}
\end{equation}
where $M = \frac{4\pi^2}{\beta} \text{diag}(1,2,\cdots )$. The boundary state \eqref{eq:bd_state} in terms of bosonic operators is
\begin{equation}
  |B \rangle = \exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R  
\begin{pmatrix}
  \bar{\vec{b}}^{\dagger}_1\\
  \bar{\vec{b}}^{\dagger}_2\\
\end{pmatrix}\right\}  | 0 \rangle 
\end{equation}
The choice of $R$ depend on different boundary conditions
\begin{equation}
\label{eq:R-bs}
R =
\left\lbrace
\begin{aligned}
   \text{diag}( \mathbb{I}, \mathbb{I} )  &  \quad \text{DD} \\
   \text{diag}( -\mathbb{I}, \mathbb{I} )  &  \quad \text{ND} \\
   \text{diag}( \mathbb{I}, -\mathbb{I} )  &  \quad \text{DN} \\
   \text{diag}( -\mathbb{I}, -\mathbb{I} )  &  \quad \text{NN} \\
\end{aligned} \right.  
\quad
\text{gluing condition:}\quad 
R = 
\begin{bmatrix}
\cos 2 \theta \, \mathbb{I} &  \sin 2 \theta \, \mathbb{I} \\
 \sin 2 \theta \, \mathbb{I}& -\cos 2\theta \, \mathbb{I}\\  
\end{bmatrix} = S_1 \otimes \mathbb{I} 
\end{equation}
the trivial boundary condition in the previous calculation corresponds to $\theta = \frac{\theta}{2}$.

According to App.~\ref{app:pf_of_id}, the amplitude we are interested is
\begin{equation}
\begin{aligned}
Z_{ab} &= \langle B_{\rm gluing} | e^{- H\pi } | B_{\rm open}  \rangle \\
&= \langle 0 | 
\exp\left\{ ( \vec{b}_1 \vec{b}_2 ) R^*_a
\begin{pmatrix}
  \bar{\vec{b}}_1\\
  \bar{\vec{b}}_2\\
\end{pmatrix}\right\} 
\exp \Big\{ (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) 
\begin{bmatrix}
-M & \\
& -M 
\end{bmatrix}
\begin{pmatrix}
\vec{\bar{b}}_1\\
\vec{\bar{b}}_2
\end{pmatrix}\Big\} 
\exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R_b
\begin{pmatrix}
  \bar{\vec{b}}^{\dagger}_1\\
  \bar{\vec{b}}^{\dagger}_2\\
\end{pmatrix}\right\} 
| 0 \rangle \\
& =  \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[e^{-M}, e^{-M} ] R_b \Big)} \\
\end{aligned}
\end{equation}
We parameterize the boundary condition at the open end by $R_b = \text{diag}(b_1 \mathbb{I} , b_2 \mathbb{I})$($1$ for Dirichlet, $-1$ for Neumann). In this notation,
\begin{equation}
\begin{aligned}
Z_{ab} & = \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[(b_1)e^{-M}, (b_2)e^{-M} ]\Big)} \\
& = \frac{1}{\det\Big(1 - ( S_1 \otimes \mathbb{I})  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
& = \frac{1}{\det\Big(S^{-1}_1 \otimes \mathbb{I}  -  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
\end{aligned}
\end{equation}
The Casimir energy from this partition function is thus 
\begin{equation}
\begin{aligned}
E_c   &= - \ln |Z_{ab}| = \ln \det 
\begin{bmatrix}
\cos 2 \theta \, \mathbb{I}  - (b_1) e^{-M} & - \sin 2 \theta \, \mathbb{I} \\
-\sin 2 \theta \, \mathbb{I}  & -\cos 2 \theta \, \mathbb{I}  - (b_2) e^{-M} \\
\end{bmatrix}\\
&= \sum_i \ln [1  - ( b_1 - b_2 ) \cos 2 \theta e^{-\lambda_i } + ( b_1 b_2) e^{-2 \lambda_i } ]  \\
&= \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 -( b_1 - b_2 ) \cos 2 \theta e^{-x } - ( b_1 b_2) e^{-2 x} ] 
\end{aligned}
\end{equation}

There are two different cases
\begin{enumerate}
\item $b_1 = b_2 = \pm 1$, DD, NN. Then
\begin{equation}
  E_c = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln (1 - e^{-2 x} ) = \frac{\beta}{8\pi^2}( - \text{Li}_2 (1) ) = {\color{blue}- \frac{1}{48}\beta}
\end{equation}
\item $b_1 = -b_2 = \pm 1$, DN, ND. First consider $b_1 = 1$, then
\begin{equation}
\label{eq:dn_lambda_bd_state}
\begin{aligned}
E_c &=  \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 - 2  \cos 2 \theta e^{-x } + e^{-2 x} ] \\
&= \frac{\beta}{4\pi^2} \Big[-\text{Li}_2(e^{2i \theta} ) -  \text{Li}_2(e^{-2i \theta} ) \Big]  = \frac{\beta}{4\pi^2} \Big[-2 \pi^2 B_2 ( \frac{\theta}{\pi }) \Big]\\
&= - \frac{\beta}{2} B_2 ( \frac{\theta}{\pi })
\end{aligned}
\end{equation}
where we have used the identity
\begin{equation}
\text{Li}_n( e^{ 2\pi i x }) + (-1)^n \text{Li}_n ( e^{-2\pi i x} ) = - \frac{(2\pi i )^n}{ n!} B_n ( x) , \qquad 0 \le \text{Re}(x)<1, \text{Im}(x) > 0 
\end{equation}
For $n = 2$, we need the second Bernoulli polynomial
\begin{equation}
B_2( x) = x^2 - x + \frac{1}{6} , \quad B_2( \frac{1}{4} ) = - \frac{1}{48} 
\end{equation}
hence
\begin{equation}
E_c = {\color{blue} \frac{1}{96}\beta } 
\end{equation}
The other case with $b_1 = -1$ corresponds to the $\theta \rightarrow \frac{\pi}{2} - \theta$, and we have the same answer. 
\end{enumerate}

The folding trick boundary state agrees with all the other calculations. With the Casimir energy correction, it reproduces the logarithmic echo in Tab.~\ref{tab:log_echo}.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [echo_folding.tex]

% configure hyperref to remove ugly boxes from links

\section{Bipartite Fidelity}
\subsection{Finite Size Scaling}
% flatex input: [fidel_fs.tex]

Bipartite fidelity is the overlap of the groundstates of two Hamiltonians. It is diagrammatically shown in Fig.~\ref{fig:fidel}. Regarding it as a partition function, we analyze the finite size dependence on $L$ of the free energy
\begin{equation}
\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z   = 2 E_c = \sim \# \ln L 
\end{equation}
In some sense it is the echo diagram with $\tau \gg L$ and can provide the same information yet easier to be computed numerically. 
% flatex input: [fig_fidel.tex]

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 1.2]
\draw (0,0) -- (3,0);
\draw (0,2) -- (3,2);
\draw (0,1.02) --++( 1.5, 0);
\draw (0,0.98) --++( 1.5, 0);
\draw[dashed] (1.5,1) --++( 1.5, 0);
\node () at (4.5,1.2) {\Large $\xrightarrow{\rm folding}$};
\begin{scope}[shift={(6,0.5)}]
\draw (0,0) -- (1.5,0);
\draw[dashed] (1.5,0) -- (3,0);
\draw (0,1.2) -- (3,1.2);
\draw[-stealth] (2,0.9)--(2, 1.18);
\draw[-stealth] (2,0.3)--(2, 0.02);
\node () at (2,0.6) {$L$};
\end{scope}
\end{tikzpicture}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution on the two infinitely extended side produces the groundstate of the disconnected/connected Hamiltonian. The right diagram is the result of folding the lower part of the diagram up, so that all the edges are conformal invariant boundary states.}
\label{fig:fidel}
\end{figure}
% flatex input end: [fig_fidel.tex]

% flatex input: [fig_fidel_map.tex]
\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 1.5]
\draw (0,0) -- (1.4,0);
\draw[dashed] (1.6,0) -- (3,0);
\draw[fill] (1.5,0) circle (0.02);
\draw[blue] [domain=0:180] plot ({1.5+0.1*cos(\x)}, {0.1*sin(\x)});
\draw (0,1.2) -- (3,1.2);
\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
\node () at (2.5,0.6) {$L$};
\node[below] () at (0.75,0) {$a$};
\node[below] () at (2.25,0) {$b$};
\node[above] () at (1.5,1.2) {$c$};
\draw[blue] (3,0)--++(0,1.2);
\begin{scope}[shift={(0.5,0.6)}]
\node () at (0.1,0.1) {$w$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\begin{scope}[shift={(7,0)}]
\draw (-1.5,0)--(0.3,0);
\draw[dashed] (0.5,0)--(1.5,0);
\draw[fill] (.4,0) circle (0.02);
\draw[fill] (0,0) circle (0.02);
\draw[blue] [domain=0:180] plot ({0.4+0.1*cos(\x)}, {0.1*sin(\x)});
\draw[blue] [domain=0:180] plot ({1.5*cos(\x)}, {1.5*sin(\x)});
\begin{scope}[shift={(0.6,0.8)}]
\node () at (0.1,0.1) {$z$};
\draw (0,0.1)--(0,0)--(0.1,0);
\end{scope}
\end{scope}
\end{tikzpicture}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}

% flatex input end: [fig_fidel_map.tex]

As usual, we map the diagram to the upper half plane and close it, as shown in Fig.~\ref{fig:fidel-map}. If the three boundary conditions are all different, then there are two bcc operators on the real axis. We first deal with the easy one where $a = c$. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. We can then machinery developed in the echo calculation. In this case, the length of the cylinder is
\begin{equation}
\beta = \ln e^{\pi \frac{W}{L}} - \ln \pi \frac{\epsilon}{L}  \sim \ln L 
\end{equation}
Since the fidelity is twice the Casimir energy, we shall make the replacement recipe $\beta \sim 2 \ln L$.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [fidel_fs.tex]

% configure hyperref to remove ugly boxes from links
% flatex input: [fidel_num_res.tex]

\subsection{Comparison with Numerical Results}

We check several interesting cases in the numerical fidelity calculation of free boson interface.

From our previous calculation, DD/NN $\rightarrow \lambda$ is trivial. The interesting case is the DN $\rightarrow \lambda$ interface. Using either the boundary state or ground state energy calculation in App.~\ref{app:gnd_dn_lambda} plus the correction, we have
\begin{equation}
\begin{aligned}
\mathcal{F} &= \frac{\beta}{2}( - x^2 + x - \frac{1}{6} ) + {\color{red} \frac{\beta}{12}} = \frac{\beta}{2}( - x^2 + x ) \\
&= ( - x^2 + x ) \ln L  \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
\end{aligned}
\end{equation}
% flatex input: [fig_dn_lambda.tex]

\begin{figure}[h]
% settings for subfigure 1
\begin{minipage}[t]{0.3\linewidth}
\centering
\begin{tikzpicture}[scale = 1.5]
\draw (0,0.2) -- ++(3,0);
\draw (0,1.8) -- ++(3,0);
\draw (0,1.02) --++( 1.5, 0);
\draw (0,0.98) --++( 1.5, 0);
\node[above] () at (1.5,1.8) {N};
\node[below] () at (1.5,0.2) {D};
\node[above] () at (0.75,1) {N};
\node[below] () at (0.75,1) {D};
\node[below] () at (1.75,1) {$\lambda$};
\draw[dashed] (1.5,1) --++( 1.5, 0);
\node[right] () at (1.2,-0.5) {$\downarrow$};
\node[right] () at (1.4,-0.5) {\large folding};
\begin{scope}[shift={(0,-2.5)}]
\draw (0,0) -- (1.5,0);
\draw[dashed] (1.5,0) -- (3,0);
\draw[fill] (1.5,0) circle (0.02);
\draw (0,1.2) -- (3,1.2);
\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
\node () at (2.5,0.6) {$L$};
\node[below] () at (0.75,0) {DN};
\node[below] () at (2.25,0) {$\lambda$};
\node[above] () at (1.5,1.2) {DN};
\end{scope}
\end{tikzpicture}
\caption{DN $\rightarrow \lambda$ diagram before and after folding}
\end{minipage}
\hfill
% settings for subfigure 2
\begin{minipage}[t]{0.65\linewidth}
\centering
\includegraphics[width=\textwidth]{DN_DN2tan.pdf}
\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
\end{minipage}
\end{figure}
% flatex input end: [fig_dn_lambda.tex]

\begin{figure}[!h]
% settings for subfigure 1
\begin{minipage}[t]{0.3\linewidth}
\centering
\begin{tikzpicture}[scale = 1.5]
\begin{scope}[shift={(0.5,0)}]
\draw (0,1) arc (90:270:0.15 and 0.5);
\draw[dashed] (0,0) arc (-90:90:0.15 and 0.5);
\draw (0,1) --++(2, 0);
\draw (0,0) --++(2, 0);
\draw[dashed] (1,0.5) --++(0.8, 0);
\node[below] () at (1.3,0.5) {$\lambda$};
\draw (2,0.5) ellipse (0.15 and 0.5);
\end{scope}
\node[right] () at (1,-0.5) {$\downarrow$};
\node[right] () at (1.2,-0.5) {\large squeezing};
\begin{scope}[shift={(0,-2.5)}]
\draw (0,0) -- (1.5,0);
\draw[dashed] (1.5,0) -- (3,0);
\draw[fill] (1.5,0) circle (0.02);
\draw (0,1.2) -- (3,1.2);
\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
\node () at (2.5,0.6) {$L$};
\node[below] () at (0.75,0) {$\lambda = 1$};
\node[below] () at (2.25,0) {$\lambda$};
\node[above] () at (1.5,1.2) {$\lambda = 1$};
\end{scope}
\end{tikzpicture}
\caption{P $\rightarrow \lambda$ diagram before and after squeezing}
\end{minipage}
\hfill
% settings for subfigure 2
\begin{minipage}[t]{0.65\linewidth}
\centering
\includegraphics[width=\textwidth]{p_p2tan.pdf}
\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
\end{minipage}
\end{figure}

Another interesting case is the when the far ends of the initial chains are connected(through periodic or a $\lambda$ interface). The analytic result is
\begin{equation}
\begin{aligned}
  \mathcal{F}( \lambda = 1 \rightarrow \lambda ) &=  \frac{\beta}{2}\Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | - \frac{1}{6} \Big]  + {\color{red} \frac{\beta}{12}} \\
  &= \Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | \Big]  \ln L \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
\end{aligned}
\end{equation}

{\bf A note for the zero mode:} When zero mode is present, the boson groundstate is not well-defined; numerically instability kicks in. Adding a small mass is the common remedy, but doesn't work in the fidelity calculation. What we do here is to perturb the boundary condition by a small angle.

In the DN$\rightarrow \lambda$ diagram, zero mode exists when the two sides of the chain $NN$ boundary condition. The combination DN is actually a $\lambda = 0$ interface. We modify one of them to $\lambda = \tan( 0.001 \pi )$ to avoid the zero mode. In the periodic case, we take the one of them to be $\lambda = \tan(0.251\pi)$ although precise periodic boundary condition corresponds to $\lambda = \tan(\frac{\pi}{4})$. This is a numerical way of regularization that matches with our no-zero-mode analytic calculation.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [fidel_num_res.tex]

% configure hyperref to remove ugly boxes from links

\appendix

\section{DN-$\lambda$ Casimir Energy from Groundstate Energy Calculation}
\label{app:gnd_dn_lambda}
% flatex input: [gnd_dn_lambda.tex]

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 1]
\draw (0,0)--(0,2);
\draw (1.5,0)--++(0,2);
\node () at (-0.5,1) {DN};
\node () at (1.8,1) {$\lambda$};
\draw[-stealth] (0.75,0.75)--++(0,0.5);
\begin{scope}[shift={(5,0)}]
\draw (0,0)--(0,2);
\draw (3,0)--++(0,2);
\draw[dashed] (1.5,0)--++(0,2);
\node () at (-0.5,1) {N};
\node () at (3.5,1) {D};
\node () at (1.7,1) {$\lambda$};
\end{scope}
\end{tikzpicture}
\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions. The width of the strip is $\pi$ due to folding. We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle. }
\end{figure}

{\bf Eigenfunction}:

The unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$. The general solutions can be written as
\begin{equation}
f(k, x) = 
\left\lbrace
\begin{aligned}
  A_1 e^{i kt} \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  A_2 e^{ikt}  \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\end{equation}
At the junction we have $\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2}$, which cancels the $A$s and gives
\begin{equation}
\tan ^2 (\frac{1}{2} kL ) = \lambda^2 
\end{equation}
Hence
\begin{equation}
 \frac{kL}{2} = \pm \theta + n \pi \implies  k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad \theta \in [0,\frac{\pi}{2} ]  
\end{equation}
The normalized eigenfunctions are
\begin{equation}
f_n(x) = \sqrt{\frac{2}{L}}
\left\lbrace
\begin{aligned}
  \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
  \pm \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
\end{aligned} \right. 
\qquad 
k = \frac{2\pi}{L}( n \pm  \frac{\theta}{\pi} )  \quad n \in \mathbb{Z} 
\end{equation}

{\bf Mode Expansion and Casimir Energy}:

Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
\begin{equation}
  S = \frac{g}{2} \int dt \, \sum_{n \in \mathbb{Z} }\left(  \dot{\phi}^2_n + k^2 \phi_n^2 \right) \implies\quad   g \dot{\phi}_n  = \pi_n \quad \implies H =  
\frac{1}{2g}\sum_{n \in \mathbb{Z} } \pi_n^2 + ( kg )^2  \phi_n^2 
\end{equation}
Define the creation and annihilation operators as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
a^{\dagger}_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
\end{aligned}
\end{equation}
then
\begin{equation}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
\end{equation}
The Casimir energy is 
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  )  = \frac{\pi}{L} ( \sum_{n \in \mathbb{Z}}  | n + x |  )\quad x = \frac{\theta}{\pi}\\  
&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
&= \frac{\pi}{L} ( - x^2 + x - \frac{1}{6})  = \frac{1}{2} ( - x^2 + x - \frac{1}{6})
\end{aligned}
\end{equation}
The free energy is
\begin{equation}
F = \frac{\beta}{2} ( - x^2 + x - \frac{1}{6}) = - \frac{\beta}{2} B_2( x) 
\end{equation}
The full expression also agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [gnd_dn_lambda.tex]

% configure hyperref to remove ugly boxes from links

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Calculation}
\label{app:lambda_12}
% flatex input: [lambda_1_lambda_2.tex]

This calculation is very similar to the presented in App.~\ref{app:casimir_energy_DD_DN}.

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale = 1]
\draw (0,0)--(2,0);
\draw (0,1.5)--++(2,0);
\node () at (1,-0.5) {$\lambda_1$};
\node () at (1,2) {$\lambda_2$};
\draw[-stealth] (1,0.5)--++(0,0.5);
\end{tikzpicture}
\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
\end{figure}

The wanted partition function is
\begin{equation}
Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} \mathbb{I}_2 \otimes M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det ( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b) }
\end{equation}
where
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots )
\end{equation}
$R_a$($R_b$) correspond to the $\lambda_1$ and $\lambda_2$ boundary conditions. Using the fact that their determinants are $\det( R_a R_b^{\dagger})  = 1$, we have
\begin{equation}
\begin{aligned}
F &= - \ln Z_{ab} = \ln \det( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b ) = \ln \det ( R_a R_b^{\dagger} - e^{- \mathbb{I}_2 \otimes M} )\\
& = \ln \det 
\begin{bmatrix}
\cos 2 \Delta \theta \mathbb{I} - e^{-M}   & \sin 2 \Delta \theta \mathbb{I}\\
- \sin 2\Delta \theta \mathbb{I}  &   \cos 2 \Delta \theta \mathbb{I} - e^{-M} \\ 
\end{bmatrix} \quad \text{where } \Delta \theta = \theta_2 - \theta_1 \\
& = \sum_i \ln [ 1 - 2 \cos 2 \Delta \theta e^{- \lambda_i } + e^{- 2 \lambda_i }  ] \\
& = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \ln [ 1 - 2 \cos 2 \Delta \theta e^{-x} + e^{-2x} ] 
\end{aligned}
\end{equation}
This integral is an even function of $\Delta \theta$ and the $\Delta \theta > 0$ case reduce to the polylog and Bernoulli polynomial
\begin{equation}
\begin{aligned}
  F &= \frac{\beta}{4\pi^2} \left[ - \text{Li}_2 ( e^{2i |\Delta \theta|} ) - \text{Li}_2 ( e^{- 2i |\Delta \theta|} ) \right]  = \frac{\beta}{4\pi^2}  \left[ - 2\pi^2 B_2 (x) \right] \\
  &= - \frac{\beta}{2} B_2( |x| ) = \frac{\beta}{2} (|x| - x^2 - \frac{1}{6}) \quad x = \frac{\Delta \theta}{ \pi} \\
\end{aligned}
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [lambda_1_lambda_2.tex]

% configure hyperref to remove ugly boxes from links

\section{Determinant Identity for Amplitude between Boundary States}
\label{app:pf_of_id}
% flatex input: [pf_of_id.tex]

For real symmetric matrix $M$
\begin{equation}
\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{equation}

{\bf Proof:}  
We first restrict to the case when $R = I$. To avoid confusion, we assume the daggered vector are row vectors and write $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\} $ as $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{*}  \Big\} $.

{\it Diagonal Basis}: We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
\begin{equation}
  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^{*} = O^T \vec{\bar{b}}^{*}
\end{equation}
so that the whole expression can be written as
\begin{equation}
\begin{aligned}
  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}  =  
  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^{*}  \Big\} \\
& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
\end{aligned}
\end{equation}
{\it Baker-Campbell-Hausdorff formula}: For $ [X, Y] = sY $, we have a solvable case of Baker-Campbell-Hausdorff formula
\begin{equation}
  e^X e^{Y} = e^{\exp (s ) Y} e^{X}
\end{equation}
Taking $X = -\lambda_i d_i^{\dagger} d_i$, $Y = d_i^{\dagger}, \bar{d}^{\dagger}$, we have
\begin{equation}
[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
\end{equation}
and so $s = - \lambda_i$ for each $\lambda_i$. This enable us to commute those exponentials
\begin{equation}
\begin{aligned}
 \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}   &= \prod_i \exp \Big\{ \alpha e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
 & = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^{*}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{aligned}
\end{equation}

{\it The General Case}: When $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$. The role of $\bar{b}$ is decorative; it is effectively a $c$-number and we only use its independence w.r.t. $\vec{b}$. Hence the rest of the proof follows the same way.

{\bf Corollary :} 
\begin{equation}
Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} 
\end{equation}
{\bf Proof:}

Using the identity we have just proved, 
\begin{equation}
Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle 
\end{equation}
A direct application of the MacMahon master theorem
\begin{equation}
  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
 = \frac{1}{\det(1 - X^T Y )}
\end{equation}
proves the result.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [pf_of_id.tex]

\bibliographystyle{unsrt}
\bibliography{bCFT_notes}

\end{document}
%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [bCFT_notes.tex]

### 2017-04-17 bCFT_paper.tex
[init] establish repository

\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\cf}{\textit{cf.} } 
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }

\begin{document}

\title{Bipartite Fidelity and Loschmidt echo of bosonic conformal interface}

\author{Tianci Zhou}
\email{tzhou13@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\author{Mao Lin}
\email{maolin2@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\date{\today}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}
% the last one to be finished.

\section{Bosonic Conformal Interface}
\subsection{General Formulation}
% M, S
% special case
\subsection{Physical Realization: Connecting Bosons of Different Compactification Radii}
% free boson + compact
\subsection{A Free Boson Lattice Model}
% cite Calabrese, introduce the model
% lattice model S matrix

\section{Bipartite Fidelity and Loschmidt Echo}
\subsection{Definition}
% definition
% general discussion

\section{Analytic and Numerical Results}
\subsection{Fidelity}
% analytic: conformal transformation
% numerical comparison 
\subsection{Loschmidt Echo}
% analytic: conformal transformation
% numerical comparison

\section{Discussion}

\begin{acknowledgments}
\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
    TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
    Supercomputing Applications (NCSA) and which is supported by funds from the University of
    Illinois at Urbana-Champaign.
\end{acknowledgments}

\appendix
\section{Corrections to the Free Energy}
% two corrections:
% 1. staircase geometry
% 2. contribution from the boundary: cite Cardy

\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
% basis transformation, Bogoliubov state, overlap(master theorem)
% Peschel_EE.pdf

\section{A Determinant Identity for the Boundary State Amplitude}
% copy notes app. C

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
% copy notes app. B

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
% copy notes app. A

\bibliographystyle{plain}
\bibliography{bCFT}

\end{document}

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

### 2017-04-18 gnd_dn_lambda.tex
Initial commit

--- 2017-04-17 bCFT_notes.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage[compact]{titlesec}
-\usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage{tikz}
-\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
-\usepackage{wrapfig}
-\usepackage{bm}
-\usepackage{todonotes}
-
-\graphicspath{{./}{./images/}}
-
-\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
-\newcommand{\tr}[0]{\text{tr}}
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-
-\tikzset{
-    partial ellipse/.style args={#1:#2:#3}{
-        insert path={+ (#1:#3) arc (#1:#2:#3)}
-    }
-}
-
-\textwidth = 6.5 in
-\textheight = 9 in
-\oddsidemargin = 0.0 in
-\evensidemargin = 0.0 in
-\topmargin = 0.0 in
-\headheight = 0.0 in
-\headsep = 0.0 in
-\parskip = 0.2in
-\parindent = 0.0in
-
-% configure hyperref to remove ugly boxes from links
-\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
-\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
-
-\title{Boundary Conformal Field Theory}
-\author{Tianci Zhou}
-
-\begin{document}
-\maketitle
-\large
-
-\section{Conformal Interface of Free Boson}
-% flatex input: [boson_interface.tex]
-\label{sec:var-boson}
-[Section 2.1-2.2 of \cite{bachas_permeable_2002}.]
-
-Let's consider the conformal interface connecting two possibly different free boson CFTs. Suppose the interface is located at $x = 0$ that glues the two theories in such a way that 
-\begin{equation}
-\begin{bmatrix}
-\partial_t \phi\\
-\partial_x \phi\\ 
-\end{bmatrix}_{x = 0^-} 
- = M \begin{bmatrix}
-\partial_t \phi\\
-\partial_x \phi\\ 
-\end{bmatrix}_{x = 0^+} 
-\end{equation}
-One may write the field on the left/right as $\phi^1$($\phi^2$), and then the gluing condition is
-\begin{equation}
-\partial_{\mu} \phi^1 = M_{\mu\nu} \partial_{\nu} \phi^2 
-\end{equation}
-The interface is now penetrable, and condition \eqref{eq:stress-cond} is weakened that only requires continuity of the momentum across the interface. From the explicit expression
-\begin{equation}
-T^{xt} = - g \partial_x \phi \partial_t \phi  = -g(\partial_{\mu} \phi \sigma^x_{\mu\nu}  \partial_{\nu} \phi ) 
-\end{equation}
-we have the relation
-\begin{equation}
-\partial_{\mu} \phi^2 \sigma^x_{\mu\nu}  \partial^2_{\nu} \phi -  \partial_{\mu} \phi^1 \sigma^x_{\mu\nu}  \partial^1_{\nu} \phi = 
-\partial_{\mu} \phi^2 [\sigma^x_{\mu\nu} - M^T  \sigma^x M)_{\mu\nu} ]  \partial_{\nu} \phi^2 = 0
-\end{equation}
-For generic field configuration $\phi^2$, the condition is satisfied only when
-\begin{equation}
-\sigma^x = M^T \sigma^x M 
-\end{equation}
-By diagonalizing $\sigma^x$ and doing corresponding orthogonal transformation on $M$, 
-\begin{equation}
-\sigma^z = ( OMO^T  )^T \sigma^z ( OMO^T )  \quad 
-O = \frac{1}{\sqrt{2}} 
-\begin{bmatrix}
-1 & 1 \\
-1 & -1 \\                       
-\end{bmatrix}
-\end{equation}
-we realize $O M O^T$ is in the Lorentz group $O( 1, 1 )$, whose 4 disconnected components that are determined by the sign of determinants and the $00$ element. A natural boost parameterization are 
-\begin{equation} 
-\Lambda = O M O^T = \pm 
-\begin{bmatrix}
-\cosh \beta & \sinh \beta \\
-\sinh \beta & \cosh \beta \\  
-\end{bmatrix}
-\quad \pm 
-\begin{bmatrix}
-\cosh \beta & -\sinh \beta \\
-\sinh \beta & -\cosh \beta \\  
-\end{bmatrix}
-\end{equation}
-Reverting back to $M$, we have $\lambda = e^{-\beta}$
-\begin{equation}
-M_1 = \pm 
-\begin{bmatrix}
-\lambda^{-1} & 0 \\
-0 & \lambda \\
-\end{bmatrix}
-\quad 
-M_2 = \pm 
-\begin{bmatrix}
-0 & \lambda\\
-\lambda^{-1} & 0 \\
-\end{bmatrix}
-\end{equation}
-The $\pm$ branches in each $M$ can be combined if we set $\lambda = \text{tan} \theta$ for $\theta \in [- \frac{\pi}{2}, \frac{\pi}{2} ] $.
-
-The physical significance of $\theta$ can be seen in the following scattering picture.
-The solutions of equation of motion are the left and right moving waves.
-The derivative $\partial_{-} = \partial_t - \partial_x$ removes the left moving component($x+t$) and hence can generate right moving fields $\partial_{-} \phi$.
-The process of right moving $\phi^1$ combined with left moving $\phi^2$ to generate a left moving $\phi^1$ and right moving $\phi^2$
-\begin{equation}
-\partial_{-} \phi^1 + \partial_{+} \phi^2 \rightarrow \partial_{+} \phi^1 + \partial_{-} \phi^2
-\end{equation}
-can be described by the scattering matrix
-\begin{equation}
-\begin{bmatrix}
-\partial_{+} \phi^1 \\
-\partial_{-} \phi^2 \\
-\end{bmatrix}
- = S
-\begin{bmatrix}
-\partial_{-} \phi^1 \\
-\partial_{+} \phi^2 \\
-\end{bmatrix}
-\end{equation}
-After some linear algebra, we find that $2\theta$ is the angle that parameterize the scattering matrix\footnote{I adopt several different conventions from \cite{bachas_permeable_2002}.
-1.
-I put $\partial_t$ as the first entry of the vector.
-2.
-The matrices $M(\lambda)$ is actually $M(\lambda^{-1} )$ in \cite{bachas_permeable_2002}.
-These two cancel out and the resulting gluing conditions are the same.
-3.
-I take $\partial_{-} \phi^1, \partial_{+} \phi^2$ as incoming wave, so that the $S$ matrix maps it to the outgoing waves, while \cite{bachas_permeable_2002} use the opposite: they obtain $S^{-1}$.
-Incidentally, $S = S^{-1}$.
-4.
-I take $\partial_{-} = \partial_t - \partial_x $, while \cite{bachas_permeable_2002} seems to take $\partial_{-} = \partial_x - \partial_t$.
-Interchanging $x$ and $t$ amounts to change $\lambda$ to $\lambda^{-1}$, or $\theta$ to $\frac{\pi}{2}- \theta$, which indeed converts $S$ here to the $S$ in \cite{bachas_permeable_2002}.
-}
-\begin{equation}
-\label{eq:S1-S2}
-S_1 =
-\begin{bmatrix}
-\cos 2 \theta & \sin 2 \theta \\
-\sin 2 \theta & - \cos 2 \theta     
-\end{bmatrix}
-\qquad
-S_2 = 
-\begin{bmatrix}
--\cos 2 \theta & \sin 2 \theta \\
--\sin 2 \theta & - \cos 2 \theta   
-\end{bmatrix}
-\end{equation}
-
-\subsection{Example: Free Boson with Different Compactification Radii}
-
-[Section 2.2 of \cite{bachas_permeable_2002}.]
-
-Suppose $\phi^1$ and $\phi^2$ are compact Bosons with compactification radii $2\pi R_1$ and $2\pi R_2$. We can rescale them to a single field 
-\begin{equation}
-\phi = \left\lbrace
-       \begin{aligned}
-         R_1^{-1} \phi^2  & \quad  x < 0 \\
-         R_2^{-1} \phi^2  & \quad x > 0  \\
-       \end{aligned} \right. 
-\end{equation}
-such that $\phi$ is a compact boson on the whole plane with radius $2\pi$, whose action(in Euclidean time) reads
-\begin{equation}
-S = \frac{g}{2} R_1^2 \int_{x \le 0 } \left(  \nabla \phi \right)^2 d\tau dt  + \frac{g}{2} R_2^2 \int_{x > 0 } \left(  \nabla \phi  \right)^2 d\tau dt 
-\end{equation}
-Both the bulk action as well as the interface should be invariant under the conformal transformation.
-We do such a conformal transformation, which induces a change on the field $\phi \rightarrow \delta \phi $, and since the bulk is invariant, we only need to check the boundary term
-\begin{equation}
-S = \frac{g}{2} \int_{x = 0 } ( R_1^2 \partial_x \phi\big|_{x = 0^{-}}   - R_2 ^2 \partial_x \phi \big|_{x = 0^{+}} ) \delta \phi  d\tau = 0
-\end{equation}
-The boundary condition
-\begin{equation}
-R_1^2 \partial_x \phi\big|_{x = 0^{-}}  = R_2 ^2 \partial_x \phi \big|_{x = 0^{+}}
-\end{equation}
-which makes any variation vanish must be conformal invariant. In terms of the $\phi^1$, $\phi^2$ fields
-\begin{equation}
-\partial_x \phi^1 = \frac{R_2}{R_1} \partial_x \phi^2 
-\end{equation}
-According to our previous analysis, it corresponds to $M_1$ with $\lambda = \frac{R_2}{R_1} = \tan \theta$, namely
-\begin{equation}
-\label{eq:cpt_boson_bd}
-\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  - \cos \theta \phi^2 ) = 0
-\end{equation}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-
-% flatex input end: [boson_interface.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\subsection{Folding Trick and Boundary State}
-% flatex input: [folding.tex]
-
-[Section 2.3-2.4 of \cite{bachas_permeable_2002}]
-
-We can fold the field $\phi^2$ to the left half plane on top of $\phi^1$, then the boundary at $x = 0$ is impenetrable for the tensor theory and therefore is a boundary state of Boson.
-
-The folding takes $x$ to $-x$ in $\phi^2$, so its $x$ derivative in the boundary condition \eqref{eq:cpt_boson_bd} will change sign and becomes\footnote{Change $\theta$ to $\frac{\pi}{2} - \theta$ to compare relevant result with in \cite{bachas_permeable_2002}.
-I believe the \cite{bachas_permeable_2002} made a mistake here.
-Nevertheless the Casimir energy is insensitive to this change.},
-\begin{equation}
-\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  + \cos \theta \phi^2 ) = 0
-\end{equation}
-It looks like the rotated field within $\partial_t$ takes Dirichlet boundary condition and the other orthogonal field within $\partial_x $ takes Neumann boundary condition, so we have\footnote{We will deal with the winding sector in Sec.~\ref{sec:winding}}
-\begin{equation}
-\label{eq:rot-D-N}
-\begin{aligned}
-\cos  \theta a^1_n - \sin \theta a^2_n  &= + \left( \cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} \right)\\
-\sin  \theta a^1_n + \cos \theta a^2_n  &= - \left( \sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} \right) 
-\end{aligned}
-\end{equation}
-The left and right sides can be regarded as two new sets of $a^1$ and $a^2$ whose commutation relation is preserved by the orthogonal rotation. Consequently, the boundary state is
-\begin{equation}
-\label{eq:bd_state}
-\begin{aligned}
-| B \rangle &= \exp\Big\{ \sum_{n > 0 } \frac{1}{n} (\cos  \theta a^1_{-n} - \sin \theta a ^2_{-n} )(\cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} ) \\
-& \,\,  \qquad \qquad -\frac{1}{n} (\sin  \theta a^1_{-n} + \cos \theta a ^2_{-n} )(\sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} )
-\Big\} | 0 \rangle \\
-& = \exp\Big\{ \sum_{n > 0 } \frac{1}{n} \left( \cos 2\theta a^1_{-n} \bar{a}^1_{-n}  - \cos 2\theta a ^2_{-n} \bar{a}^2_{-n}   
-- \sin 2 \theta a ^2_{-n}\bar{a}^1_{-n}  - \sin 2 \theta a ^1_{-n}\bar{a}^2_{-n}  \right ) \Big\}| 0 \rangle \\
-& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
-\begin{bmatrix}
-a_{-n}^1\\
-a_{-n}^2\\                              
-\end{bmatrix}
-S_1
-\begin{bmatrix}
-\bar{a}_{-n}^1  \bar{a}_{-n}^2
-\end{bmatrix} \Big\}
-\end{aligned}
-\end{equation}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [folding.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\section{Compact Boson Winding Modes}
-\label{sec:winding}
-% flatex input: [D_and_N.tex]
-
-\subsection{Dirichlet and Neumann Boundary Conditions}
-
-[Section 2 of \cite{bachas_fusion_2008}, Section 6.3.5 of \cite{di_francesco_conformal_1997}]
-
-The winding modes of compact boson determines the conformal dimensions of the primary fields.
-It therefore restrict possible bcc operators on the boundary.
-In this section we work the simple Dirichlet and Neumann conditions for the winding modes.
-
-{\bf Mode Expansion:} 
-Suppose the boson is compactified as $\phi \rightarrow \phi + 2\pi R$, then mode expansion in Eq.~\ref{eq:boson-mode-exp} will have a different zero mode\footnote{The sign of the $x$ term is different from Eq.
-(6.91) in \cite{di_francesco_conformal_1997}, but calculation later shows that the $-$ sign is correct to give the $(\frac{n}{4\pi gR} + \frac{1}{2} \frac{m}{R})$ combination for $z$.
-}
-\begin{equation}
-\begin{aligned}
-\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \text{oscillator part}  \\
-&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  + \text{oscillator part}  \\
-\end{aligned}
-\end{equation}
-where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$.
-A particle living on unit circle $[0, 2\pi]$ have integer($m \hbar$) angular momentum(conjugate momentum), and so momentum of Boson living on $[0, 2\pi R]$ will have $\frac{n}{R}$ as its eigenvalues.
-
-The left and right mode decomposition is again done by complex variables
-\begin{equation}
-z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
-\end{equation}
-which leads to
-\begin{equation}
-\label{eq:boson-mode-exp}
-\begin{aligned}
-\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
-&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
-\end{aligned}
-\end{equation}
-From the holomorphic derivative 
-\begin{equation}
-i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1}  \qquad a_0 = \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)
-\end{equation}
-we make up the zero mode term in $L_0$ is absent for free boson, 
-\begin{equation}
-L_0 = \sum_{n> 0 } a_{-n} a_n + \frac{1}{2} a_0^2 =   2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2 + \sum_{n> 0 } a_{-n} a_n
-\end{equation}
-The ground state now has dimension $h = 2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2$.
-
-{\bf Dirichlet and Neumann}:
-
-Now that we have a legitimate $a_0$ that behaves similar with other oscillator modes, we can then impose the same Dirichlet condition in Eq.~\ref{eq:D-mode-cond}, on the unit circle, the logarithmic term gives
-\begin{equation}
- -i \frac{1}{\sqrt{ 4\pi g}}  ( a_0 \ln z  + \bar{a}_0 \ln \bar{z} )\Big|_{\text{unit circle }} = 0 \quad \implies \quad a_0 - \bar{a}_0 = 0  \quad \implies \quad m = 0
-\end{equation}
-The boundary states satisfying this boundary condition can be a linear superposition of the zero winding states.
-Since it's Dirichlet, it is an eigenstate of $\hat{\phi}_0$\footnote{We have quantized the theory such that $[\phi_0, \frac{n}{R}] = i $.
-},
-\begin{equation}
-|{\rm D} \rangle  = g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle
-\end{equation}
-With this one can show
-\begin{equation}
-\phi( x, t = 0 ) | {\rm D} \rangle = \phi_0 | {\rm D} \rangle
-\end{equation}
-
-Similarly, the Neumann boundary condition now has the $n = 0$ term in Eq.~\ref{eq:N-mode-cond}
-\begin{equation}
- a_0 + \bar{a}_0 = 0  \quad \implies \quad n = 0 
-\end{equation}
-the resulting boundary state is a linear superposition over the winding sector
-\begin{equation}
-| {\rm N} \rangle = g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
-\end{equation}
-In fact, Neumann becomes Dirichlet in the dual field, so $\bar{\phi}_0$ is related to the boundary value of the dual field.
-
-One can check that this indeed satisfies the Neumann boundary condition
-\begin{equation}
-\partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
-\end{equation}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [D_and_N.tex]
-
-% configure hyperref to remove ugly boxes from links
-\subsection{Gluing Condition for Winding Modes}
-% flatex input: [glue_zero.tex]
-[Appendix A of Oshikawa\cite{oshikawa_boundary_2010}]
-
-In Sec.~\ref{sec:var-boson}, we use variational approach to find conformal invariant boundary conditions, but the resulting equation \eqref{eq:cpt_boson_bd} do not provide information about the winding sector.
-The variational method fails because winding is a global properties of the Boson configuration, meaning insensitive to the local perturbation.
-
-Here we present a general treatment about the winding modes.
-From the discussion of the Dirichlet and Neumann boundary condition in previous subsection, it seems that the constraints on the oscillator modes can be naturally extended to the zero mode for $n = 0$.
-We can show that this is in compliance with the conformal invariance.
-
-Suppose in the junction we have a boundary condition that result in the following scattering relation
-\begin{equation}
-\begin{bmatrix}
-\partial_{+} \phi^1 \\
-\partial_{-} \phi^2 \\
-\end{bmatrix}
- = S
-\begin{bmatrix}
-\partial_{-} \phi^1 \\
-\partial_{+} \phi^2 \\
-\end{bmatrix}
-\end{equation}
-the conformal invariance constraint gives two solutions $S_1$ and $S_2$ in Eq.~\eqref{eq:S1-S2}.
-Imagining that we fold $\phi^2$ on top of $\phi^1$, the $x$ derivative on $\phi^2$ then changes sign, we therefore have
-\begin{equation}
-\begin{bmatrix}
-\partial_{+} \phi^1 \\
-\partial_{+} \phi^2 \\
-\end{bmatrix}
- = S
-\begin{bmatrix}
-\partial_{-} \phi^1 \\
-\partial_{-} \phi^2 \\
-\end{bmatrix}
-\end{equation}
-It it convenient to work in the holomorphic mode expansion \eqref{eq:boson-mode-exp} for the left and right separation. Specifically
-\begin{equation}
-\partial_{+} = \frac{4\pi i }{L} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = \frac{4\pi i }{L} z\partial_{z}
-\end{equation}
-and
-\begin{equation}
-\sum_{n \in \mathbb{Z}}  
-\begin{bmatrix}
-\bar{a}^1_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n}\\ 
-\bar{a}^2_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n} 
-\end{bmatrix}
- = S
-\sum_{n \in \mathbb{Z}}
-\begin{bmatrix}
-a^1_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
-a^2_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
-\end{bmatrix}
-\end{equation}
-We impose boundary condition at $t = 0$\footnote{In Sec.~\ref{subsec:free-boson}, we interchange $x$ and $t$, and impose boundary condition at $x = 0$.
-For whatever convention, the boundary is on the unit circle $|z| = 1$.
-}, so $z$  is on the unit circle and $\bar{z} = \frac{1}{z}$.
-By comparing the modes(Fourier series on circle), we have
-\begin{equation}
-\label{eq:mode-eq}
-a_n^i - (S^{\scalebox{0.5}[0.8]{\( - \)}1})_{ij} \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^j = 0
-\end{equation}
-This is clearly a generalization of the Dirichlet and Neumann boundary conditions, where the orthogonal matrix $S$ is replaced by $\pm \mathbb{I}$.
-In fact, the rotation does not change the quadratic relation
-\begin{equation}
-\sum_i a^i_n a^i_m =  \sum_i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}m}^i
-\end{equation}
-Hence for the quadratics in the Virasolo generators
-\begin{equation}
-\begin{aligned}
-L_n &= \frac{1}{2} \sum_i  \sum_{m > -1 } (a^i_{n-m} a^i_m  + a^i_{-m} a^i_{n+m } ) - \frac{1}{2} a^i_0 a^i_n 
-\end{aligned}
-\end{equation}
-the cancellation works the same way,
-\begin{equation}
-\begin{aligned}
-L_n - \bar{L}_{-n} &= \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m + a^i_{-m} a^i_{n+m} - \bar{a}^i_{-n-m} \bar{a}^i_{-m} - \bar{a}^i_{m} \bar{a}^i_{-n+m }  )  - \frac{1}{2}( a_0^i a_n^i - \bar{a}_0^i \bar{a}^i _{-n})\\
-& = \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m  - \bar{a}^i_{-n+m}\bar{a}^i_{-m})+ (a^i_{-m} a^i_{n+m} - \bar{a}^i_{m} \bar{a}^i_{-n -m }  )\\
-& = 0 
-\end{aligned}
-\end{equation}
-We now specialize to the two cases $S = S_1$ and $S_2$.
-
-{\bf Boson $\lambda$ Junction: $S = S_1$}
-
-We need to solve the $n = 0$ of \eqref{eq:mode-eq} for $S^{-1} = S_1^{-1} = S_1$\footnote{Recall that the solution of Eq.~\eqref{eq:mode-eq} for the nonzero mode is $\exp(\frac{1}{n} a_{-n}^{i} S^{-1}_{ij} a_{-n}^j |0\rangle)$.
-In Eq.~\eqref{eq:R-bs} we do have $R = S_1$.
-} and
-\begin{equation}
-a^i_0 = \sqrt{4\pi g}  \frac{1}{4\pi} (2\pi m_i R_i + \frac{1}{g} \frac{n_i}{R_i})
-\end{equation}
-For notational simplicity, we introduce the compactification lattice and its dual\cite{oshikawa_boundary_2010}
-\begin{equation}
-\label{eq:lattice}
-\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
-\end{equation}
-the constraint then becomes 
-\begin{equation}
-  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
-\end{equation}
-which is basically the two dimensional case of the multi-component Boson constraints in Eq.~(86) of \cite{oshikawa_boundary_2010}.
-
-Given the $S_1$ matrix in Eq.~\eqref{eq:S1-S2}, we have
-\begin{equation}
-1 + S_1 = 2  
-\begin{bmatrix}
-\cos^2 \theta & \sin \theta \cos\theta \\
-\sin \theta \cos \theta  & \sin^2 \theta \\
-\end{bmatrix}
-\quad 
-1 - S_1 = 2
-\begin{bmatrix}
-\sin^2 \theta & -\sin \theta \cos\theta \\
--\sin \theta \cos \theta  & \cos^2 \theta \\
-\end{bmatrix}
-\end{equation}
-both have determinant zero. So the solution of the two lattice vectors in 
-\begin{equation}
-( 1 + S_1) \vec{M} = -( 1 - S_1 ) \frac{1}{g} \vec{M}^*
-\end{equation}
-must be the null vectors of the corresponding matrices, i.e. 
-\begin{equation}
-\vec{M} = ( \cos \theta, -\sin \theta )^\top \qquad \vec{M}^{*} = ( \sin \theta, \cos \theta )^\top 
-\end{equation}
-In terms of the winding numbers
-\begin{equation}
-  \tan \theta =  \frac{n_1 R_2}{n_2 R_1 } = -\frac{m_2 R_2}{ m_1 R_1}
-\end{equation}
-One can take a pair of coprime integers $k_1$ and $k_2$($k_1>0$), such that $-\frac{m_1}{m_2} = \frac{k_1}{k_2}$.
-That determines all the possible winding numbers of the basis\footnote{\cite{bachas_fusion_2008} takes $-S_1$ as the S matrix, so they have $\vec{M} = ( \cos \theta, \sin \theta)^\top $ and $\tan \theta = -\frac{n_1 R_2}{n_2 R_1 } = \frac{m_2 R_2}{ m_1 R_1} = \frac{k_2 R_2}{k_1 R_1}$ for $\frac{m_1}{m_2} = \frac{k_1}{k_2}$.
-And this is consistent with their parameterization  $ \left\lbrace
-  \begin{aligned}
-    m_1 = k_1 M  & \quad n_1 = k_2 N  \\
-    m_2 = k_2 M &  \quad n_2 = -k_1 N \\
-  \end{aligned} \right. $ }. The linear superposition is beyond conformal invariance, which should be determined by Cardy's consistency condition.
-
-This set of boundary conditions can be viewed as Dirichlet and Neumann on the rotated basis, hence a reasonable conjecture is also the Fourier sum of the basis(constrained by $S_1$)
-\begin{equation}
-g_{\,\!_{S_1}} \sum_{S_1} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
-\end{equation}
-
-{\bf The T-dual Boundary State $S = S_2$}
-
-Now we take $S = S_2$, the zero mode condition becomes
-\begin{equation}
-( \vec{M} + \frac{1}{g}\vec{M}^* ) =  S_2^{-1}  ( -\vec{M} + \frac{1}{g}\vec{M}^* )
-\end{equation}
-the solution is
-\begin{equation}
-\vec{M} =  \frac{1}{g} \frac{1 - S_2}{1 + S_2} \vec{M}^{*} = \frac{1}{g}  \frac{1}{ 1 - \cos 2\theta}
-\begin{bmatrix}
-  0 & - \sin 2 \theta \\
-\sin 2\theta & 0 \\
-\end{bmatrix} \vec{M}^*
- = \frac{\cot \theta}{g} \begin{bmatrix}
-  0 & - 1 \\
-1 & 0 \\
-\end{bmatrix}\vec{M}^*
-\end{equation}
-Using the basis vectors in Eq.~\ref{eq:lattice}, we have
-\begin{equation}
-\begin{bmatrix}
-m_1\\
-m_2\\
-\end{bmatrix}
- = \frac{2 \cot \theta}{ 4\pi g  R_1 R_2 }
-\begin{bmatrix}
--n_2 \\
-n_1 
-\end{bmatrix}
-\end{equation}
-Taking the same coprime interger $\frac{m_2}{n_1} = \frac{k_2}{k_1}$, we have the angle\footnote{It takes some effort to match the results with \cite{bachas_fusion_2008}.
-We both use $\frac{k_2}{k_1}$ the same way, so the parameterization is the same.
-They use $-S_2$ as oppose to $S_2$ to be the S matrix, so $\vec{M} = \frac{1}{g} \frac{1 + S_2}{1 - S_2} = \frac{\tan \theta}{g}\begin{bmatrix}
-  0 & - 1 \\
-1 & 0 \\
-\end{bmatrix} \vec{M}^*$, their $\tan \theta$ is my $\cot \theta = \frac{k_2}{2k_1 } 4\pi g R_1 R_2$.
-They use $R \rightarrow \frac{1}{2R}$ as T-duality transformation.
-If they were to use $R \rightarrow \frac{1}{2R}$(this point corresponds to $g = \frac{1}{4\pi}$), then their $\tan \theta = \frac{k_2}{2 k_1} R_1 R_2$ which will be the same as our $\cot \theta$.
-So we agree.},
-\begin{equation}
-  \tan \theta = \frac{2 k_1}{k_2} \frac{1}{4 \pi g R_1 R_2}
-\end{equation}
-This state can be obtained by taking T duality for one of the bosons, hence it is a Dirichlet/Neumann boundary conditions for these two Bosons.
-It is then reasonable to use Fourier sum as the physical boundary state
-\begin{equation}
-g_{_{\,\!_{S_2}}}\sum_{S_2} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
-\end{equation}
-
-{\bf The $g$ Factor}:
-
-The $g$ factor can only be determined by Cardy condition, which means that the occurrence $n^h_{ab}$ for each irreducible representation
-\begin{equation}
-Z_{ab} = \langle a | e^{- \beta  H }  | b \rangle  = \sum_{h} n_{ab}^h \chi_h 
-\end{equation}
-is an non-negative integer.
-
-Since the character for the compact boson theory is known, we can just compute the amplitude, say $Z_{\lambda_1, \lambda_2}$ adjust the coefficient such the occurrence is an integer.
-\cite{bachas_fusion_2008} contains a calculation for Dirichlet case.
-I will not repeat it here.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [glue_zero.tex]
-
-% configure hyperref to remove ugly boxes from links
-\subsection{Winding Modes Contribution to Partition Function}
-% flatex input: [Z-winding.tex]
-
-In this section, we address the concern about how the winding mode will affect the partition function.
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[scale = 1]
-\draw (0,0)--(2,0);
-\draw (0,1.5)--++(2,0);
-\node () at (1,-0.5) {$\lambda_1$};
-\node () at (1,2) {$\lambda_2$};
-\draw[-stealth] (1,0.5)--++(0,0.5);
-\end{tikzpicture}
-\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
-\end{figure}
-
-Let the cylinder to have width $\beta$ and the length of in time direction is $\pi$(after folding), we have
-\begin{equation}
-Z = \langle \lambda_2 | e^{-\pi H} | \lambda_1 \rangle   \qquad H = \frac{4\pi}{ \beta} L_0 
-\end{equation}
-For the winding mode part, we just replace $L_0$ to be $a_0$. When the two boundary states are identical, the result will be a theta-function
-\begin{equation}
-Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
-\end{equation}
-In the $\beta \rightarrow \infty$ limit, it will be proportional to $\beta$ by Poisson's resummation formula\footnote{One can also approximate the sum by integral in this limit: it will be a two dimensional Gaussian integral and the result is proportional to $\beta$}.
-So the winding mode part will at most contribute a $\ln \beta$ term in the free energy, which can be neglected in our leading $\beta$ scaling analysis.
-
-The conclusion still holds for different $\lambda$ boundary states, in which case the only change is the possible values of $n_1$ and $m_1$(the lattice).
-The overlap $\langle \lambda_1 | \lambda_2 \rangle $ will not be zero even if the two sets of coprime integers are different for the two boundary states: they can meet in their least common divisor.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [Z-winding.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\section{Loschmidt Echo of Connecting Free Bosons}
-\subsection{Corrections to Casimir Energy}
-% flatex input: [free_boson_echo.tex]
-
-To test our boundary state formalism, we consider the Loschmidt echo of connecting two (non-chiral) non-compact Bosons on the two half planes. 
-% flatex input: [fig_H_tau.tex]
-
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[scale = 2]
-\draw (0,0) --(0.9,0);
-\draw (2.1,0)--++(.9,0);
-\node[below] () at (1,-0.15) {$0$};
-\fill (1,0) circle (0.02);
-\node[below] () at (2,-0.13) {$\tau$};
-\fill (2,0) circle (0.02);
-\draw[blue] [domain=0:360] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[blue] [domain=0:360] plot ({2+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[red] [-stealth,domain=10:170] plot ({1+0.4*cos(\x)}, {0.4*sin(\x)});
-\draw[red] [-stealth,domain=170:10] plot ({2+0.4*cos(\x)}, {0.4*sin(\x)});
-\begin{scope}[shift={(2.6,0.6)}]
-\node () at (0.08,0.08) {$z$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\begin{scope}[shift={(3.5,0)}]
-\draw (1.1,0)--++(0.9,0);
-\node[below] () at (1,0.1) {$0$};
-\draw[blue] [domain=0:360] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[blue] (1,0) circle (1);
-\draw[red] [-stealth,domain=10:170] plot ({1+0.5*cos(\x)}, {0.5*sin(\x)});
-\end{scope}
-\begin{scope}[shift={(5.6,0.6)}]
-\node () at (0.08,0.1) {$\xi$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\begin{scope}[shift={(6.5,0)}]
-\draw[dashed] (0,0)--(1.5,0);
-\draw[blue] (0,0)--(0,1);
-\draw (0,1)--(1.5,1);
-\draw[blue] (1.5,1)--(1.5,0);
-\draw[-stealth,red] (0.75,0.3)--++(0,0.5);
-\end{scope}
-\begin{scope}[shift={(7.7,0.6)}]
-\node () at (0.09,0.08) {$w$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\end{tikzpicture}
-\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction.
-The solid lines are cuts on the plane, where the upper and lower surfaces are boundary states.
-Red arrows are the directions of Hamiltonian flow that propagates one boundary state(lower surface) to another(upper surface).
-The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice).
-Middle: image of the map $\xi = \frac{z}{\tau - z}$.
-Right: image of $w = \ln \xi$.
-It is a cylinder by identifying the blue lines and standard radial quantization can be applied.
-}
-\label{fig:H-tau}
-\end{figure}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [fig_H_tau.tex]
-
-After doing the conformal map shown in \label{fig:fig_H}, we can relate the Loschmidt echo we are interested to the Casimir energy of a cylinder subject to different boundary conditions on the top and bottom
-\begin{equation}
-\mathcal{F} = - \ln |\langle a | e^{- 2\pi H} | b \rangle |^2 = 2 E_c 
-\end{equation}
-The width of the cylinder $\beta$ contains information of the scale $\tau$ as well as the regulator.
-Specifically, we set the radii of both blue the semi-circles on the left panel as $\epsilon$, so that the two end points of the dashed line are $(\frac{\tau - \epsilon}{\epsilon}, 0 )$ and $ (\frac{\epsilon}{ \tau - \epsilon}, 0 )$.
-The resulting width on the right panel is then
-\begin{equation}
-\beta  = \ln  \frac{\tau - \epsilon}{\epsilon} -  \ln \frac{\epsilon}{ \tau - \epsilon}  = 2 \ln \frac{\tau - \epsilon}{ \epsilon} 
-= 2 \ln \frac{\tau}{\epsilon} + \mathcal{O}(\frac{\epsilon}{\tau})
-\end{equation}
-We calculate the Casimir energy by canonical quantization, zeta function regularized path integral and boundary states in App.~\ref{app:casimir_energy_DD_DN}.
-All these methods give the following table
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c| } 
- \hline
-  & P & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
-  $E_c $ & $ {\color{red} - \dfrac{1}{12}\beta } $ & ${\color{blue}- \dfrac{1}{48} \beta }$ & ${\color{blue} \dfrac{1}{96} \beta }$ &  ${\color{blue}- \dfrac{1}{48} \beta }$ \\[2ex]
- \hline
-\end{tabular}
-\end{center}
-\caption{Boson Casimir energy subject to different boundary conditions.}
-\label{tab:casimir}
-\end{table}
-
-{\bf Tom's Argument: } It does not make sense to have positive power for the echo. We must have missed some contributions from the Schwartzian etc.
-
-A simple argument is that by doing periodic boundary conditions, the groundstate energy (Casimir energy) on the original $z$ plane must be zero.
-So for all these results we should compensate ${\color{red}\frac{1}{12}\beta}$.
-With this recipe, we have
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{ |c|c|c|c| } 
- \hline
-   & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
-  $E_c $ &  ${\color{purple} \dfrac{1}{16} \beta }$ & ${\color{purple} \dfrac{3}{32} \beta }$ &  ${\color{purple} \dfrac{1}{16} \beta} $ \\[2ex] \hline   \rule[4ex]{0pt}{1pt}
-  $\mathcal{F} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} }$ & ${\color{purple} \dfrac{3}{8}\ln \frac{\tau}{\epsilon}} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} } $ \\[2ex]
- \hline
-\end{tabular}
-\end{center}
-\caption{Logarithm of Loschmidt echo of different boundary conditions.}
-\label{tab:log_echo}
-\end{table}
-
-{\bf Cardy-Peschel Formula:}
-
-One can also apply the Cardy-Peschel formula for the two corners of angle $2\pi$
-\begin{equation}
-F =  \left\{ \frac{\pi}{\theta} h + \frac{c}{24} \Big(  \frac{\theta}{\pi} - \frac{\pi}{\theta}  \Big)   \right\} \ln \tau 
-= \left( \frac{1}{2} h + \frac{c}{16}  \right) \ln \tau 
-\end{equation}
-Since there are two corners, and the echo corresponds to twice the free energy, we have 
-\begin{equation}
-  \mathcal{F} = ( 2h + \frac{c}{4} ) \ln \tau 
-= \left\lbrace
-  \begin{aligned}
-    {\color{purple}\frac{1}{4} \ln \tau}  &\quad   h = 0 \text{ for DD, NN } \\
-    {\color{purple}\frac{3}{8} \ln \tau}  &\quad   h = \frac{1}{16} \text{ for DN, ND}  \\
-  \end{aligned} \right. 
-\end{equation}
-
-{\bf Various Corrections}
-
-We identify the various corrections needed in the $z \rightarrow \xi \rightarrow w$ transformation.
-
-On the $z$ plane of Fig.~\ref{fig:H-tau}, the blue lines are short distance regulators for the two corners.
-As discussed in the corner case of App.~\ref{app:cardy-peschel}, the inner circle regulator only contribute $\frac{c}{6}\ln \frac{\epsilon}{a} $, which is negligible when $\epsilon$ is the of cutoff order.
-However, after mapping to the $\xi$ plane, the outer circle will contribute $-\frac{c}{6} \beta$, which should not be there.
-So
-\begin{equation}
-F_{\xi } = F_{z} + \frac{c}{6} \beta 
-\end{equation}
-
-In App.~\ref{app:H_in_r}, we showed that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian
-\begin{equation}
-H_{z} = H_{\xi} - \frac{c}{24\pi} \beta 
-\end{equation}
-After the evolution for $2\pi$, the difference in the free energy is
-\begin{equation}
-F_w = F_{\xi} - \frac{c}{12} \beta 
-\end{equation}
-Gathering the two together, we obtain the missing $\frac{c}{12} \beta$ between the echo diagram and the Casimir energy, 
-\begin{equation}
-F_{w} = F_z + {\color{red} \frac{c}{12}\beta }
-\end{equation}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [free_boson_echo.tex]
-
-% configure hyperref to remove ugly boxes from links
-\subsection{Folding Trick}
-% flatex input: [echo_folding.tex]
-
-We use the folding trick to compute it again but using gluing condition(dashed line in Fig.~\ref{fig:H-tau_fold}) in place of trivial boundary condition after connecting the two bosons.
-These will corresponds to connecting boundary condition for bosons of different radii.
-% flatex input: [fig_H_tau_fold.tex]
-
-\begin{figure}[htb]
-\centering
-\begin{tikzpicture}[scale = 2]
-\draw (0,0) --(0.9,0);
-\draw[dashed] (1.1,0)--++(0.8,0);
-\draw (2.1,0)--++(.9,0);
-\node[below] () at (1,0) {$0$};
-\fill (1,0) circle (0.02);
-\node[below] () at (2,0) {$\tau$};
-\fill (2,0) circle (0.02);
-\draw[blue] [domain=0:180] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[blue] [domain=0:180] plot ({2+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[red] [-stealth,domain=10:170] plot ({1+0.4*cos(\x)}, {0.4*sin(\x)});
-\draw[red] [-stealth,domain=170:10] plot ({2+0.4*cos(\x)}, {0.4*sin(\x)});
-\begin{scope}[shift={(2.6,0.6)}]
-\node () at (0.08,0.08) {$z$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\begin{scope}[shift={(3.5,0)}]
-\draw (0,0) --(0.9,0);
-\draw[dashed] (1.1,0)--++(0.9,0);
-\node[below] () at (1,0) {$0$};
-\draw[blue] [domain=0:180] plot ({1+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[blue] [domain=0:180] plot ({1+1*cos(\x)}, {1*sin(\x)});
-\draw[red] [-stealth,domain=10:170] plot ({1+0.5*cos(\x)}, {0.5*sin(\x)});
-\end{scope}
-\begin{scope}[shift={(5.6,0.6)}]
-\node () at (0.08,0.1) {$\xi$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\begin{scope}[shift={(6.5,0)}]
-\draw[dashed] (0,0)--(1.5,0);
-\draw[blue] (0,0)--(0,1);
-\draw (0,1)--(1.5,1);
-\draw[blue] (1.5,1)--(1.5,0);
-\draw[-stealth,red] (0.75,0.3)--++(0,0.5);
-\end{scope}
-\begin{scope}[shift={(7.7,0.6)}]
-\node () at (0.09,0.08) {$w$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\end{tikzpicture}
-\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions.
-Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
-The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice).
-Middle: image of the map $\xi = \frac{z}{\tau - z}$.
-Right: image of $w = \ln \xi$.
-It is a cylinder by identifying the blue lines and standard radial quantization can be applied.
-}
-\label{fig:H-tau_fold}
-\end{figure}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [fig_H_tau_fold.tex]
-
-Set aside the corrections from the various Schwartzian, we check the dilation part the Hamiltonian with App.~\ref{app:casimir_energy_DD_DN}, 
-\begin{equation}
-H =  \frac{2\pi }{\beta} ( L_0 + \bar{L}_0 )
-\end{equation}
-Acting on the boundary state, it is effectively
-\begin{equation}
-H = \frac{4\pi}{\beta} L_0 
-\end{equation}
-We use the matrix notation to represent the 4 sets of bosons in this problem: $\vec{b}_1, \vec{b}_2, \bar{\vec{b}}_1, \bar{\vec{b}}_2$. The Hamiltonian(without shifting) is
-\begin{equation}
-H = ( \vec{b}_1^{\dagger}, \vec{b}_2^{\dagger}) 
-\begin{bmatrix}
-M & 0 \\
-0& M \\                                                
-\end{bmatrix} 
-\begin{pmatrix}
-\vec{b }_1\\
-\vec{b }_2 \\
-\end{pmatrix}
-\end{equation}
-where $M = \frac{4\pi^2}{\beta} \text{diag}(1,2,\cdots )$. The boundary state \eqref{eq:bd_state} in terms of bosonic operators is
-\begin{equation}
-  |B \rangle = \exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R  
-\begin{pmatrix}
-  \bar{\vec{b}}^{\dagger}_1\\
-  \bar{\vec{b}}^{\dagger}_2\\
-\end{pmatrix}\right\}  | 0 \rangle 
-\end{equation}
-The choice of $R$ depend on different boundary conditions
-\begin{equation}
-\label{eq:R-bs}
-R =
-\left\lbrace
-\begin{aligned}
-   \text{diag}( \mathbb{I}, \mathbb{I} )  &  \quad \text{DD} \\
-   \text{diag}( -\mathbb{I}, \mathbb{I} )  &  \quad \text{ND} \\
-   \text{diag}( \mathbb{I}, -\mathbb{I} )  &  \quad \text{DN} \\
-   \text{diag}( -\mathbb{I}, -\mathbb{I} )  &  \quad \text{NN} \\
-\end{aligned} \right.  
-\quad
-\text{gluing condition:}\quad 
-R = 
-\begin{bmatrix}
-\cos 2 \theta \, \mathbb{I} &  \sin 2 \theta \, \mathbb{I} \\
- \sin 2 \theta \, \mathbb{I}& -\cos 2\theta \, \mathbb{I}\\  
-\end{bmatrix} = S_1 \otimes \mathbb{I} 
-\end{equation}
-the trivial boundary condition in the previous calculation corresponds to $\theta = \frac{\theta}{2}$.
-
-According to App.~\ref{app:pf_of_id}, the amplitude we are interested is
-\begin{equation}
-\begin{aligned}
-Z_{ab} &= \langle B_{\rm gluing} | e^{- H\pi } | B_{\rm open}  \rangle \\
-&= \langle 0 | 
-\exp\left\{ ( \vec{b}_1 \vec{b}_2 ) R^*_a
-\begin{pmatrix}
-  \bar{\vec{b}}_1\\
-  \bar{\vec{b}}_2\\
-\end{pmatrix}\right\} 
-\exp \Big\{ (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) 
-\begin{bmatrix}
--M & \\
-& -M 
-\end{bmatrix}
-\begin{pmatrix}
-\vec{\bar{b}}_1\\
-\vec{\bar{b}}_2
-\end{pmatrix}\Big\} 
-\exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R_b
-\begin{pmatrix}
-  \bar{\vec{b}}^{\dagger}_1\\
-  \bar{\vec{b}}^{\dagger}_2\\
-\end{pmatrix}\right\} 
-| 0 \rangle \\
-& =  \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[e^{-M}, e^{-M} ] R_b \Big)} \\
-\end{aligned}
-\end{equation}
-We parameterize the boundary condition at the open end by $R_b = \text{diag}(b_1 \mathbb{I} , b_2 \mathbb{I})$($1$ for Dirichlet, $-1$ for Neumann). In this notation,
-\begin{equation}
-\begin{aligned}
-Z_{ab} & = \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[(b_1)e^{-M}, (b_2)e^{-M} ]\Big)} \\
-& = \frac{1}{\det\Big(1 - ( S_1 \otimes \mathbb{I})  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
-& = \frac{1}{\det\Big(S^{-1}_1 \otimes \mathbb{I}  -  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
-\end{aligned}
-\end{equation}
-The Casimir energy from this partition function is thus 
-\begin{equation}
-\begin{aligned}
-E_c   &= - \ln |Z_{ab}| = \ln \det 
-\begin{bmatrix}
-\cos 2 \theta \, \mathbb{I}  - (b_1) e^{-M} & - \sin 2 \theta \, \mathbb{I} \\
--\sin 2 \theta \, \mathbb{I}  & -\cos 2 \theta \, \mathbb{I}  - (b_2) e^{-M} \\
-\end{bmatrix}\\
-&= \sum_i \ln [1  - ( b_1 - b_2 ) \cos 2 \theta e^{-\lambda_i } + ( b_1 b_2) e^{-2 \lambda_i } ]  \\
-&= \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 -( b_1 - b_2 ) \cos 2 \theta e^{-x } - ( b_1 b_2) e^{-2 x} ] 
-\end{aligned}
-\end{equation}
-
-There are two different cases
-\begin{enumerate}
-\item $b_1 = b_2 = \pm 1$, DD, NN. Then
-\begin{equation}
-  E_c = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln (1 - e^{-2 x} ) = \frac{\beta}{8\pi^2}( - \text{Li}_2 (1) ) = {\color{blue}- \frac{1}{48}\beta}
-\end{equation}
-\item $b_1 = -b_2 = \pm 1$, DN, ND. First consider $b_1 = 1$, then
-\begin{equation}
-\label{eq:dn_lambda_bd_state}
-\begin{aligned}
-E_c &=  \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 - 2  \cos 2 \theta e^{-x } + e^{-2 x} ] \\
-&= \frac{\beta}{4\pi^2} \Big[-\text{Li}_2(e^{2i \theta} ) -  \text{Li}_2(e^{-2i \theta} ) \Big]  = \frac{\beta}{4\pi^2} \Big[-2 \pi^2 B_2 ( \frac{\theta}{\pi }) \Big]\\
-&= - \frac{\beta}{2} B_2 ( \frac{\theta}{\pi })
-\end{aligned}
-\end{equation}
-where we have used the identity
-\begin{equation}
-\text{Li}_n( e^{ 2\pi i x }) + (-1)^n \text{Li}_n ( e^{-2\pi i x} ) = - \frac{(2\pi i )^n}{ n!} B_n ( x) , \qquad 0 \le \text{Re}(x)<1, \text{Im}(x) > 0 
-\end{equation}
-For $n = 2$, we need the second Bernoulli polynomial
-\begin{equation}
-B_2( x) = x^2 - x + \frac{1}{6} , \quad B_2( \frac{1}{4} ) = - \frac{1}{48} 
-\end{equation}
-hence
-\begin{equation}
-E_c = {\color{blue} \frac{1}{96}\beta } 
-\end{equation}
-The other case with $b_1 = -1$ corresponds to the $\theta \rightarrow \frac{\pi}{2} - \theta$, and we have the same answer. 
-\end{enumerate}
-
-The folding trick boundary state agrees with all the other calculations. With the Casimir energy correction, it reproduces the logarithmic echo in Tab.~\ref{tab:log_echo}.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [echo_folding.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\section{Bipartite Fidelity}
-\subsection{Finite Size Scaling}
-% flatex input: [fidel_fs.tex]
-
-Bipartite fidelity is the overlap of the groundstates of two Hamiltonians.
-It is diagrammatically shown in Fig.~\ref{fig:fidel}.
-Regarding it as a partition function, we analyze the finite size dependence on $L$ of the free energy
-\begin{equation}
-\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z   = 2 E_c = \sim \# \ln L 
-\end{equation}
-In some sense it is the echo diagram with $\tau \gg L$ and can provide the same information yet easier to be computed numerically. 
-% flatex input: [fig_fidel.tex]
-
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[scale = 1.2]
-\draw (0,0) -- (3,0);
-\draw (0,2) -- (3,2);
-\draw (0,1.02) --++( 1.5, 0);
-\draw (0,0.98) --++( 1.5, 0);
-\draw[dashed] (1.5,1) --++( 1.5, 0);
-\node () at (4.5,1.2) {\Large $\xrightarrow{\rm folding}$};
-\begin{scope}[shift={(6,0.5)}]
-\draw (0,0) -- (1.5,0);
-\draw[dashed] (1.5,0) -- (3,0);
-\draw (0,1.2) -- (3,1.2);
-\draw[-stealth] (2,0.9)--(2, 1.18);
-\draw[-stealth] (2,0.3)--(2, 0.02);
-\node () at (2,0.6) {$L$};
-\end{scope}
-\end{tikzpicture}
-\caption{Fidelity of connecting two CFTs.
-The horizontal axis the imaginary time.
-Evolution on the two infinitely extended side produces the groundstate of the disconnected/connected Hamiltonian.
-The right diagram is the result of folding the lower part of the diagram up, so that all the edges are conformal invariant boundary states.}
-\label{fig:fidel}
-\end{figure}
-% flatex input end: [fig_fidel.tex]
-
-% flatex input: [fig_fidel_map.tex]
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[scale = 1.5]
-\draw (0,0) -- (1.4,0);
-\draw[dashed] (1.6,0) -- (3,0);
-\draw[fill] (1.5,0) circle (0.02);
-\draw[blue] [domain=0:180] plot ({1.5+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw (0,1.2) -- (3,1.2);
-\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
-\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
-\node () at (2.5,0.6) {$L$};
-\node[below] () at (0.75,0) {$a$};
-\node[below] () at (2.25,0) {$b$};
-\node[above] () at (1.5,1.2) {$c$};
-\draw[blue] (3,0)--++(0,1.2);
-\begin{scope}[shift={(0.5,0.6)}]
-\node () at (0.1,0.1) {$w$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\begin{scope}[shift={(7,0)}]
-\draw (-1.5,0)--(0.3,0);
-\draw[dashed] (0.5,0)--(1.5,0);
-\draw[fill] (.4,0) circle (0.02);
-\draw[fill] (0,0) circle (0.02);
-\draw[blue] [domain=0:180] plot ({0.4+0.1*cos(\x)}, {0.1*sin(\x)});
-\draw[blue] [domain=0:180] plot ({1.5*cos(\x)}, {1.5*sin(\x)});
-\begin{scope}[shift={(0.6,0.8)}]
-\node () at (0.1,0.1) {$z$};
-\draw (0,0.1)--(0,0)--(0.1,0);
-\end{scope}
-\end{scope}
-\end{tikzpicture}
-\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $.
-The two black dots represent possible insertion of bcc operators.
-The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries.
-The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
-To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
-\label{fig:fidel-map}
-\end{figure}
-
-% flatex input end: [fig_fidel_map.tex]
-
-As usual, we map the diagram to the upper half plane and close it, as shown in Fig.~\ref{fig:fidel-map}.
-If the three boundary conditions are all different, then there are two bcc operators on the real axis.
-We first deal with the easy one where $a = c$.
-The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
-\begin{equation}
-\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
-\end{equation}
-The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $.
-Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
-We can then machinery developed in the echo calculation.
-In this case, the length of the cylinder is
-\begin{equation}
-\beta = \ln e^{\pi \frac{W}{L}} - \ln \pi \frac{\epsilon}{L}  \sim \ln L 
-\end{equation}
-Since the fidelity is twice the Casimir energy, we shall make the replacement recipe $\beta \sim 2 \ln L$.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [fidel_fs.tex]
-
-% configure hyperref to remove ugly boxes from links
-% flatex input: [fidel_num_res.tex]
-
-\subsection{Comparison with Numerical Results}
-
-We check several interesting cases in the numerical fidelity calculation of free boson interface.
-
-From our previous calculation, DD/NN $\rightarrow \lambda$ is trivial.
-The interesting case is the DN $\rightarrow \lambda$ interface.
-Using either the boundary state or ground state energy calculation in App.~\ref{app:gnd_dn_lambda} plus the correction, we have
-\begin{equation}
-\begin{aligned}
-\mathcal{F} &= \frac{\beta}{2}( - x^2 + x - \frac{1}{6} ) + {\color{red} \frac{\beta}{12}} = \frac{\beta}{2}( - x^2 + x ) \\
-&= ( - x^2 + x ) \ln L  \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
-\end{aligned}
-\end{equation}
-% flatex input: [fig_dn_lambda.tex]
-
-\begin{figure}[h]
-% settings for subfigure 1
-\begin{minipage}[t]{0.3\linewidth}
-\centering
-\begin{tikzpicture}[scale = 1.5]
-\draw (0,0.2) -- ++(3,0);
-\draw (0,1.8) -- ++(3,0);
-\draw (0,1.02) --++( 1.5, 0);
-\draw (0,0.98) --++( 1.5, 0);
-\node[above] () at (1.5,1.8) {N};
-\node[below] () at (1.5,0.2) {D};
-\node[above] () at (0.75,1) {N};
-\node[below] () at (0.75,1) {D};
-\node[below] () at (1.75,1) {$\lambda$};
-\draw[dashed] (1.5,1) --++( 1.5, 0);
-\node[right] () at (1.2,-0.5) {$\downarrow$};
-\node[right] () at (1.4,-0.5) {\large folding};
-\begin{scope}[shift={(0,-2.5)}]
-\draw (0,0) -- (1.5,0);
-\draw[dashed] (1.5,0) -- (3,0);
-\draw[fill] (1.5,0) circle (0.02);
-\draw (0,1.2) -- (3,1.2);
-\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
-\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
-\node () at (2.5,0.6) {$L$};
-\node[below] () at (0.75,0) {DN};
-\node[below] () at (2.25,0) {$\lambda$};
-\node[above] () at (1.5,1.2) {DN};
-\end{scope}
-\end{tikzpicture}
-\caption{DN $\rightarrow \lambda$ diagram before and after folding}
-\end{minipage}
-\hfill
-% settings for subfigure 2
-\begin{minipage}[t]{0.65\linewidth}
-\centering
-\includegraphics[width=\textwidth]{DN_DN2tan.pdf}
-\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
-\end{minipage}
-\end{figure}
-% flatex input end: [fig_dn_lambda.tex]
-
-\begin{figure}[!h]
-% settings for subfigure 1
-\begin{minipage}[t]{0.3\linewidth}
-\centering
-\begin{tikzpicture}[scale = 1.5]
-\begin{scope}[shift={(0.5,0)}]
-\draw (0,1) arc (90:270:0.15 and 0.5);
-\draw[dashed] (0,0) arc (-90:90:0.15 and 0.5);
-\draw (0,1) --++(2, 0);
-\draw (0,0) --++(2, 0);
-\draw[dashed] (1,0.5) --++(0.8, 0);
-\node[below] () at (1.3,0.5) {$\lambda$};
-\draw (2,0.5) ellipse (0.15 and 0.5);
-\end{scope}
-\node[right] () at (1,-0.5) {$\downarrow$};
-\node[right] () at (1.2,-0.5) {\large squeezing};
-\begin{scope}[shift={(0,-2.5)}]
-\draw (0,0) -- (1.5,0);
-\draw[dashed] (1.5,0) -- (3,0);
-\draw[fill] (1.5,0) circle (0.02);
-\draw (0,1.2) -- (3,1.2);
-\draw[-stealth] (2.5,0.9)--(2.5, 1.18);
-\draw[-stealth] (2.5,0.3)--(2.5, 0.02);
-\node () at (2.5,0.6) {$L$};
-\node[below] () at (0.75,0) {$\lambda = 1$};
-\node[below] () at (2.25,0) {$\lambda$};
-\node[above] () at (1.5,1.2) {$\lambda = 1$};
-\end{scope}
-\end{tikzpicture}
-\caption{P $\rightarrow \lambda$ diagram before and after squeezing}
-\end{minipage}
-\hfill
-% settings for subfigure 2
-\begin{minipage}[t]{0.65\linewidth}
-\centering
-\includegraphics[width=\textwidth]{p_p2tan.pdf}
-\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
-\end{minipage}
-\end{figure}
-
-Another interesting case is the when the far ends of the initial chains are connected(through periodic or a $\lambda$ interface). The analytic result is
-\begin{equation}
-\begin{aligned}
-  \mathcal{F}( \lambda = 1 \rightarrow \lambda ) &=  \frac{\beta}{2}\Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | - \frac{1}{6} \Big]  + {\color{red} \frac{\beta}{12}} \\
-  &= \Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | \Big]  \ln L \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
-\end{aligned}
-\end{equation}
-
-{\bf A note for the zero mode:} When zero mode is present, the boson groundstate is not well-defined; numerically instability kicks in.
-Adding a small mass is the common remedy, but doesn't work in the fidelity calculation.
-What we do here is to perturb the boundary condition by a small angle.
-
-In the DN$\rightarrow \lambda$ diagram, zero mode exists when the two sides of the chain $NN$ boundary condition.
-The combination DN is actually a $\lambda = 0$ interface.
-We modify one of them to $\lambda = \tan( 0.001 \pi )$ to avoid the zero mode.
-In the periodic case, we take the one of them to be $\lambda = \tan(0.251\pi)$ although precise periodic boundary condition corresponds to $\lambda = \tan(\frac{\pi}{4})$.
-This is a numerical way of regularization that matches with our no-zero-mode analytic calculation.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [fidel_num_res.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\appendix
-
-\section{DN-$\lambda$ Casimir Energy from Groundstate Energy Calculation}
-\label{app:gnd_dn_lambda}
 % flatex input: [gnd_dn_lambda.tex]
@@
 \centering
-\begin{tikzpicture}[scale = 1]
-\draw (0,0)--(0,2);
-\draw (1.5,0)--++(0,2);
-\node () at (-0.5,1) {DN};
-\node () at (1.8,1) {$\lambda$};
-\draw[-stealth] (0.75,0.75)--++(0,0.5);
-\begin{scope}[shift={(5,0)}]
-\draw (0,0)--(0,2);
-\draw (3,0)--++(0,2);
-\draw[dashed] (1.5,0)--++(0,2);
-\node () at (-0.5,1) {N};
-\node () at (3.5,1) {D};
-\node () at (1.7,1) {$\lambda$};
-\end{scope}
-\end{tikzpicture}
+\includegraphics{fig_gnd_dn_lambda.pdf}
 \caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions.
@@
 The full expression also agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [gnd_dn_lambda.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Calculation}
-\label{app:lambda_12}
-% flatex input: [lambda_1_lambda_2.tex]
-
-This calculation is very similar to the presented in App.~\ref{app:casimir_energy_DD_DN}.
-
-\begin{figure}[h]
-\centering
-\begin{tikzpicture}[scale = 1]
-\draw (0,0)--(2,0);
-\draw (0,1.5)--++(2,0);
-\node () at (1,-0.5) {$\lambda_1$};
-\node () at (1,2) {$\lambda_2$};
-\draw[-stealth] (1,0.5)--++(0,0.5);
-\end{tikzpicture}
-\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
-\end{figure}
-
-The wanted partition function is
-\begin{equation}
-Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} \mathbb{I}_2 \otimes M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det ( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b) }
-\end{equation}
-where
-\begin{equation}
-M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots )
-\end{equation}
-$R_a$($R_b$) correspond to the $\lambda_1$ and $\lambda_2$ boundary conditions. Using the fact that their determinants are $\det( R_a R_b^{\dagger})  = 1$, we have
-\begin{equation}
-\begin{aligned}
-F &= - \ln Z_{ab} = \ln \det( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b ) = \ln \det ( R_a R_b^{\dagger} - e^{- \mathbb{I}_2 \otimes M} )\\
-& = \ln \det 
-\begin{bmatrix}
-\cos 2 \Delta \theta \mathbb{I} - e^{-M}   & \sin 2 \Delta \theta \mathbb{I}\\
-- \sin 2\Delta \theta \mathbb{I}  &   \cos 2 \Delta \theta \mathbb{I} - e^{-M} \\ 
-\end{bmatrix} \quad \text{where } \Delta \theta = \theta_2 - \theta_1 \\
-& = \sum_i \ln [ 1 - 2 \cos 2 \Delta \theta e^{- \lambda_i } + e^{- 2 \lambda_i }  ] \\
-& = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \ln [ 1 - 2 \cos 2 \Delta \theta e^{-x} + e^{-2x} ] 
-\end{aligned}
-\end{equation}
-This integral is an even function of $\Delta \theta$ and the $\Delta \theta > 0$ case reduce to the polylog and Bernoulli polynomial
-\begin{equation}
-\begin{aligned}
-  F &= \frac{\beta}{4\pi^2} \left[ - \text{Li}_2 ( e^{2i |\Delta \theta|} ) - \text{Li}_2 ( e^{- 2i |\Delta \theta|} ) \right]  = \frac{\beta}{4\pi^2}  \left[ - 2\pi^2 B_2 (x) \right] \\
-  &= - \frac{\beta}{2} B_2( |x| ) = \frac{\beta}{2} (|x| - x^2 - \frac{1}{6}) \quad x = \frac{\Delta \theta}{ \pi} \\
-\end{aligned}
-\end{equation}
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [lambda_1_lambda_2.tex]
-
-% configure hyperref to remove ugly boxes from links
-
-\section{Determinant Identity for Amplitude between Boundary States}
-\label{app:pf_of_id}
-% flatex input: [pf_of_id.tex]
-
-For real symmetric matrix $M$
-\begin{equation}
-\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
-\end{equation}
-
-{\bf Proof:}  
-We first restrict to the case when $R = I$.
-To avoid confusion, we assume the daggered vector are row vectors and write $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\} $ as $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{*}  \Big\} $.
-
-{\it Diagonal Basis}: We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
-\begin{equation}
-  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^{*} = O^T \vec{\bar{b}}^{*}
-\end{equation}
-so that the whole expression can be written as
-\begin{equation}
-\begin{aligned}
-  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}  =  
-  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^{*}  \Big\} \\
-& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
-\end{aligned}
-\end{equation}
-{\it Baker-Campbell-Hausdorff formula}: For $ [X, Y] = sY $, we have a solvable case of Baker-Campbell-Hausdorff formula
-\begin{equation}
-  e^X e^{Y} = e^{\exp (s ) Y} e^{X}
-\end{equation}
-Taking $X = -\lambda_i d_i^{\dagger} d_i$, $Y = d_i^{\dagger}, \bar{d}^{\dagger}$, we have
-\begin{equation}
-[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
-\end{equation}
-and so $s = - \lambda_i$ for each $\lambda_i$. This enable us to commute those exponentials
-\begin{equation}
-\begin{aligned}
- \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}   &= \prod_i \exp \Big\{ \alpha e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
- & = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^{*}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
-\end{aligned}
-\end{equation}
-
-{\it The General Case}: When $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$.
-The role of $\bar{b}$ is decorative; it is effectively a $c$-number and we only use its independence w.r.t.
-$\vec{b}$.
-Hence the rest of the proof follows the same way.
-
-{\bf Corollary :} 
-\begin{equation}
-Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
-\end{equation}
-{\bf Proof:}
-
-Using the identity we have just proved, 
-\begin{equation}
-Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle 
-\end{equation}
-A direct application of the MacMahon master theorem
-\begin{equation}
-  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
- = \frac{1}{\det(1 - X^T Y )}
-\end{equation}
-proves the result.
-
-%%% Local Variables:
-%%% TeX-master: "bCFT_notes"
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [pf_of_id.tex]
-
-\bibliographystyle{unsrt}
-\bibliography{bCFT_notes}
-
-\end{document}
-%%% Local Variables: 
-%%% TeX-PDF-mode: t
-%%% End:
-% flatex input end: [bCFT_notes.tex]

### 2017-04-18 pf_of_id.tex
Initial commit

% flatex input: [pf_of_id.tex]

In this appendix, we provide more details for calculating the amplitude $Z_{ab}$ in Sec.{\bf\color{red}where}. We started to prove the following identity for a real symmetric matrix $M$
\begin{equation}
\label{1st id in app.pf_of_id}
\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{equation}
where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators. {\bf\color{red}As emphasized in the main text}, the matrix notation, for example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.

To prove Eq.(\ref{1st id in app.pf_of_id}), we first consider the special case where $R={\bf I}$. We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
\begin{equation}
  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^\dagger = O^T \vec{\bar{b}}^\dagger
\end{equation}
where we understood $\vec{\bar{b}}^\dagger$ is a column vector and independent to $\vec{{b}}^\dagger$. Thus the whole expression can be written as
\begin{equation}
\begin{aligned}
  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}  =  
  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger  \Big\} \\
& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
\end{aligned}
\end{equation}
We recall for $ [X, Y] = sY $, 
\begin{equation}
  e^X e^{Y} = e^{\exp (s ) Y} e^{X}
\end{equation}
which is a solvable case of Baker-Campbell-Hausdorff formula. Upon taking $X = -\lambda_i d_i^{\dagger} d_i$, $Y = d_i^{\dagger} \bar{d}^{\dagger}_i$, we have
\begin{equation}
\label{lambda commutator}
[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
\end{equation}
and so $s = - \lambda_i$ for each $\lambda_i$. This enable us to commute those exponentials
\begin{equation}
\begin{aligned}
 \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}   &= \prod_i \exp \Big\{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
 & = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{aligned}
\end{equation}
For the general case where $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$. This will not change the commutation relation of ${\bf d}$, and the role of $\bar{b}$ is decorative in Eq.(\ref{lambda commutator}). Hence the rest of the proof follows the same way. \hfill$\blacksquare$

A direct consequence of Eq.(\ref{1st id in app.pf_of_id}) is the following
\begin{equation}
\label{2nd id in app.pf_of_id}
Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} 
\end{equation}
where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$. Using the identity we have just proved, 
\begin{equation}
Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle 
\end{equation}
A direct application of the MacMahon master theorem
\begin{equation}
  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
 = \frac{1}{\det(1 - X^T Y )}
\end{equation}
proves Eq.(\ref{2nd id in app.pf_of_id}). \hfill$\blacksquare$

### 2017-04-19 comp_fid_echo.tex
Initial commit

% flatex input: [comp_fid_echo.tex]

In this appendix, we provide the technical details on numerical calculation of bipartite fidelity and Loschmidt echo. We shall {\bf\color{red}1. lay out the plan for this long appendix. 2. Point out out method is different from Moore. 3. This is more general as Moore's does not apply to boson (say why?) but ours can be easily generalized to fermion 4. Say sth on Williamson. For fermion, Schur's decomposition replaces Williamson (probably in the end?). 5. Compare to the fermionic case in the echo section. }

\subsection{Boson Bogoliubov transformation}
\label{Boson BdG}
We consider the following quadratic bosonic Hamiltonian
\begin{eqnarray}\begin{aligned}
\label{Quadratic boson H}
\hat{H}&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
&=\frac{1}{2}
\left(\begin{array}{ccc}
{\bf b}^\dagger & -{\bf b}
\end{array}\right)
\left(\begin{array}{ccc}
H & \Delta\\
-\Delta^\dagger & -H^T
\end{array}\right)
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right)-\frac{1}{2}\text{tr}H,
\end{aligned}\end{eqnarray}
where ${\bf b}\equiv(b_{1},...,b_{N})$ is a vector of annihilation operators. Notice $H$ is a $N\times N$ single-particle Hamiltonian, and $\Delta$ is a symmetric paring matrix. The use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ is due to the Sp(2N,{\bf C}) character of the bosonic Bogoliubov transformation, as we now demonstrate.

The Bogoliubov transformation that diagonalizes the Hamiltonian
\begin{eqnarray}\begin{aligned}
\label{Def. of a}
({\bf a} , {\bf a}^\dagger)\equiv({\bf b} , {\bf b}^\dagger)S
\end{aligned}\end{eqnarray}
should preserve the commutation relation
\begin{eqnarray}\begin{aligned}
\label{Preserve commutator}
J\equiv\left(\begin{array}{ccc}
0 & {\bf I}\\
-{\bf I} & 0
\end{array}\right)
=\left[
\left(\begin{array}{ccc}
{\bf a} \\
{\bf a}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf a} & {\bf a}^\dagger
\end{array}\right)\right]
=S^T\left[
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right),
\left(\begin{array}{ccc}
{\bf b} & {\bf b}^\dagger
\end{array}\right)\right]S
=S^T JS,
\end{aligned}\end{eqnarray}
where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$. It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C}){\bf\color{red}Cite sth}. Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
\begin{eqnarray}\begin{aligned}
\label{Block of S}
S=\left(\begin{array}{ccc}
u & v^*\\
v & u^*
\end{array}\right).
\end{aligned}\end{eqnarray}
The symplectic property of S implies the following constraints 
\begin{eqnarray}
u^\dagger u-v^\dagger v&={\bf I}\label{Constraint 1}\\
u^T u-v^T v&=0\label{Constraint 2}
\end{eqnarray}
which will be important for calculation of the ground state.

For the ground state of the quadratic Hamiltonian in Eq.(\ref{Boson BdG}), it is the vacuum of the annihilation operators defined in Eq.(\ref{Def. of a}) and satisfies
\begin{eqnarray}\begin{aligned}
\label{a Vacuum condition}
(b_iu_{ij}+b_i^\dagger v_{ij})|0\rangle_{{\bf a}}=0.
\end{aligned}\end{eqnarray}
If the matrix $u$ is invertible, then we can introduce a matrix
\begin{eqnarray}\begin{aligned}
T=vu^{-1}
\end{aligned}\end{eqnarray}
such that Eq.(\ref{a Vacuum condition}) reduces to
\begin{eqnarray}\begin{aligned}
(b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0,
\end{aligned}\end{eqnarray}
One can use Eq.(\ref{Constraint 2}) to show that $T$ is symmetric, and observe that
\begin{eqnarray}\begin{aligned}
\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}b_i\exp\left\{\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}=b_i+T_{ij}b^\dagger_j.
\end{aligned}\end{eqnarray}
Thus we conclude that 
\begin{eqnarray}\begin{aligned}
\label{Boson BCS gnd}
|0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
&=|\text{det}(u)|^{-\frac{1}{2}}\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}.
\end{aligned}\end{eqnarray}
where we have used Eq.(\ref{Constraint 1}) in the second line. From the following McMahon master theorem
\begin{eqnarray}\begin{aligned}\label{Bosonic McMahon}
\langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY)
\end{aligned}\end{eqnarray}
one can easily check that the ground state in Eq.(\ref{Boson BCS gnd}) is correctly normalized.

{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. }

\subsection{Boson fidelity} 
\label{Boson fidelity}

Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians{\bf\color{red}cite sth}. We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.(\ref{Quadratic boson H}). From the discussion in App.{\bf\color{red}where}, we are able to diagonalize it in ${\bf a}$ basis. At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis. The corresponding Bogoliubov transformations read
\begin{eqnarray}\begin{aligned}
\label{Two BdG}
({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
such that
\begin{eqnarray}\begin{aligned}
\label{S0invS}
({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
\end{aligned}\end{eqnarray}
One immediately realizes Eq.(\ref{S0invS}) takes the same form as Eq.(\ref{Def. of a}) such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
\begin{eqnarray}
S_0^{-1}S_1=\left(\begin{array}{ccc}
u_1 & v_1^*\\
v_1 & u_1^*
\end{array}\right).
\end{eqnarray}
Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.(\ref{Boson BCS gnd}), and their overlap, which is the fidelity, reads
\begin{eqnarray}\begin{aligned}
|_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|}
\end{aligned}\end{eqnarray}

\subsection{Boson Loschmidt echo}

The Loschmidt echo is defined as the overlap of the evolved state
\begin{eqnarray}\begin{aligned}
|0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a}
\end{aligned}\end{eqnarray}
with the $\hat{H}_0$ ground state $|0\rangle_{\bf a}$. We introduce the third dynamical basis
\begin{eqnarray}\begin{aligned}
a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t}
\end{aligned}\end{eqnarray}
which annihilate the evolved state at time t: $a_i(t)|0\rangle_{{\bf a}(t)}=0$. Upon using the expression $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time t can be represented as a chain of symplectic transformation
\begin{eqnarray}\begin{aligned}
\label{BdG transformation for echo}
({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
({\bf a} , {\bf a}^\dagger)e^{iHt}=({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
\end{aligned}\end{eqnarray}
It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.(\ref{Boson BCS gnd}). In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.(\ref{BdG transformation for echo}), and it {\bf\color{red}reads}
\begin{eqnarray}\begin{aligned}
\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=\frac{1}{|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|}
\end{aligned}\end{eqnarray}

\subsection{Description on how to get S}

As demonstrated in App.{\bf\color{red}where}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.(\ref{Two BdG}). Here, for a quadratic bosonic Hamiltonian
\begin{eqnarray}\begin{aligned}
\label{Quadratic boson H2}
\hat{H}&=\frac{1}{2}
\left(\begin{array}{ccc}
{\bf b}^\dagger & -{\bf b}
\end{array}\right)
\left(\begin{array}{ccc}
H & \Delta\\
-\Delta^\dagger & -H^T
\end{array}\right)
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right)\\
&=\frac{1}{2}
\left(\begin{array}{ccc}
{\bf b}^\dagger & -{\bf b}
\end{array}\right)
M
\left(\begin{array}{ccc}
{\bf b} \\
{\bf b}^\dagger
\end{array}\right)
\end{aligned}\end{eqnarray}
we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,{\bf C}) that diagonalizes M. The basic idea is {\bf\color{red}what}.

We introduce the real basis 
\begin{eqnarray}\begin{aligned}
\label{Real basis}
\left(\begin{array}{ccc}
{\bf b}\\
{\bf b}^\dagger
\end{array}\right)
=C\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{\sqrt{2}}\left(\begin{array}{ccc}
1 & i \\
1 & -i
\end{array}\right)\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
in which the Hamiltonian reads
\begin{eqnarray}\begin{aligned}
\hat{H}
&=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\text{Re}(H+\Delta) & -\text{Im}(H-\Delta)\\
\text{Im}(H+\Delta)& \text{Re}(H-\Delta) \\
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
It is not hard to realize $\mathcal{M}$ is real and symmetric. We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
d\\
&d
\end{array}\right)\tilde{S}^T
\end{aligned}\end{eqnarray}
where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. Thus we have
\begin{eqnarray}\begin{aligned}
\label{Diagonalization of M}
M=J(C^{-1})^T\tilde{S}C^TJ^{-1}\left(\begin{array}{ccc}
d\\
&-d
\end{array}\right)C\tilde{S}^TC^{-1}.
\end{aligned}\end{eqnarray}
Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.(\ref{Diagonalization of M}) is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form as in Eq.(\ref{Block of S}), is an element of complex symplectic group. Thus we identify 
\begin{eqnarray*}\begin{aligned}
S\equiv C\tilde{S}^TC^{-1}
\end{aligned}\end{eqnarray*}
as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.(\ref{Quadratic boson H2}).

Notice in the above construction, we have assumed the Hamiltonian in the real basis to be positive definite. {\bf\color{red}This is not as restrictive as it may appear}, and in App.{\bf\color{red}where} we shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain.
\subsection{Harmonic chain}

{\bf\color{red}Say sth on harmonic chain}

In the real basis defined in Eq.(\ref{Real basis}), the Hamiltonian for 1D harmonic chain reads
\begin{eqnarray}\begin{aligned}
\hat{H}
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\mathcal{M}
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
=\frac{1}{2}
\left(\begin{array}{ccc}
\phi & \pi
\end{array}\right)
\left(\begin{array}{ccc}
\mathcal{V} \\
& {\bf I}
\end{array}\right)
\left(\begin{array}{ccc}
\phi\\
\pi
\end{array}\right)
\end{aligned}\end{eqnarray}
where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$. We construct the following real symplectic matrix
\begin{eqnarray}\begin{aligned}
\tilde{S}\equiv\left(\begin{array}{ccc}
\mathcal{O}D^{1/2} \\
& \mathcal{O}D^{-1/2}
\end{array}\right)
\end{aligned}\end{eqnarray}
such that 
\begin{eqnarray}\begin{aligned}
\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
D \\ 
& D
\end{array}\right)
\tilde{S}^T
\end{aligned}\end{eqnarray}
in accordance with Williamson's theorem. Thus the second quantized Hamiltonian will be diagonalized as
\begin{eqnarray}\begin{aligned}
M=S^{-1}\left(\begin{array}{ccc}
D \\
& -D
\end{array}\right)S
\end{aligned}\end{eqnarray}
where the Bogoliubov transformation take the desired block form
\begin{eqnarray}\begin{aligned}
S&=C\tilde{S}C^{-1}
&=\left(\begin{array}{ccc}
O(D^{1/2}+D^{-1/2}) & O(D^{1/2}-D^{-1/2}) \\
O(D^{1/2}-D^{-1/2}) & O(D^{1/2}+D^{-1/2}) 
\end{array}\right)
\end{aligned}\end{eqnarray}

### 2017-04-28 bCFT_paper.tex
Initial commit
[draft]intro content done.

@@
 \usepackage{todonotes}
+\graphicspath{{./}{./images/}}
 \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
@@
 
-\title{Bipartite Fidelity and Loschmidt echo of bosonic conformal interface}
+\title{Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface}
 
@@
 \section{Introduction}
-% the last one to be finished.
+\input{intro}
 
@@
 
+% connecting Luttinger liquid(quantum wire) using votage to control the boundary condition.
+X-ray edge singularity.
+examples include Taylor santo's topological phases.
+Hope to have experimental setup.
+There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
+For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions.
+The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides.
+
 \begin{acknowledgments}
@@
 \section{A Determinant Identity for the Boundary State Amplitude}
+\label{app:pf_of_id}
 % copy notes app. C
+\input{pf_of_id}
 
 \section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
+\label{app:lambda_12}
 % copy notes app. B
+\input{lambda_1_lambda_2}
 
 \section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
+\label{app:gnd_dn_lambda}
 % copy notes app. A
+\input{gnd_dn_lambda}
 

### 2017-04-28 intro.tex

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing operator\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}. One example is the "Anderson orthogonality catastrophe", where the core hole creates a potential that act as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problem of this kind that has been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc.

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The "cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system. As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitation emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} take A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this mode, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{fig_cut_and_join.pdf}
\caption{Cut-and-join quench protocol. Left panel: prepare the ground states of two separated chains and joined them at $t = 0$, then do the time evolution with whole chain Hamiltonian. Right panel: spacetime diagram of the cut and join protocol. The solid line represents the boundaries of the two disconnected chains. It is totally reflective for the incident particles on both sides. The dashed line is the world line of the junction, which we will call interface. It could either be totally transparent or partially permeable, depending the types of theories of A and B.}
\label{fig:cut-and-join}
\end{figure}

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the "cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit before $t = 0$ represents the boundary that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of \onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to consider to connect two different CFTs in the "cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There is also non-compact free boson/free fermion lattice realization, which was used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses. We expect it to be tunable in the a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench. There is no dynamic information in fidelity, nevertheless its finite size effect also reveal the boundary critical exponent that maybe be diagnostic in Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFT in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. What we do in this paper is to extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.

% structure of the paper.
\todo[inline]{structure of the paper}

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-04-28 bCFT_paper.tex
add bCFT_paper.tex
[draft]all embedding tikz figures are standalone

--- 2017-04-17 bCFT_paper.tex
@@
-\documentclass[preprint, prb]{revtex4-1}
+\documentclass{article}
 \usepackage{amsmath}
 \usepackage{amssymb}
+\usepackage[compact]{titlesec}
+\usepackage{xcolor}
 \usepackage{graphicx}
-\usepackage{enumitem}
+\usepackage{tikz}
+\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
+\usepackage{wrapfig}
 \usepackage{bm}
-\usepackage[font={footnotesize}]{caption}
 \usepackage{todonotes}
+
+\graphicspath{{./}{./images/}}
+
+\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
+\newcommand{\tr}[0]{\text{tr}}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+
+\tikzset{
+    partial ellipse/.style args={#1:#2:#3}{
+        insert path={+ (#1:#3) arc (#1:#2:#3)}
+    }
+}
+
+\textwidth = 6.5 in
+\textheight = 9 in
+\oddsidemargin = 0.0 in
+\evensidemargin = 0.0 in
+\topmargin = 0.0 in
+\headheight = 0.0 in
+\headsep = 0.0 in
+\parskip = 0.2in
+\parindent = 0.0in
+
+% configure hyperref to remove ugly boxes from links
 \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
 \usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
-\usepackage[all]{hypcap}
 
-\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
-
-\newcommand{\cf}{\textit{cf.} } 
-\newcommand{\ie}{\textit{i.e.} } 
-\newcommand{\eg}{\textit{e.g.} }
-\newcommand{\vs}{\textit{vs.} } 
-\newcommand{\etal}{\textit{et al.} }
-\newcommand{\etc}{\textit{etc.} }
+\title{Boundary Conformal Field Theory}
+\author{Tianci Zhou}
 
 \begin{document}
+\maketitle
+\large
 
-\title{Bipartite Fidelity and Loschmidt echo of bosonic conformal interface}
+\section{Conformal Interface of Free Boson}
+% flatex input: [boson_interface.tex]
+\label{sec:var-boson}
+[Section 2.1-2.2 of \cite{bachas_permeable_2002}.]
 
-\author{Tianci Zhou}
-\email{tzhou13@illinois.edu}
-\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}
+Let's consider the conformal interface connecting two possibly different free boson CFTs. Suppose the interface is located at $x = 0$ that glues the two theories in such a way that 
+\begin{equation}
+\begin{bmatrix}
+\partial_t \phi\\
+\partial_x \phi\\ 
+\end{bmatrix}_{x = 0^-} 
+ = M \begin{bmatrix}
+\partial_t \phi\\
+\partial_x \phi\\ 
+\end{bmatrix}_{x = 0^+} 
+\end{equation}
+One may write the field on the left/right as $\phi^1$($\phi^2$), and then the gluing condition is
+\begin{equation}
+\partial_{\mu} \phi^1 = M_{\mu\nu} \partial_{\nu} \phi^2 
+\end{equation}
+The interface is now penetrable, and condition \eqref{eq:stress-cond} is weakened that only requires continuity of the momentum across the interface. From the explicit expression
+\begin{equation}
+T^{xt} = - g \partial_x \phi \partial_t \phi  = -g(\partial_{\mu} \phi \sigma^x_{\mu\nu}  \partial_{\nu} \phi ) 
+\end{equation}
+we have the relation
+\begin{equation}
+\partial_{\mu} \phi^2 \sigma^x_{\mu\nu}  \partial^2_{\nu} \phi -  \partial_{\mu} \phi^1 \sigma^x_{\mu\nu}  \partial^1_{\nu} \phi = 
+\partial_{\mu} \phi^2 [\sigma^x_{\mu\nu} - M^T  \sigma^x M)_{\mu\nu} ]  \partial_{\nu} \phi^2 = 0
+\end{equation}
+For generic field configuration $\phi^2$, the condition is satisfied only when
+\begin{equation}
+\sigma^x = M^T \sigma^x M 
+\end{equation}
+By diagonalizing $\sigma^x$ and doing corresponding orthogonal transformation on $M$, 
+\begin{equation}
+\sigma^z = ( OMO^T  )^T \sigma^z ( OMO^T )  \quad 
+O = \frac{1}{\sqrt{2}} 
+\begin{bmatrix}
+1 & 1 \\
+1 & -1 \\                       
+\end{bmatrix}
+\end{equation}
+we realize $O M O^T$ is in the Lorentz group $O( 1, 1 )$, whose 4 disconnected components that are determined by the sign of determinants and the $00$ element. A natural boost parameterization are 
+\begin{equation} 
+\Lambda = O M O^T = \pm 
+\begin{bmatrix}
+\cosh \beta & \sinh \beta \\
+\sinh \beta & \cosh \beta \\  
+\end{bmatrix}
+\quad \pm 
+\begin{bmatrix}
+\cosh \beta & -\sinh \beta \\
+\sinh \beta & -\cosh \beta \\  
+\end{bmatrix}
+\end{equation}
+Reverting back to $M$, we have $\lambda = e^{-\beta}$
+\begin{equation}
+M_1 = \pm 
+\begin{bmatrix}
+\lambda^{-1} & 0 \\
+0 & \lambda \\
+\end{bmatrix}
+\quad 
+M_2 = \pm 
+\begin{bmatrix}
+0 & \lambda\\
+\lambda^{-1} & 0 \\
+\end{bmatrix}
+\end{equation}
+The $\pm$ branches in each $M$ can be combined if we set $\lambda = \text{tan} \theta$ for $\theta \in [- \frac{\pi}{2}, \frac{\pi}{2} ] $.
 
-\author{Mao Lin}
-\email{maolin2@illinois.edu}
-\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}
+The physical significance of $\theta$ can be seen in the following scattering picture.
+The solutions of equation of motion are the left and right moving waves.
+The derivative $\partial_{-} = \partial_t - \partial_x$ removes the left moving component($x+t$) and hence can generate right moving fields $\partial_{-} \phi$.
+The process of right moving $\phi^1$ combined with left moving $\phi^2$ to generate a left moving $\phi^1$ and right moving $\phi^2$
+\begin{equation}
+\partial_{-} \phi^1 + \partial_{+} \phi^2 \rightarrow \partial_{+} \phi^1 + \partial_{-} \phi^2
+\end{equation}
+can be described by the scattering matrix
+\begin{equation}
+\begin{bmatrix}
+\partial_{+} \phi^1 \\
+\partial_{-} \phi^2 \\
+\end{bmatrix}
+ = S
+\begin{bmatrix}
+\partial_{-} \phi^1 \\
+\partial_{+} \phi^2 \\
+\end{bmatrix}
+\end{equation}
+After some linear algebra, we find that $2\theta$ is the angle that parameterize the scattering matrix\footnote{I adopt several different conventions from \cite{bachas_permeable_2002}.
+1.
+I put $\partial_t$ as the first entry of the vector.
+2.
+The matrices $M(\lambda)$ is actually $M(\lambda^{-1} )$ in \cite{bachas_permeable_2002}.
+These two cancel out and the resulting gluing conditions are the same.
+3.
+I take $\partial_{-} \phi^1, \partial_{+} \phi^2$ as incoming wave, so that the $S$ matrix maps it to the outgoing waves, while \cite{bachas_permeable_2002} use the opposite: they obtain $S^{-1}$.
+Incidentally, $S = S^{-1}$.
+4.
+I take $\partial_{-} = \partial_t - \partial_x $, while \cite{bachas_permeable_2002} seems to take $\partial_{-} = \partial_x - \partial_t$.
+Interchanging $x$ and $t$ amounts to change $\lambda$ to $\lambda^{-1}$, or $\theta$ to $\frac{\pi}{2}- \theta$, which indeed converts $S$ here to the $S$ in \cite{bachas_permeable_2002}.
+}
+\begin{equation}
+\label{eq:S1-S2}
+S_1 =
+\begin{bmatrix}
+\cos 2 \theta & \sin 2 \theta \\
+\sin 2 \theta & - \cos 2 \theta     
+\end{bmatrix}
+\qquad
+S_2 = 
+\begin{bmatrix}
+-\cos 2 \theta & \sin 2 \theta \\
+-\sin 2 \theta & - \cos 2 \theta   
+\end{bmatrix}
+\end{equation}
 
-\date{\today}
+\subsection{Example: Free Boson with Different Compactification Radii}
 
-\begin{abstract}
-\end{abstract}
+[Section 2.2 of \cite{bachas_permeable_2002}.]
 
-\maketitle
+Suppose $\phi^1$ and $\phi^2$ are compact Bosons with compactification radii $2\pi R_1$ and $2\pi R_2$. We can rescale them to a single field 
+\begin{equation}
+\phi = \left\lbrace
+       \begin{aligned}
+         R_1^{-1} \phi^2  & \quad  x < 0 \\
+         R_2^{-1} \phi^2  & \quad x > 0  \\
+       \end{aligned} \right. 
+\end{equation}
+such that $\phi$ is a compact boson on the whole plane with radius $2\pi$, whose action(in Euclidean time) reads
+\begin{equation}
+S = \frac{g}{2} R_1^2 \int_{x \le 0 } \left(  \nabla \phi \right)^2 d\tau dt  + \frac{g}{2} R_2^2 \int_{x > 0 } \left(  \nabla \phi  \right)^2 d\tau dt 
+\end{equation}
+Both the bulk action as well as the interface should be invariant under the conformal transformation.
+We do such a conformal transformation, which induces a change on the field $\phi \rightarrow \delta \phi $, and since the bulk is invariant, we only need to check the boundary term
+\begin{equation}
+S = \frac{g}{2} \int_{x = 0 } ( R_1^2 \partial_x \phi\big|_{x = 0^{-}}   - R_2 ^2 \partial_x \phi \big|_{x = 0^{+}} ) \delta \phi  d\tau = 0
+\end{equation}
+The boundary condition
+\begin{equation}
+R_1^2 \partial_x \phi\big|_{x = 0^{-}}  = R_2 ^2 \partial_x \phi \big|_{x = 0^{+}}
+\end{equation}
+which makes any variation vanish must be conformal invariant. In terms of the $\phi^1$, $\phi^2$ fields
+\begin{equation}
+\partial_x \phi^1 = \frac{R_2}{R_1} \partial_x \phi^2 
+\end{equation}
+According to our previous analysis, it corresponds to $M_1$ with $\lambda = \frac{R_2}{R_1} = \tan \theta$, namely
+\begin{equation}
+\label{eq:cpt_boson_bd}
+\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  - \cos \theta \phi^2 ) = 0
+\end{equation}
 
-\section{Introduction}
-% the last one to be finished.
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
 
-\section{Bosonic Conformal Interface}
-\subsection{General Formulation}
-% M, S
-% special case
-\subsection{Physical Realization: Connecting Bosons of Different Compactification Radii}
-% free boson + compact
-\subsection{A Free Boson Lattice Model}
-% cite Calabrese, introduce the model
-% lattice model S matrix
+% flatex input end: [boson_interface.tex]
 
-\section{Bipartite Fidelity and Loschmidt Echo}
-\subsection{Definition}
-% definition
-% general discussion
+% configure hyperref to remove ugly boxes from links
 
-\section{Analytic and Numerical Results}
-\subsection{Fidelity}
-% analytic: conformal transformation
-% numerical comparison 
-\subsection{Loschmidt Echo}
-% analytic: conformal transformation
-% numerical comparison
+\subsection{Folding Trick and Boundary State}
+% flatex input: [folding.tex]
 
-\section{Discussion}
+[Section 2.3-2.4 of \cite{bachas_permeable_2002}]
 
-\begin{acknowledgments}
-\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
-    TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
-    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
-    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
-    Supercomputing Applications (NCSA) and which is supported by funds from the University of
-    Illinois at Urbana-Champaign.
-\end{acknowledgments}
+We can fold the field $\phi^2$ to the left half plane on top of $\phi^1$, then the boundary at $x = 0$ is impenetrable for the tensor theory and therefore is a boundary state of Boson.
+
+The folding takes $x$ to $-x$ in $\phi^2$, so its $x$ derivative in the boundary condition \eqref{eq:cpt_boson_bd} will change sign and becomes\footnote{Change $\theta$ to $\frac{\pi}{2} - \theta$ to compare relevant result with in \cite{bachas_permeable_2002}.
+I believe the \cite{bachas_permeable_2002} made a mistake here.
+Nevertheless the Casimir energy is insensitive to this change.},
+\begin{equation}
+\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  + \cos \theta \phi^2 ) = 0
+\end{equation}
+It looks like the rotated field within $\partial_t$ takes Dirichlet boundary condition and the other orthogonal field within $\partial_x $ takes Neumann boundary condition, so we have\footnote{We will deal with the winding sector in Sec.~\ref{sec:winding}}
+\begin{equation}
+\label{eq:rot-D-N}
+\begin{aligned}
+\cos  \theta a^1_n - \sin \theta a^2_n  &= + \left( \cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} \right)\\
+\sin  \theta a^1_n + \cos \theta a^2_n  &= - \left( \sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} \right) 
+\end{aligned}
+\end{equation}
+The left and right sides can be regarded as two new sets of $a^1$ and $a^2$ whose commutation relation is preserved by the orthogonal rotation. Consequently, the boundary state is
+\begin{equation}
+\label{eq:bd_state}
+\begin{aligned}
+| B \rangle &= \exp\Big\{ \sum_{n > 0 } \frac{1}{n} (\cos  \theta a^1_{-n} - \sin \theta a ^2_{-n} )(\cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} ) \\
+& \,\,  \qquad \qquad -\frac{1}{n} (\sin  \theta a^1_{-n} + \cos \theta a ^2_{-n} )(\sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} )
+\Big\} | 0 \rangle \\
+& = \exp\Big\{ \sum_{n > 0 } \frac{1}{n} \left( \cos 2\theta a^1_{-n} \bar{a}^1_{-n}  - \cos 2\theta a ^2_{-n} \bar{a}^2_{-n}   
+- \sin 2 \theta a ^2_{-n}\bar{a}^1_{-n}  - \sin 2 \theta a ^1_{-n}\bar{a}^2_{-n}  \right ) \Big\}| 0 \rangle \\
+& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
+\begin{bmatrix}
+a_{-n}^1\\
+a_{-n}^2\\                              
+\end{bmatrix}
+S_1
+\begin{bmatrix}
+\bar{a}_{-n}^1  \bar{a}_{-n}^2
+\end{bmatrix} \Big\}
+\end{aligned}
+\end{equation}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [folding.tex]
+
+% configure hyperref to remove ugly boxes from links
+
+\section{Compact Boson Winding Modes}
+\label{sec:winding}
+% flatex input: [D_and_N.tex]
+
+\subsection{Dirichlet and Neumann Boundary Conditions}
+
+[Section 2 of \cite{bachas_fusion_2008}, Section 6.3.5 of \cite{di_francesco_conformal_1997}]
+
+The winding modes of compact boson determines the conformal dimensions of the primary fields.
+It therefore restrict possible bcc operators on the boundary.
+In this section we work the simple Dirichlet and Neumann conditions for the winding modes.
+
+{\bf Mode Expansion:} 
+Suppose the boson is compactified as $\phi \rightarrow \phi + 2\pi R$, then mode expansion in Eq.~\ref{eq:boson-mode-exp} will have a different zero mode\footnote{The sign of the $x$ term is different from Eq.
+(6.91) in \cite{di_francesco_conformal_1997}, but calculation later shows that the $-$ sign is correct to give the $(\frac{n}{4\pi gR} + \frac{1}{2} \frac{m}{R})$ combination for $z$.
+}
+\begin{equation}
+\begin{aligned}
+\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \text{oscillator part}  \\
+&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  + \text{oscillator part}  \\
+\end{aligned}
+\end{equation}
+where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$.
+A particle living on unit circle $[0, 2\pi]$ have integer($m \hbar$) angular momentum(conjugate momentum), and so momentum of Boson living on $[0, 2\pi R]$ will have $\frac{n}{R}$ as its eigenvalues.
+
+The left and right mode decomposition is again done by complex variables
+\begin{equation}
+z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
+\end{equation}
+which leads to
+\begin{equation}
+\label{eq:boson-mode-exp}
+\begin{aligned}
+\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
+&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
+\end{aligned}
+\end{equation}
+From the holomorphic derivative 
+\begin{equation}
+i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1}  \qquad a_0 = \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)
+\end{equation}
+we make up the zero mode term in $L_0$ is absent for free boson, 
+\begin{equation}
+L_0 = \sum_{n> 0 } a_{-n} a_n + \frac{1}{2} a_0^2 =   2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2 + \sum_{n> 0 } a_{-n} a_n
+\end{equation}
+The ground state now has dimension $h = 2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2$.
+
+{\bf Dirichlet and Neumann}:
+
+Now that we have a legitimate $a_0$ that behaves similar with other oscillator modes, we can then impose the same Dirichlet condition in Eq.~\ref{eq:D-mode-cond}, on the unit circle, the logarithmic term gives
+\begin{equation}
+ -i \frac{1}{\sqrt{ 4\pi g}}  ( a_0 \ln z  + \bar{a}_0 \ln \bar{z} )\Big|_{\text{unit circle }} = 0 \quad \implies \quad a_0 - \bar{a}_0 = 0  \quad \implies \quad m = 0
+\end{equation}
+The boundary states satisfying this boundary condition can be a linear superposition of the zero winding states.
+Since it's Dirichlet, it is an eigenstate of $\hat{\phi}_0$\footnote{We have quantized the theory such that $[\phi_0, \frac{n}{R}] = i $.
+},
+\begin{equation}
+|{\rm D} \rangle  = g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle
+\end{equation}
+With this one can show
+\begin{equation}
+\phi( x, t = 0 ) | {\rm D} \rangle = \phi_0 | {\rm D} \rangle
+\end{equation}
+
+Similarly, the Neumann boundary condition now has the $n = 0$ term in Eq.~\ref{eq:N-mode-cond}
+\begin{equation}
+ a_0 + \bar{a}_0 = 0  \quad \implies \quad n = 0 
+\end{equation}
+the resulting boundary state is a linear superposition over the winding sector
+\begin{equation}
+| {\rm N} \rangle = g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
+\end{equation}
+In fact, Neumann becomes Dirichlet in the dual field, so $\bar{\phi}_0$ is related to the boundary value of the dual field.
+
+One can check that this indeed satisfies the Neumann boundary condition
+\begin{equation}
+\partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
+\end{equation}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [D_and_N.tex]
+
+% configure hyperref to remove ugly boxes from links
+\subsection{Gluing Condition for Winding Modes}
+% flatex input: [glue_zero.tex]
+[Appendix A of Oshikawa\cite{oshikawa_boundary_2010}]
+
+In Sec.~\ref{sec:var-boson}, we use variational approach to find conformal invariant boundary conditions, but the resulting equation \eqref{eq:cpt_boson_bd} do not provide information about the winding sector.
+The variational method fails because winding is a global properties of the Boson configuration, meaning insensitive to the local perturbation.
+
+Here we present a general treatment about the winding modes.
+From the discussion of the Dirichlet and Neumann boundary condition in previous subsection, it seems that the constraints on the oscillator modes can be naturally extended to the zero mode for $n = 0$.
+We can show that this is in compliance with the conformal invariance.
+
+Suppose in the junction we have a boundary condition that result in the following scattering relation
+\begin{equation}
+\begin{bmatrix}
+\partial_{+} \phi^1 \\
+\partial_{-} \phi^2 \\
+\end{bmatrix}
+ = S
+\begin{bmatrix}
+\partial_{-} \phi^1 \\
+\partial_{+} \phi^2 \\
+\end{bmatrix}
+\end{equation}
+the conformal invariance constraint gives two solutions $S_1$ and $S_2$ in Eq.~\eqref{eq:S1-S2}.
+Imagining that we fold $\phi^2$ on top of $\phi^1$, the $x$ derivative on $\phi^2$ then changes sign, we therefore have
+\begin{equation}
+\begin{bmatrix}
+\partial_{+} \phi^1 \\
+\partial_{+} \phi^2 \\
+\end{bmatrix}
+ = S
+\begin{bmatrix}
+\partial_{-} \phi^1 \\
+\partial_{-} \phi^2 \\
+\end{bmatrix}
+\end{equation}
+It it convenient to work in the holomorphic mode expansion \eqref{eq:boson-mode-exp} for the left and right separation. Specifically
+\begin{equation}
+\partial_{+} = \frac{4\pi i }{L} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = \frac{4\pi i }{L} z\partial_{z}
+\end{equation}
+and
+\begin{equation}
+\sum_{n \in \mathbb{Z}}  
+\begin{bmatrix}
+\bar{a}^1_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n}\\ 
+\bar{a}^2_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n} 
+\end{bmatrix}
+ = S
+\sum_{n \in \mathbb{Z}}
+\begin{bmatrix}
+a^1_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
+a^2_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
+\end{bmatrix}
+\end{equation}
+We impose boundary condition at $t = 0$\footnote{In Sec.~\ref{subsec:free-boson}, we interchange $x$ and $t$, and impose boundary condition at $x = 0$.
+For whatever convention, the boundary is on the unit circle $|z| = 1$.
+}, so $z$  is on the unit circle and $\bar{z} = \frac{1}{z}$.
+By comparing the modes(Fourier series on circle), we have
+\begin{equation}
+\label{eq:mode-eq}
+a_n^i - (S^{\scalebox{0.5}[0.8]{\( - \)}1})_{ij} \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^j = 0
+\end{equation}
+This is clearly a generalization of the Dirichlet and Neumann boundary conditions, where the orthogonal matrix $S$ is replaced by $\pm \mathbb{I}$.
+In fact, the rotation does not change the quadratic relation
+\begin{equation}
+\sum_i a^i_n a^i_m =  \sum_i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}m}^i
+\end{equation}
+Hence for the quadratics in the Virasolo generators
+\begin{equation}
+\begin{aligned}
+L_n &= \frac{1}{2} \sum_i  \sum_{m > -1 } (a^i_{n-m} a^i_m  + a^i_{-m} a^i_{n+m } ) - \frac{1}{2} a^i_0 a^i_n 
+\end{aligned}
+\end{equation}
+the cancellation works the same way,
+\begin{equation}
+\begin{aligned}
+L_n - \bar{L}_{-n} &= \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m + a^i_{-m} a^i_{n+m} - \bar{a}^i_{-n-m} \bar{a}^i_{-m} - \bar{a}^i_{m} \bar{a}^i_{-n+m }  )  - \frac{1}{2}( a_0^i a_n^i - \bar{a}_0^i \bar{a}^i _{-n})\\
+& = \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m  - \bar{a}^i_{-n+m}\bar{a}^i_{-m})+ (a^i_{-m} a^i_{n+m} - \bar{a}^i_{m} \bar{a}^i_{-n -m }  )\\
+& = 0 
+\end{aligned}
+\end{equation}
+We now specialize to the two cases $S = S_1$ and $S_2$.
+
+{\bf Boson $\lambda$ Junction: $S = S_1$}
+
+We need to solve the $n = 0$ of \eqref{eq:mode-eq} for $S^{-1} = S_1^{-1} = S_1$\footnote{Recall that the solution of Eq.~\eqref{eq:mode-eq} for the nonzero mode is $\exp(\frac{1}{n} a_{-n}^{i} S^{-1}_{ij} a_{-n}^j |0\rangle)$.
+In Eq.~\eqref{eq:R-bs} we do have $R = S_1$.
+} and
+\begin{equation}
+a^i_0 = \sqrt{4\pi g}  \frac{1}{4\pi} (2\pi m_i R_i + \frac{1}{g} \frac{n_i}{R_i})
+\end{equation}
+For notational simplicity, we introduce the compactification lattice and its dual\cite{oshikawa_boundary_2010}
+\begin{equation}
+\label{eq:lattice}
+\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
+\end{equation}
+the constraint then becomes 
+\begin{equation}
+  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
+\end{equation}
+which is basically the two dimensional case of the multi-component Boson constraints in Eq.~(86) of \cite{oshikawa_boundary_2010}.
+
+Given the $S_1$ matrix in Eq.~\eqref{eq:S1-S2}, we have
+\begin{equation}
+1 + S_1 = 2  
+\begin{bmatrix}
+\cos^2 \theta & \sin \theta \cos\theta \\
+\sin \theta \cos \theta  & \sin^2 \theta \\
+\end{bmatrix}
+\quad 
+1 - S_1 = 2
+\begin{bmatrix}
+\sin^2 \theta & -\sin \theta \cos\theta \\
+-\sin \theta \cos \theta  & \cos^2 \theta \\
+\end{bmatrix}
+\end{equation}
+both have determinant zero. So the solution of the two lattice vectors in 
+\begin{equation}
+( 1 + S_1) \vec{M} = -( 1 - S_1 ) \frac{1}{g} \vec{M}^*
+\end{equation}
+must be the null vectors of the corresponding matrices, i.e. 
+\begin{equation}
+\vec{M} = ( \cos \theta, -\sin \theta )^\top \qquad \vec{M}^{*} = ( \sin \theta, \cos \theta )^\top 
+\end{equation}
+In terms of the winding numbers
+\begin{equation}
+  \tan \theta =  \frac{n_1 R_2}{n_2 R_1 } = -\frac{m_2 R_2}{ m_1 R_1}
+\end{equation}
+One can take a pair of coprime integers $k_1$ and $k_2$($k_1>0$), such that $-\frac{m_1}{m_2} = \frac{k_1}{k_2}$.
+That determines all the possible winding numbers of the basis\footnote{\cite{bachas_fusion_2008} takes $-S_1$ as the S matrix, so they have $\vec{M} = ( \cos \theta, \sin \theta)^\top $ and $\tan \theta = -\frac{n_1 R_2}{n_2 R_1 } = \frac{m_2 R_2}{ m_1 R_1} = \frac{k_2 R_2}{k_1 R_1}$ for $\frac{m_1}{m_2} = \frac{k_1}{k_2}$.
+And this is consistent with their parameterization  $ \left\lbrace
+  \begin{aligned}
+    m_1 = k_1 M  & \quad n_1 = k_2 N  \\
+    m_2 = k_2 M &  \quad n_2 = -k_1 N \\
+  \end{aligned} \right. $ }. The linear superposition is beyond conformal invariance, which should be determined by Cardy's consistency condition.
+
+This set of boundary conditions can be viewed as Dirichlet and Neumann on the rotated basis, hence a reasonable conjecture is also the Fourier sum of the basis(constrained by $S_1$)
+\begin{equation}
+g_{\,\!_{S_1}} \sum_{S_1} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
+\end{equation}
+
+{\bf The T-dual Boundary State $S = S_2$}
+
+Now we take $S = S_2$, the zero mode condition becomes
+\begin{equation}
+( \vec{M} + \frac{1}{g}\vec{M}^* ) =  S_2^{-1}  ( -\vec{M} + \frac{1}{g}\vec{M}^* )
+\end{equation}
+the solution is
+\begin{equation}
+\vec{M} =  \frac{1}{g} \frac{1 - S_2}{1 + S_2} \vec{M}^{*} = \frac{1}{g}  \frac{1}{ 1 - \cos 2\theta}
+\begin{bmatrix}
+  0 & - \sin 2 \theta \\
+\sin 2\theta & 0 \\
+\end{bmatrix} \vec{M}^*
+ = \frac{\cot \theta}{g} \begin{bmatrix}
+  0 & - 1 \\
+1 & 0 \\
+\end{bmatrix}\vec{M}^*
+\end{equation}
+Using the basis vectors in Eq.~\ref{eq:lattice}, we have
+\begin{equation}
+\begin{bmatrix}
+m_1\\
+m_2\\
+\end{bmatrix}
+ = \frac{2 \cot \theta}{ 4\pi g  R_1 R_2 }
+\begin{bmatrix}
+-n_2 \\
+n_1 
+\end{bmatrix}
+\end{equation}
+Taking the same coprime interger $\frac{m_2}{n_1} = \frac{k_2}{k_1}$, we have the angle\footnote{It takes some effort to match the results with \cite{bachas_fusion_2008}.
+We both use $\frac{k_2}{k_1}$ the same way, so the parameterization is the same.
+They use $-S_2$ as oppose to $S_2$ to be the S matrix, so $\vec{M} = \frac{1}{g} \frac{1 + S_2}{1 - S_2} = \frac{\tan \theta}{g}\begin{bmatrix}
+  0 & - 1 \\
+1 & 0 \\
+\end{bmatrix} \vec{M}^*$, their $\tan \theta$ is my $\cot \theta = \frac{k_2}{2k_1 } 4\pi g R_1 R_2$.
+They use $R \rightarrow \frac{1}{2R}$ as T-duality transformation.
+If they were to use $R \rightarrow \frac{1}{2R}$(this point corresponds to $g = \frac{1}{4\pi}$), then their $\tan \theta = \frac{k_2}{2 k_1} R_1 R_2$ which will be the same as our $\cot \theta$.
+So we agree.},
+\begin{equation}
+  \tan \theta = \frac{2 k_1}{k_2} \frac{1}{4 \pi g R_1 R_2}
+\end{equation}
+This state can be obtained by taking T duality for one of the bosons, hence it is a Dirichlet/Neumann boundary conditions for these two Bosons.
+It is then reasonable to use Fourier sum as the physical boundary state
+\begin{equation}
+g_{_{\,\!_{S_2}}}\sum_{S_2} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
+\end{equation}
+
+{\bf The $g$ Factor}:
+
+The $g$ factor can only be determined by Cardy condition, which means that the occurrence $n^h_{ab}$ for each irreducible representation
+\begin{equation}
+Z_{ab} = \langle a | e^{- \beta  H }  | b \rangle  = \sum_{h} n_{ab}^h \chi_h 
+\end{equation}
+is an non-negative integer.
+
+Since the character for the compact boson theory is known, we can just compute the amplitude, say $Z_{\lambda_1, \lambda_2}$ adjust the coefficient such the occurrence is an integer.
+\cite{bachas_fusion_2008} contains a calculation for Dirichlet case.
+I will not repeat it here.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [glue_zero.tex]
+
+% configure hyperref to remove ugly boxes from links
+\subsection{Winding Modes Contribution to Partition Function}
+% flatex input: [Z-winding.tex]
+
+In this section, we address the concern about how the winding mode will affect the partition function.
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_part-lambda1-lambda2}\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
+\label{fig:part-lambda1-lambda2}
+\end{figure}
+
+Let the cylinder to have width $\beta$ and the length of in time direction is $\pi$(after folding), we have
+\begin{equation}
+Z = \langle \lambda_2 | e^{-\pi H} | \lambda_1 \rangle   \qquad H = \frac{4\pi}{ \beta} L_0 
+\end{equation}
+For the winding mode part, we just replace $L_0$ to be $a_0$. When the two boundary states are identical, the result will be a theta-function
+\begin{equation}
+Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
+\end{equation}
+In the $\beta \rightarrow \infty$ limit, it will be proportional to $\beta$ by Poisson's resummation formula\footnote{One can also approximate the sum by integral in this limit: it will be a two dimensional Gaussian integral and the result is proportional to $\beta$}.
+So the winding mode part will at most contribute a $\ln \beta$ term in the free energy, which can be neglected in our leading $\beta$ scaling analysis.
+
+The conclusion still holds for different $\lambda$ boundary states, in which case the only change is the possible values of $n_1$ and $m_1$(the lattice).
+The overlap $\langle \lambda_1 | \lambda_2 \rangle $ will not be zero even if the two sets of coprime integers are different for the two boundary states: they can meet in their least common divisor.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [Z-winding.tex]
+
+% configure hyperref to remove ugly boxes from links
+
+\section{Loschmidt Echo of Connecting Free Bosons}
+\subsection{Corrections to Casimir Energy}
+% flatex input: [free_boson_echo.tex]
+
+To test our boundary state formalism, we consider the Loschmidt echo of connecting two (non-chiral) non-compact Bosons on the two half planes. 
+% flatex input: [fig_H_tau.tex]
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_H-tau}\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction.
+The solid lines are cuts on the plane, where the upper and lower surfaces are boundary states.
+Red arrows are the directions of Hamiltonian flow that propagates one boundary state(lower surface) to another(upper surface).
+The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice).
+Middle: image of the map $\xi = \frac{z}{\tau - z}$.
+Right: image of $w = \ln \xi$.
+It is a cylinder by identifying the blue lines and standard radial quantization can be applied.
+}
+\label{fig:H-tau}
+\end{figure}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [fig_H_tau.tex]
+
+After doing the conformal map shown in \label{fig:fig_H}, we can relate the Loschmidt echo we are interested to the Casimir energy of a cylinder subject to different boundary conditions on the top and bottom
+\begin{equation}
+\mathcal{F} = - \ln |\langle a | e^{- 2\pi H} | b \rangle |^2 = 2 E_c 
+\end{equation}
+The width of the cylinder $\beta$ contains information of the scale $\tau$ as well as the regulator.
+Specifically, we set the radii of both blue the semi-circles on the left panel as $\epsilon$, so that the two end points of the dashed line are $(\frac{\tau - \epsilon}{\epsilon}, 0 )$ and $ (\frac{\epsilon}{ \tau - \epsilon}, 0 )$.
+The resulting width on the right panel is then
+\begin{equation}
+\beta  = \ln  \frac{\tau - \epsilon}{\epsilon} -  \ln \frac{\epsilon}{ \tau - \epsilon}  = 2 \ln \frac{\tau - \epsilon}{ \epsilon} 
+= 2 \ln \frac{\tau}{\epsilon} + \mathcal{O}(\frac{\epsilon}{\tau})
+\end{equation}
+We calculate the Casimir energy by canonical quantization, zeta function regularized path integral and boundary states in App.~\ref{app:casimir_energy_DD_DN}.
+All these methods give the following table
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c| } 
+ \hline
+  & P & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
+  $E_c $ & $ {\color{red} - \dfrac{1}{12}\beta } $ & ${\color{blue}- \dfrac{1}{48} \beta }$ & ${\color{blue} \dfrac{1}{96} \beta }$ &  ${\color{blue}- \dfrac{1}{48} \beta }$ \\[2ex]
+ \hline
+\end{tabular}
+\end{center}
+\caption{Boson Casimir energy subject to different boundary conditions.}
+\label{tab:casimir}
+\end{table}
+
+{\bf Tom's Argument: } It does not make sense to have positive power for the echo. We must have missed some contributions from the Schwartzian etc.
+
+A simple argument is that by doing periodic boundary conditions, the groundstate energy (Casimir energy) on the original $z$ plane must be zero.
+So for all these results we should compensate ${\color{red}\frac{1}{12}\beta}$.
+With this recipe, we have
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{ |c|c|c|c| } 
+ \hline
+   & DD & DN & NN \\ \hline  \rule[4ex]{0pt}{1pt}
+  $E_c $ &  ${\color{purple} \dfrac{1}{16} \beta }$ & ${\color{purple} \dfrac{3}{32} \beta }$ &  ${\color{purple} \dfrac{1}{16} \beta} $ \\[2ex] \hline   \rule[4ex]{0pt}{1pt}
+  $\mathcal{F} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} }$ & ${\color{purple} \dfrac{3}{8}\ln \frac{\tau}{\epsilon}} $ & ${\color{purple} \dfrac{1}{4}\ln \frac{\tau}{\epsilon} } $ \\[2ex]
+ \hline
+\end{tabular}
+\end{center}
+\caption{Logarithm of Loschmidt echo of different boundary conditions.}
+\label{tab:log_echo}
+\end{table}
+
+{\bf Cardy-Peschel Formula:}
+
+One can also apply the Cardy-Peschel formula for the two corners of angle $2\pi$
+\begin{equation}
+F =  \left\{ \frac{\pi}{\theta} h + \frac{c}{24} \Big(  \frac{\theta}{\pi} - \frac{\pi}{\theta}  \Big)   \right\} \ln \tau 
+= \left( \frac{1}{2} h + \frac{c}{16}  \right) \ln \tau 
+\end{equation}
+Since there are two corners, and the echo corresponds to twice the free energy, we have 
+\begin{equation}
+  \mathcal{F} = ( 2h + \frac{c}{4} ) \ln \tau 
+= \left\lbrace
+  \begin{aligned}
+    {\color{purple}\frac{1}{4} \ln \tau}  &\quad   h = 0 \text{ for DD, NN } \\
+    {\color{purple}\frac{3}{8} \ln \tau}  &\quad   h = \frac{1}{16} \text{ for DN, ND}  \\
+  \end{aligned} \right. 
+\end{equation}
+
+{\bf Various Corrections}
+
+We identify the various corrections needed in the $z \rightarrow \xi \rightarrow w$ transformation.
+
+On the $z$ plane of Fig.~\ref{fig:H-tau}, the blue lines are short distance regulators for the two corners.
+As discussed in the corner case of App.~\ref{app:cardy-peschel}, the inner circle regulator only contribute $\frac{c}{6}\ln \frac{\epsilon}{a} $, which is negligible when $\epsilon$ is the of cutoff order.
+However, after mapping to the $\xi$ plane, the outer circle will contribute $-\frac{c}{6} \beta$, which should not be there.
+So
+\begin{equation}
+F_{\xi } = F_{z} + \frac{c}{6} \beta 
+\end{equation}
+
+In App.~\ref{app:H_in_r}, we showed that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian
+\begin{equation}
+H_{z} = H_{\xi} - \frac{c}{24\pi} \beta 
+\end{equation}
+After the evolution for $2\pi$, the difference in the free energy is
+\begin{equation}
+F_w = F_{\xi} - \frac{c}{12} \beta 
+\end{equation}
+Gathering the two together, we obtain the missing $\frac{c}{12} \beta$ between the echo diagram and the Casimir energy, 
+\begin{equation}
+F_{w} = F_z + {\color{red} \frac{c}{12}\beta }
+\end{equation}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [free_boson_echo.tex]
+
+% configure hyperref to remove ugly boxes from links
+\subsection{Folding Trick}
+% flatex input: [echo_folding.tex]
+
+We use the folding trick to compute it again but using gluing condition(dashed line in Fig.~\ref{fig:H-tau_fold}) in place of trivial boundary condition after connecting the two bosons.
+These will corresponds to connecting boundary condition for bosons of different radii.
+% flatex input: [fig_H_tau_fold.tex]
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=	extwidth]{fig_H-tau_fold}\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions.
+Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
+The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice).
+Middle: image of the map $\xi = \frac{z}{\tau - z}$.
+Right: image of $w = \ln \xi$.
+It is a cylinder by identifying the blue lines and standard radial quantization can be applied.
+}
+\label{fig:H-tau_fold}
+\end{figure}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [fig_H_tau_fold.tex]
+
+Set aside the corrections from the various Schwartzian, we check the dilation part the Hamiltonian with App.~\ref{app:casimir_energy_DD_DN}, 
+\begin{equation}
+H =  \frac{2\pi }{\beta} ( L_0 + \bar{L}_0 )
+\end{equation}
+Acting on the boundary state, it is effectively
+\begin{equation}
+H = \frac{4\pi}{\beta} L_0 
+\end{equation}
+We use the matrix notation to represent the 4 sets of bosons in this problem: $\vec{b}_1, \vec{b}_2, \bar{\vec{b}}_1, \bar{\vec{b}}_2$. The Hamiltonian(without shifting) is
+\begin{equation}
+H = ( \vec{b}_1^{\dagger}, \vec{b}_2^{\dagger}) 
+\begin{bmatrix}
+M & 0 \\
+0& M \\                                                
+\end{bmatrix} 
+\begin{pmatrix}
+\vec{b }_1\\
+\vec{b }_2 \\
+\end{pmatrix}
+\end{equation}
+where $M = \frac{4\pi^2}{\beta} \text{diag}(1,2,\cdots )$. The boundary state \eqref{eq:bd_state} in terms of bosonic operators is
+\begin{equation}
+  |B \rangle = \exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R  
+\begin{pmatrix}
+  \bar{\vec{b}}^{\dagger}_1\\
+  \bar{\vec{b}}^{\dagger}_2\\
+\end{pmatrix}\right\}  | 0 \rangle 
+\end{equation}
+The choice of $R$ depend on different boundary conditions
+\begin{equation}
+\label{eq:R-bs}
+R =
+\left\lbrace
+\begin{aligned}
+   \text{diag}( \mathbb{I}, \mathbb{I} )  &  \quad \text{DD} \\
+   \text{diag}( -\mathbb{I}, \mathbb{I} )  &  \quad \text{ND} \\
+   \text{diag}( \mathbb{I}, -\mathbb{I} )  &  \quad \text{DN} \\
+   \text{diag}( -\mathbb{I}, -\mathbb{I} )  &  \quad \text{NN} \\
+\end{aligned} \right.  
+\quad
+\text{gluing condition:}\quad 
+R = 
+\begin{bmatrix}
+\cos 2 \theta \, \mathbb{I} &  \sin 2 \theta \, \mathbb{I} \\
+ \sin 2 \theta \, \mathbb{I}& -\cos 2\theta \, \mathbb{I}\\  
+\end{bmatrix} = S_1 \otimes \mathbb{I} 
+\end{equation}
+the trivial boundary condition in the previous calculation corresponds to $\theta = \frac{\theta}{2}$.
+
+According to App.~\ref{app:pf_of_id}, the amplitude we are interested is
+\begin{equation}
+\begin{aligned}
+Z_{ab} &= \langle B_{\rm gluing} | e^{- H\pi } | B_{\rm open}  \rangle \\
+&= \langle 0 | 
+\exp\left\{ ( \vec{b}_1 \vec{b}_2 ) R^*_a
+\begin{pmatrix}
+  \bar{\vec{b}}_1\\
+  \bar{\vec{b}}_2\\
+\end{pmatrix}\right\} 
+\exp \Big\{ (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) 
+\begin{bmatrix}
+-M & \\
+& -M 
+\end{bmatrix}
+\begin{pmatrix}
+\vec{\bar{b}}_1\\
+\vec{\bar{b}}_2
+\end{pmatrix}\Big\} 
+\exp\left\{ ( \vec{b}^{\dagger}_1 \vec{b}^{\dagger}_2 ) R_b
+\begin{pmatrix}
+  \bar{\vec{b}}^{\dagger}_1\\
+  \bar{\vec{b}}^{\dagger}_2\\
+\end{pmatrix}\right\} 
+| 0 \rangle \\
+& =  \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[e^{-M}, e^{-M} ] R_b \Big)} \\
+\end{aligned}
+\end{equation}
+We parameterize the boundary condition at the open end by $R_b = \text{diag}(b_1 \mathbb{I} , b_2 \mathbb{I})$($1$ for Dirichlet, $-1$ for Neumann). In this notation,
+\begin{equation}
+\begin{aligned}
+Z_{ab} & = \frac{1}{\det\Big(1 - R_a^{\dagger} \text{diag}[(b_1)e^{-M}, (b_2)e^{-M} ]\Big)} \\
+& = \frac{1}{\det\Big(1 - ( S_1 \otimes \mathbb{I})  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
+& = \frac{1}{\det\Big(S^{-1}_1 \otimes \mathbb{I}  -  ( \text{diag}[(b_1), (b_2) ]\otimes e^{-M } ) \Big)} \\
+\end{aligned}
+\end{equation}
+The Casimir energy from this partition function is thus 
+\begin{equation}
+\begin{aligned}
+E_c   &= - \ln |Z_{ab}| = \ln \det 
+\begin{bmatrix}
+\cos 2 \theta \, \mathbb{I}  - (b_1) e^{-M} & - \sin 2 \theta \, \mathbb{I} \\
+-\sin 2 \theta \, \mathbb{I}  & -\cos 2 \theta \, \mathbb{I}  - (b_2) e^{-M} \\
+\end{bmatrix}\\
+&= \sum_i \ln [1  - ( b_1 - b_2 ) \cos 2 \theta e^{-\lambda_i } + ( b_1 b_2) e^{-2 \lambda_i } ]  \\
+&= \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 -( b_1 - b_2 ) \cos 2 \theta e^{-x } - ( b_1 b_2) e^{-2 x} ] 
+\end{aligned}
+\end{equation}
+
+There are two different cases
+\begin{enumerate}
+\item $b_1 = b_2 = \pm 1$, DD, NN. Then
+\begin{equation}
+  E_c = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln (1 - e^{-2 x} ) = \frac{\beta}{8\pi^2}( - \text{Li}_2 (1) ) = {\color{blue}- \frac{1}{48}\beta}
+\end{equation}
+\item $b_1 = -b_2 = \pm 1$, DN, ND. First consider $b_1 = 1$, then
+\begin{equation}
+\label{eq:dn_lambda_bd_state}
+\begin{aligned}
+E_c &=  \frac{\beta}{4\pi^2} \int_0^{\infty} dx \,\ln [1 - 2  \cos 2 \theta e^{-x } + e^{-2 x} ] \\
+&= \frac{\beta}{4\pi^2} \Big[-\text{Li}_2(e^{2i \theta} ) -  \text{Li}_2(e^{-2i \theta} ) \Big]  = \frac{\beta}{4\pi^2} \Big[-2 \pi^2 B_2 ( \frac{\theta}{\pi }) \Big]\\
+&= - \frac{\beta}{2} B_2 ( \frac{\theta}{\pi })
+\end{aligned}
+\end{equation}
+where we have used the identity
+\begin{equation}
+\text{Li}_n( e^{ 2\pi i x }) + (-1)^n \text{Li}_n ( e^{-2\pi i x} ) = - \frac{(2\pi i )^n}{ n!} B_n ( x) , \qquad 0 \le \text{Re}(x)<1, \text{Im}(x) > 0 
+\end{equation}
+For $n = 2$, we need the second Bernoulli polynomial
+\begin{equation}
+B_2( x) = x^2 - x + \frac{1}{6} , \quad B_2( \frac{1}{4} ) = - \frac{1}{48} 
+\end{equation}
+hence
+\begin{equation}
+E_c = {\color{blue} \frac{1}{96}\beta } 
+\end{equation}
+The other case with $b_1 = -1$ corresponds to the $\theta \rightarrow \frac{\pi}{2} - \theta$, and we have the same answer. 
+\end{enumerate}
+
+The folding trick boundary state agrees with all the other calculations. With the Casimir energy correction, it reproduces the logarithmic echo in Tab.~\ref{tab:log_echo}.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [echo_folding.tex]
+
+% configure hyperref to remove ugly boxes from links
+
+\section{Bipartite Fidelity}
+\subsection{Finite Size Scaling}
+% flatex input: [fidel_fs.tex]
+
+Bipartite fidelity is the overlap of the groundstates of two Hamiltonians.
+It is diagrammatically shown in Fig.~\ref{fig:fidel}.
+Regarding it as a partition function, we analyze the finite size dependence on $L$ of the free energy
+\begin{equation}
+\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z   = 2 E_c = \sim \# \ln L 
+\end{equation}
+In some sense it is the echo diagram with $\tau \gg L$ and can provide the same information yet easier to be computed numerically. 
+% flatex input: [fig_fidel.tex]
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_fidel}\caption{Fidelity of connecting two CFTs.
+The horizontal axis the imaginary time.
+Evolution on the two infinitely extended side produces the groundstate of the disconnected/connected Hamiltonian.
+The right diagram is the result of folding the lower part of the diagram up, so that all the edges are conformal invariant boundary states.}
+\label{fig:fidel}
+\end{figure}
+% flatex input end: [fig_fidel.tex]
+
+% flatex input: [fig_fidel_map.tex]
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_fidel-map}\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $.
+The two black dots represent possible insertion of bcc operators.
+The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries.
+The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
+To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
+\label{fig:fidel-map}
+\end{figure}
+
+% flatex input end: [fig_fidel_map.tex]
+
+As usual, we map the diagram to the upper half plane and close it, as shown in Fig.~\ref{fig:fidel-map}.
+If the three boundary conditions are all different, then there are two bcc operators on the real axis.
+We first deal with the easy one where $a = c$.
+The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
+\begin{equation}
+\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
+\end{equation}
+The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $.
+Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
+We can then machinery developed in the echo calculation.
+In this case, the length of the cylinder is
+\begin{equation}
+\beta = \ln e^{\pi \frac{W}{L}} - \ln \pi \frac{\epsilon}{L}  \sim \ln L 
+\end{equation}
+Since the fidelity is twice the Casimir energy, we shall make the replacement recipe $\beta \sim 2 \ln L$.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [fidel_fs.tex]
+
+% configure hyperref to remove ugly boxes from links
+% flatex input: [fidel_num_res.tex]
+
+\subsection{Comparison with Numerical Results}
+
+We check several interesting cases in the numerical fidelity calculation of free boson interface.
+
+From our previous calculation, DD/NN $\rightarrow \lambda$ is trivial.
+The interesting case is the DN $\rightarrow \lambda$ interface.
+Using either the boundary state or ground state energy calculation in App.~\ref{app:gnd_dn_lambda} plus the correction, we have
+\begin{equation}
+\begin{aligned}
+\mathcal{F} &= \frac{\beta}{2}( - x^2 + x - \frac{1}{6} ) + {\color{red} \frac{\beta}{12}} = \frac{\beta}{2}( - x^2 + x ) \\
+&= ( - x^2 + x ) \ln L  \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
+\end{aligned}
+\end{equation}
+% flatex input: [fig_dn_lambda.tex]
+
+\begin{figure}[h]
+% settings for subfigure 1
+\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics[width=	extwidth]{fig_DN-lambda-folding}\caption{DN $\rightarrow \lambda$ diagram before and after folding}
+\label{fig:DN-lambda-folding}
+\end{minipage}
+\hfill
+% settings for subfigure 2
+\begin{minipage}[t]{0.65\linewidth}
+\centering
+\includegraphics[width=\textwidth]{DN_DN2tan.pdf}
+\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
+\end{minipage}
+\end{figure}
+% flatex input end: [fig_dn_lambda.tex]
+
+\begin{figure}[!h]
+% settings for subfigure 1
+\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics[width=	extwidth]{fig_P-squeeze}\caption{P $\rightarrow \lambda$ diagram before and after squeezing}
+\label{fig:P-squeeze}
+\end{minipage}
+\hfill
+% settings for subfigure 2
+\begin{minipage}[t]{0.65\linewidth}
+\centering
+\includegraphics[width=\textwidth]{p_p2tan.pdf}
+\caption{DN $\rightarrow \lambda$ diagram fidelity power law exponent.}
+\end{minipage}
+\end{figure}
+
+Another interesting case is the when the far ends of the initial chains are connected(through periodic or a $\lambda$ interface). The analytic result is
+\begin{equation}
+\begin{aligned}
+  \mathcal{F}( \lambda = 1 \rightarrow \lambda ) &=  \frac{\beta}{2}\Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | - \frac{1}{6} \Big]  + {\color{red} \frac{\beta}{12}} \\
+  &= \Big[  -( x - \frac{1}{4} )^2  + | x - \frac{1}{4} | \Big]  \ln L \quad x = \frac{\theta}{\pi}, \lambda = \tan \theta 
+\end{aligned}
+\end{equation}
+
+{\bf A note for the zero mode:} When zero mode is present, the boson groundstate is not well-defined; numerically instability kicks in.
+Adding a small mass is the common remedy, but doesn't work in the fidelity calculation.
+What we do here is to perturb the boundary condition by a small angle.
+
+In the DN$\rightarrow \lambda$ diagram, zero mode exists when the two sides of the chain $NN$ boundary condition.
+The combination DN is actually a $\lambda = 0$ interface.
+We modify one of them to $\lambda = \tan( 0.001 \pi )$ to avoid the zero mode.
+In the periodic case, we take the one of them to be $\lambda = \tan(0.251\pi)$ although precise periodic boundary condition corresponds to $\lambda = \tan(\frac{\pi}{4})$.
+This is a numerical way of regularization that matches with our no-zero-mode analytic calculation.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [fidel_num_res.tex]
+
+% configure hyperref to remove ugly boxes from links
 
 \appendix
-\section{Corrections to the Free Energy}
-% two corrections:
-% 1. staircase geometry
-% 2. contribution from the boundary: cite Cardy
 
-\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
-% basis transformation, Bogoliubov state, overlap(master theorem)
-% Peschel_EE.pdf
+\section{DN-$\lambda$ Casimir Energy from Groundstate Energy Calculation}
+\label{app:gnd_dn_lambda}
+% flatex input: [gnd_dn_lambda.tex]
 
-\section{A Determinant Identity for the Boundary State Amplitude}
-% copy notes app. C
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_DN-lambda-gnd}\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions.
+The width of the strip is $\pi$ due to folding.
+We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle.
+}
+\label{fig:DN-lambda-gnd}
+\end{figure}
 
-\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
-% copy notes app. B
+{\bf Eigenfunction}:
 
-\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
-% copy notes app. A
+The unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$. The general solutions can be written as
+\begin{equation}
+f(k, x) = 
+\left\lbrace
+\begin{aligned}
+  A_1 e^{i kt} \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
+  A_2 e^{ikt}  \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
+\end{aligned} \right. 
+\end{equation}
+At the junction we have $\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2}$, which cancels the $A$s and gives
+\begin{equation}
+\tan ^2 (\frac{1}{2} kL ) = \lambda^2 
+\end{equation}
+Hence
+\begin{equation}
+ \frac{kL}{2} = \pm \theta + n \pi \implies  k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad \theta \in [0,\frac{\pi}{2} ]  
+\end{equation}
+The normalized eigenfunctions are
+\begin{equation}
+f_n(x) = \sqrt{\frac{2}{L}}
+\left\lbrace
+\begin{aligned}
+  \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
+  \pm \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
+\end{aligned} \right. 
+\qquad 
+k = \frac{2\pi}{L}( n \pm  \frac{\theta}{\pi} )  \quad n \in \mathbb{Z} 
+\end{equation}
 
-\bibliographystyle{plain}
-\bibliography{bCFT}
+{\bf Mode Expansion and Casimir Energy}:
+
+Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
+\begin{equation}
+  S = \frac{g}{2} \int dt \, \sum_{n \in \mathbb{Z} }\left(  \dot{\phi}^2_n + k^2 \phi_n^2 \right) \implies\quad   g \dot{\phi}_n  = \pi_n \quad \implies H =  
+\frac{1}{2g}\sum_{n \in \mathbb{Z} } \pi_n^2 + ( kg )^2  \phi_n^2 
+\end{equation}
+Define the creation and annihilation operators as usual
+\begin{equation}
+\begin{aligned}
+a_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
+a^{\dagger}_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
+\end{aligned}
+\end{equation}
+then
+\begin{equation}
+H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
+\end{equation}
+The Casimir energy is 
+\begin{equation}
+\begin{aligned}
+E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  )  = \frac{\pi}{L} ( \sum_{n \in \mathbb{Z}}  | n + x |  )\quad x = \frac{\theta}{\pi}\\
+&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
+&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
+&= \frac{\pi}{L} ( - x^2 + x - \frac{1}{6})  = \frac{1}{2} ( - x^2 + x - \frac{1}{6})
+\end{aligned}
+\end{equation}
+The free energy is
+\begin{equation}
+F = \frac{\beta}{2} ( - x^2 + x - \frac{1}{6}) = - \frac{\beta}{2} B_2( x) 
+\end{equation}
+The full expression also agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [gnd_dn_lambda.tex]
+
+% configure hyperref to remove ugly boxes from links
+
+\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Calculation}
+\label{app:lambda_12}
+% flatex input: [lambda_1_lambda_2.tex]
+
+This calculation is very similar to the presented in App.~\ref{app:casimir_energy_DD_DN}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=	extwidth]{fig_part-lambda1-lambda2-2}\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
+\label{fig:part-lambda1-lambda2-2}
+\end{figure}
+
+The wanted partition function is
+\begin{equation}
+Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} \mathbb{I}_2 \otimes M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det ( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b) }
+\end{equation}
+where
+\begin{equation}
+M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots )
+\end{equation}
+$R_a$($R_b$) correspond to the $\lambda_1$ and $\lambda_2$ boundary conditions. Using the fact that their determinants are $\det( R_a R_b^{\dagger})  = 1$, we have
+\begin{equation}
+\begin{aligned}
+F &= - \ln Z_{ab} = \ln \det( 1 - R^{\dagger} _a  e^{- \mathbb{I}_2 \otimes M} R_b ) = \ln \det ( R_a R_b^{\dagger} - e^{- \mathbb{I}_2 \otimes M} )\\
+& = \ln \det 
+\begin{bmatrix}
+\cos 2 \Delta \theta \mathbb{I} - e^{-M}   & \sin 2 \Delta \theta \mathbb{I}\\
+- \sin 2\Delta \theta \mathbb{I}  &   \cos 2 \Delta \theta \mathbb{I} - e^{-M} \\ 
+\end{bmatrix} \quad \text{where } \Delta \theta = \theta_2 - \theta_1 \\
+& = \sum_i \ln [ 1 - 2 \cos 2 \Delta \theta e^{- \lambda_i } + e^{- 2 \lambda_i }  ] \\
+& = \frac{\beta}{4\pi^2} \int_0^{\infty} dx \ln [ 1 - 2 \cos 2 \Delta \theta e^{-x} + e^{-2x} ] 
+\end{aligned}
+\end{equation}
+This integral is an even function of $\Delta \theta$ and the $\Delta \theta > 0$ case reduce to the polylog and Bernoulli polynomial
+\begin{equation}
+\begin{aligned}
+  F &= \frac{\beta}{4\pi^2} \left[ - \text{Li}_2 ( e^{2i |\Delta \theta|} ) - \text{Li}_2 ( e^{- 2i |\Delta \theta|} ) \right]  = \frac{\beta}{4\pi^2}  \left[ - 2\pi^2 B_2 (x) \right] \\
+  &= - \frac{\beta}{2} B_2( |x| ) = \frac{\beta}{2} (|x| - x^2 - \frac{1}{6}) \quad x = \frac{\Delta \theta}{ \pi} \\
+\end{aligned}
+\end{equation}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [lambda_1_lambda_2.tex]
+
+% configure hyperref to remove ugly boxes from links
+
+\section{Determinant Identity for Amplitude between Boundary States}
+\label{app:pf_of_id}
+% flatex input: [pf_of_id.tex]
+
+For real symmetric matrix $M$
+\begin{equation}
+\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
+\end{equation}
+
+{\bf Proof:}  
+We first restrict to the case when $R = I$.
+To avoid confusion, we assume the daggered vector are row vectors and write $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\} $ as $\exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{*}  \Big\} $.
+
+{\it Diagonal Basis}: We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
+\begin{equation}
+  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^{*} = O^T \vec{\bar{b}}^{*}
+\end{equation}
+so that the whole expression can be written as
+\begin{equation}
+\begin{aligned}
+  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}  =  
+  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^{*}  \Big\} \\
+& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
+\end{aligned}
+\end{equation}
+{\it Baker-Campbell-Hausdorff formula}: For $ [X, Y] = sY $, we have a solvable case of Baker-Campbell-Hausdorff formula
+\begin{equation}
+  e^X e^{Y} = e^{\exp (s ) Y} e^{X}
+\end{equation}
+Taking $X = -\lambda_i d_i^{\dagger} d_i$, $Y = d_i^{\dagger}, \bar{d}^{\dagger}$, we have
+\begin{equation}
+[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
+\end{equation}
+and so $s = - \lambda_i$ for each $\lambda_i$. This enable us to commute those exponentials
+\begin{equation}
+\begin{aligned}
+ \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^{*}  \Big\}   &= \prod_i \exp \Big\{ \alpha e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
+ & = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^{*}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
+\end{aligned}
+\end{equation}
+
+{\it The General Case}: When $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$.
+The role of $\bar{b}$ is decorative; it is effectively a $c$-number and we only use its independence w.r.t.
+$\vec{b}$.
+Hence the rest of the proof follows the same way.
+
+{\bf Corollary :} 
+\begin{equation}
+Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
+\end{equation}
+{\bf Proof:}
+
+Using the identity we have just proved, 
+\begin{equation}
+Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle 
+\end{equation}
+A direct application of the MacMahon master theorem
+\begin{equation}
+  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
+ = \frac{1}{\det(1 - X^T Y )}
+\end{equation}
+proves the result.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_notes"
+%%% TeX-PDF-mode: t
+%%% End:
+% flatex input end: [pf_of_id.tex]
+
+\bibliographystyle{unsrt}
+\bibliography{bCFT_notes}
 
 \end{document}
-
 %%% Local Variables: 
@@
 %%% End:
+% flatex input end: [bCFT_notes.tex]

### 2017-04-30 comp_fid_echo.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)

@@
 where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$.
-It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C}){\bf\color{red}Cite sth}.
+It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}.
 Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
@@
 
-{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. }
+{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. We will see similar construction of BCS in fidelity and echo.}
 
@@
 From the discussion in App.{\bf\color{red}where}, we are able to diagonalize it in ${\bf a}$ basis.
-At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis.
+At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis.
 The corresponding Bogoliubov transformations read
@@
 
-\subsection{Description on how to get S}
+\subsection{Explicit construction of symplectic Bogoliubov transformation}
 
@@
 \end{aligned}\end{eqnarray}
-It is not hard to realize $\mathcal{M}$ is real and symmetric. We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have
+It is not hard to realize $\mathcal{M}$ is real and symmetric.
+We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have the decomposition
 \begin{eqnarray}\begin{aligned}
@@
 
-Notice in the above construction, we have assumed the Hamiltonian in the real basis to be positive definite.
-{\bf\color{red}This is not as restrictive as it may appear}, and in App.{\bf\color{red}where} we shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain.
+Notice in the above construction, we have assumed the Hamiltonian $\mathcal{M}$ in the real basis to be positive definite.
+It is not hard find such a system, for example a harmonic chain, that meets the assumption.
+We shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain in App.{\bf\color{red}where}.
 \subsection{Harmonic chain}
@@
 \end{aligned}\end{eqnarray}
-where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$. We construct the following real symplectic matrix
+where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$.
+The explicit form of $\mathcal{V}$ depends on the boundary condition which is not important in the following construction.
+We define the following real symplectic matrix
 \begin{eqnarray}\begin{aligned}

### 2017-04-30 gnd_dn_lambda.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)

@@
 }
+\label{Fig in gnd_dn_lambda}
 \end{figure}
 
-{\bf Eigenfunction}:
-
-The unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$. The general solutions can be written as
+In this appendix, we would like to calculate the amplitude for the setup shown in Fig.\ref{Fig in gnd_dn_lambda}.
+In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$.
+The general solutions can be written as
 \begin{equation}
+\label{Normalized f in gnd_dn_lambda}
 f(k, x) = 
@@
 \end{equation}
-At the junction we have $\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2}$, which cancels the $A$s and gives
+As demonstrated in the {\bf\color{red}main text}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
+\begin{eqnarray}\begin{aligned}
+\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2} \quad \theta \in [0,\frac{\pi}{2} ]  
+\end{aligned}\end{eqnarray}
+which implies
 \begin{equation}
-\tan ^2 (\frac{1}{2} kL ) = \lambda^2 
+\label{Momentum in gnd_dn_lambda}
+k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad n\in{\bf Z}
 \end{equation}
-Hence
-\begin{equation}
- \frac{kL}{2} = \pm \theta + n \pi \implies  k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad \theta \in [0,\frac{\pi}{2} ]  
-\end{equation}
-The normalized eigenfunctions are
+It is evident that the momentum $k$ is shifted from integer multiple of $2\pi/L$ due to the $\lambda$ boundary condition in the middle. 
+\begin{comment}
+Thus, the normalized eigenfunctions are
 \begin{equation}
@@
 \end{equation}
-
-{\bf Mode Expansion and Casimir Energy}:
-
 Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
@@
 \end{equation}
-Define the creation and annihilation operators as usual
+\end{comment}
+
+It is clear that the normalized eigenfunctions in Eq.(\ref{Normalized f in gnd_dn_lambda}) serves as orthonormal basis in mode expansion.
+Follow the same procedure in {\bf\color{red}citeDiFrancesco}, we have the Hamiltonian as
+\begin{equation}
+\label{H in gnd_dn_lambda}
+H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
+\end{equation}
+where the momentum $k$ is defined in Eq.(\ref{Momentum in gnd_dn_lambda}), and the creation and annihilation operators defined as usual
 \begin{equation}
@@
 \end{equation}
-then
-\begin{equation}
-H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
-\end{equation}
-The Casimir energy is 
+
+The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.(\ref{H in gnd_dn_lambda}) and define $x\equiv\theta/\pi$ in Eq.(\ref{Momentum in gnd_dn_lambda}), we have
 \begin{equation}
 \begin{aligned}
-E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  )  = \frac{\pi}{L} ( \sum_{n \in \mathbb{Z}}  | n + x |  )\quad x = \frac{\theta}{\pi}\\
+E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  ) \\  
 &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
 &= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
-&= \frac{\pi}{L} ( - x^2 + x - \frac{1}{6})  = \frac{1}{2} ( - x^2 + x - \frac{1}{6})
+&= \frac{1}{2} ( - x^2 + x - \frac{1}{6})
 \end{aligned}
 \end{equation}
-The free energy is
+where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy reads
 \begin{equation}
-F = \frac{\beta}{2} ( - x^2 + x - \frac{1}{6}) = - \frac{\beta}{2} B_2( x) 
+F = \beta E_c = - \frac{\beta}{2} B_2( x) 
 \end{equation}
-The full expression also agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}
+{\bf\color{red}which agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}}

### 2017-04-30 comp_fid_echo.tex
add two bib App B C D done except some references ~\eqref, ~\ref done

@@
 In this appendix, we provide the technical details on numerical calculation of bipartite fidelity and Loschmidt echo.
-We shall {\bf\color{red}1.
-lay out the plan for this long appendix.
-2.
-Point out out method is different from Moore.
-3.
-This is more general as Moore's does not apply to boson (say why?) but ours can be easily generalized to fermion 4.
-Say sth on Williamson.
-For fermion, Schur's decomposition replaces Williamson (probably in the end?).
-5.
-Compare to the fermionic case in the echo section.
-}
+We first demonstrate the symplectic character of the bosonic Bogoliubov transformation, for which the ground state will take a form similar to the superconducting ground state.
+It is explicitly shown that fidelity and Loschmidt echo take simple form in such construction.
+We note that this is different from the method in \onlinecite{vasseur_universal_2014,stephan_local_2011}.
+With slight modification, the similar technique can be applied to the fermionic case.
 
 \subsection{Boson Bogoliubov transformation}
-\label{Boson BdG}
+\label{app: Boson BdG}
 We consider the following quadratic bosonic Hamiltonian
@@
 where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$.
-It is clear from Eq.(\ref{Preserve commutator}) that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}.
+It is clear from Eq.~\eqref{Preserve commutator} that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}.
 Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
@@
 
-For the ground state of the quadratic Hamiltonian in Eq.(\ref{Boson BdG}), it is the vacuum of the annihilation operators defined in Eq.(\ref{Def. of a}) and satisfies
+For the ground state of the quadratic Hamiltonian in Eq.~\eqref{Quadratic boson H}, it is the vacuum of the annihilation operators defined in Eq.~\eqref{Def. of a} and satisfies
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-such that Eq.(\ref{a Vacuum condition}) reduces to
+such that Eq.~\eqref{a Vacuum condition} reduces to
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-One can use Eq.(\ref{Constraint 2}) to show that $T$ is symmetric, and observe that
+One can use Eq.~\eqref{Constraint 2} to show that $T$ is symmetric, and observe that
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-where we have used Eq.(\ref{Constraint 1}) in the second line. From the following McMahon master theorem
+where we have used Eq.~\eqref{Constraint 1} in the second line. From the following McMahon master theorem
 \begin{eqnarray}\begin{aligned}\label{Bosonic McMahon}
@@
 \end{aligned}\end{eqnarray}
-one can easily check that the ground state in Eq.(\ref{Boson BCS gnd}) is correctly normalized.
+one can easily check that the ground state in Eq.~\eqref{Boson BCS gnd} is correctly normalized.
 
-{\bf\color{red} 1. Comment of BCS; 2. Say sth of deferment of the discussion of how to find S explicitly; 3. We will see similar construction of BCS in fidelity and echo.}
+Eq.~\eqref{Boson BCS gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
+We shall defer the explicit construction of Bogoliubov transformation until App.~\ref{app: Explicit construction of symplectic Bogoliubov transformation}.
+Before that, we shall see that similar constructions of superconducting ground state greatly simplify the expressions for fidelity and Loschmidt echo.
 
 \subsection{Boson fidelity} 
-\label{Boson fidelity}
+\label{app: Boson fidelity}
 
-Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians{\bf\color{red}cite sth}.
-We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.(\ref{Quadratic boson H}).
-From the discussion in App.{\bf\color{red}where}, we are able to diagonalize it in ${\bf a}$ basis.
+Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians.
+We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.\eqref{Quadratic boson H}.
+From the discussion in App.~\ref{app: Boson BdG}, we are able to diagonalize it in ${\bf a}$ basis.
 At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis.
@@
 \end{aligned}\end{eqnarray}
-One immediately realizes Eq.(\ref{S0invS}) takes the same form as Eq.(\ref{Def. of a}) such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
+One immediately realizes Eq.~\eqref{S0invS} takes the same form as Eq.~\eqref{Def. of a} such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
 \begin{eqnarray}
@@
 \end{eqnarray}
-Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.(\ref{Boson BCS gnd}), and their overlap, which is the fidelity, reads
+Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{Boson BCS gnd}, and their overlap, which is the fidelity, reads
 \begin{eqnarray}\begin{aligned}
@@
 \subsection{Boson Loschmidt echo}
+\label{app: Boson Loschmidt echo}
 
@@
 \end{aligned}\end{eqnarray}
-It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.(\ref{Boson BCS gnd}).
-In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.(\ref{BdG transformation for echo}), and it {\bf\color{red}reads}
+It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.~\eqref{Boson BCS gnd}.
+In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.~\eqref{BdG transformation for echo}, and it {\bf\color{red}reads}
 \begin{eqnarray}\begin{aligned}
-\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=\frac{1}{|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|}
+\label{eq in app: Echo}
+\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
 \end{aligned}\end{eqnarray}
@@
 \subsection{Explicit construction of symplectic Bogoliubov transformation}
-
-As demonstrated in App.{\bf\color{red}where}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.(\ref{Two BdG}).
+\label{app: Explicit construction of symplectic Bogoliubov transformation}
+As demonstrated in App.~\ref{app: Boson fidelity} and \ref{app: Boson Loschmidt echo}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.~\eqref{Two BdG}.
 Here, for a quadratic bosonic Hamiltonian
@@
 \end{aligned}\end{eqnarray}
-we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,{\bf C}) that diagonalizes M. The basic idea is {\bf\color{red}what}.
+we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,{\bf C}) that diagonalizes $M$.
 
@@
 It is not hard to realize $\mathcal{M}$ is real and symmetric.
-We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem{\bf\color{red}cite sth} we have the decomposition
+We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem\cite{arnold_mathematical_2010} we have the decomposition
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. Thus we have
+where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.(\ref{Diagonalization of M}) is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form as in Eq.(\ref{Block of S}), is an element of complex symplectic group.
+Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.~\eqref{Diagonalization of M} is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{Block of S}, is an element of complex symplectic group.
 Thus we identify
@@
 \end{aligned}\end{eqnarray*}
-as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.(\ref{Quadratic boson H2}).
+as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.~\eqref{Quadratic boson H2}.
 
-Notice in the above construction, we have assumed the Hamiltonian $\mathcal{M}$ in the real basis to be positive definite.
-It is not hard find such a system, for example a harmonic chain, that meets the assumption.
-We shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain in App.{\bf\color{red}where}.
+We note that Majorana basis will play the role of real basis for the fermionic case.
+The Hamiltonian can be further decomposed via real Schur decomposition.
+Similar expression for Loschmidt echo holds with exponent replaced by $+1$ in Eq.~\eqref{eq in app: Echo}, and the results in \onlinecite{vasseur_universal_2014} can be reproduced.
+
 \subsection{Harmonic chain}
+\label{app: Harmonic chain}
 
-{\bf\color{red}Say sth on harmonic chain}
-
-In the real basis defined in Eq.(\ref{Real basis}), the Hamiltonian for 1D harmonic chain reads
+We notice in the above construction, the Hamiltonian $\mathcal{M}$ in the real basis is assumed to be positive definite.
+It is not hard find such a system that meets the assumption.
+Here we shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain.
+In the basis defined in Eq.~\eqref{Real basis}, the Hamiltonian for 1D harmonic chain reads
 \begin{eqnarray}\begin{aligned}

### 2017-04-30 gnd_dn_lambda.tex
add two bib App B C D done except some references ~\eqref, ~\ref done

@@
 
-In this appendix, we would like to calculate the amplitude for the setup shown in Fig.\ref{Fig in gnd_dn_lambda}.
+In this appendix, we would like to calculate the amplitude for the setup shown in Fig.~\ref{Fig in gnd_dn_lambda}.
 In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$.
@@
 
-It is clear that the normalized eigenfunctions in Eq.(\ref{Normalized f in gnd_dn_lambda}) serves as orthonormal basis in mode expansion.
-Follow the same procedure in {\bf\color{red}citeDiFrancesco}, we have the Hamiltonian as
+It is clear that the normalized eigenfunctions in Eq.~\eqref{Normalized f in gnd_dn_lambda} serves as orthonormal basis in mode expansion.
+Following the same procedure in \onlinecite{di_francesco_conformal_1997}, we have the Hamiltonian as
 \begin{equation}
@@
 \end{equation}
-where the momentum $k$ is defined in Eq.(\ref{Momentum in gnd_dn_lambda}), and the creation and annihilation operators defined as usual
+where the momentum $k$ is defined in Eq.~\eqref{Momentum in gnd_dn_lambda}, and the creation and annihilation operators defined as usual
 \begin{equation}
@@
 
-The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.(\ref{H in gnd_dn_lambda}) and define $x\equiv\theta/\pi$ in Eq.(\ref{Momentum in gnd_dn_lambda}), we have
+The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.~\eqref{H in gnd_dn_lambda} and define $x\equiv\theta/\pi$ in Eq.~\eqref{Momentum in gnd_dn_lambda}, we have
 \begin{equation}
@@
 \end{equation}
-{\bf\color{red}which agrees with the boundary state calculation in Eq.~\ref{eq:dn_lambda_bd_state}}
+which agrees with the boundary state calculation in Eq.{\bf\color{red}where}

### 2017-04-30 pf_of_id.tex
[draft]intro content done.
[draft]bib file error cleared
add two bib App B C D done except some references ~\eqref, ~\ref done

@@
 where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators.
-{\bf\color{red}As emphasized in the main text}, the matrix notation, for example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
+As emphasized in the {\bf\color{red}main text}, the matrix notation, for example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
 
-To prove Eq.(\ref{1st id in app.pf_of_id}), we first consider the special case where $R={\bf I}$. We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
+To prove Eq.~\eqref{1st id in app.pf_of_id}, we first consider the special case where $R={\bf I}$.
+We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
 \begin{equation}
@@
 For the general case where $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$.
-This will not change the commutation relation of ${\bf d}$, and the role of $\bar{b}$ is decorative in Eq.(\ref{lambda commutator}).
+This will not change the commutation relation of ${\bf d}$, and the role of $\bar{b}$ is decorative in Eq.~\eqref{lambda commutator}.
 Hence the rest of the proof follows the same way.
@@
 
-A direct consequence of Eq.(\ref{1st id in app.pf_of_id}) is the following
+A direct consequence of Eq.~\eqref{1st id in app.pf_of_id} is the following
 \begin{equation}
@@
 \end{equation}
-proves Eq.(\ref{2nd id in app.pf_of_id}). \hfill$\blacksquare$
+proves Eq.~\eqref{2nd id in app.pf_of_id}. \hfill$\blacksquare$
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-01 boson_bogoliubov.tex
[draft] add boson bogoliubov transformation original tex file

We write the quadratic bosonic Hamiltonian in the following form
\begin{equation}
H = \frac{1}{2} (b^{\dagger}, -b)
M 
\begin{pmatrix}
b\\
b^{\dagger} 
\end{pmatrix} \qquad 
M = 
\begin{bmatrix}
A & -B^* \\
B & -A^* \\
\end{bmatrix}
\end{equation}
where $A$ is Hermitian and $B$ is symmetric. The use of $(b^{\dagger}, -b)$ instead of $(b^{\dagger}, b)$ is intentional to facilitate intensive symplectic calculation. The Bogoliubov transformation that diagonalizes the Hamiltonian
\begin{equation}
(b, b^{\dagger}) S = ( a, a^{\dagger} ) 
\end{equation}
should preserve the commutation relation
\begin{equation}
J \equiv \begin{bmatrix}
0 & \mathbb{I}\\
-\mathbb{I} & 0 
\end{bmatrix} =  
[
\begin{pmatrix}
a \\
a^{\dagger} 
\end{pmatrix}, 
\begin{pmatrix}
a \, a^{\dagger}
\end{pmatrix}]
=
S^{\top}
[
\begin{pmatrix}
b \\
b^{\dagger} 
\end{pmatrix}, 
\begin{pmatrix}
b \, b^{\dagger}
\end{pmatrix}]S
 = S^{\top} J S 
\end{equation}
and it is therefore in ${\rm Sp}( 2n, \mathbb{C} ) $. On the other hand, the requirement that $a^{\dagger}$ still be the complex conjugation of $a$ leads to the block structure of $S$
\begin{equation}
S = 
\begin{bmatrix}
u & v^*\\
v & u^*\\    
\end{bmatrix}
\end{equation}
In turns of the new bosonic variable $a$,
\begin{equation}
\begin{aligned}
H &= \frac{1}{2} ( b,  b^{\dagger} ) J^{-1} M 
\begin{pmatrix}
b\\
b^{\dagger} 
\end{pmatrix}
 = \frac{1}{2} ( a,  a^{\dagger} ) S^{-1} J^{-1} M (S^{\top})^{-1} 
\begin{pmatrix}
a\\
a^{\dagger} 
\end{pmatrix}\\
& = \frac{1}{2} ( a^{\dagger}, -a )  (S^{\top} M (S^{\top})^{-1} )
\begin{pmatrix}
a\\
a^{\dagger} 
\end{pmatrix}
\end{aligned}
\end{equation}
Out goal is to find such a $S \in {\rm Sp}( 2n, \mathbb{C} )$ that diagonalize $M$\footnote{This particular diagonal form is dictated by the symmetric $P M^* P^{-1} = -M, P S P^{-1} = S $. This is also evident when one realizes the diagonal matrix $\in \mathfrak{sp}(2n, \mathbb{C} )$}
\begin{equation}
M = (S^{\top})^{-1} 
  \begin{bmatrix}
    d & 0\\
    0 & -d \\
  \end{bmatrix} S^{\top}  
\end{equation}
By matching to the standard form symplectic Lie algebra $\begin{bmatrix} a & b \\ c & -a^{\top} \end{bmatrix}$ where $b$ and $c$ are symmetric, we immediately see that $M \in \mathfrak{sp}( 2n, \mathbb{C} ) $. The adjoint action of $S^{\top}$ conjugates $M$ to the maximal torus.

In the real basis
\begin{equation}
\begin{bmatrix}
b \\
b^{\dagger} \\
\end{bmatrix}
=
C
\begin{bmatrix}
\phi \\
\pi \\
\end{bmatrix}
\end{equation}
the Hamiltonian becomes
\begin{equation}
H = \frac{1}{2} ( b, b^{\dagger}) J^{-1} M 
\begin{bmatrix}
b \\
b^{\dagger} 
\end{bmatrix}
= \frac{1}{2} ( \phi, \pi )
\mathcal{M} 
\begin{pmatrix}
\phi \\
\pi 
\end{pmatrix}
\end{equation}
where
\begin{equation}
\mathcal{M} = C^{\top} J^{-1} M C = C^{\dagger} 
\begin{bmatrix}
A & - B^* \\
-B & A^* \\                                             
\end{bmatrix}C =
\begin{bmatrix}
{\rm Re}(A - B ) & -{\rm Im}( A ) + {\rm Im}( B  )\\
{\rm Im}(A) + {\rm Im} B & {\rm Re}(A+ B ) 
\end{bmatrix} 
\end{equation}
is a real symmetric matrix based on the symmetry of $A$ and $B$. If we can diagonalize the matrix $\mathcal{M}$ by a real symplectic matrix $\mathcal{S} \in \mathfrak{sp}( 2n, \mathbb{R} ) $
\begin{equation}
\mathcal{M} = \mathcal{S}
\begin{bmatrix}
d & 0 \\
0 & d \\
\end{bmatrix} \mathcal{S}^{\top}
\end{equation}
then in the $a$ basis
\begin{equation}
\begin{bmatrix}
a \\
a^{\dagger}\\
\end{bmatrix}
= C \mathcal{S}^{\top}
\begin{bmatrix}
\phi \\
\pi 
\end{bmatrix}
\end{equation}
the Hamiltonian is diagonal,
\begin{equation}
\begin{aligned}
( \phi , \pi ) \mathcal{S}
\begin{bmatrix}
d & 0 \\
0 & d \\ 
\end{bmatrix} \mathcal{S}^{\top} 
\begin{pmatrix}
\phi \\
\pi 
\end{pmatrix}
 &= ( a, a^{\dagger} ) C^*
\begin{bmatrix}
d & 0 \\
0 & d \\ 
\end{bmatrix}
C^{\dagger}
\begin{pmatrix}
a \\
a^{\dagger} 
\end{pmatrix} 
=( a^{\dagger}, a )J 
\begin{bmatrix}
0 & d \\
d & 0 \\ 
\end{bmatrix}
\begin{pmatrix}
a \\
a^{\dagger} 
\end{pmatrix}\\
&=( a^{\dagger}, -a )
\begin{bmatrix}
d & 0 \\
0 & -d \\ 
\end{bmatrix}
\begin{pmatrix}
a \\
a^{\dagger} 
\end{pmatrix}
\end{aligned}
\end{equation}
Tracing back to the complex basis, we have
\begin{equation}
\begin{bmatrix}
d & 0 \\
0 & -d \\ 
\end{bmatrix}
 = J C^* \mathcal{S}^{-1} C^{\top} J^{-1} M C (\mathcal{S}^{\top})^{-1} C^{\dagger} 
\end{equation}
or equivalently
\begin{equation}
\label{eq:M-diag}
M = J C^* \mathcal{S} C^{\top} J^{-1}
\begin{bmatrix}
d & 0 \\
0 & -d \\
\end{bmatrix} C \mathcal{S}^{\top} C^{\dagger}
\end{equation}
One then identifies
\begin{equation}
C \mathcal{S}^{\top} C^{\dagger} = S^{\top} 
\end{equation}
Let's check this is the wanted $S^{\top}$: 
\begin{enumerate}
\item $S^{\top}$ so constructed has the correct block structure $[u, v^*; v, u^*]$. The computation to verify this is similar to the fermionic case where $U = C \mathcal{O} C^{\dagger} $ has the correct block structure for a real orthogonal matrix $\mathcal{O}$. 
\item $C \mathcal{S}^{\top} C^{\dagger}  \in {\rm Sp}(2n, \mathbb{C} )$. It is easily verified that $C^{\dagger} J C^* = iJ$ and $C J C^{\top} = - i J$, so
\begin{equation}
C\mathcal{S}^{\top} C^{\dagger} J (C\mathcal{S}^{\top} C^{\dagger})^{\top} = i C\mathcal{S}^{\top} J (C\mathcal{S}^{\top})^{\top} = i C J C^{\top} = J 
\end{equation}
\item Eq.~\eqref{eq:M-diag} is a similarity transformation. 
\begin{equation}
J C^* \mathcal{S} C^{\top} J^{-1} = J C^* J (\mathcal{S}^{\top})^{-1} J C^{\top} J = C(\mathcal{S}^{\top})^{-1}  C^{\dagger} 
\end{equation}
\end{enumerate}

Now we come back to the case when the symplectic diagonalization is possible. It is the Williamson theorem\footnote{\cite{simon_congruences_1999,pirandola_correlation_2009} and the Stackexchange post \cite{_linear_stexg} contains the same simple constructive proof. \cite{xiao_theory_2009} was inspired from solving the dynamics(which is a canonical transformation). Chapter 3 of \cite{gosson_symplectic_2006} contains a basis independent proof. Also see a complete classification of Williamson theorem in Appendix 6 of Arnold\cite{arnold_mathematical_1997}}: for a real symmetric and positive definite matrix $\mathcal{M}$, there exist $\mathcal{S} \in \mathfrak{sp}( 2n, \mathbb{R} )$, such that
\begin{equation}
\label{eq:M-diag2}
\mathcal{M}  = \mathcal{S}
\begin{bmatrix}
d & 0 \\
0 & d \\
\end{bmatrix} \mathcal{S}^{\top}
\end{equation}
where the diagonal matrix is positive and contains positive eigenvalues of $i J\mathcal{M}$. I here present a constructive proof[Appendix A of \cite{pirandola_correlation_2009}]. The general solution of Eq.~\eqref{eq:M-diag2} is 
\begin{equation}
 \mathcal{S} = \mathcal{M}^{\frac{1}{2}} O 
\begin{bmatrix}
d^{-\frac{1}{2}} & 0 \\
0 & d^{-\frac{1}{2}}\\
\end{bmatrix}
\end{equation}
where $O$ is an orthogonal matrix to be fixed. Since $\mathcal{S}$ is symplectic, we have
\begin{equation}
O^{\top} \mathcal{M}^{\frac{1}{2}} J \mathcal{M}^{\frac{1}{2}} O  = 
\begin{bmatrix}
d^{\frac{1}{2}} & 0 \\
0 & d^{\frac{1}{2}} \\
\end{bmatrix}
J
\begin{bmatrix}
d^{\frac{1}{2}} & 0 \\
0 & d^{\frac{1}{2}} \\
\end{bmatrix}
=
\begin{bmatrix}
0 & d\\
-d & 0 \\
\end{bmatrix}
\end{equation}
Hence matrix $O$ actually diagonalize the anti-symmetric $ \mathcal{M}^{\frac{1}{2}} J \mathcal{M}^{\frac{1}{2}}$. The eigenvalues of $ \mathcal{M}^{\frac{1}{2}} J \mathcal{M}^{\frac{1}{2}}$ are $\pm i d$, which are also the eigenvalues of $  J \mathcal{M}$. And since $\mathcal{S}$ uses $d^{-\frac{1}{2}}$, $d$ should be the positive eigenvalues of  $iJ \mathcal{M}$.

%%% Local Variables:
%%% TeX-master: "Peschel_EE"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-01 comp_fid_echo.tex
[draft] add boson bogoliubov transformation original tex file

@@
-% flatex input: [comp_fid_echo.tex]
-
-In this appendix, we provide the technical details on numerical calculation of bipartite fidelity and Loschmidt echo.
-We first demonstrate the symplectic character of the bosonic Bogoliubov transformation, for which the ground state will take a form similar to the superconducting ground state.
-It is explicitly shown that fidelity and Loschmidt echo take simple form in such construction.
-We note that this is different from the method in \onlinecite{vasseur_universal_2014,stephan_local_2011}.
-With slight modification, the similar technique can be applied to the fermionic case.
+In this appendix, we provide technical details about the numerical calculation of the bipartite fidelity and Loschmidt echo.
+It is different from the method for fermionic cases used in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011} but can by applied to with slight modification.
+What we do takes advantage of the symplectic structure of the bosonic Bogoliubov transformation, which gives the explicit form of ground state that similar to that of the superconductor.
 
@@
 \hat{H}&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
-&=\frac{1}{2}
+&=
+\frac{1}{2} (b^{\dagger}, -b)
+M 
+\begin{pmatrix}
+b\\
+b^{\dagger} 
+\end{pmatrix} \qquad 
+M = 
+\begin{bmatrix}
+A & -B^* \\
+B & -A^* \\
+\end{bmatrix}
+\frac{1}{2}
 \left(\begin{array}{ccc}
@@
 \end{aligned}\end{eqnarray}
-where ${\bf b}\equiv(b_{1},...,b_{N})$ is a vector of annihilation operators.
-Notice $H$ is a $N\times N$ single-particle Hamiltonian, and $\Delta$ is a symmetric paring matrix.
+where ${\bf b}\equiv(b_{1},...,b_{N})$ is a vector of bosonic annihilation operators.
+Notice $H$ is a $N\times N$ single-particle Hamiltonian, and $\Delta$ is a symmetric pairing matrix.
 The use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ is due to the Sp(2N,{\bf C}) character of the bosonic Bogoliubov transformation, as we now demonstrate.
@@
 \end{aligned}\end{eqnarray}
-where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $\left[b_i,b_j^\dagger\right]=\delta_{ij}$.
+where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $[b_i,b_j^\dagger]=\delta_{ij}$.
 It is clear from Eq.~\eqref{Preserve commutator} that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}.
@@
 \end{aligned}\end{eqnarray}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-01 comp_fid_echo.tex
1. Hamiltonian changed to A B notation 2. bmatrix, pmatrix used 3. \tilde{S} changed to \mathcal{S} 4. labeling changed

@@
 \subsection{Boson Bogoliubov transformation}
-\label{app: Boson BdG}
+\label{app_sub:boson_BdG}
 We consider the following quadratic bosonic Hamiltonian
 \begin{eqnarray}\begin{aligned}
-\label{Quadratic boson H}
-\hat{H}&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
+\label{eq:quadratic_boson_H}
+\hat{H}%&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
 &=
@@
 b^{\dagger} 
-\end{pmatrix} \qquad 
+\end{pmatrix}-\frac{1}{2}\text{tr}H, \qquad 
 M = 
@@
 \end{bmatrix}
-\frac{1}{2}
-\left(\begin{array}{ccc}
-{\bf b}^\dagger & -{\bf b}
-\end{array}\right)
-\left(\begin{array}{ccc}
-H & \Delta\\
--\Delta^\dagger & -H^T
-\end{array}\right)
-\left(\begin{array}{ccc}
-{\bf b} \\
-{\bf b}^\dagger
-\end{array}\right)-\frac{1}{2}\text{tr}H,
 \end{aligned}\end{eqnarray}
 where ${\bf b}\equiv(b_{1},...,b_{N})$ is a vector of bosonic annihilation operators.
-Notice $H$ is a $N\times N$ single-particle Hamiltonian, and $\Delta$ is a symmetric pairing matrix.
-The use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ is due to the Sp(2N,{\bf C}) character of the bosonic Bogoliubov transformation, as we now demonstrate.
+Notice $A$ is a $N\times N$ single-particle Hamiltonian, and $B$ is a symmetric pairing matrix.
+The use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ is due to the Sp(2N,$\mathbb{C}$) character of the bosonic Bogoliubov transformation, as we now demonstrate.
 
@@
 \begin{eqnarray}\begin{aligned}
-\label{Def. of a}
+\label{eq:def_a}
 ({\bf a} , {\bf a}^\dagger)\equiv({\bf b} , {\bf b}^\dagger)S
@@
 \begin{eqnarray}\begin{aligned}
-\label{Preserve commutator}
-J\equiv\left(\begin{array}{ccc}
-0 & {\bf I}\\
--{\bf I} & 0
-\end{array}\right)
-=\left[
-\left(\begin{array}{ccc}
+\label{eq:preserve_commutator}
+J\equiv\begin{bmatrix}
+0 & \mathbb{I}\\
+-\mathbb{I} & 0
+\end{bmatrix}
+=[
+\begin{pmatrix}
 {\bf a} \\
 {\bf a}^\dagger
-\end{array}\right),
-\left(\begin{array}{ccc}
+\end{pmatrix},
+\begin{pmatrix}
 {\bf a} & {\bf a}^\dagger
-\end{array}\right)\right]
-=S^T\left[
-\left(\begin{array}{ccc}
+\end{pmatrix}]
+=S^T[
+\begin{pmatrix}
 {\bf b} \\
 {\bf b}^\dagger
-\end{array}\right),
-\left(\begin{array}{ccc}
+\end{pmatrix},
+\begin{pmatrix}
 {\bf b} & {\bf b}^\dagger
-\end{array}\right)\right]S
+\end{pmatrix}]S
 =S^T JS,
@@
 where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $[b_i,b_j^\dagger]=\delta_{ij}$.
-It is clear from Eq.~\eqref{Preserve commutator} that $S\in$Sp(2N,{\bf C})\cite{fulton_representation_2004}.
+It is clear from Eq.~\eqref{eq:preserve_commutator} that $S\in$Sp(2N,$\mathbb{C}$)\cite{fulton_representation_2004}.
 Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
-\begin{eqnarray}\begin{aligned}
-\label{Block of S}
-S=\left(\begin{array}{ccc}
+\begin{eqnarray}
+\label{eq:block_S}
+S=
+\begin{bmatrix}
 u & v^*\\
 v & u^*
-\end{array}\right).
-\end{aligned}\end{eqnarray}
+\end{bmatrix}
+\end{eqnarray}
 The symplectic property of S implies the following constraints 
 \begin{eqnarray}
-u^\dagger u-v^\dagger v&={\bf I}\label{Constraint 1}\\
-u^T u-v^T v&=0\label{Constraint 2}
+u^\dagger u-v^\dagger v&=\mathbb{I}\label{eq:constraint_1}\\
+u^T u-v^T v&=0\label{eq:constraint_2}
 \end{eqnarray}
@@
 
-For the ground state of the quadratic Hamiltonian in Eq.~\eqref{Quadratic boson H}, it is the vacuum of the annihilation operators defined in Eq.~\eqref{Def. of a} and satisfies
+For the ground state of the quadratic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}, it is the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and satisfies
 \begin{eqnarray}\begin{aligned}
-\label{a Vacuum condition}
+\label{eq:a_vacuum_condition}
 (b_iu_{ij}+b_i^\dagger v_{ij})|0\rangle_{{\bf a}}=0.
@@
 \end{aligned}\end{eqnarray}
-such that Eq.~\eqref{a Vacuum condition} reduces to
+such that Eq.~\eqref{eq:a_vacuum_condition} reduces to
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-One can use Eq.~\eqref{Constraint 2} to show that $T$ is symmetric, and observe that
+One can use Eq.~\eqref{eq:constraint_2} to show that $T$ is symmetric, and observe that
 \begin{eqnarray}\begin{aligned}
@@
 \begin{eqnarray}\begin{aligned}
-\label{Boson BCS gnd}
+\label{eq:boson_BCS_gnd}
 |0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
@@
 \end{aligned}\end{eqnarray}
-where we have used Eq.~\eqref{Constraint 1} in the second line. From the following McMahon master theorem
-\begin{eqnarray}\begin{aligned}\label{Bosonic McMahon}
+where we have used Eq.~\eqref{eq:constraint_1} in the second line. From the following McMahon master theorem
+\begin{eqnarray}\begin{aligned}
+\label{eq:bosonic_McMahon}
 \langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY)
 \end{aligned}\end{eqnarray}
-one can easily check that the ground state in Eq.~\eqref{Boson BCS gnd} is correctly normalized.
+one can easily check that the ground state in Eq.~\eqref{eq:boson_BCS_gnd} is correctly normalized.
 
-Eq.~\eqref{Boson BCS gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
-We shall defer the explicit construction of Bogoliubov transformation until App.~\ref{app: Explicit construction of symplectic Bogoliubov transformation}.
+Eq.~\eqref{eq:boson_BCS_gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
+We shall defer the explicit construction of Bogoliubov transformation until App.~\ref{app_sub:construction_Bogoliubov}.
 Before that, we shall see that similar constructions of superconducting ground state greatly simplify the expressions for fidelity and Loschmidt echo.
@@
 \subsection{Boson fidelity} 
-\label{app: Boson fidelity}
+\label{app_sub:boson_fidelity}
 
 Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians.
-We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.\eqref{Quadratic boson H}.
-From the discussion in App.~\ref{app: Boson BdG}, we are able to diagonalize it in ${\bf a}$ basis.
+We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.\eqref{eq:quadratic_boson_H}.
+From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis.
 At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis.
@@
 \begin{eqnarray}\begin{aligned}
-\label{Two BdG}
+\label{eq:two_BdG}
 ({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
@@
 \begin{eqnarray}\begin{aligned}
-\label{S0invS}
+\label{eq:S0invS}
 ({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
 \end{aligned}\end{eqnarray}
-One immediately realizes Eq.~\eqref{S0invS} takes the same form as Eq.~\eqref{Def. of a} such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
+One immediately realizes Eq.~\eqref{eq:S0invS} takes the same form as Eq.~\eqref{eq:def_a} such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
 \begin{eqnarray}
-S_0^{-1}S_1=\left(\begin{array}{ccc}
+S_0^{-1}S_1=\begin{bmatrix}
 u_1 & v_1^*\\
 v_1 & u_1^*
-\end{array}\right).
+\end{bmatrix}.
 \end{eqnarray}
-Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{Boson BCS gnd}, and their overlap, which is the fidelity, reads
+Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}, and their overlap, which is the fidelity, reads
 \begin{eqnarray}\begin{aligned}
@@
 \subsection{Boson Loschmidt echo}
-\label{app: Boson Loschmidt echo}
+\label{app_sub:boson_Loschmidt_echo}
 
@@
 \begin{eqnarray}\begin{aligned}
-\label{BdG transformation for echo}
+\label{eq:BdG_transformation_echo}
 ({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
@@
 \end{aligned}\end{eqnarray}
-It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.~\eqref{Boson BCS gnd}.
-In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.~\eqref{BdG transformation for echo}, and it {\bf\color{red}reads}
+It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
+In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.~\eqref{eq:BdG_transformation_echo}, and it {\bf\color{red}reads}
 \begin{eqnarray}\begin{aligned}
-\label{eq in app: Echo}
+\label{eq:echo_t}
 \mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
@@
 \subsection{Explicit construction of symplectic Bogoliubov transformation}
-\label{app: Explicit construction of symplectic Bogoliubov transformation}
-As demonstrated in App.~\ref{app: Boson fidelity} and \ref{app: Boson Loschmidt echo}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.~\eqref{Two BdG}.
-Here, for a quadratic bosonic Hamiltonian
-\begin{eqnarray}\begin{aligned}
-\label{Quadratic boson H2}
-\hat{H}&=\frac{1}{2}
-\left(\begin{array}{ccc}
-{\bf b}^\dagger & -{\bf b}
-\end{array}\right)
-\left(\begin{array}{ccc}
-H & \Delta\\
--\Delta^\dagger & -H^T
-\end{array}\right)
-\left(\begin{array}{ccc}
-{\bf b} \\
-{\bf b}^\dagger
-\end{array}\right)\\
-&=\frac{1}{2}
-\left(\begin{array}{ccc}
-{\bf b}^\dagger & -{\bf b}
-\end{array}\right)
-M
-\left(\begin{array}{ccc}
-{\bf b} \\
-{\bf b}^\dagger
-\end{array}\right)
-\end{aligned}\end{eqnarray}
-we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,{\bf C}) that diagonalizes $M$.
+\label{app_sub:construction_Bogoliubov}
+As demonstrated in App.~\ref{app_sub:boson_fidelity} and \ref{app_sub:boson_Loschmidt_echo}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.~\eqref{eq:two_BdG}.
+Here, we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,$\mathbb{C}$) that diagonalizes the quadratic bosonic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
 
@@
 \begin{eqnarray}\begin{aligned}
-\label{Real basis}
-\left(\begin{array}{ccc}
+\label{eq:real_basis}
+\begin{pmatrix}
 {\bf b}\\
 {\bf b}^\dagger
-\end{array}\right)
-=C\left(\begin{array}{ccc}
+\end{pmatrix}
+=C\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
-=\frac{1}{\sqrt{2}}\left(\begin{array}{ccc}
+\end{pmatrix}
+=\frac{1}{\sqrt{2}}\begin{bmatrix}
 1 & i \\
 1 & -i
-\end{array}\right)\left(\begin{array}{ccc}
+\end{bmatrix}\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
+\end{pmatrix}
 \end{aligned}\end{eqnarray}
@@
 &=\frac{1}{2}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi & \pi
-\end{array}\right)
-\left(\begin{array}{ccc}
-\text{Re}(H+\Delta) & -\text{Im}(H-\Delta)\\
-\text{Im}(H+\Delta)& \text{Re}(H-\Delta) \\
-\end{array}\right)
-\left(\begin{array}{ccc}
+\end{pmatrix}
+\begin{bmatrix}
+\text{Re}(A-B^*) & -\text{Im}(A)+\text{Im}(B)\\
+\text{Im}(A)+\text{Im}(B)& \text{Re}(A+B) \\
+\end{bmatrix}
+\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
+\end{pmatrix}
 =\frac{1}{2}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi & \pi
-\end{array}\right)
+\end{pmatrix}
 \mathcal{M}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
+\end{pmatrix}
 \end{aligned}\end{eqnarray}
@@
 \begin{eqnarray}\begin{aligned}
-\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
+\mathcal{M}=\mathcal{S}
+\begin{bmatrix}
 d\\
 &d
-\end{array}\right)\tilde{S}^T
+\end{bmatrix}
+\mathcal{S}^T
 \end{aligned}\end{eqnarray}
-where $\tilde{S}\in$Sp(2N,{\bf R}) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
+where $\mathcal{S}\in$Sp(2N,$\mathbb{R}$) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
 \begin{eqnarray}\begin{aligned}
-\label{Diagonalization of M}
-M=J(C^{-1})^T\tilde{S}C^TJ^{-1}\left(\begin{array}{ccc}
+\label{eq:diagonalization_M}
+M=J(C^{-1})^T\mathcal{S}C^TJ^{-1}
+\begin{bmatrix}
 d\\
 &-d
-\end{array}\right)C\tilde{S}^TC^{-1}.
+\end{bmatrix}
+C\mathcal{S}^TC^{-1}.
 \end{aligned}\end{eqnarray}
-Using the fact that $\tilde{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.~\eqref{Diagonalization of M} is a similarity transformation, and $C\tilde{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{Block of S}, is an element of complex symplectic group.
+Using the fact that $\mathcal{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.~\eqref{eq:diagonalization_M} is a similarity transformation, and $C\mathcal{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{eq:block_S}, is an element of complex symplectic group.
 Thus we identify
 \begin{eqnarray*}\begin{aligned}
-S\equiv C\tilde{S}^TC^{-1}
+S\equiv C\mathcal{S}^TC^{-1}
 \end{aligned}\end{eqnarray*}
-as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.~\eqref{Quadratic boson H2}.
+as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
 
@@
 The Hamiltonian can be further decomposed via real Schur decomposition.
-Similar expression for Loschmidt echo holds with exponent replaced by $+1$ in Eq.~\eqref{eq in app: Echo}, and the results in \onlinecite{vasseur_universal_2014} can be reproduced.
+Similar expression for Loschmidt echo holds with exponent replaced by $+1$ in Eq.~\eqref{eq:echo_t}, and the results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced.
 
 \subsection{Harmonic chain}
-\label{app: Harmonic chain}
+\label{app_sub:harmonic_chain}
 
@@
 It is not hard find such a system that meets the assumption.
-Here we shall explicitly construct the matrix $\tilde{S}$ for the case of harmonic chain.
-In the basis defined in Eq.~\eqref{Real basis}, the Hamiltonian for 1D harmonic chain reads
+Here we shall explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain.
+In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
 \begin{eqnarray}\begin{aligned}
@@
 =\frac{1}{2}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi & \pi
-\end{array}\right)
+\end{pmatrix}
 \mathcal{M}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
+\end{pmatrix}
 =\frac{1}{2}
-\left(\begin{array}{ccc}
+\begin{pmatrix}
 \phi & \pi
-\end{array}\right)
-\left(\begin{array}{ccc}
+\end{pmatrix}
+\begin{bmatrix}
 \mathcal{V} \\
 & {\bf I}
-\end{array}\right)
-\left(\begin{array}{ccc}
+\end{bmatrix}
+\begin{pmatrix}
 \phi\\
 \pi
-\end{array}\right)
+\end{pmatrix}
 \end{aligned}\end{eqnarray}
@@
 \begin{eqnarray}\begin{aligned}
-\tilde{S}\equiv\left(\begin{array}{ccc}
+\mathcal{S}\equiv
+\begin{bmatrix}
 \mathcal{O}D^{1/2} \\
 & \mathcal{O}D^{-1/2}
-\end{array}\right)
+\end{bmatrix}
 \end{aligned}\end{eqnarray}
@@
 \begin{eqnarray}\begin{aligned}
-\mathcal{M}=\tilde{S}\left(\begin{array}{ccc}
+\mathcal{M}=\mathcal{S}
+\begin{bmatrix}
 D \\ 
 & D
-\end{array}\right)
-\tilde{S}^T
+\end{bmatrix}
+\mathcal{S}^T
 \end{aligned}\end{eqnarray}
@@
 \begin{eqnarray}\begin{aligned}
-M=S^{-1}\left(\begin{array}{ccc}
+M=S^{-1}
+\begin{bmatrix}
 D \\
 & -D
-\end{array}\right)S
+\end{bmatrix}
+S
 \end{aligned}\end{eqnarray}
@@
 \begin{eqnarray}\begin{aligned}
-S&=C\tilde{S}C^{-1}
-&=\left(\begin{array}{ccc}
+S&=C\mathcal{S}C^{-1}
+&=\begin{bmatrix}
 O(D^{1/2}+D^{-1/2}) & O(D^{1/2}-D^{-1/2}) \\
 O(D^{1/2}-D^{-1/2}) & O(D^{1/2}+D^{-1/2}) 
-\end{array}\right)
+\end{bmatrix}
 \end{aligned}\end{eqnarray}

### 2017-05-01 gnd_dn_lambda.tex
1. Hamiltonian changed to A B notation 2. bmatrix, pmatrix used 3. \tilde{S} changed to \mathcal{S} 4. labeling changed

@@
 }
-\label{Fig in gnd_dn_lambda}
+\label{fig:Fig_gnd_dn_lambda}
 \end{figure}
 
-In this appendix, we would like to calculate the amplitude for the setup shown in Fig.~\ref{Fig in gnd_dn_lambda}.
+In this appendix, we would like to calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}.
 In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$.
@@
 \begin{equation}
-\label{Normalized f in gnd_dn_lambda}
+\label{eq:normalized_f}
 f(k, x) = 
@@
 \begin{aligned}
-  A_1 e^{i kt} \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
-  A_2 e^{ikt}  \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
+  A_1 e^{i kt} \cos\left(kx +\frac{1}{2}kL \right) &  \quad x < 0  \\
+  A_2 e^{ikt}  \sin\left(kx - \frac{1}{2}kL \right) & \quad x > 0   \\
 \end{aligned} \right. 
@@
 \begin{eqnarray}\begin{aligned}
-\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2} \quad \theta \in [0,\frac{\pi}{2} ]  
+\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2} \quad \theta \in \left[0,\frac{\pi}{2} \right]
 \end{aligned}\end{eqnarray}
@@
 \begin{equation}
-\label{Momentum in gnd_dn_lambda}
-k = \frac{2\pi}{L}( n \pm \frac{\theta}{\pi} )  \quad n\in{\bf Z}
+\label{eq:momentum_gnd_dn_lambda}
+k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right)  \quad n\in\mathbb{Z}
 \end{equation}
@@
 \qquad 
-k = \frac{2\pi}{L}( n \pm  \frac{\theta}{\pi} )  \quad n \in \mathbb{Z} 
+k = \frac{2\pi}{L}\left( n \pm  \frac{\theta}{\pi} \right)  \quad n \in \mathbb{Z} 
 \end{equation}
@@
 
-It is clear that the normalized eigenfunctions in Eq.~\eqref{Normalized f in gnd_dn_lambda} serves as orthonormal basis in mode expansion.
+It is clear that the normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in mode expansion.
 Following the same procedure in \onlinecite{di_francesco_conformal_1997}, we have the Hamiltonian as
 \begin{equation}
-\label{H in gnd_dn_lambda}
-H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  (a^{\dagger}_n a_n + \frac{1}{2} )
+\label{eq:H_in_gnd_dn_lambda}
+H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right)
 \end{equation}
-where the momentum $k$ is defined in Eq.~\eqref{Momentum in gnd_dn_lambda}, and the creation and annihilation operators defined as usual
+where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators defined as usual
 \begin{equation}
 \begin{aligned}
-a_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
-a^{\dagger}_n = \frac{1}{\sqrt{2}} ( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  ) \\
+a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) \\
+a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) \\
 \end{aligned}
@@
 
-The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.~\eqref{H in gnd_dn_lambda} and define $x\equiv\theta/\pi$ in Eq.~\eqref{Momentum in gnd_dn_lambda}, we have
+The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and define $x\equiv\theta/\pi$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
 \begin{equation}
 \begin{aligned}
-E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} ( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  ) \\  
+E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\  
 &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
 &= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
-&= \frac{1}{2} ( - x^2 + x - \frac{1}{6})
+&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right)
 \end{aligned}

### 2017-05-01 pf_of_id.tex
1. Hamiltonian changed to A B notation 2. bmatrix, pmatrix used 3. \tilde{S} changed to \mathcal{S} 4. labeling changed

@@
 \begin{equation}
-\label{1st id in app.pf_of_id}
+\label{eq:first_id_app_pf_of_id}
 \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
@@
 
-To prove Eq.~\eqref{1st id in app.pf_of_id}, we first consider the special case where $R={\bf I}$.
+To prove Eq.~\eqref{eq:first_id_app_pf_of_id}, we first consider the special case where $R=\mathbb{I}$.
 We diagonalize $M = O^{T} \Lambda O $ and rotate the two sets of boson operators to the diagonal basis
@@
 \begin{equation}
-\label{lambda commutator}
+\label{eq:lambda_commutator}
 [- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
@@
 \end{equation}
-For the general case where $R \ne I$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$.
-This will not change the commutation relation of ${\bf d}$, and the role of $\bar{b}$ is decorative in Eq.~\eqref{lambda commutator}.
+For the general case where $R \neq\mathbb{I}$, we take $\vec{\bar{d}}^* = O^T R \vec{\bar{b}}^*$.
+This will not change the commutation relation of ${\bf d}$, and the role of $\bar{b}$ is decorative in Eq.~\eqref{eq:lambda_commutator}.
 Hence the rest of the proof follows the same way.
@@
 
-A direct consequence of Eq.~\eqref{1st id in app.pf_of_id} is the following
+A direct consequence of Eq.~\eqref{eq:first_id_app_pf_of_id} is the following
 \begin{equation}
-\label{2nd id in app.pf_of_id}
+\label{eq:second_id_in_app_pf_of_id}
 Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
@@
 \end{equation}
-proves Eq.~\eqref{2nd id in app.pf_of_id}. \hfill$\blacksquare$
+proves Eq.~\eqref{eq:second_id_in_app_pf_of_id}. \hfill$\blacksquare$
 

### 2017-05-02 comp_fid_echo.tex
[draft] App.B. revised

@@
 What we do takes advantage of the symplectic structure of the bosonic Bogoliubov transformation, which gives the explicit form of ground state that similar to that of the superconductor.
+
+During the course of derivation in this and other appendices, we will repeatedly use the combinatorial identity called McMahon Master theorem
+\begin{equation}
+\label{eq:bosonic_McMahon}
+\langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY)
+\end{equation}
+for symmetric matrix $X$ and $Y$ and set of independent Bosonic creation operators $b_i^{\dagger}$.
+One can prove its legitimacy for (simultaneously) diagonalizable matrices and then claim it's true for its combinatorial nature.
 
@@
 \label{eq:quadratic_boson_H}
-\hat{H}%&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
+%&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
+\hat{H}
 &=
-\frac{1}{2} (b^{\dagger}, -b)
+\frac{1}{2} (\vec{b}^{\dagger}, -\vec{b})
 M 
 \begin{pmatrix}
-b\\
-b^{\dagger} 
-\end{pmatrix}-\frac{1}{2}\text{tr}H, \qquad 
+\vec{b}\\
+\vec{b}^{\dagger} 
+\end{pmatrix},  \qquad 
 M = 
@@
 \end{aligned}\end{eqnarray}
-where ${\bf b}\equiv(b_{1},...,b_{N})$ is a vector of bosonic annihilation operators.
-Notice $A$ is a $N\times N$ single-particle Hamiltonian, and $B$ is a symmetric pairing matrix.
-The use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ is due to the Sp(2N,$\mathbb{C}$) character of the bosonic Bogoliubov transformation, as we now demonstrate.
+where ${\bf b}\equiv(b_{1},...,b_{n})^T$ is a vector of bosonic annihilation operators.
+The matrix $M$ consists of a $n\times n$ Hermitian block $A$ which plays the role of single particle Hamiltonian in the fermionic case and symmetric block $B$ for the pairing interaction.
 
-The Bogoliubov transformation that diagonalizes the Hamiltonian
+We want to use a Bogoliubov transformation, which utilizes a $2n \times 2n$ matrix $S$ to define a diagonal basis 
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-should preserve the commutation relation
-\begin{eqnarray}\begin{aligned}
+of the Hamiltonian. The transformation is canonical, meaning that it preserves the commutation relation
+
+\begin{eqnarray}
+\begin{aligned}
 \label{eq:preserve_commutator}
@@
 \end{pmatrix}]S
-=S^T JS,
-\end{aligned}\end{eqnarray}
-where the commutator, for example, $\left[{\bf b},{\bf b}^\dagger\right]$ is understood as a matrix with component $[b_i,b_j^\dagger]=\delta_{ij}$.
-It is clear from Eq.~\eqref{eq:preserve_commutator} that $S\in$Sp(2N,$\mathbb{C}$)\cite{fulton_representation_2004}.
-Further, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of S
+=S^T JS.
+\end{aligned}
+\end{eqnarray}
+where we have used the compact notation of the sort $([\vec{b}, \vec{b}^{\dagger}])_{ij} =  [b_i, b_j^\dagger]$ to denote the commutator matrix.
+Consequently, $S$ is in the symplectic group ${\rm Sp}( 2n, \mathbb{C} ) $\cite{blaizot_quantum_1986,fulton_representation_2004}.
+Furthermore, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of $S$
 \begin{eqnarray}
@@
 v & u^*
-\end{bmatrix}
+\end{bmatrix}.
 \end{eqnarray}
-The symplectic property of S implies the following constraints 
+and the symplectic property of $S$ implies the following constraints on the blocks 
 \begin{eqnarray}
@@
 \end{eqnarray}
-which will be important for calculation of the ground state.
+With these conditions, the Hamiltonian in basis $a$ becomes (the use of $({\bf b}^\dagger , -{\bf b})$ rather than $({\bf b}^\dagger , {\bf b})$ can be appreciated in this step)
+\begin{equation}
+H = \frac{1}{2} ( a^{\dagger}, -a )  (S^{\top} M (S^{\top})^{-1} )
+\begin{pmatrix}
+a\\
+a^{\dagger} 
+\end{pmatrix}.
+\end{equation}
+A symplectic matrix $S$ solves the problem if it diagonalizes $M$.
 
-For the ground state of the quadratic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}, it is the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and satisfies
+The solution depend on the types of $M$.
+For the positive definite matrix $M$, one can rewrite the Hamiltonian in the position and momentum basis and invoke the Williamson theorem\cite{arnold_mathematical_2010}, which address the existence, uniqueness and construction of the matrix $S$.
+We defer the derivation in this route in App.~\ref{app_sub:construction_Bogoliubov}, but will not elaborate the theorem and its proof there (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in entanglement entropy context\cite{coser_contour_2017}).
+Instead we will show in App.~\ref{app_sub:harmonic_chain} that for the problem of harmonic chain we are interested in, the diagonalization can be easily done without using the general recipe in the Williamson theorem.
+
+It is nevertheless nice to know that the formalism works for the all positive definite matrix $M$.
+And granted that we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and satisfies
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-If the matrix $u$ is invertible, then we can introduce a matrix
+If the matrix $u$ is invertible, then we can introduce a matrix $T=vu^{-1}$ to rewrite Eq.~\eqref{eq:a_vacuum_condition} as
 \begin{eqnarray}\begin{aligned}
-T=vu^{-1}
+(b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0. 
 \end{aligned}\end{eqnarray}
-such that Eq.~\eqref{eq:a_vacuum_condition} reduces to
-\begin{eqnarray}\begin{aligned}
-(b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0,
-\end{aligned}\end{eqnarray}
-One can use Eq.~\eqref{eq:constraint_2} to show that $T$ is symmetric, and observe that
+The constraint Eq.~\eqref{eq:constraint_2} on the blocks of $u$ and $v$ (followed by the symplectic constraint of $S$) implies that $T$ is a symmetric matrix, 
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-Thus we conclude that 
+we therefore solve the vacuum state
 \begin{eqnarray}\begin{aligned}
@@
 |0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
-&=|\text{det}(u)|^{-\frac{1}{2}}\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}.
 \end{aligned}\end{eqnarray}
-where we have used Eq.~\eqref{eq:constraint_1} in the second line. From the following McMahon master theorem
-\begin{eqnarray}\begin{aligned}
-\label{eq:bosonic_McMahon}
-\langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY)
-\end{aligned}\end{eqnarray}
-one can easily check that the ground state in Eq.~\eqref{eq:boson_BCS_gnd} is correctly normalized.
-
+where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}. Apply constrain in Eq.~\eqref{eq:constraint_1}, it simplifies to
+\begin{equation}
+\text{det}^{\frac{1}{4}}(1-T^\dagger T) =|\text{det}(u)|^{-\frac{1}{2}}
+\end{equation}
 Eq.~\eqref{eq:boson_BCS_gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
-We shall defer the explicit construction of Bogoliubov transformation until App.~\ref{app_sub:construction_Bogoliubov}.
-Before that, we shall see that similar constructions of superconducting ground state greatly simplify the expressions for fidelity and Loschmidt echo.
+We will see that the normalization factor gives the fidelity and Loschmidt echo.
 
@@
 
-Fidelity is defined as the overlap of groundstates of two different bosonic Hamiltonians.
+Fidelity is defined as the (squared) overlap of groundstates of two different bosonic Hamiltonians.
+
 We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.\eqref{eq:quadratic_boson_H}.
@@
 \end{aligned}\end{eqnarray}
-such that
+and so
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-One immediately realizes Eq.~\eqref{eq:S0invS} takes the same form as Eq.~\eqref{eq:def_a} such that $S_0^{-1}S_1$ is in the same symplectic group, and takes the following block form
+One realizes Eq.~\eqref{eq:S0invS} is another Bogoliubov transformation and so the corresponding matrix has the block structure
 \begin{eqnarray}
@@
 \end{eqnarray}
-Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}, and their overlap, which is the fidelity, reads
+Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}. Their overlap is therefore given by the normalization factor
 \begin{eqnarray}\begin{aligned}
@@
 
-The Loschmidt echo is defined as the overlap of the evolved state
+The Loschmidt echo is defined as the (squared) overlap of the evolved state
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-with the $\hat{H}_0$ ground state $|0\rangle_{\bf a}$. We introduce the third dynamical basis
+with $|0\rangle_{\bf a}$ the ground state of the Hamiltonian $\hat{H}_0$ before the quench. We introduce a dynamical basis
 \begin{eqnarray}\begin{aligned}
@@
 which annihilate the evolved state at time t: $a_i(t)|0\rangle_{{\bf a}(t)}=0$.
-Upon using the expression $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time t can be represented as a chain of symplectic transformation
+Upon using the expression $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time $t$ can be represented as a chain of symplectic transformation
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ via the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
-In order to calculate the Loschmidt echo, we simply take the left top corner of the Bogoliubov transformation in Eq.~\eqref{eq:BdG_transformation_echo}, and it {\bf\color{red}reads}
+It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ through the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
+The overlap, as we have seen in the fidelity case, is the normalization factor of the "BCS" ground state.
+It is related to the top left block of the Bogoliubov transformation in Eq.~\eqref{eq:BdG_transformation_echo},
+\todo[inline]{Mao: you have highlights "it reads", anything wrong here?}
 \begin{eqnarray}\begin{aligned}
@@
 
-\subsection{Explicit construction of symplectic Bogoliubov transformation}
+\subsection{Explicit Construction of Symplectic Bogoliubov Transformation}
 \label{app_sub:construction_Bogoliubov}
+
 As demonstrated in App.~\ref{app_sub:boson_fidelity} and \ref{app_sub:boson_Loschmidt_echo}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.~\eqref{eq:two_BdG}.
-Here, we shall describe how to find such a Bogoliubov transformation S$\in$Sp(2N,$\mathbb{C}$) that diagonalizes the quadratic bosonic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
+Here, we shall describe how to find such a Bogoliubov transformation $S \in {\rm Sp}(2n, \mathbb{C})$ that diagonalizes the quadratic bosonic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
 
@@
 \end{aligned}\end{eqnarray}
-It is not hard to realize $\mathcal{M}$ is real and symmetric.
-We shall further assume that $\mathcal{M}$ is positive definite, and from Williamson's theorem\cite{arnold_mathematical_2010} we have the decomposition
+It is not hard to check that $\mathcal{M}$ is real and symmetric.
+We shall further assume that $\mathcal{M}$ is positive definite.
+From Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} we have the decomposition
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-where $\mathcal{S}\in$Sp(2N,$\mathbb{R}$) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
+where $\mathcal{S}\in$Sp(2n,$\mathbb{R}$) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-Using the fact that $\mathcal{S}$ is an element of real symplectic group and the explicit form of C-matrix, one can show that Eq.~\eqref{eq:diagonalization_M} is a similarity transformation, and $C\mathcal{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{eq:block_S}, is an element of complex symplectic group.
+Using the fact that $\mathcal{S}$ is an element of real symplectic group and the explicit form of $C$-matrix, one can show that Eq.~\eqref{eq:diagonalization_M} is a similarity transformation, and $C\mathcal{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{eq:block_S}, is an element of complex symplectic group.
 Thus we identify
@@
 
-We note that Majorana basis will play the role of real basis for the fermionic case.
-The Hamiltonian can be further decomposed via real Schur decomposition.
-Similar expression for Loschmidt echo holds with exponent replaced by $+1$ in Eq.~\eqref{eq:echo_t}, and the results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced.
+The analogous situation for the quadratic fermion Hamiltonian is write the problem in the Majorana basis.
+The real symplectic matrix $\mathcal{S}$ becomes a real orthogonal matrix and can be found by a real Schur decomposition.
+In the complex basis, it is the unitary matrix in place of the complex symplectic matrix.
+The Loschmidt echo will become $|\det ( u )|$ as opposite to the Bosonic $\frac{1}{|\det u|}$ in Eq.~\eqref{eq:echo_t}, where $u$ is the top left corner of the unitary matrix $U$.
+The results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced.
 
@@
 
-We notice in the above construction, the Hamiltonian $\mathcal{M}$ in the real basis is assumed to be positive definite.
-It is not hard find such a system that meets the assumption.
-Here we shall explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain.
-In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
+In this section, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain. In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
 \begin{eqnarray}\begin{aligned}
@@
 where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$.
-The explicit form of $\mathcal{V}$ depends on the boundary condition which is not important in the following construction.
-We define the following real symplectic matrix
+The explicit form of $\mathcal{V}$ depends on the boundary condition, but positive definiteness is the only requirement here.
+
+The matrix $\mathcal{S}$ that appears in Williamson theorem
+\begin{eqnarray}
+\begin{aligned}
+\mathcal{M}=\mathcal{S}
+\begin{bmatrix}
+D \\ 
+& D
+\end{bmatrix}
+\mathcal{S}^T
+\end{aligned}
+\end{eqnarray}
+is given by the following real symplectic matrix
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-such that 
-\begin{eqnarray}\begin{aligned}
-\mathcal{M}=\mathcal{S}
-\begin{bmatrix}
-D \\ 
-& D
-\end{bmatrix}
-\mathcal{S}^T
-\end{aligned}\end{eqnarray}
-in accordance with Williamson's theorem. Thus the second quantized Hamiltonian will be diagonalized as
+
+Thus the second quantized Hamiltonian is therefore diagonalized as
 \begin{eqnarray}\begin{aligned}

### 2017-05-02 general_formulation.tex
[draft] general_formulation.tex added

We consider a conformal interface connecting two potentially different CFTs. The interface is located at $x=0$ and characterized by the ``gluing condition''
\begin{eqnarray}\begin{aligned}
\label{Def. of M}
\begin{pmatrix}
\partial_x\phi\\
\partial_t\phi
\end{pmatrix}_{x=0^-}
=M\begin{pmatrix}
\partial_x\phi\\
\partial_t\phi
\end{pmatrix}_{x=0^+}
\end{aligned}\end{eqnarray}
The interface is now penetrable. Instead of requiring the normal components of the stress tensor to vanish\cite{cardy_conformal_1984}, one only needs the stress tensor to be continuous across the defect. From the explicit expression of the stress tensor $T^{xt}=-\partial_x\phi\partial_t\phi$, one can show that\cite{bachas_permeable_2002} $M$ is an element of the Lorentz group $O(1,1)$. In terms of the boost parametrization, we have
\begin{eqnarray}\begin{aligned}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix}\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix}
\end{aligned}\end{eqnarray}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

We note the following special cases. For $\theta=0,\pm\pi/2$, $\lambda$ appears to be singular and the fields on either side of the defect do not communicate to each other. For example, $M_1(0)$ implies $\partial_x\phi(0^+)=\partial_t\phi(0^-)=0$. For the two CFTs, this corresponds to Dirichlet boundary condition on the left, and Neumann condition on the right. Hereafter we shall denote it as `DN'. %Similarly one can check that $M_1(\pm\pi/2),M_2(0),M_2(\pm\pi/2)$ correspond to ND, NN, DD respectively. 
For $\theta=\pm\pi/4$, on the other hand, characterizes a perfectly transmitting defect. For example, there is effectively no defect in the case $M(\pi/4)$. For the other three cases, although the field $\phi$ may pick up a phase across the defect, the two counter propagating waves are still fully transmitted.

It proves useful to rewrite Eq.~\eqref{Def. of M} in the ``light cone'' coordinate $x^\pm\equiv t\pm x$, where the physical meaning of $\theta$ is most transparent. For clarity, we denote the field on the negative (positive) real axis as $\phi^1$ ($\phi^2$). {\bf\color{red}Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}. After some algebra, we have
\begin{eqnarray}\begin{aligned}
\label{Def. of S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{eqnarray}
where 
\begin{eqnarray}\begin{aligned}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{eqnarray}
The scattering matrix $S_1$ and $S_2$ relate the incoming and outgoing waves at the defect. For example, $S_1(0)$ implies that $\partial_\pm\phi^{1}=\partial_\pm\phi^{2}$ as discussed above. For other nontrivial values of $\theta$, the defect becomes partially-transmitting. The transmission and reflection coefficients, which are determined by $\theta$, can be read off from the scattering matrices.

{\bf\color{red}As we shall show explicitly in Sec.~\ref{sec: A Free Boson Lattice Model}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.}

### 2017-05-02 comp_fid_echo.tex
[draft] App. B 2nd revision

@@
 In this appendix, we provide technical details about the numerical calculation of the bipartite fidelity and Loschmidt echo.
-It is different from the method for fermionic cases used in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011} but can by applied to with slight modification.
-What we do takes advantage of the symplectic structure of the bosonic Bogoliubov transformation, which gives the explicit form of ground state that similar to that of the superconductor.
+It can also be applied with slight modification to the fermionic case in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011}.
+Our strategy takes advantage of the symplectic structure of the bosonic Bogoliubov transformation and explicitly construct the "BCS" like ground state.
 
@@
 for symmetric matrix $X$ and $Y$ and set of independent Bosonic creation operators $b_i^{\dagger}$.
-One can prove its legitimacy for (simultaneously) diagonalizable matrices and then claim it's true for its combinatorial nature.
+One can prove it for (simultaneously) diagonalizable matrices and then claim its legitimacy for the combinatorial nature.
 
@@
 We consider the following quadratic bosonic Hamiltonian
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:quadratic_boson_H}
@@
 \end{bmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where ${\bf b}\equiv(b_{1},...,b_{n})^T$ is a vector of bosonic annihilation operators.
@@
 
-We want to use a Bogoliubov transformation, which utilizes a $2n \times 2n$ matrix $S$ to define a diagonal basis 
-\begin{eqnarray}\begin{aligned}
+We want to do a Bogoliubov transformation, which uses a $2n \times 2n$ matrix $S$ to define a diagonal basis 
+\begin{equation}\begin{aligned}
 \label{eq:def_a}
 ({\bf a} , {\bf a}^\dagger)\equiv({\bf b} , {\bf b}^\dagger)S
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 of the Hamiltonian. The transformation is canonical, meaning that it preserves the commutation relation 
-
-\begin{eqnarray}
+\begin{equation}
 \begin{aligned}
@@
 \end{aligned}
-\end{eqnarray}
+\end{equation}
 where we have used the compact notation of the sort $([\vec{b}, \vec{b}^{\dagger}])_{ij} =  [b_i, b_j^\dagger]$ to denote the commutator matrix.
-Consequently, $S$ is in the symplectic group ${\rm Sp}( 2n, \mathbb{C} ) $\cite{blaizot_quantum_1986,fulton_representation_2004}.
+The appearance of $J$ makes the symplectic nature of the problem manifest and we find $S$ is in the symplectic group ${\rm Sp}( 2n, \mathbb{C} ) $\cite{blaizot_quantum_1986,fulton_representation_2004}.
 Furthermore, the requirement that $a^\dagger$ is a complex conjugation of $a$ leads to the block structure of $S$
-\begin{eqnarray}
+\begin{equation}
 \label{eq:block_S}
@@
 \end{bmatrix}.
-\end{eqnarray}
-and the symplectic property of $S$ implies the following constraints on the blocks 
+\end{equation}
+and the blocks are constrained by the symplectic property
 \begin{eqnarray}
@@
 \end{equation}
-A symplectic matrix $S$ solves the problem if it diagonalizes $M$.
+Quiet unusually, the diagonalization is performed by the symplectic group element.
 
-The solution depend on the types of $M$.
-For the positive definite matrix $M$, one can rewrite the Hamiltonian in the position and momentum basis and invoke the Williamson theorem\cite{arnold_mathematical_2010}, which address the existence, uniqueness and construction of the matrix $S$.
+The solution of $S$ depends on the types of $M$.
+For the positive definite matrix $M$, one can rewrite the Hamiltonian in the position and momentum basis and invoke the Williamson theorem\cite{arnold_mathematical_2010}, which addresses the existence, uniqueness and construction of the matrix $S$.
 We defer the derivation in this route in App.~\ref{app_sub:construction_Bogoliubov}, but will not elaborate the theorem and its proof there (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in entanglement entropy context\cite{coser_contour_2017}).
@@
 It is nevertheless nice to know that the formalism works for the all positive definite matrix $M$.
-And granted that we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and satisfies
-\begin{eqnarray}\begin{aligned}
+And granted that we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and in $b$ basis it satisfies
+\begin{equation}\begin{aligned}
 \label{eq:a_vacuum_condition}
 (b_iu_{ij}+b_i^\dagger v_{ij})|0\rangle_{{\bf a}}=0.
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 If the matrix $u$ is invertible, then we can introduce a matrix $T=vu^{-1}$ to rewrite Eq.~\eqref{eq:a_vacuum_condition} as
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 (b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0. 
-\end{aligned}\end{eqnarray}
-The constraint Eq.~\eqref{eq:constraint_2} on the blocks of $u$ and $v$ (followed by the symplectic constraint of $S$) implies that $T$ is a symmetric matrix, 
-\begin{eqnarray}\begin{aligned}
-\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}b_i\exp\left\{\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}=b_i+T_{ij}b^\dagger_j.
-\end{aligned}\end{eqnarray}
-we therefore solve the vacuum state
-\begin{eqnarray}\begin{aligned}
+\end{aligned}\end{equation}
+The constraint Eq.~\eqref{eq:constraint_2} on the blocks of $u$ and $v$ (followed by the symplectic constraint of $S$) implies that $T$ is a symmetric matrix. With the observation of 
+\begin{equation}\begin{aligned}
+\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}b_i\exp\left\{\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}=b_i+T_{ij}b^\dagger_j,
+\end{aligned}\end{equation}
+we solve the ground state
+\begin{equation}\begin{aligned}
 \label{eq:boson_BCS_gnd}
 |0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
-\end{aligned}\end{eqnarray}
-where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}. Apply constrain in Eq.~\eqref{eq:constraint_1}, it simplifies to
+\end{aligned}\end{equation}
+where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}.
+Apply constraint in Eq.~\eqref{eq:constraint_1}, it simplifies to the top left corner of the symplectic matrix
 \begin{equation}
@@
 \end{equation}
+
 Eq.~\eqref{eq:boson_BCS_gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
-We will see that the normalization factor gives the fidelity and Loschmidt echo.
+In the next section, we will see that the normalization factor gives the fidelity and Loschmidt echo.
 
@@
 
-We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.\eqref{eq:quadratic_boson_H}.
-From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis.
-At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new ${\bf c}$ basis.
+We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.~\eqref{eq:quadratic_boson_H}.
+From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis for positive definite $M$.
+At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new basis ${\bf c}$.
 The corresponding Bogoliubov transformations read
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:two_BdG}
@@
 ({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 and so
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:S0invS}
 ({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
-\end{aligned}\end{eqnarray}
-One realizes Eq.~\eqref{eq:S0invS} is another Bogoliubov transformation and so the corresponding matrix has the block structure
-\begin{eqnarray}
+\end{aligned}\end{equation}
+One realizes that Eq.~\eqref{eq:S0invS} is another Bogoliubov transformation and so the corresponding matrix has the block structure
+\begin{equation}
 S_0^{-1}S_1=\begin{bmatrix}
@@
 \end{bmatrix}.
-\end{eqnarray}
+\end{equation}
 Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}. Their overlap is therefore given by the normalization factor
-\begin{eqnarray}\begin{aligned}
-|_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|}
-\end{aligned}\end{eqnarray}
+\begin{equation}\begin{aligned}
+|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|} \Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2   = \frac{1}{|\text{det}(u_1)|}
+\end{aligned}\end{equation}
 
@@
 The Loschmidt echo is defined as the (squared) overlap of the evolved state
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 |0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 with $|0\rangle_{\bf a}$ the ground state of the Hamiltonian $\hat{H}_0$ before the quench. We introduce a dynamical basis
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t}
-\end{aligned}\end{eqnarray}
-which annihilate the evolved state at time t: $a_i(t)|0\rangle_{{\bf a}(t)}=0$.
-Upon using the expression $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time $t$ can be represented as a chain of symplectic transformation
-\begin{eqnarray}\begin{aligned}
+\end{aligned}\end{equation}
+which annihilate the evolved state at time $t$: $a_i(t)|0\rangle_{{\bf a}(t)}=0$.
+Upon using the diagonal basis $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time $t$ can be represented as a chain of symplectic transformation
+\begin{equation}\begin{aligned}
 \label{eq:BdG_transformation_echo}
@@
 ({\bf a} , {\bf a}^\dagger)e^{iHt}=({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ through the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
@@
 \todo[inline]{Mao: you have highlights "it reads", anything wrong here?}
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:echo_t}
 \mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 
@@
 We introduce the real basis 
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:real_basis}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 in which the Hamiltonian reads
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \hat{H}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 It is not hard to check that $\mathcal{M}$ is real and symmetric.
@@
 From Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} we have the decomposition
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \mathcal{M}=\mathcal{S}
 \begin{bmatrix}
-d\\
-&d
+\, d \, & \\
+ & \, d\, \\
 \end{bmatrix}
 \mathcal{S}^T
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where $\mathcal{S}\in$Sp(2n,$\mathbb{R}$) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:diagonalization_M}
@@
 C\mathcal{S}^TC^{-1}.
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 Using the fact that $\mathcal{S}$ is an element of real symplectic group and the explicit form of $C$-matrix, one can show that Eq.~\eqref{eq:diagonalization_M} is a similarity transformation, and $C\mathcal{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{eq:block_S}, is an element of complex symplectic group.
 Thus we identify
-\begin{eqnarray*}\begin{aligned}
+\begin{equation*}\begin{aligned}
 S\equiv C\mathcal{S}^TC^{-1}
-\end{aligned}\end{eqnarray*}
+\end{aligned}\end{equation*}
 as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
 
-The analogous situation for the quadratic fermion Hamiltonian is write the problem in the Majorana basis.
+In the analogous situation for the quadratic fermion Hamiltonian, we can rewrite the problem in the real Majorana basis.
 The real symplectic matrix $\mathcal{S}$ becomes a real orthogonal matrix and can be found by a real Schur decomposition.
-In the complex basis, it is the unitary matrix in place of the complex symplectic matrix.
+Reverting back to the complex basis, it is the unitary matrix $U$ that plays the role of the complex symplectic matrix $S$ here.
 The Loschmidt echo will become $|\det ( u )|$ as opposite to the Bosonic $\frac{1}{|\det u|}$ in Eq.~\eqref{eq:echo_t}, where $u$ is the top left corner of the unitary matrix $U$.
-The results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced.
+The results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced in this way.
 
@@
 
-In this section, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain. In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
-\begin{eqnarray}\begin{aligned}
+In this subsection, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain. In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
+\begin{equation}\begin{aligned}
 \hat{H}
@@
 \mathcal{V} \\
-& {\bf I}
+& {\mathbb{ I}}
 \end{bmatrix}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$.
@@
 
-The matrix $\mathcal{S}$ that appears in Williamson theorem
-\begin{eqnarray}
+The matrix $\mathcal{S}$ that diagonalize $\mathcal{M}$
+\begin{equation}
 \begin{aligned}
@@
 \end{aligned}
-\end{eqnarray}
+\end{equation}
 is given by the following real symplectic matrix
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \mathcal{S}\equiv
@@
 \end{bmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 
-Thus the second quantized Hamiltonian is therefore diagonalized as
-\begin{eqnarray}\begin{aligned}
+Thus the second quantized Hamiltonian is diagonalized as
+\begin{equation}\begin{aligned}
 M=S^{-1}
@@
 S
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where the Bogoliubov transformation take the desired block form
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 S&=C\mathcal{S}C^{-1}
@@
 \end{bmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 

### 2017-05-02 F_correction.tex
[draft] App. A draft finished.

\todo[inline]{cite main text figure for conformal transformation}
In the course of derivation the free energy subject to various boundary conditions, we use conformal transformation to convert the space time diagram with slits to a cylinder diagram, where the boundary state (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable. However, free energy, especially its constant part, is not invariant under the conformal transformation, because the boundaries partially break the conformal symmetry. In this Appendix, we point out two corrections -- one from the outer boundary and the other from the inhomogeneous Schwartzian term -- to get the correct exponent of the fidelity and Loschmidt echo.

% outer boundary correction
It is discussed in the pioneering work\cite{cardy_finite-size_1988} by Cardy and Peschel that boundary will contribute logarithmic term, which manifest itself as the geodesic curvature integral in the trace anomaly. Here we demonstrate this principle using the disk free energy example in Ref.~\cite{cardy_finite-size_1988}. Consider an annulus on flat space with inner radius $r_1$ and outer radius $r_2$. Its free energy is
\begin{equation}
F({\rm annulus}) = -  \frac{c}{6} \ln \frac{r_2}{r_1} 
\end{equation}
On the other hand the free energy of a disk of radius $r_2$ is
\begin{equation}
  F( {\rm disk} ) = - \frac{c}{6} \ln \frac{r_2}{a}
\end{equation}
where $a$ is the short distance regulator. The disk free energy is completely contributed by its outer boundary and so the one can interpret the annulus free energy as the additive contribution from its outer and inner surfaces (which is also consistent with the geodesic curvature integral calculation),
\begin{equation}
F( {\rm annulus} ) = -  \frac{c}{6} \ln \frac{r_2}{a} +  \frac{c}{6} \ln \frac{r_1}{a} = - \frac{c}{6} \ln \frac{r_2}{r_1}
\end{equation}
An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible.

\todo[inline]{citing figure}
We now scrutinize the conformation transformation from the slit diagram to the annulus. In the slit diagram, the regulators all have radius that is order of the short distance cut-off. They will have negligible contributions to the free energy. However, after doing the conformal transformation (passive), the outer surface will contribute $-\frac{c}{6} \ln \frac{r_2}{r_1}$ which should not be there. Using the parameters in the free energy calculation in other appendices, we have 
\begin{equation}
F_{\xi } = F_{z} + \frac{c}{6} \beta 
\end{equation}

% staircase geometry correction
The annulus is called staircase geometry Ref.~\onlinecite{cardy_finite-size_1988} due to its angular direction of time evolution. The traditional radial quantization however has radial direction to be the time direction. One can go through a series of conformal maps, one can show that that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian
\begin{equation}
H_{z} = H_{\xi} - \frac{c}{24\pi} \beta 
\end{equation}
After the evolution for $2\pi$, the difference in the free energy is
\begin{equation}
F_w = F_{\xi} - \frac{c}{12} \beta 
\end{equation}
Gathering the two together, we obtain the missing $\frac{c}{12} \beta$ between the echo diagram and the Casimir energy, 
\begin{equation}
F_{w} = F_z + {\color{red} \frac{c}{12}\beta }
\end{equation}
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_uncon_rq.pdf}
\caption{Unconventional radial quantization on annulus(torus). Left panel: unlike the conventional radial quantization, we view the dashed line as a state and to time evolution in the radial direction. The blue circles are regarded as boundaries conditions rather than asymptotic states. Middle panel: $\xi = \ln w$ plane. Right panel: $z = \exp(i \frac{2\pi}{\beta} \xi)$ plane. We treat those dashed lines as asymptotic states and perform standard radial quantization here.}
\label{fig:uncon_rq}
\end{figure}

\todo[inline]{There are two series of conformal transformation, one is the main text, the other is the staircase geometry. Both use $w, z, \xi$, I will fix the notation after the main text figure is complete. Maybe detailed computation of the Schwartzian term is necessary, because of the sign. }

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-03 compact_boson.tex
[draft] 1. compact boson moved to appendix 2. added compact_boson but just started 3. general formulation nearly finished

{\bf\color{red}Remember to mention in the main text, winding sectors have no contribution}

{\bf\color{red} say motivation: Winding sectors cannot be determined from above. Extension of constraint to zero mode. Conformal invariance is intact. Say linear combination and constraints }

{\bf\color{red} say objective: Has only $\ln\beta$ contribution}

### 2017-05-03 general_formulation.tex
[draft] 1. compact boson moved to appendix 2. added compact_boson but just started 3. general formulation nearly finished

@@
-We consider a conformal interface connecting two potentially different CFTs. The interface is located at $x=0$ and characterized by the ``gluing condition''
+We consider a conformal interface connecting two potentially different CFTs in $1+1$ dimensions. The interface is located at $x=0$ and characterized by the ``gluing condition''
 \begin{eqnarray}\begin{aligned}
-\label{Def. of M}
+\label{eq:def_M}
 \begin{pmatrix}
@@
 \end{aligned}\end{eqnarray}
-The interface is now penetrable.
+The interface is assumed to be penetrable.
 Instead of requiring the normal components of the stress tensor to vanish\cite{cardy_conformal_1984}, one only needs the stress tensor to be continuous across the defect.
@@
 Hereafter we shall denote it as `DN'.
-%Similarly one can check that $M_1(\pm\pi/2),M_2(0),M_2(\pm\pi/2)$ correspond to ND, NN, DD respectively.
+Similarly one can check that $M_1(\pm\pi/2),M_2(0),M_2(\pm\pi/2)$ correspond to ND, NN, DD respectively.
 For $\theta=\pm\pi/4$, on the other hand, characterizes a perfectly transmitting defect.
@@
 
-It proves useful to rewrite Eq.~\eqref{Def.
-of M} in the ``light cone'' coordinate $x^\pm\equiv t\pm x$, where the physical meaning of $\theta$ is most transparent.
+It proves useful to rewrite Eq.~\eqref{eq:def_M} in the ``light cone'' coordinate $x^\pm\equiv t\pm x$, where the physical meaning of $\theta$ is most transparent.
 For clarity, we denote the field on the negative (positive) real axis as $\phi^1$ ($\phi^2$).
@@
 \begin{eqnarray}\begin{aligned}
-\label{Def. of S}
+\label{eq:def_S}
 \begin{pmatrix}
@@
 {\bf\color{red}As we shall show explicitly in Sec.~\ref{sec: A Free Boson Lattice Model}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.}
+
+The problem of conformal interface can be studied in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984} after we fold the field $\phi^2$ to the left half plane on top of $\phi^1$\cite{oshikawa_boundary_2010}.
+The boundary at $x=0$ is impenetrable for the tensor theory, and there hosts a conformal boundary states for the bosons.
+The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$.
+Therefore the gluing condition in Eq.~\eqref{eq:def_M} with $M_1(\theta)$ reads{\bf\color{red}say why M1?}
+\begin{eqnarray}\begin{aligned}
+\partial_t(\cos\theta\phi^1-\sin\theta\phi^2)=0 \quad
+\partial_x(\sin\theta\phi^1+\cos\theta\phi^2)=0 
+\end{aligned}\end{eqnarray}
+After performing explicit mode expansion for both $\phi^{1,2}$, {\bf\color{red}write down mode expansion, or simply write down the physical meanings of a's as follows?}we have
+\begin{eqnarray}\begin{aligned}
+\label{eq:rotation_a_basis}
+\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
+\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
+\end{aligned}\end{eqnarray}
+where $n>0$ is an integer.
+$a_n^{1,2}$ ($\bar{a}_n^{1,2}$) annihilate the left (right)-moving modes of $\phi^{1,2}$, and $a_{-n}^{1,2}$ ($\bar{a}_{-n}^{1,2}$) are the corresponding creation operators.
+Eq.~\eqref{eq:rotation_a_basis} is essentially a rotation of basis, and the conformal boundary state reads\cite{oshikawa_boundary_2010}
+\begin{equation}
+\label{eq:bd_state}
+\begin{aligned}
+| B \rangle 
+& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
+\begin{pmatrix}
+a_{-n}^1\\
+a_{-n}^2\\                              
+\end{pmatrix}
+S_1
+\begin{pmatrix}
+\bar{a}_{-n}^1  \bar{a}_{-n}^2
+\end{pmatrix} \Big\} |0\rangle
+\end{aligned}
+\end{equation}
+where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.  {\bf\color{red}say sth}

### 2017-05-04 compact_boson.tex
[draft]1. Sec.IIA general_formulation nearly done 2. App.F compact boson nearly done 但是写的跟屎一样...学长先别动它... 3. Sec.IIB free_boson_lattice barely started..

@@
 
-{\bf\color{red} say motivation: Winding sectors cannot be determined from above. Extension of constraint to zero mode. Conformal invariance is intact. Say linear combination and constraints }
+We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculate various partition functions from the boundary state approach in Sec.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}.
+We have not talk about the winding mode for compact bosons.
+In this appendix, we shall show that winding modes will not contribute to the free energy, at least in the leading order.
+In fact the gluing condition in Eq.~\eqref{eq:def_M} can be derived from the variational approach\cite{blumenhagen_introduction_2009,bachas_permeable_2002}, from which it is clear that conformal invariance provides no constraint for the winding mode.
+This is expected since winding is a global property of the boson configuration.
+Thus one needs a general treatment for the winding modes.
+This is first illustrated for the simple cases of Dirichlet and Neumann boundary conditions in Sec.~\ref{app_sub:compact_DN_boundary} and generalized to gluing condition in Sec.~\ref{app_sub:compact_gluing_boundary}.
+We demonstrate that winding mode does not contribute to the free energy in Sec.~\ref{app_sub:winding_contribution}.
 
-{\bf\color{red} say objective: Has only $\ln\beta$ contribution}
+%\subsection{Free Boson with Different Compactification Radii}
+
+\subsection{Winding Mode with Dirichlet and Neumann Boundary Conditions}
+\label{app_sub:compact_DN_boundary}
+
+We consider the following boson configuration
+\begin{eqnarray}\begin{aligned}
+\phi(x+L,t)=\phi(x,t)+2\pi mR
+\end{aligned}\end{eqnarray}
+where $m$ is the winding number of the field. Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$. Thus the mode expansion reads
+\begin{eqnarray}\begin{aligned}
+\label{eq:mode_expand_compact}
+\phi(x,t)&=\phi_0-\frac{2\pi Rm}{L}x+\frac{\pi_0}{gL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})\\ 
+&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x+i\tau)/L}+\bar{a}_{n}e^{2\pi i n(x-i\tau)/L})
+\end{aligned}\end{eqnarray}
+Further, the holomorphic coordinates are introduced as
+\begin{eqnarray}\begin{aligned}
+z=\exp\left(2\pi i\frac{t-x}{L}\right)\qquad\bar{z}=\exp\left(2\pi i\frac{t+x}{L}\right)
+\end{aligned}\end{eqnarray}
+which leads to 
+\begin{eqnarray}\begin{aligned}
+\label{eq:phi_in_z}
+\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln z+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
+\end{aligned}\end{eqnarray}
+The key observation is that if one defines
+\begin{eqnarray}\begin{aligned}
+a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\frac{mR}{2}
+\end{aligned}\end{eqnarray}
+then the holomorphic and anti-holomorphic derivatives can be written compactly as
+\begin{eqnarray}\begin{aligned}
+i\partial\phi(z)=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}a_{n}z^{-n-1}\qquad i\bar{\partial}\phi(\bar{z})=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}\bar{a}_{n}\bar{z}^{-n-1}
+\end{aligned}\end{eqnarray}
+The Virasoro algebra takes the same form as before
+\begin{eqnarray}\begin{aligned}
+L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
+\end{aligned}\end{eqnarray}
+In particular for the conformal boundary state $|B\rangle$, the condition
+\begin{eqnarray}\begin{aligned}
+(L_n-\bar{L}_{-n})|B\rangle=0
+\end{aligned}\end{eqnarray}
+reduces to 
+\begin{eqnarray}\begin{aligned}
+\label{eq:DN_a}
+\text{Dirichlet}&:a_0-\bar{a}_0=0\rightarrow m=0 \\
+\text{Neumann}&:a_0+\bar{a}_0=0\rightarrow n=0
+\end{aligned}\end{eqnarray}
+The conformal boundary state for Dirichlet and Neumann are respectively
+\begin{eqnarray}\begin{aligned}
+\label{eq:DN_state}
+|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
+| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
+\end{aligned}\end{eqnarray}
+It is clear that the desired boundary conditions are satisfied
+\begin{eqnarray}\begin{aligned}
+\phi(x,t=0)|{\rm D} \rangle=\phi_0|{\rm D} \rangle\qquad \partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
+\end{aligned}\end{eqnarray}
+
+\subsection{Winding mode with Gluing Condition}
+\label{app_sub:compact_gluing_boundary}
+We recall that the conformal boundary condition can be written as
+\begin{eqnarray}\begin{aligned}
+\label{eq:def_S_in_app}
+\begin{pmatrix}
+\partial_+\phi^1\\
+\partial_-\phi^2
+\end{pmatrix}
+=S(\theta)
+\begin{pmatrix}
+\partial_-\phi^1\\
+\partial_+\phi^2
+\end{pmatrix}
+\end{aligned}\end{eqnarray}
+where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}.
+We shall specialize to the case $S=S_1$ first.
+The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x\phi^2$ term changes sign, we therefore have
+\begin{eqnarray}\begin{aligned}
+\label{eq:def_S_in_app_2}
+\begin{pmatrix}
+\partial_+\phi^1\\
+\partial_+\phi^2
+\end{pmatrix}
+=S_1(\theta)
+\begin{pmatrix}
+\partial_-\phi^1\\
+\partial_-\phi^2
+\end{pmatrix}
+\end{aligned}\end{eqnarray}
+Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have{\bf\color{red} I will re-check this one}
+\begin{eqnarray}\begin{aligned}
+\label{eq:def_S_in_app_2}
+\sum_{n\in\mathbb{Z}}\begin{pmatrix}
+\bar{a}_n^1\bar{z}^{-n}\\
+\bar{a}_n^2\bar{z}^{-n}
+\end{pmatrix}
+=S_1(\theta)
+\sum_{n\in\mathbb{Z}}
+\begin{pmatrix}
+a_n^1{z}^{-n}\\
+a_n^2{z}^{-n}
+\end{pmatrix}
+\end{aligned}\end{eqnarray}
+{\bf\color{red}The boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$}, therefore we have
+\begin{eqnarray}\begin{aligned}
+a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
+\end{aligned}\end{eqnarray}
+This is clearly a generalization of Dirichlet and Neumann boundary conditions which correspond to Eq.~\eqref{eq:DN_a}.
+We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint {\bf\color{red}check this one in the note}
+\begin{eqnarray}\begin{aligned}
+\label{eq:S_1_constraint}
+\tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
+\end{aligned}\end{eqnarray}
+Thus we conclude that the conformal boundary state reads
+\begin{eqnarray}\begin{aligned}
+g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
+\end{aligned}\end{eqnarray}
+where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}.
+
+{\bf\color{red}comment of S2, g factor}
+
+\subsection{Winding Mode Contribution to the Partition Function}
+\label{app_sub:winding_contribution}
+We are ready to demonstrate that the winding mode will have no contribution to the leading order of $\beta$. We shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
+\begin{eqnarray}\begin{aligned}
+Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
+\end{aligned}\end{eqnarray}
+For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the same boundary state, we have the winding mode contribution as
+\begin{eqnarray}\begin{aligned}
+\label{eq:Z0}
+Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
+\end{aligned}\end{eqnarray}
+In the $\beta\rightarrow\infty$ limit, Eq.~\eqref{eq:Z0} reduces to a simple two dimensional integral
+\begin{eqnarray}\begin{aligned}
+Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
+\end{aligned}\end{eqnarray}
+Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy, and thus negligible.
+
+{\bf\color{red}comment of S2, different boundary state}

### 2017-05-04 free_boson_lattice.tex
[draft]1. Sec.IIA general_formulation nearly done 2. App.F compact boson nearly done 但是写的跟屎一样...学长先别动它... 3. Sec.IIB free_boson_lattice barely started..

{\bf\color{red} Say motivation: in low energy go to CFT}

{\bf\color{red} Say goal: Demonstrate the S matrix is conformal invariance}

### 2017-05-04 general_formulation.tex
[draft]1. Sec.IIA general_formulation nearly done 2. App.F compact boson nearly done 但是写的跟屎一样...学长先别动它... 3. Sec.IIB free_boson_lattice barely started..
[draft] fix one reference error

@@
 \begin{eqnarray}\begin{aligned}
+\label{eq:S1_S2}
 S_1(\theta)=\begin{bmatrix}
@@
 
-{\bf\color{red}As we shall show explicitly in Sec.~\ref{sec: A Free Boson Lattice Model}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.}
+{\bf\color{red}As we shall show explicitly in Sec.~\ref{sec_sub:free_boson_lattice}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.}
 
@@
 \end{equation}
-where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.  {\bf\color{red}say sth}
+where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.  {\bf\color{red}say sth: We shall make use of the above equation extensively. }

### 2017-05-04 compact_boson.tex
[draft] 1. general formulation & App. F almost done. Pass 2. Next I will do free boson lattice and fidelity definition

@@
-{\bf\color{red}Remember to mention in the main text, winding sectors have no contribution}
+\todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
+In this appendix, we address the issue of winding modes of compact bosons. Up to now we have exclusively worked with the oscillator modes of free bosons. 
+%We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculated various partition functions from the boundary state approach in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}.
+We have not talk about the winding mode for compact bosons.
+Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo, at least in the leading order.
+Therefore, the result presented in the main text are ready applied to the case where two compactified bosons of different radii are connected by a conformal interface.
+\todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}
 
-We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculate various partition functions from the boundary state approach in Sec.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}.
-We have not talk about the winding mode for compact bosons.
-In this appendix, we shall show that winding modes will not contribute to the free energy, at least in the leading order.
-In fact the gluing condition in Eq.~\eqref{eq:def_M} can be derived from the variational approach\cite{blumenhagen_introduction_2009,bachas_permeable_2002}, from which it is clear that conformal invariance provides no constraint for the winding mode.
-This is expected since winding is a global property of the boson configuration.
-Thus one needs a general treatment for the winding modes.
-This is first illustrated for the simple cases of Dirichlet and Neumann boundary conditions in Sec.~\ref{app_sub:compact_DN_boundary} and generalized to gluing condition in Sec.~\ref{app_sub:compact_gluing_boundary}.
-We demonstrate that winding mode does not contribute to the free energy in Sec.~\ref{app_sub:winding_contribution}.
+We recall the gluing condition in Eq.~\eqref{eq:def_M} is a constraint from conformal invariance\cite{blumenhagen_introduction_2009,bachas_permeable_2002}, which provides no constraint for the winding modes.
+Indeed, the winding mode is a global property of the boson which is insensitive to the local variations.
+Thus one needs a more general treatment for the compactified bosons.
+This is summarized for the well known cases of Dirichlet and Neumann boundary conditions in App.~\ref{app_sub:compact_DN_boundary} and generalized to gluing condition in App.~\ref{app_sub:compact_gluing_boundary}.
+We demonstrate that winding mode does not contribute to the free energy through boundary state calculation in App.~\ref{app_sub:winding_contribution}.
+Throughout this appendix, the term ``conformal boundary state'' refers to its winding sector exclusively.
 
@@
 \end{aligned}\end{eqnarray}
-where $m$ is the winding number of the field. Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$. Thus the mode expansion reads
+where $m\in\mathbb{Z}$ is the winding number of the field.
+Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$ with $n\in\mathbb{Z}$.
+Thus the mode expansion reads
 \begin{eqnarray}\begin{aligned}
@@
 \phi(x,t)&=\phi_0-\frac{2\pi Rm}{L}x+\frac{\pi_0}{gL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})\\ 
-&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x+i\tau)/L}+\bar{a}_{n}e^{2\pi i n(x-i\tau)/L})
+&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})
 \end{aligned}\end{eqnarray}
@@
 which leads to 
+\todo[inline]{Take care of the format for long equation later, for two columns}
 \begin{eqnarray}\begin{aligned}
 \label{eq:phi_in_z}
-\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln z+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
+\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln \bar{z}+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
 \end{aligned}\end{eqnarray}
@@
 \end{aligned}\end{eqnarray}
-The Virasoro algebra takes the same form as before
+\todo[inline]{I will think about how to say this part}
+{\bf\color{red}
+The Virasoro generators takes the same form as before
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
+}
+
 The conformal boundary state for Dirichlet and Neumann are respectively
@@
 \end{aligned}\end{eqnarray}
-It is clear that the desired boundary conditions are satisfied
+with the desired boundary conditions
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have{\bf\color{red} I will re-check this one}
+Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have
+\todo[inline]{Check this one}
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-This is clearly a generalization of Dirichlet and Neumann boundary conditions which correspond to Eq.~\eqref{eq:DN_a}.
-We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint {\bf\color{red}check this one in the note}
+This is clearly a generalization of Dirichlet and Neumann boundary conditions in Eq.~\eqref{eq:DN_a}.
+We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint
+\todo[inline]{check this one in the note}
 \begin{eqnarray}\begin{aligned}
@@
 where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}.
-
-{\bf\color{red}comment of S2, g factor}
+The g-factor can only be determined by Cardy condition\cite{oshikawa_boundary_2010}.
+Since it is not important for what follows, we shall not repeat the calculation here.
+For the case of $S=S_2$, it is evident that the same calculation can be carried out, and one will arrive at the similar boundary state.
 
@@
 \end{aligned}\end{eqnarray}
-For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the same boundary state, we have the winding mode contribution as
+For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the case of same boundary state $\lambda_1=\lambda_2$, we have the winding mode contribution as
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-In the $\beta\rightarrow\infty$ limit, Eq.~\eqref{eq:Z0} reduces to a simple two dimensional integral
+In the $\beta\rightarrow\infty$ limit, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy, and thus negligible.
+Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy.
+Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.
 
-{\bf\color{red}comment of S2, different boundary state}
+For the case $\lambda_1=\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$.
+The same conclusion still holds in the limit $\beta\rightarrow\infty$.

### 2017-05-04 gnd_dn_lambda.tex
[draft]1. Sec.IIA general_formulation nearly done 2. App.F compact boson nearly done 但是写的跟屎一样...学长先别动它... 3. Sec.IIB free_boson_lattice barely started..
[draft] 1. general formulation & App. F almost done. Pass 2. Next I will do free boson lattice and fidelity definition

@@
 \end{equation}
-As demonstrated in the {\bf\color{red}main text}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
+As demonstrated in the \todo[inline]{main text}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
 \begin{eqnarray}\begin{aligned}
@@
 \end{equation}
-which agrees with the boundary state calculation in Eq.{\bf\color{red}where}
+which agrees with the boundary state calculation in Sec.~\ref{app:lambda_12}.

### 2017-05-05 defect.tex
[file] add defect notes

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathdots}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,decorations.markings,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

\title{Localized (Point) Defect}
\author{Tianci Zhou}
\begin{document}
\maketitle
\large

{\bf Boson Point Defect}

\noindent\rule{\linewidth}{0.4pt}

\underline{Background}: Boson scale invariant defect. Specifically for a continuous free boson field, we impose
\begin{equation}
\partial_t \phi_1 = \frac{1}{\lambda} \partial_t \phi_2 \quad \partial_x \phi_1 = \lambda \partial_x \phi_2 
\end{equation}
where $\phi_1$ and $\phi_2$ are the boundary values of $\phi$ field on the two sides of the defect at $x = 0$. See bCFT notes for details.

\underline{$S$ matrix}: We match the free solution on the two sides
\begin{equation}
\phi_1 = A_{-} e^{i \omega t - i k x } + A_{+} e^{i \omega t + ikx } \quad \phi_2 = B_{-} e^{i \omega t - i k x } + B_{+} e^{i \omega t + ikx }
\end{equation}
which gives
\begin{equation}
\begin{aligned}
- A_{-} + A_{+} =\lambda (  - B_{-} +  B_{+} ) \\
A_{-} + A_{+} = \frac{1}{\lambda} (B_{-} + B_{+}) \\
\end{aligned}
\end{equation}
The $S$ matrix converts the incoming wave to the outgoing wave $\begin{bmatrix} A_{+}\\ B_{-}\\ \end{bmatrix} = S \begin{bmatrix} A_{-}\\ B_{+}\\ \end{bmatrix}$  is 
\begin{equation}
S = 
\begin{bmatrix}
\frac{1 - \lambda^2}{1 + \lambda^2} & \frac{2\lambda }{1 + \lambda^2} \\
\frac{2\lambda }{1 + \lambda^2} & \frac{-1 + \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
 = 
\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & - \cos2  \theta \\
\end{bmatrix}
\quad \text{where } \lambda = \tan \theta 
\end{equation}
\noindent\rule{\linewidth}{0.4pt}

{\bf Harmonic Chain}

We construct the same defect in a discrete model. It corresponds to connecting two chains with different spring constant(rescaling for the compact case in the continuum limit.)

Consider a uniform infinite harmonic chain with a bond defect between site $0$ and $1$,
\begin{equation}
  H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{bmatrix}  \phi_0, \phi_1 \end{bmatrix}
\begin{bmatrix}
1 + \Sigma_{11}  & \Sigma_{12} \\
\Sigma_{21} &  1 + \Sigma_{22} \\
\end{bmatrix}
\begin{bmatrix}
\phi_0 \\
\phi_1 
\end{bmatrix}
\end{equation}
where we parameterize all possible interactions between size $0$ and $1$ with $\Sigma_{ij}$.

The equation of motion is
\begin{equation}
-\frac{d^2}{dt^2} 
\begin{bmatrix}
\vdots\\
\phi_{-1}\\
\phi_0\\
\phi_1\\
\phi_2\\
\vdots 
\end{bmatrix}
 =  
\begin{bmatrix}
\ddots & & & & &\\
-1 & 2 & -1 & & &  \\
&-1 & 2 + \Sigma_{11} & \Sigma_{12} & & &\\ 
& & \Sigma_{21} & 2 + \Sigma_{22} & -1 & &\\
& & & -1 & 2 & -1 & \\
& & & & & \ddots &
\end{bmatrix}
\begin{bmatrix}
\vdots\\
\phi_{-1}\\
\phi_0\\
\phi_1\\
\phi_2\\
\vdots 
\end{bmatrix}
\end{equation}
Again we match the solution between site $\phi_0$ and $\phi_1$ (the $n -1$ in $B$ simplifies the calculation)
\begin{equation}
\phi_n
= \left\lbrace
  \begin{aligned}
    \phi_n^A &= A_{-} e^{i \omega t  - ikn}  + A_{+} e^{i \omega t  + ikn}  & \quad  n \le 0 \\
    \phi_n^B &= B_{-} e^{i \omega t  - ik(n-1)}  + B_{+} e^{i \omega t  + ik(n-1)} & \quad n \ge 1 \\
  \end{aligned} \right. 
 \quad 
\end{equation}
At the junction we have
\begin{equation}
\begin{aligned}
- \phi_{-1}^A + ( 2+ \Sigma_{11} ) \phi_{0}^A + \Sigma_{12} \phi_1^B =  \omega^2 \phi_0^A = - \phi_{-1}^A + 2 \phi_{0}^A - \phi_1^A\\
\Sigma_{21} \phi_0^A + ( 2 + \Sigma_{22}) \phi_1^B - \phi_2^B = \omega^2 \phi_1^B  = - \phi_0^B + 2 \phi_1^B - \phi_2^B 
\end{aligned}
\end{equation}
which simplifies to
\begin{equation}
\begin{aligned}
\Sigma_{11} \phi_0^A + \Sigma_{12} \phi_1^B + \phi_1^A  =0 \\
\Sigma_{21} \phi_0^A + \Sigma_{22} \phi_1^B + \phi_0^B = 0 \\
\end{aligned}
\end{equation}
From the relation of the amplitudes
\begin{equation}
\begin{bmatrix}
\Sigma_{11} + e^{-ik} & \Sigma_{12} \\
\Sigma_{21} & \Sigma_{22}  + e^{-ik}  \\
\end{bmatrix}
\begin{bmatrix}
A_{-} \\
B_{+}\\
\end{bmatrix}
=-
\begin{bmatrix}
\Sigma_{11} +e^{ik} & \Sigma_{12}\\
\Sigma_{21} & \Sigma_{22} + e^{ik}
\end{bmatrix}
\begin{bmatrix}
A_{+}\\
B_{-}\\
\end{bmatrix}
\end{equation}
we solve the $S$ matrix
\begin{equation}
  S = \frac{-1}{ \det \Sigma  + e^{-ik} \text{tr} \Sigma   + e^{-2ik}}
\begin{bmatrix}
\det \Sigma+ \Sigma_{11} e^{-ik} + \Sigma_{22} e^{ik}+1  & -2i \sin k \Sigma_{12}  \\
-2i \sin k \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ik} + \Sigma_{22} e^{-ik}+1\\
\end{bmatrix}
\end{equation}

The magnitudes of the $S$ matrix elements are refection and transmission coefficients. In order to have a scale invariant defect, they need to be $k$ independent. In particular there are two ways to generate $k$ independence of $|S_{12}|$:
\begin{enumerate}
\item $\Sigma_{12} = \Sigma_{21} = 0$, then the $\Sigma$ matrix is diagonal, and 
\begin{equation}
  -S_{11} = \frac{\det \Sigma + \Sigma_{11} e^{-ik} + \Sigma_{22} e^{ik} + 1}{\det \Sigma + \text{tr} \Sigma + e^{-ik} } = \frac{(\Sigma_{11} + e^{ik})(\Sigma_{22} + e^{-ik} ) }{(\Sigma_{11} + e^{-ik})(\Sigma_{22} + e^{-ik} ) }= \frac{\Sigma_{11} + e^{ik} }{\Sigma_{11} + e^{-ik} }
\end{equation}
it is not possible to make the modulus $k$ independent.
\item The determinant is cancels the $\sin k$
\begin{equation}
|e^{-ik} \det \Sigma + \text{tr} \Sigma + e^{-ik } | \sim \sin k \quad \implies \quad \det \Sigma = -1, \, \, \text{tr} \Sigma = 0
\end{equation}
\end{enumerate}
Consequently, the scale invariant $S$ matrix is
\begin{equation}
S = \frac{1}{1 - e^{-2ik } } ( -2i \sin k ) \Sigma
 = - e^{ik} \Sigma
\end{equation}
The phase $e^{ik}$ is the phase difference between neighboring site, which should really be $e^{ika}$ where $a$ is the lattice spacing. Hence in continuum limit, $e^{ik a} \rightarrow 1$,
\begin{equation}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
It corresponds to the potential term $\frac{1}{1+ \lambda^2}( \lambda \phi_0 - \phi_1 ) ^2 $, which is derived by transfer matrix method in \cite{peschel_exact_2012}.

On the other hand, if one of the $\det$ and $\text{tr}$ conditions are not satisfied, then
\begin{equation}
\lim_{a \rightarrow 0 } S = \frac{-1}{\det \Sigma  + \text{tr} \Sigma   + 1}
\begin{bmatrix}
 \det \Sigma+ \Sigma_{11}  + \Sigma_{22} +1  & 0  \\
0 &   \det \Sigma+ \Sigma_{11} + \Sigma_{22} +1 \\
\end{bmatrix} = - I 
\end{equation}
which corresponds to Dirichlet-Dirichlet boundary condition.

\underline{Boundary}

For a boundary at $x =0$, we restrict to the corner of the discrete Laplacian,
\begin{equation}
-\frac{d^2}{dt^2} 
\begin{bmatrix}
\vdots\\
\phi_{-1}\\
\phi_0\\
\end{bmatrix}
=
\begin{bmatrix}
\ddots & & \\
-1 & 2 & -1\\
  &-1 & 2+\Sigma\\
\end{bmatrix}
\begin{bmatrix}
\vdots\\
\phi_{-1}\\
\phi_0\\
\end{bmatrix}
\end{equation}
The discrete equation on the corner is
\begin{equation}
\begin{aligned}
-\phi_{-1}^A + ( 2 + \Sigma ) \phi_0^A  &= \omega^2 \phi_0^A = -\phi_{-1}^A + 2 \phi_0^A  - \phi_1^A \\
\implies \quad \Sigma \phi_0^A + \phi_1^A &= 0 \\
\implies \quad A_{+} &= - \frac{\Sigma + e^{ika}}{ \Sigma + e^{-ika} } A_{-} 
\end{aligned}
\end{equation}
In the long wavelength limit, the boundary conditions will flow to two fixed points
\begin{equation}
S = - \lim_{a\rightarrow 0 } \frac{\Sigma + e^{ika}}{ \Sigma + e^{-ika} } = 
\left\lbrace
\begin{aligned}
  -1 & \quad \Sigma \ne -1  \quad \text{Dirichlet}(\text{fixed point } \Sigma = \pm \infty)\\
   1&  \quad \Sigma =-1 \quad \text{Neumann}\\
\end{aligned} \right. 
\end{equation}

{\bf T-dual Boundary Condition}

There is another type of scale invariant defect, which is the T-dual of the original one, 
\begin{equation}
\partial_t \phi_1 = \lambda \partial_x \phi_2 \quad \partial_x \phi_1 = \frac{1}{\lambda} \partial_t \phi_2 
\end{equation}

\underline{$S$ matrix}: We match the free solution on the two sides
\begin{equation}
\phi_1 = A_{-} e^{i \omega t - i k x } + A_{+} e^{i \omega t + ikx } \quad \phi_2 = B_{-} e^{i \omega t - i k x } + B_{+} e^{i \omega t + ikx }
\end{equation}
which gives
\begin{equation}
\begin{aligned}
i \sigma( A_{-} + A_{+} )  =\lambda  ik (  - B_{-} +  B_{+} ) \\
i\omega( B_{-} + B_{+} ) = \lambda  ik( - A_{-} + A_{+}) \\
\end{aligned}
\end{equation}
Let $\omega = k$, the $S$ matrix converts the incoming wave to the outgoing wave $\begin{bmatrix} A_{+}\\ B_{-}\\ \end{bmatrix} = S \begin{bmatrix} A_{-}\\ B_{+}\\ \end{bmatrix}$  is 
\begin{equation}
S = 
\begin{bmatrix}
\frac{\lambda^2 - 1}{1 + \lambda^2} & \frac{2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{\lambda^2 - 1}{1 + \lambda^2} \\
\end{bmatrix}
 = 
\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & - \cos2  \theta \\
\end{bmatrix}
\quad \text{where } \lambda = \tan \theta 
\end{equation}
which is the $S_2$ in the bCFT notes. \\
\noindent\rule{\linewidth}{0.4pt}

[tentative]
Since time derivative is involved, this is a dynamical boundary condition; we would expect that the Hamiltonian will contain $xp$ term.

A guess would be
\begin{equation}
H = - \lambda \partial_x \phi_1 \pi_2 - - \lambda \partial_x \phi_2 \pi_1
\end{equation}
in this way, the resulting equation of motion will be
\begin{equation}
\partial_t \phi_2  = \lambda \partial_x \phi_1 \quad \partial_t \phi_1  = \lambda \partial_x \phi_2
\end{equation}
and the momentum part upon integration by part (which is not allowed, since this Hamiltonian is at the boundary), 
\begin{equation}
\partial_t \pi_2  = \lambda \partial_x \pi_1 \quad \partial_t \pi_1  = \lambda \partial_x \pi_2
\end{equation}

\bibliographystyle{unsrt}
\bibliography{defect}

\end{document}
%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-05 general_formulation.tex

@@
 We note the following special cases.
-For $\theta=0,\pm\pi/2$, $\lambda$ appears to be singular and the fields on either side of the defect do not communicate to each other.
-For example, $M_1(0)$ implies $\partial_x\phi(0^+)=\partial_t\phi(0^-)=0$.
-For the two CFTs, this corresponds to Dirichlet boundary condition on the left, and Neumann condition on the right.
+For $\theta=0,\pm\pi/2$, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the defect cannot transmit to the other side.
+For example, $M_1(0)$ implies $\partial_x\phi(0^+)=\partial_t\phi(0^-)=0$ which correspond to Dirichlet boundary condition on the left, and Neumann condition on the right.
 Hereafter we shall denote it as `DN'.
 Similarly one can check that $M_1(\pm\pi/2),M_2(0),M_2(\pm\pi/2)$ correspond to ND, NN, DD respectively.
-For $\theta=\pm\pi/4$, on the other hand, characterizes a perfectly transmitting defect.
+For $\theta=\pm\pi/4$, on the other hand, $M(\theta)$ characterizes a perfectly transmitting defect.
 For example, there is effectively no defect in the case $M(\pi/4)$.
 For the other three cases, although the field $\phi$ may pick up a phase across the defect, the two counter propagating waves are still fully transmitted.
+{\bf\color{red} shall we follow permeable wall paper to denote them as PP, etc?
+it is a bit confusing though..}
 
@@
 The scattering matrix $S_1$ and $S_2$ relate the incoming and outgoing waves at the defect.
-For example, $S_1(0)$ implies that $\partial_\pm\phi^{1}=\partial_\pm\phi^{2}$ as discussed above.
+For example, $S_1(0)$ implies that $\partial_\pm\phi^{1}=\pm\partial_\mp\phi^{2}$ as discussed above.
 For other nontrivial values of $\theta$, the defect becomes partially-transmitting.
 The transmission and reflection coefficients, which are determined by $\theta$, can be read off from the scattering matrices.
-
-{\bf\color{red}As we shall show explicitly in Sec.~\ref{sec_sub:free_boson_lattice}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.}
+As we shall show explicitly in Sec.~\ref{sec_sub:free_boson_lattice}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.
 
 The problem of conformal interface can be studied in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984} after we fold the field $\phi^2$ to the left half plane on top of $\phi^1$\cite{oshikawa_boundary_2010}.
-The boundary at $x=0$ is impenetrable for the tensor theory, and there hosts a conformal boundary states for the bosons.
-The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$.
-Therefore the gluing condition in Eq.~\eqref{eq:def_M} with $M_1(\theta)$ reads{\bf\color{red}say why M1?}
+The boundary at $x=0$ becomes impenetrable for the tensor theory, and there hosts a conformal boundary states for the bosons.
+The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, therefore the gluing condition reads
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
+for the case $M=M_1(\theta)$.
 After performing explicit mode expansion for both $\phi^{1,2}$, {\bf\color{red}write down mode expansion, or simply write down the physical meanings of a's as follows?}we have
@@
 \end{equation}
-where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.  {\bf\color{red}say sth: We shall make use of the above equation extensively. }
+where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.
+As one can explicitly check, Eq.~\eqref{eq:bd_state} satisfies the condition for the conformal boundary state\cite{oshikawa_boundary_2010}.
+The calculation for the case $M=M_2(\theta)$ is completely analogue.
+Eq.~\eqref{eq:bd_state} will be the starting point of calculating fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.
+In particular,
+\todo[inline]{say sth: connecting to what will follow etc. }

### 2017-05-07 compact_boson.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

@@
 \todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
-In this appendix, we address the issue of winding modes of compact bosons. Up to now we have exclusively worked with the oscillator modes of free bosons. 
+In this appendix, we address the issue of winding modes of compact bosons. In the main text, we have exclusively worked with the oscillator modes of free bosons. 
 %We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculated various partition functions from the boundary state approach in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}.
@@
 Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo, at least in the leading order.
-Therefore, the result presented in the main text are ready applied to the case where two compactified bosons of different radii are connected by a conformal interface.
+Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.
 \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}
@@
 \begin{eqnarray}\begin{aligned}
-a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\frac{mR}{2}
+a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)
 \end{aligned}\end{eqnarray}
@@
 \end{aligned}\end{eqnarray}
-\todo[inline]{I will think about how to say this part}
-{\bf\color{red}
-The Virasoro generators takes the same form as before
-\begin{eqnarray}\begin{aligned}
-L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
-\end{aligned}\end{eqnarray}
-In particular for the conformal boundary state $|B\rangle$, the condition
-\begin{eqnarray}\begin{aligned}
-(L_n-\bar{L}_{-n})|B\rangle=0
-\end{aligned}\end{eqnarray}
-reduces to 
+%The Virasoro generators takes the same form as before
+%\begin{eqnarray}\begin{aligned}
+%L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
+%\end{aligned}\end{eqnarray}
+%In particular for the conformal boundary state $|B\rangle$, the condition
+%\begin{eqnarray}\begin{aligned}
+%(L_n-\bar{L}_{-n})|B\rangle=0
+%\end{aligned}\end{eqnarray}
+
+$a_0$ and $\bar{a}_0$ are not independent for the conformal boundary states. It turns out that from the Virasoro generators, one can deduce that
 \begin{eqnarray}\begin{aligned}
 \label{eq:DN_a}
-\text{Dirichlet}&:a_0-\bar{a}_0=0\rightarrow m=0 \\
-\text{Neumann}&:a_0+\bar{a}_0=0\rightarrow n=0
+\text{Dirichlet}&:a_0-\bar{a}_0=0\\
+\text{Neumann}&:a_0+\bar{a}_0=0
 \end{aligned}\end{eqnarray}
-}
-
-The conformal boundary state for Dirichlet and Neumann are respectively
+Therefore, the conformal boundary state for Dirichlet and Neumann are respectively
 \begin{eqnarray}\begin{aligned}
 \label{eq:DN_state}
-|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
-| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
+|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
+| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
 \end{aligned}\end{eqnarray}
@@
 \end{aligned}\end{eqnarray}
+We have included the oscillator part in Eq.~\eqref{eq:DN_state}, with the vacuum being a linear combination of different winding sectors.
+In the following sections, the oscillator part will be the same, and we shall write down only the vacuum which is subject to the more general gluing condition.
 
@@
 \label{app_sub:compact_gluing_boundary}
+
+\todo[inline]{Say the caveat, where is the bounadry}
+
 We recall that the conformal boundary condition can be written as
@@
 Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have
-\todo[inline]{Check this one}
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-{\bf\color{red}The boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$}, therefore we have
+As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
 \begin{eqnarray}\begin{aligned}
@@
 We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint
-\todo[inline]{check this one in the note}
 \begin{eqnarray}\begin{aligned}
@@
 \label{app_sub:winding_contribution}
-We are ready to demonstrate that the winding mode will have no contribution to the leading order of $\beta$. We shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
+In order to demonstrate that the winding mode will have no contribution to the leading order of $\beta$, we shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-In the $\beta\rightarrow\infty$ limit, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
+In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
 \begin{eqnarray}\begin{aligned}
@@
 
-For the case $\lambda_1=\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$.
+For the case $\lambda_1\neq\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$.
 The same conclusion still holds in the limit $\beta\rightarrow\infty$.

### 2017-05-07 free_boson_lattice.tex
[draft] 1. general formulation & App. F almost done. Pass 2. Next I will do free boson lattice and fidelity definition
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

@@
-{\bf\color{red} Say motivation: in low energy go to CFT}
+In this section, we consider a lattice model with bosonic defect at the center, which reduces to the one considered in Sec.~\ref{sec_sub:general_formulation} in the continuum limit\cite{calabrese_entanglement_2012}.
+Therefore, it serves as a numerical tool to check our analytic results in Sec.~\ref{sec:analytic_numerics}.
+Despite its simpleness, such discrete bosonic defect can be considered in more general quadratic bosonic\cite{PhysRevA.74.022329}, or fermionic\cite{PhysRevB.64.064412} systems.
+It also sheds light on the possible application of our CFT results in condensed matter experiments\cite{Rohringer2015,Trotzky2012}.
 
-{\bf\color{red} Say goal: Demonstrate the S matrix is conformal invariance}
+\todo[inline]{Remove the citations if not relevant...}
+
+We imagine connecting two coupled harmonic chains, which consists in total $2n$ coupled harmonic oscillators labeled by $\left\{\phi_{-n+1},...,\phi_0,\phi_1,...,\phi_n\right\}$.
+There is a bond defect between site $0$ and $1$, and the Hamiltonian reads
+\begin{eqnarray}\begin{aligned}
+H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\begin{bmatrix}
+1 + \Sigma_{11}  & \Sigma_{12} \\
+\Sigma_{21} &  1 + \Sigma_{22} \\
+\end{bmatrix}
+\begin{pmatrix}
+\phi_0 \\
+\phi_1 
+\end{pmatrix}
+\end{aligned}\end{eqnarray}
+where $\pi_i$ is the conjugate momentum.
+Later we shall see the matrix $\Sigma_{ij}$ is related to the scattering matrix in Sec.~\ref{sec_sub:general_formulation}, and thus characterizes all possible bosonic defects discussed there.
+
+It is straightforward to write down the ansatz for this quantum mechanical problem, (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
+\begin{equation}
+\label{eq:ansatz}
+\phi_n
+= \left\lbrace
+  \begin{aligned}
+    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
+    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
+  \end{aligned} \right. 
+ \quad 
+\end{equation}
+where $a$ is the lattice constant. The dispersion of the system reads
+\begin{eqnarray}\begin{aligned}
+\label{eq:dispersion}
+\omega=\left|2\sin\frac{k}{2}\right|
+\end{aligned}\end{eqnarray}
+which implies the system is gapless.
+The defect will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
+Upon plugging Eq.~\eqref{eq:ansatz}-\eqref{eq:dispersion} into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
+\begin{equation}
+\label{eq:discrete_S}
+\begin{bmatrix}
+\Sigma_{11} + e^{-ik} & \Sigma_{12} \\
+\Sigma_{21} & \Sigma_{22}  + e^{-ik}  \\
+\end{bmatrix}
+\begin{pmatrix}
+A_{-} \\
+B_{+}\\
+\end{pmatrix}
+=-
+\begin{bmatrix}
+\Sigma_{11} +e^{ik} & \Sigma_{12}\\
+\Sigma_{21} & \Sigma_{22} + e^{ik}
+\end{bmatrix}
+\begin{pmatrix}
+A_{+}\\
+B_{-}\\
+\end{pmatrix}
+\end{equation}
+and the scattering matrix can be solved as
+\begin{equation}
+  S = \frac{-1}{ \det \Sigma  + e^{-ik} \text{tr} \Sigma   + e^{-2ik}}
+\begin{bmatrix}
+\det \Sigma+ \Sigma_{11} e^{-ik} + \Sigma_{22} e^{ik}+1  & -2i \sin k \Sigma_{12}  \\
+-2i \sin k \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ik} + \Sigma_{22} e^{-ik}+1\\
+\end{bmatrix}
+\end{equation}
+It is clear that Eq.~\eqref{eq:discrete_S} is a discrete analogue of Eq.~\eqref{eq:def_S}, with momentum dependence.
+The necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$.
+This implies
+\begin{equation}
+\label{eq:Sigma_condition}
+\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
+\end{equation}
+Therefore, we have the scale invariant S-matrix as
+\begin{equation}
+S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
+ = - e^{ika} \Sigma
+\end{equation}
+In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
+\begin{equation}
+\Sigma = -\lim_{a \rightarrow 0 } S = 
+\begin{bmatrix}
+\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
+\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
+\end{bmatrix}
+\end{equation}
+in accordance to Eq.~\eqref{eq:Sigma_condition}.
+
+{\bf\color{red}
+Say in the continuum limit, what happens
+
+say in the long time, what happens?
+
+say the special case in the boundary
+}
+
+This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.

### 2017-05-07 general_formulation.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

@@
 \end{aligned}\end{eqnarray}
-The interface is assumed to be penetrable.
-Instead of requiring the normal components of the stress tensor to vanish\cite{cardy_conformal_1984}, one only needs the stress tensor to be continuous across the defect.
+The interface is assumed to be penetrable, and the stress tensor is continuous across the defect.
 From the explicit expression of the stress tensor $T^{xt}=-\partial_x\phi\partial_t\phi$, one can show that\cite{bachas_permeable_2002} $M$ is an element of the Lorentz group $O(1,1)$.
@@
 For the other three cases, although the field $\phi$ may pick up a phase across the defect, the two counter propagating waves are still fully transmitted.
-{\bf\color{red} shall we follow permeable wall paper to denote them as PP, etc?
-it is a bit confusing though..}
+\todo[inline]{shall we follow permeable wall paper to denote them as PP, etc? it is a bit confusing though..}
 
@@
 For clarity, we denote the field on the negative (positive) real axis as $\phi^1$ ($\phi^2$).
-{\bf\color{red}Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}.
+\todo[inline]{Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}
 After some algebra, we have
@@
 For example, $S_1(0)$ implies that $\partial_\pm\phi^{1}=\pm\partial_\mp\phi^{2}$ as discussed above.
-For other nontrivial values of $\theta$, the defect becomes partially-transmitting.
-The transmission and reflection coefficients, which are determined by $\theta$, can be read off from the scattering matrices.
-As we shall show explicitly in Sec.~\ref{sec_sub:free_boson_lattice}, the scattering matrices are independent of the wavelengths, as required by the scale invariance.
+For other nontrivial values of $\theta$, the defect becomes partially-transmitting, and the transmission and reflection coefficients can be read off from the scattering matrices.
+In particular, these coefficients depend only on the parameter $\theta$ of the defect, not on the wavelength of the incoming wave, which is in contrast to the case in mesoscopic system.\cite{datta_1995} This is expected due to the scale invariance.
 
 The problem of conformal interface can be studied in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984} after we fold the field $\phi^2$ to the left half plane on top of $\phi^1$\cite{oshikawa_boundary_2010}.
-The boundary at $x=0$ becomes impenetrable for the tensor theory, and there hosts a conformal boundary states for the bosons.
+The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary states for the bosons.
 The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, therefore the gluing condition reads
@@
 \end{aligned}\end{eqnarray}
-for the case $M=M_1(\theta)$.
-After performing explicit mode expansion for both $\phi^{1,2}$, {\bf\color{red}write down mode expansion, or simply write down the physical meanings of a's as follows?}we have
+for the case $M=M_1(\theta)$. After performing explicit mode expansion for both $\phi^{1,2}$, we have
 \begin{eqnarray}\begin{aligned}
@@
 The calculation for the case $M=M_2(\theta)$ is completely analogue.
-Eq.~\eqref{eq:bd_state} will be the starting point of calculating fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.
-In particular,
-\todo[inline]{say sth: connecting to what will follow etc. }
+Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.
+
+\todo[inline]{say sth: connecting to what will follow etc? }

### 2017-05-07 gnd_dn_lambda.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later

@@
 \end{equation}
-As demonstrated in the \todo[inline]{main text}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
+As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
 \begin{eqnarray}\begin{aligned}
-\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2} \quad \theta \in \left[0,\frac{\pi}{2} \right]
+\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2}, \quad \theta \in \left[0,\frac{\pi}{2} \right]
 \end{aligned}\end{eqnarray}
@@
 \label{eq:momentum_gnd_dn_lambda}
-k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right)  \quad n\in\mathbb{Z}
+k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right),  \quad n\in\mathbb{Z}
 \end{equation}
@@
 It is clear that the normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in mode expansion.
-Following the same procedure in \onlinecite{di_francesco_conformal_1997}, we have the Hamiltonian as
+Following the same procedure in Ref.~\onlinecite{di_francesco_conformal_1997}, we have the Hamiltonian as
 \begin{equation}

### 2017-05-08 free_boson_lattice.tex
[draft] general formulation revision 1 free boson lattice -> appendix?

--- 2017-05-04 free_boson_lattice.tex
@@
-{\bf\color{red} Say motivation: in low energy go to CFT}
+In this section, we consider a lattice model with bosonic interface at the center\cite{peschel_exact_2012,calabrese_entanglement_2012}, which reduces to the one considered in Sec.~\ref{sec_sub:general_formulation} in the continuum limit\cite{sakai_entanglement_2008}.
+Therefore, it serves as a numerical tool to check our analytic results in Sec.~\ref{sec:analytic_numerics}.
 
-{\bf\color{red} Say goal: Demonstrate the S matrix is conformal invariance}
+% Despite its simpleness, such discrete bosonic defect can be considered in more general quadratic bosonic\cite{PhysRevA.74.022329}, or fermionic\cite{PhysRevB.64.064412} systems.
+It also sheds light on the possible application of our CFT results in condensed matter experiments\cite{Rohringer2015,Trotzky2012}.
+
+\todo[inline]{I think the reference cited here are irrelevant.}
+
+We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
+\begin{eqnarray}\begin{aligned}
+H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\begin{bmatrix}
+1 + \Sigma_{11}  & \Sigma_{12} \\
+\Sigma_{21} &  1 + \Sigma_{22} \\
+\end{bmatrix}
+\begin{pmatrix}
+\phi_0 \\
+\phi_1 
+\end{pmatrix}
+\end{aligned}\end{eqnarray}
+where the matrix $\Sigma$ parameterize two-site interaction.
+In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.
+
+\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$.
+In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}
+
+To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
+\begin{equation}
+\label{eq:ansatz}
+\phi_n
+= \left\lbrace
+  \begin{aligned}
+    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
+    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
+  \end{aligned} \right. 
+ \quad 
+\end{equation}
+where $a$ is the lattice constant.
+The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless.
+The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
+Upon plugging Eq.~\eqref{eq:ansatz}-\eqref{eq:dispersion} into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
+\begin{equation}
+\label{eq:discrete_S}
+\begin{pmatrix}
+A_{-} \\
+B_{+}\\
+\end{pmatrix}
+=-
+\begin{bmatrix}
+\Sigma_{11} + e^{-ika} & \Sigma_{12} \\
+\Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
+\end{bmatrix}^{-1}
+\begin{bmatrix}
+\Sigma_{11} +e^{ika} & \Sigma_{12}\\
+\Sigma_{21} & \Sigma_{22} + e^{ika}
+\end{bmatrix}
+\begin{pmatrix}
+A_{+}\\
+B_{-}\\
+\end{pmatrix}
+\end{equation}
+and the scattering matrix can be solved as
+\begin{equation}
+  S = \frac{-1}{ \det \Sigma  + e^{-ika} \text{tr} \Sigma   + e^{-2ika}}
+\begin{bmatrix}
+\det \Sigma+ \Sigma_{11} e^{-ika} + \Sigma_{22} e^{ika}+1  & -2i \sin ka \Sigma_{12}  \\
+-2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
+\end{bmatrix}
+\end{equation}
+A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
+\begin{equation}
+\label{eq:Sigma_condition}
+\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
+\end{equation}
+Therefore, we have the scale invariant S-matrix as
+\begin{equation}
+S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
+ = - e^{ika} \Sigma
+\end{equation}
+In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
+\begin{equation}
+\Sigma = -\lim_{a \rightarrow 0 } S = 
+\begin{bmatrix}
+\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
+\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
+\end{bmatrix}
+\end{equation}
+in accordance to Eq.~\eqref{eq:Sigma_condition}.
+
+{\bf\color{red}
+Say in the continuum limit, what happens
+
+say in the long time, what happens?
+
+say the special case in the boundary
+}
+
+This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-08 general_formulation.tex
[draft] general formulation revision 1 free boson lattice -> appendix?

@@
-We consider a conformal interface connecting two potentially different CFTs in $1+1$ dimensions. The interface is located at $x=0$ and characterized by the ``gluing condition''
+The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous.
+An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other.
+The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends here.
+This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}.
+In the Boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.
+
+There are however many successful attempts to construct a subset of those bosonic boundary states.
+One way to do is to impose current operator rather than Virasolo generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+Other example utilizes the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.
+
+We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantize it give the boundary state.
+The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.
+
+Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the "gluing condition"
+
+\todo[inline]{Mao: I put $\partial_t$ on the top in my notes. The 'DN' 'ND' convention seems to be wrong here. I'll think about it.}
 \begin{eqnarray}\begin{aligned}
@@
 \begin{pmatrix}
-\partial_x\phi\\
-\partial_t\phi
-\end{pmatrix}_{x=0^-}
+\partial_t\phi^1\\
+\partial_x\phi^1
+\end{pmatrix}
 =M\begin{pmatrix}
-\partial_x\phi\\
-\partial_t\phi
-\end{pmatrix}_{x=0^+}
+\partial_t\phi^2\\
+\partial_x\phi^2
+\end{pmatrix}
 \end{aligned}\end{eqnarray}
-The interface is assumed to be penetrable, and the stress tensor is continuous across the defect.
-From the explicit expression of the stress tensor $T^{xt}=-\partial_x\phi\partial_t\phi$, one can show that\cite{bachas_permeable_2002} $M$ is an element of the Lorentz group $O(1,1)$.
-In terms of the boost parametrization, we have
+where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
+As argued, the momentum component of stress tensor is continuous across the interface.
+As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
 \begin{eqnarray}\begin{aligned}
@@
 
-We note the following special cases.
-For $\theta=0,\pm\pi/2$, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the defect cannot transmit to the other side.
-For example, $M_1(0)$ implies $\partial_x\phi(0^+)=\partial_t\phi(0^-)=0$ which correspond to Dirichlet boundary condition on the left, and Neumann condition on the right.
-Hereafter we shall denote it as `DN'.
-Similarly one can check that $M_1(\pm\pi/2),M_2(0),M_2(\pm\pi/2)$ correspond to ND, NN, DD respectively.
-For $\theta=\pm\pi/4$, on the other hand, $M(\theta)$ characterizes a perfectly transmitting defect.
-For example, there is effectively no defect in the case $M(\pi/4)$.
-For the other three cases, although the field $\phi$ may pick up a phase across the defect, the two counter propagating waves are still fully transmitted.
-\todo[inline]{shall we follow permeable wall paper to denote them as PP, etc? it is a bit confusing though..}
+Several special choice of $\theta$ need to be noted. 
+\begin{enumerate}
+\item $\theta=0,\pm \frac{\pi}{2}$.
+In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the defect cannot transmit to the other side, so the interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
+For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition are imposed on the right and Neumann boundary condition on the left.
+Hereafter we shall denote this combination as 'DN'.
+Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to DN, DD, NN respectively.
+\item $\theta = \pm \frac{\pi}{4}$.
+In this case, $M(\theta)$ characterizes a perfectly transmitting defect.
+For example, there is effectively no defect in the case $M( \frac{\pi}{4})$.
+For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
+\end{enumerate}
 
-It proves useful to rewrite Eq.~\eqref{eq:def_M} in the ``light cone'' coordinate $x^\pm\equiv t\pm x$, where the physical meaning of $\theta$ is most transparent.
-For clarity, we denote the field on the negative (positive) real axis as $\phi^1$ ($\phi^2$).
-\todo[inline]{Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}
-After some algebra, we have
+The physical significance of $\theta$ will be manifest in the scattering process described below.
+We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ derivative to extract the left and right going modes.
+For example, $\partial_{-} \phi^2$ will be a function $t - x$ only and hence represent a right going mode on the right half plane.
+It is then one of the scattering products that leave the interface.
+On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain.
+We therefore establish the scattering relation
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-where 
+
+\todo[inline]{Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}
+and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-The scattering matrix $S_1$ and $S_2$ relate the incoming and outgoing waves at the defect.
-For example, $S_1(0)$ implies that $\partial_\pm\phi^{1}=\pm\partial_\mp\phi^{2}$ as discussed above.
-For other nontrivial values of $\theta$, the defect becomes partially-transmitting, and the transmission and reflection coefficients can be read off from the scattering matrices.
-In particular, these coefficients depend only on the parameter $\theta$ of the defect, not on the wavelength of the incoming wave, which is in contrast to the case in mesoscopic system.\cite{datta_1995} This is expected due to the scale invariance.
+\todo[inline]{Mao: please do not interchangably use defect or interface. We use interface throughout the text.}
+For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices.
+The fact of their wavelength independence is an indication of the interface's scale invariance.
 
-The problem of conformal interface can be studied in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984} after we fold the field $\phi^2$ to the left half plane on top of $\phi^1$\cite{oshikawa_boundary_2010}.
-The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary states for the bosons.
-The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, therefore the gluing condition reads
+We now work in the folding picture as shown in Fig.{\color{red} TODO}.
+The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary state.
+The folding sends $\phi^2(x)$ to $\phi^2(-x)$ and hence the gluing condition becomes
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-for the case $M=M_1(\theta)$. After performing explicit mode expansion for both $\phi^{1,2}$, we have
+for the case $M=M_1(\theta)$.
+
+If we quantize the Boson theory on the interface line $x = 0$, these gluing condition becomes an operator identity for the Boson creation and annihilation of the modes.
+We shall interpret these identities to be valid only when acting on the boundary states.
+The mode expansion of free Boson on $x = 0$\cite{di_francesco_conformal_1997} is
+\begin{equation}
+\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^n - \bar{a}_{-n } \bar{z}^{-n}   \right)
+\end{equation}
+where take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
+\begin{equation}
+z= e^{ 2\pi ( i\tau - x ) / T } \quad \bar{z} = e^{ -2\pi ( i\tau + x ) / T }
+\end{equation}
+We end up with a set of operator identities for each mode
 \begin{eqnarray}\begin{aligned}
@@
 \end{aligned}\end{eqnarray}
-where $n>0$ is an integer.
-$a_n^{1,2}$ ($\bar{a}_n^{1,2}$) annihilate the left (right)-moving modes of $\phi^{1,2}$, and $a_{-n}^{1,2}$ ($\bar{a}_{-n}^{1,2}$) are the corresponding creation operators.
-Eq.~\eqref{eq:rotation_a_basis} is essentially a rotation of basis, and the conformal boundary state reads\cite{oshikawa_boundary_2010}
+which is valid on the following boundary state
 \begin{equation}
@@
 \end{pmatrix}
-S_1
+S_1( \theta )
 \begin{pmatrix}
@@
 \end{equation}
-where $S^1$ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.
-As one can explicitly check, Eq.~\eqref{eq:bd_state} satisfies the condition for the conformal boundary state\cite{oshikawa_boundary_2010}.
-The calculation for the case $M=M_2(\theta)$ is completely analogue.
+where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.
+The calculation for the case $M=M_2(\theta)$ is completely analogous.
 Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.
@@
 \todo[inline]{say sth: connecting to what will follow etc? }
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-08 free_boson_lattice.tex
[draft] fix reference error

@@
 The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
-Upon plugging Eq.~\eqref{eq:ansatz}-\eqref{eq:dispersion} into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
+Upon plugging ansatz and dispersion relation into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
 \begin{equation}

### 2017-05-08 analy_eval.tex
[draft] combine the introduction of fidelity and loschmidt echo with the numerical and analytic results. Write a draft for this section.

In this subsection, we will demonstrate that the diagrams drawn in the last subsections are all related to the amplitudes between boundary states.

We notice that there is only one apparent length scale in these diagram: in the case of fidelity it is the finite size $L$ for fidelity and $\tau$ for Loschmidt echo. In the absence of the regulators, the conformal invariance can rescale them to $1$ by doing a conformal transformation, thus getting rid of their dependences. Therefore, regulator is necessary in keeping track of the scale dependence in doing the conformal transformation. This is also required by the lattice realization of the systems.

We work in the folding picture, add small semi-circles to the point where the boundary condition changing operator resides. For the fidelity case, the conformal mapping is depicted in Fig.~\ref{fig:fidel-map} 
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
If the three boundary conditions $a, b, c$ are all different, then there are two boundary condition changing operators on the real axis. We focus on the one where $a = c$. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line are then regarded as two boundary states. The imaginary time evolution is performed in the angular direction and the partition function we are looking for is
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
\end{equation}

The Loschmidt echo can also be evaluated the same way. We therefore introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform a series conformal transformation as shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{fig_H-tau_fold}
\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice). Middle: image of the map $\xi = \frac{z}{\tau - z}$. Right: image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and standard radial quantization can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One should however notice that in performing the conformal transformation, we have introduced shifts in free energy. In fact, the free energy in the boundary state calculation gives a positive exponent, meaning a power law increase of the fidelity and echo, which does not make sense. We inspect the shifts in App.~\ref{app:F_correction}, generally speaking it comes from the Schwartzian term and the regulator.

The amplitude between different boundary states can be computed by the technique presented in App.~\ref{app:lambda_12} and App.~\ref{app:gnd_dn_lambda}, where we set the width of the cylinder to be $\beta$. Adding back the correction in App.~\ref{app:F_correction}, the final result is
\begin{equation}
 - \ln Z_{ab }( \beta ) + \frac{1}{6} \beta 
\end{equation}
where $a,b$ denotes different boundary condition (including the $\lambda$ junction) and $\beta = 2 \ln L$ or  $ 4 \ln \tau$ in the fidelity and echo.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-08 def_fidel_echo.tex
[draft] combine the introduction of fidelity and loschmidt echo with the numerical and analytic results. Write a draft for this section.

Bipartite fidelity is the overlap of the groundstates of two Hamiltonians. In the path integral language, the groundstates can be produced by imaginary time evolution. If we take the horizontal axis as the Euclidean time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}. Treating it as a partition function, we analyze its finite size dependence on the total chain size $L$. The logarithmic fidelity should then follow the general discussion of Cardy and Peschel\cite{cardy_finite-size_1988} of the finite size dependence of free energy and give a term proportional to $\ln L$
\begin{equation}
\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z  \sim  \ln L 
\end{equation}
The proportionality constant is the exponent characterizing the interface.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_fidel.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution on the two infinitely extended side produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundary are now boundary states.}
\label{fig:fidel}
\end{figure}

\todo[inline]{echo diagram folding}

The Loschmidt echo is defined to be defined as the overlap of the ground state and the quenched states, 
\begin{equation}
\mathcal{L} = |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2
\end{equation}
We have drawn the path integral definition of this quantity in Fig.~\ref{fig:cut-and-join}; for convenience of the latter conformal mapping, we turn the diagram by a right angle and take the horizontal axis as time. The slits represents disconnected boundary conditions like Dirichlet and Neumann, the dashed line represent partially transmitting boundary condition parameterized by $\lambda$. We may as well fold the lower half plane up and everything on the real axis should be regarded as boundary states. Again by Cardy and Peschel\cite{cardy_finite-size_1988}, the logarithm of the Loschmidt echo is the free energy and should have logarithmic dependence on the characterizing length scale in the problem. In other words
\begin{equation}
\mathcal{L} = - \ln |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2 \propto \ln \tau 
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-10 analy_eval.tex
[draft] definition and analytic results draft 1

@@
-In this subsection, we will demonstrate that the diagrams drawn in the last subsections are all related to the amplitudes between boundary states.
+In this subsection, we relate the free energy to the amplitudes between boundary states and give analytic results.
 
-We notice that there is only one apparent length scale in these diagram: in the case of fidelity it is the finite size $L$ for fidelity and $\tau$ for Loschmidt echo.
-In the absence of the regulators, the conformal invariance can rescale them to $1$ by doing a conformal transformation, thus getting rid of their dependences.
-Therefore, regulator is necessary in keeping track of the scale dependence in doing the conformal transformation.
-This is also required by the lattice realization of the systems.
+We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo.
+These are the characteristic size of the corner at the tip of the slit.
+However, without regulators the conformal invariance can rescale both to $1$ by doing a dilation transformation, thus getting rid of their dependence.
+Therefore, regulators are necessary in keeping track of the scale dependence and also physically sensible considering the lattice realization of the systems.
 
-We work in the folding picture, add small semi-circles to the point where the boundary condition changing operator resides.
-For the fidelity case, the conformal mapping is depicted in Fig.~\ref{fig:fidel-map}
+We thus add small semi-circles around the points where the boundary condition changing operator resides and then do a series of conformal mapping.
+
+For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map} 
 \begin{figure}[h]
@@
 \end{figure}
-If the three boundary conditions $a, b, c$ are all different, then there are two boundary condition changing operators on the real axis.
-We focus on the one where $a = c$.
-The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
+We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
 \begin{equation}
@@
 \end{equation}
-The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $.
+The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $.
 Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
-The dashed line and solid line are then regarded as two boundary states.
-The imaginary time evolution is performed in the angular direction and the partition function we are looking for is
+The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function
 \begin{equation}
@@
 
-The Loschmidt echo can also be evaluated the same way.
-We therefore introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform a series conformal transformation as shown in Fig.~\ref{fig:H-tau_fold}.
+The Loschmidt echo can be evaluated the same way.
+Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
 In the $\xi$ plane, we end with the same diagram as fidelity.
@@
 
-One should however notice that in performing the conformal transformation, we have introduced shifts in free energy.
-In fact, the free energy in the boundary state calculation gives a positive exponent, meaning a power law increase of the fidelity and echo, which does not make sense.
-We inspect the shifts in App.~\ref{app:F_correction}, generally speaking it comes from the Schwartzian term and the regulator.
+The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$.
+But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation.
+In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law increase of Loschmidt echo, which does not agree with the known results.
+One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence
+\begin{equation}
+\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta 
+\end{equation}
+where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$.
+A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.
 
-The amplitude between different boundary states can be computed by the technique presented in App.~\ref{app:lambda_12} and App.~\ref{app:gnd_dn_lambda}, where we set the width of the cylinder to be $\beta$.
-Adding back the correction in App.~\ref{app:F_correction}, the final result is
+For the process ($c$ is assumed to be the same as $a$)
 \begin{equation}
- - \ln Z_{ab }( \beta ) + \frac{1}{6} \beta 
+S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
 \end{equation}
-where $a,b$ denotes different boundary condition (including the $\lambda$ junction) and $\beta = 2 \ln L$ or  $ 4 \ln \tau$ in the fidelity and echo.
+the free energy is
+\begin{equation}
+\mathcal{F}( \beta )  = 
+\left\lbrace
+\begin{aligned}
+  &\frac{1}{2}(-|x| + x^2 )\beta  \quad &i = j \\
+  &\frac{1}{16}\beta   \quad &i \ne j   \\
+\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} 
+\end{equation}
+We can then read off the fidelity and Loschmidt echo power law decay exponent with the identification $\beta = 2 \ln L$ and $ 4 \ln \tau$.
 

### 2017-05-10 bd_notation.tex
[draft] definition and analytic results draft 1

We use chemical reaction equation style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~{\color{red} TODO}, there are three boundary conditions $a,b,c$ in the folding picture, which represents status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition form the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) 
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we usually take $a = c$ in the numerical calculation.

In the "cut-and-join" protocol we considered, $a$ should be one of 'DD', 'DN', 'ND', 'NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of the boundary condition. For instance, the notation for the process presented in Fig.~{\color{red} TODO} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} 
\end{equation}
The scaling dimension of this bcc operator does indeed deviate from the completely transmitting case for certain choice of boundary conditions.

Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-10 def_fidel_echo.tex
[draft] definition and analytic results draft 1

@@
-Bipartite fidelity is the overlap of the groundstates of two Hamiltonians.
-In the path integral language, the groundstates can be produced by imaginary time evolution.
-If we take the horizontal axis as the Euclidean time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}.
-Treating it as a partition function, we analyze its finite size dependence on the total chain size $L$.
-The logarithmic fidelity should then follow the general discussion of Cardy and Peschel\cite{cardy_finite-size_1988} of the finite size dependence of free energy and give a term proportional to $\ln L$
+In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams.
+It will then be evident that these quantities are just the free energy of Boson with conformal interfaces (or boundaries).
+
+Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
 \begin{equation}
-\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z  \sim  \ln L 
+{\rm fidelity} = |\langle \psi_1 |\psi_2  \rangle |^2 
 \end{equation}
-The proportionality constant is the exponent characterizing the interface.
+For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal defect.
+Both of them can be produced by the imaginary time evolution.
+Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
+The logarithmic fidelity is then (twice) the free energy of this diagram
+\begin{equation}
+\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z
+\end{equation}
 
@@
 \centering
-\includegraphics[width=\textwidth]{fig_fidel.pdf}
+\includegraphics[width=0.8\textwidth]{fig_fidel.pdf}
 \caption{Fidelity of connecting two CFTs.
@@
 
-The Loschmidt echo is defined to be defined as the overlap of the ground state and the quenched states, 
+The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
+One of the them the groundstate of the disconnected chain and the other is groundstate evolved by the connected chain Hamiltonian
 \begin{equation}
-\mathcal{L} = |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2
+\mathcal{L} = |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
 \end{equation}
-We have drawn the path integral definition of this quantity in Fig.~\ref{fig:cut-and-join}; for convenience of the latter conformal mapping, we turn the diagram by a right angle and take the horizontal axis as time.
-The slits represents disconnected boundary conditions like Dirichlet and Neumann, the dashed line represent partially transmitting boundary condition parameterized by $\lambda$.
-We may as well fold the lower half plane up and everything on the real axis should be regarded as boundary states.
-Again by Cardy and Peschel\cite{cardy_finite-size_1988}, the logarithm of the Loschmidt echo is the free energy and should have logarithmic dependence on the characterizing length scale in the problem.
-In other words
+The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~{\color{red} TODO}.
+Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt is also the associated the free energy.
+
+If the interface is completely transparent, i.e.
+at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
+One would expect the fidelity and echo to have power law decay patter with respective to these scales in the long wavelength limit.
+In fact, such kind of computation has been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration.
+If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
 \begin{equation}
-\mathcal{L} = - \ln |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2 \propto \ln \tau 
+\label{eq:full-pass}
+\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
 \end{equation}
+
+The tip of the slit is no longer a twist field with presence of the conformal interface.
+Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and {\color{red} TODO} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
+From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator.
+These diagrams then becomes the one and two point functions of the bcc operators and the free energy logarithmic term extracts their scaling dimensions.
 

### 2017-05-11 F_correction.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
-\todo[inline]{cite main text figure for conformal transformation}
-In the course of derivation the free energy subject to various boundary conditions, we use conformal transformation to convert the space time diagram with slits to a cylinder diagram, where the boundary state (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable.
-However, free energy, especially its constant part, is not invariant under the conformal transformation, because the boundaries partially break the conformal symmetry.
-In this Appendix, we point out two corrections -- one from the outer boundary and the other from the inhomogeneous Schwartzian term -- to get the correct exponent of the fidelity and Loschmidt echo.
+In the course of derivation the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable.
+However, free energy is not invariant under the conformal transformation, because the boundaries partially break the conformal symmetry.
+In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term -- to get the correct exponent of the fidelity and Loschmidt echo.
 
 % outer boundary correction
-It is discussed in the pioneering work\cite{cardy_finite-size_1988} by Cardy and Peschel that boundary will contribute logarithmic term, which manifest itself as the geodesic curvature integral in the trace anomaly.
-Here we demonstrate this principle using the disk free energy example in Ref.~\cite{cardy_finite-size_1988}.
+It is discussed in Cardy and Peschel's pioneering work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy.
+The original of these term comes from the nonzero geodesic curvature of the boundary, which when adding back the bulk curvature term constitutes the trace anomaly.
+Here we demonstrate this principle using the disk free energy example in Ref.~\onlinecite{cardy_finite-size_1988}.
 Consider an annulus on flat space with inner radius $r_1$ and outer radius $r_2$.
@@
 where $a$ is the short distance regulator.
-The disk free energy is completely contributed by its outer boundary and so the one can interpret the annulus free energy as the additive contribution from its outer and inner surfaces (which is also consistent with the geodesic curvature integral calculation),
+The disk free energy is completely contributed by its outer boundary with other parts being conformal invariant.
+One can then interpret the annulus free energy as an additive contribution from its outer and inner surfaces as (which is also consistent with the geodesic curvature integral calculation),
 \begin{equation}
@@
 \end{equation}
-An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible.
+An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface, because $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible compared to the other term.
 
-\todo[inline]{citing figure}
-We now scrutinize the conformation transformation from the slit diagram to the annulus.
-In the slit diagram, the regulators all have radius that is order of the short distance cut-off.
+A similar outer surface logarithmic term also appears in the conformation transformation from the slit diagram to the annulus in Fig.~\ref{fig:H-tau_fold}.
+In the slit diagram, the regulators all have radii that are at the order of the short distance cut-off.
 They will have negligible contributions to the free energy.
-However, after doing the conformal transformation (passive), the outer surface will contribute $-\frac{c}{6} \ln \frac{r_2}{r_1}$ which should not be there.
-Using the parameters in the free energy calculation in other appendices, we have
+However, after doing the conformal transformation, the outer surface will contribute $-\frac{c}{6} \ln \frac{r_2}{r_1}$ which should not be there.
+Using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
 \begin{equation}
@@
 % staircase geometry correction
-The annulus is called staircase geometry Ref.~\onlinecite{cardy_finite-size_1988} due to its angular direction of time evolution.
-The traditional radial quantization however has radial direction to be the time direction.
-One can go through a series of conformal maps, one can show that that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian
+The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its angular time evolution.
+The traditional radial quantization however has radial direction to be the time.
+One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988}
 \begin{equation}
-H_{z} = H_{\xi} - \frac{c}{24\pi} \beta 
+H_{w} = H_{\xi} - \frac{c}{24\pi} \beta 
 \end{equation}
-After the evolution for $2\pi$, the difference in the free energy is
+After the evolution for $2\pi$ (in the folding picture, the evolution is only $\pi$ but there are two bosons), the difference in the free energy is
 \begin{equation}
@@
 \end{equation}
-Gathering the two together, we obtain the missing $\frac{c}{12} \beta$ between the echo diagram and the Casimir energy, 
+Gathering the two terms, we obtain the missing correction $\frac{c}{12} \beta$ between the slit and cylinder diagram, 
 \begin{equation}
-F_{w} = F_z + {\color{red} \frac{c}{12}\beta }
+F_{w} = F_z + \frac{c}{12}\beta
 \end{equation}
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{fig_uncon_rq.pdf}
-\caption{Unconventional radial quantization on annulus(torus).
-Left panel: unlike the conventional radial quantization, we view the dashed line as a state and to time evolution in the radial direction.
-The blue circles are regarded as boundaries conditions rather than asymptotic states.
-Middle panel: $\xi = \ln w$ plane.
-Right panel: $z = \exp(i \frac{2\pi}{\beta} \xi)$ plane.
-We treat those dashed lines as asymptotic states and perform standard radial quantization here.}
-\label{fig:uncon_rq}
-\end{figure}
-
-\todo[inline]{There are two series of conformal transformation, one is the main text, the other is the staircase geometry.
-Both use $w, z, \xi$, I will fix the notation after the main text figure is complete.
-Maybe detailed computation of the Schwartzian term is necessary, because of the sign.
-}
 

### 2017-05-11 analy_eval.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
 \begin{aligned}
-  &\frac{1}{2}(-|x| + x^2 )\beta  \quad &i = j \\
+  &\frac{1}{2}(|x| - x^2 )\beta  \quad &i = j \\
   &\frac{1}{16}\beta   \quad &i \ne j   \\
@@
 
+As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND.
+In the region accessible to the numerical calculation in the lattice model, we choose the process
+\begin{equation}
+{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD}
+\end{equation}
+to verify
+\begin{equation}
+\mathcal{F} = 
+\left\lbrace
+\begin{aligned}
+\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
+\frac{1}{4}\ln t   &\quad \text{echo}   \\
+\end{aligned} \right.  
+\end{equation}
+where same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
+Another process
+\begin{equation}
+{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
+\end{equation}
+is used to verify
+\begin{equation}
+\mathcal{F} = 
+\left\lbrace
+\begin{aligned}
+ (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
+ 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} \\
+\end{aligned} \right. 
+\end{equation}
+where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.
+
 %%% Local Variables:

### 2017-05-11 bd_notation.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
-We use chemical reaction equation style to represent the change of boundary conditions.
-Taking the example of the echo diagrams in Fig.~{\color{red} TODO}, there are three boundary conditions $a,b,c$ in the folding picture, which represents status on two ends of the chain before and after the quench.
+We use chemical reaction style to represent the change of boundary conditions.
+Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents status on two ends of the chain before and after the quench.
 The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface.
@@
 The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of the boundary condition.
-For instance, the notation for the process presented in Fig.~{\color{red} TODO} is
+For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
 \begin{equation}

### 2017-05-11 comp_fid_echo.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later
[draft] appendix done; analytic results done; discussion draft 1.

@@
 In this appendix, we provide technical details about the numerical calculation of the bipartite fidelity and Loschmidt echo.
-It can also be applied with slight modification to the fermionic case in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011}.
 Our strategy takes advantage of the symplectic structure of the bosonic Bogoliubov transformation and explicitly construct the "BCS" like ground state.
+With slight modification\cite{blaizot_quantum_1986}, one can work out its fermionic version and apply to quadratic fermion models for example in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011}.
 
@@
 for symmetric matrix $X$ and $Y$ and set of independent Bosonic creation operators $b_i^{\dagger}$.
-One can prove it for (simultaneously) diagonalizable matrices and then claim its legitimacy for the combinatorial nature.
+One can prove it for (simultaneously) diagonalizable matrices and then claim its legitimacy for its combinatorial nature.
 
@@
 We consider the following quadratic bosonic Hamiltonian
-\begin{equation}\begin{aligned}
+\begin{equation}
+\begin{aligned}
 \label{eq:quadratic_boson_H}
-%&=b_i^\dagger H_{ij}b_j+\frac{1}{2}b^\dagger_i\Delta_{ij}b_j^\dagger+\frac{1}{2}b_i\Delta^\dagger_{ij}b_j\\
-\hat{H}
-&=
-\frac{1}{2} (\vec{b}^{\dagger}, -\vec{b})
-M 
+\hat{H} &= \frac{1}{2} (\vec{b}^{\dagger}, -\vec{b}) M 
 \begin{pmatrix}
@@
 \end{bmatrix}
-\end{aligned}\end{equation}
+\end{aligned}
+\end{equation}
 where ${\bf b}\equiv(b_{1},...,b_{n})^T$ is a vector of bosonic annihilation operators.
-The matrix $M$ consists of a $n\times n$ Hermitian block $A$ which plays the role of single particle Hamiltonian in the fermionic case and symmetric block $B$ for the pairing interaction.
+The matrix $M$ consists of a $n\times n$ Hermitian block $A$ which plays the role of single particle Hamiltonian in the fermionic case and symmetric block $B$ of the pairing interaction.
 
@@
 \end{equation}
-and the blocks are constrained by the symplectic property
+And the blocks are constrained by the symplectic property
 \begin{eqnarray}
@@
 
-The solution of $S$ depends on the types of $M$.
-For the positive definite matrix $M$, one can rewrite the Hamiltonian in the position and momentum basis and invoke the Williamson theorem\cite{arnold_mathematical_2010}, which addresses the existence, uniqueness and construction of the matrix $S$.
-We defer the derivation in this route in App.~\ref{app_sub:construction_Bogoliubov}, but will not elaborate the theorem and its proof there (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in entanglement entropy context\cite{coser_contour_2017}).
-Instead we will show in App.~\ref{app_sub:harmonic_chain} that for the problem of harmonic chain we are interested in, the diagonalization can be easily done without using the general recipe in the Williamson theorem.
-
-It is nevertheless nice to know that the formalism works for the all positive definite matrix $M$.
-And granted that we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and in $b$ basis it satisfies
-\begin{equation}\begin{aligned}
-\label{eq:a_vacuum_condition}
-(b_iu_{ij}+b_i^\dagger v_{ij})|0\rangle_{{\bf a}}=0.
-\end{aligned}\end{equation}
-If the matrix $u$ is invertible, then we can introduce a matrix $T=vu^{-1}$ to rewrite Eq.~\eqref{eq:a_vacuum_condition} as
-\begin{equation}\begin{aligned}
-(b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0. 
-\end{aligned}\end{equation}
-The constraint Eq.~\eqref{eq:constraint_2} on the blocks of $u$ and $v$ (followed by the symplectic constraint of $S$) implies that $T$ is a symmetric matrix. With the observation of 
-\begin{equation}\begin{aligned}
-\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}b_i\exp\left\{\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}=b_i+T_{ij}b^\dagger_j,
-\end{aligned}\end{equation}
-we solve the ground state
-\begin{equation}\begin{aligned}
-\label{eq:boson_BCS_gnd}
-|0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
-\end{aligned}\end{equation}
-where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}.
-Apply constraint in Eq.~\eqref{eq:constraint_1}, it simplifies to the top left corner of the symplectic matrix
-\begin{equation}
-\text{det}^{\frac{1}{4}}(1-T^\dagger T) =|\text{det}(u)|^{-\frac{1}{2}}
-\end{equation}
-
-Eq.~\eqref{eq:boson_BCS_gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
-In the next section, we will see that the normalization factor gives the fidelity and Loschmidt echo.
-
-\subsection{Boson fidelity} 
-\label{app_sub:boson_fidelity}
-
-Fidelity is defined as the (squared) overlap of groundstates of two different bosonic Hamiltonians.
-
-We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.~\eqref{eq:quadratic_boson_H}.
-From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis for positive definite $M$.
-At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new basis ${\bf c}$.
-The corresponding Bogoliubov transformations read
-\begin{equation}\begin{aligned}
-\label{eq:two_BdG}
-({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
-({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
-\end{aligned}\end{equation}
-and so
-\begin{equation}\begin{aligned}
-\label{eq:S0invS}
-({\bf a} , {\bf a}^\dagger)S_0^{-1}S_1=({\bf c} , {\bf c}^\dagger)
-\end{aligned}\end{equation}
-One realizes that Eq.~\eqref{eq:S0invS} is another Bogoliubov transformation and so the corresponding matrix has the block structure
-\begin{equation}
-S_0^{-1}S_1=\begin{bmatrix}
-u_1 & v_1^*\\
-v_1 & u_1^*
-\end{bmatrix}.
-\end{equation}
-Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}. Their overlap is therefore given by the normalization factor
-\begin{equation}\begin{aligned}
-|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|} \Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2   = \frac{1}{|\text{det}(u_1)|}
-\end{aligned}\end{equation}
-
-\subsection{Boson Loschmidt echo}
-\label{app_sub:boson_Loschmidt_echo}
-
-The Loschmidt echo is defined as the (squared) overlap of the evolved state
-\begin{equation}\begin{aligned}
-|0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a}
-\end{aligned}\end{equation}
-with $|0\rangle_{\bf a}$ the ground state of the Hamiltonian $\hat{H}_0$ before the quench. We introduce a dynamical basis
-\begin{equation}\begin{aligned}
-a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t}
-\end{aligned}\end{equation}
-which annihilate the evolved state at time $t$: $a_i(t)|0\rangle_{{\bf a}(t)}=0$.
-Upon using the diagonal basis $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time $t$ can be represented as a chain of symplectic transformation
-\begin{equation}\begin{aligned}
-\label{eq:BdG_transformation_echo}
-({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
-({\bf a} , {\bf a}^\dagger)e^{iHt}=({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
-\end{aligned}\end{equation}
-It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ through the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
-The overlap, as we have seen in the fidelity case, is the normalization factor of the "BCS" ground state.
-It is related to the top left block of the Bogoliubov transformation in Eq.~\eqref{eq:BdG_transformation_echo},
-\todo[inline]{Mao: you have highlights "it reads", anything wrong here?}
-\begin{equation}\begin{aligned}
-\label{eq:echo_t}
-\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
-\end{aligned}\end{equation}
-
-\subsection{Explicit Construction of Symplectic Bogoliubov Transformation}
-\label{app_sub:construction_Bogoliubov}
-
-As demonstrated in App.~\ref{app_sub:boson_fidelity} and \ref{app_sub:boson_Loschmidt_echo}, the calculations of fidelity and echo boil down to calculate the Bogoliubov transformations in Eq.~\eqref{eq:two_BdG}.
-Here, we shall describe how to find such a Bogoliubov transformation $S \in {\rm Sp}(2n, \mathbb{C})$ that diagonalizes the quadratic bosonic Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
-
-We introduce the real basis 
+To proceed, we introduce the real basis 
 \begin{equation}\begin{aligned}
@@
 It is not hard to check that $\mathcal{M}$ is real and symmetric.
-We shall further assume that $\mathcal{M}$ is positive definite.
-From Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} we have the decomposition
+
+The general solution diagonalization problem is hard\cite{arnold_mathematical_2010}, however the positive definite $\mathcal{M}$ (and hence $M$) can be solved by Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006}, which states the existence, uniqueness (up to reordering of eigenvalues) and explicit construction of the matrix $\mathcal{S}\in {\rm Sp}(2n \mathbb{R}) $ such that
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where $\mathcal{S}\in$Sp(2n,$\mathbb{R}$) and the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
+where the diagonal matrix $d$ are positive eigenvalues of $iJ\mathcal{M}$. After some algebra, we have
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Using the fact that $\mathcal{S}$ is an element of real symplectic group and the explicit form of $C$-matrix, one can show that Eq.~\eqref{eq:diagonalization_M} is a similarity transformation, and $C\mathcal{S}^TC^{-1}$, which takes the block form in Eq.~\eqref{eq:block_S}, is an element of complex symplectic group.
-Thus we identify
+One can show that
 \begin{equation*}\begin{aligned}
@@
 \end{aligned}\end{equation*}
-as the desired Bogoliubov transformation that diagonalizes the Hamiltonian in Eq.~\eqref{eq:quadratic_boson_H}.
+is the required symplectic matrix in the complex basis.
 
-In the analogous situation for the quadratic fermion Hamiltonian, we can rewrite the problem in the real Majorana basis.
-The real symplectic matrix $\mathcal{S}$ becomes a real orthogonal matrix and can be found by a real Schur decomposition.
-Reverting back to the complex basis, it is the unitary matrix $U$ that plays the role of the complex symplectic matrix $S$ here.
-The Loschmidt echo will become $|\det ( u )|$ as opposite to the Bosonic $\frac{1}{|\det u|}$ in Eq.~\eqref{eq:echo_t}, where $u$ is the top left corner of the unitary matrix $U$.
-The results in Ref.~\onlinecite{vasseur_universal_2014} can be reproduced in this way.
+We will not elaborate on Williamson's theorem and its proof (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in entanglement entropy context\cite{coser_contour_2017}).
+Instead we will show in App.~\ref{app_sub:harmonic_chain} that for the problem of harmonic chain we are interested in, the diagonalization can be easily done without using the general recipe in the Williamson theorem.
+
+\subsection{Groundstate in $b$ Basis}
+
+Suppose we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and in $b$ basis it satisfies
+\begin{equation}\begin{aligned}
+\label{eq:a_vacuum_condition}
+(b_iu_{ij}+b_i^\dagger v_{ij})|0\rangle_{{\bf a}}=0.
+\end{aligned}\end{equation}
+If the matrix $u$ is invertible, then we can introduce a matrix $T=vu^{-1}$ to rewrite Eq.~\eqref{eq:a_vacuum_condition} as
+\begin{equation}\begin{aligned}
+(b_i+b_j^\dagger T_{ji})|0\rangle_{{\bf a}}=0. 
+\end{aligned}\end{equation}
+The constraint Eq.~\eqref{eq:constraint_2} on the blocks of $u$ and $v$ (followed by the symplectic constraint of $S$) implies that $T$ is a symmetric matrix. With the observation of 
+\begin{equation}\begin{aligned}
+\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}b_i\exp\left\{\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}=b_i+T_{ij}b^\dagger_j,
+\end{aligned}\end{equation}
+we solve the groundstate
+\begin{equation}\begin{aligned}
+\label{eq:boson_BCS_gnd}
+|0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
+\end{aligned}\end{equation}
+where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}.
+Apply constraint in Eq.~\eqref{eq:constraint_1}, it simplifies to the top left corner of the symplectic matrix
+\begin{equation}
+\text{det}^{\frac{1}{4}}(1-T^\dagger T) =|\text{det}(u)|^{-\frac{1}{2}}
+\end{equation}
+
+Eq.~\eqref{eq:boson_BCS_gnd} takes a similar form as the superconducting ground state, with the pairing wavefunction $T_{ij}$ determined by the Bogoliubov transformation.
+In the next section, we will see that the normalization factor gives the fidelity and Loschmidt echo.
+
+\subsection{Boson fidelity} 
+\label{app_sub:boson_fidelity}
+
+Fidelity is defined as the (squared) overlap of groundstates of two different bosonic Hamiltonians.
+
+We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.~\eqref{eq:quadratic_boson_H}.
+From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis for positive definite $M$.
+At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new basis ${\bf c}$.
+The corresponding Bogoliubov transformations read
+\begin{equation}\begin{aligned}
+\label{eq:two_BdG}
+({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
+({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
+\end{aligned}\end{equation}
+and so
+\begin{equation}\begin{aligned}
+\label{eq:S0invS}
+({\bf a} , {\bf a}^\dagger)=({\bf c} , {\bf c}^\dagger)\left(S_0^{-1}S_1\right)^{-1}
+\end{aligned}\end{equation}
+One realizes that Eq.~\eqref{eq:S0invS} is another Bogoliubov transformation and so the corresponding matrix has the block structure
+\begin{equation}
+S_1^{-1}S_0=\begin{bmatrix}
+u_1 & v_1^*\\
+v_1 & u_1^*
+\end{bmatrix}.
+\end{equation}
+Thus $|0\rangle_{\bf c}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}. Their overlap is therefore given by the normalization factor
+\begin{equation}\begin{aligned}
+|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|} \Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2   = \frac{1}{|\text{det}(u_1)|}
+\end{aligned}\end{equation}
+
+\subsection{Boson Loschmidt echo}
+\label{app_sub:boson_Loschmidt_echo}
+
+The Loschmidt echo is defined as the (squared) overlap of the evolved state
+\begin{equation}\begin{aligned}
+|0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a}
+\end{aligned}\end{equation}
+with $|0\rangle_{\bf a}$ the ground state of the Hamiltonian $\hat{H}_0$ before the quench. We introduce a dynamical basis
+\begin{equation}\begin{aligned}
+a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t}
+\end{aligned}\end{equation}
+which annihilate the evolved state at time $t$: $a_i(t)|0\rangle_{{\bf a}(t)}=0$.
+Upon using the diagonal basis $\hat{H}_1=\sum_iE_ic_i^\dagger c_i$, the Bogoliubov transformation at time $t$ can be represented as a chain of symplectic transformation
+\begin{equation}\begin{aligned}
+\label{eq:BdG_transformation_echo}
+({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
+({\bf a} , {\bf a}^\dagger)e^{iHt}=({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
+\end{aligned}\end{equation}
+It is evident that the evolved state $|0\rangle_{{\bf a}(t)}$ is related to the $|0\rangle_{{\bf a}}$ in the same way as in Eq.~\eqref{eq:boson_BCS_gnd}.
+The overlap, as we have seen in the fidelity case, is the normalization factor of the "BCS" ground state.
+It is related to the top left block of the Bogoliubov transformation in Eq.~\eqref{eq:BdG_transformation_echo},
+\begin{equation}\begin{aligned}
+\label{eq:echo_t}
+\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
+\end{aligned}\end{equation}
 
@@
 
-In this subsection, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain. In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
+In this subsection, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
+In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
 \begin{equation}\begin{aligned}
@@
 where $\mathcal{V}$ is real symmetric matrix that can be diagonalized as $\mathcal{V}=\mathcal{O}D^2\mathcal{O}^T$.
-The explicit form of $\mathcal{V}$ depends on the boundary condition, but positive definiteness is the only requirement here.
+The matrix $\mathcal{V}$ depends on the boundary condition, but positive definiteness is the only requirement here.
 
@@
 
-Thus the second quantized Hamiltonian is diagonalized as
+Thus the Hamiltonian is diagonalized as
 \begin{equation}\begin{aligned}

### 2017-05-11 compact_boson.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
 \todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
-In this appendix, we address the issue of winding modes of compact bosons. In the main text, we have exclusively worked with the oscillator modes of free bosons. 
-%We have introduced the general formulation of bosonic conformal interface in Sec.~\ref{sec_sub:general_formulation}, and calculated various partition functions from the boundary state approach in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}.
-We have not talk about the winding mode for compact bosons.
-Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo, at least in the leading order.
+
+In this appendix, we address the issue of winding modes of compact bosons.
+In the main text, we exclusively work with the oscillator modes of free bosons.
+Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order.
 Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.
@@
 
-We recall the gluing condition in Eq.~\eqref{eq:def_M} is a constraint from conformal invariance\cite{blumenhagen_introduction_2009,bachas_permeable_2002}, which provides no constraint for the winding modes.
-Indeed, the winding mode is a global property of the boson which is insensitive to the local variations.
-Thus one needs a more general treatment for the compactified bosons.
-This is summarized for the well known cases of Dirichlet and Neumann boundary conditions in App.~\ref{app_sub:compact_DN_boundary} and generalized to gluing condition in App.~\ref{app_sub:compact_gluing_boundary}.
-We demonstrate that winding mode does not contribute to the free energy through boundary state calculation in App.~\ref{app_sub:winding_contribution}.
-Throughout this appendix, the term ``conformal boundary state'' refers to its winding sector exclusively.
+Our derivation follows the general multi-component Boson constraints in Ref.~\onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}.
+A review of the detailed parameterization of the states can be found in Ref.~\onlinecite{sakai_entanglement_2008}.
 
-%\subsection{Free Boson with Different Compactification Radii}
+\subsection{Mode Expansion of Compact Boson}
+Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, then mode expansion will have zero mode
+\begin{equation}
+\begin{aligned}
+\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\  
+&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  +  \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\ 
+\end{aligned}
+\end{equation}
+where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. In the holomorphic coordinates
+\begin{equation}
+z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
+\end{equation}
+the mode expansion becomes
+\begin{equation}
+\label{eq:boson-mode-exp}
+\begin{aligned}
+\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
+&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
+\end{aligned}
+\end{equation}
+We further identify 
+\begin{equation}
+\begin{aligned}
+  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right) \\
+  \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)
+\end{aligned}
+\end{equation}
+and then 
+\begin{equation}
+i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
+\end{equation}
 
-\subsection{Winding Mode with Dirichlet and Neumann Boundary Conditions}
-\label{app_sub:compact_DN_boundary}
-
-We consider the following boson configuration
-\begin{eqnarray}\begin{aligned}
-\phi(x+L,t)=\phi(x,t)+2\pi mR
-\end{aligned}\end{eqnarray}
-where $m\in\mathbb{Z}$ is the winding number of the field.
-Since the field is compactified on a circle, its momentum $\pi_0$ takes discrete eigenvalues $\pi_0\equiv\frac{n}{R}$ with $n\in\mathbb{Z}$.
-Thus the mode expansion reads
-\begin{eqnarray}\begin{aligned}
-\label{eq:mode_expand_compact}
-\phi(x,t)&=\phi_0-\frac{2\pi Rm}{L}x+\frac{\pi_0}{gL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})\\ 
-&={\phi}_0-\frac{2\pi Rm}{L}x+\frac{n}{gRL}t+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+\bar{a}_{n}e^{2\pi i n(x+t)/L})
-\end{aligned}\end{eqnarray}
-Further, the holomorphic coordinates are introduced as
-\begin{eqnarray}\begin{aligned}
-z=\exp\left(2\pi i\frac{t-x}{L}\right)\qquad\bar{z}=\exp\left(2\pi i\frac{t+x}{L}\right)
-\end{aligned}\end{eqnarray}
-which leads to 
-\todo[inline]{Take care of the format for long equation later, for two columns}
-\begin{eqnarray}\begin{aligned}
-\label{eq:phi_in_z}
-\phi(z,\bar{z})=\phi_0-i\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\ln z-i\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)\ln \bar{z}+\frac{i}{\sqrt{4\pi g}}\sum_{n\neq0}\frac{1}{n}(a_nz^{n}+\bar{a}_{n}\bar{z}^{-n})
-\end{aligned}\end{eqnarray}
-The key observation is that if one defines
-\begin{eqnarray}\begin{aligned}
-a_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}+\frac{mR}{2}\right)\qquad\bar{a}_0=\sqrt{4\pi g}\left(\frac{n}{4\pi gR}-\frac{mR}{2}\right)
-\end{aligned}\end{eqnarray}
-then the holomorphic and anti-holomorphic derivatives can be written compactly as
-\begin{eqnarray}\begin{aligned}
-i\partial\phi(z)=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}a_{n}z^{-n-1}\qquad i\bar{\partial}\phi(\bar{z})=\frac{1}{\sqrt{4\pi g}}\sum_{n\in\mathbb{Z}}\bar{a}_{n}\bar{z}^{-n-1}
-\end{aligned}\end{eqnarray}
-%The Virasoro generators takes the same form as before
-%\begin{eqnarray}\begin{aligned}
-%L_n=\frac{1}{2}\sum_{m\in\mathbb{Z}}:a_{n-m}a_m:\qquad n\in\mathbb{Z}
-%\end{aligned}\end{eqnarray}
-%In particular for the conformal boundary state $|B\rangle$, the condition
-%\begin{eqnarray}\begin{aligned}
-%(L_n-\bar{L}_{-n})|B\rangle=0
-%\end{aligned}\end{eqnarray}
-
-$a_0$ and $\bar{a}_0$ are not independent for the conformal boundary states. It turns out that from the Virasoro generators, one can deduce that
-\begin{eqnarray}\begin{aligned}
-\label{eq:DN_a}
-\text{Dirichlet}&:a_0-\bar{a}_0=0\\
-\text{Neumann}&:a_0+\bar{a}_0=0
-\end{aligned}\end{eqnarray}
-Therefore, the conformal boundary state for Dirichlet and Neumann are respectively
-\begin{eqnarray}\begin{aligned}
-\label{eq:DN_state}
-|{\rm D} \rangle  &= g_{\,\!_\text{D}}  \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle \\
-| {\rm N} \rangle &= g_{\,\!_\text{N}} \prod_{k > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle
-\end{aligned}\end{eqnarray}
-with the desired boundary conditions
-\begin{eqnarray}\begin{aligned}
-\phi(x,t=0)|{\rm D} \rangle=\phi_0|{\rm D} \rangle\qquad \partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
-\end{aligned}\end{eqnarray}
-We have included the oscillator part in Eq.~\eqref{eq:DN_state}, with the vacuum being a linear combination of different winding sectors.
-In the following sections, the oscillator part will be the same, and we shall write down only the vacuum which is subject to the more general gluing condition.
-
-\subsection{Winding mode with Gluing Condition}
+\subsection{Gluing Condition for Winding Modes}
 \label{app_sub:compact_gluing_boundary}
@@
 We recall that the conformal boundary condition can be written as
-\begin{eqnarray}\begin{aligned}
+\begin{equation}
+\begin{aligned}
 \label{eq:def_S_in_app}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
-where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}.
-We shall specialize to the case $S=S_1$ first.
-The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x\phi^2$ term changes sign, we therefore have
-\begin{eqnarray}\begin{aligned}
+\end{aligned}
+\end{equation}
+where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}. The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
+\begin{equation}
+\begin{aligned}
 \label{eq:def_S_in_app_2}
@@
 \end{pmatrix}
-=S_1(\theta)
+=S(\theta)
 \begin{pmatrix}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
-Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:phi_in_z}, we have
-\begin{eqnarray}\begin{aligned}
+\end{aligned}
+\end{equation}
+Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
+\begin{equation}
+\begin{aligned}
 \label{eq:def_S_in_app_2}
-\sum_{n\in\mathbb{Z}}\begin{pmatrix}
+\sum_{n\in\mathbb{Z}}
+\begin{pmatrix}
 \bar{a}_n^1\bar{z}^{-n}\\
@@
 \end{pmatrix}
-=S_1(\theta)
+=S(\theta)
 \sum_{n\in\mathbb{Z}}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}
+\end{equation}
 As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
-\end{aligned}\end{eqnarray}
-This is clearly a generalization of Dirichlet and Neumann boundary conditions in Eq.~\eqref{eq:DN_a}.
-We therefore expect that the conformal boundary state is a generalization of Eq.~\eqref{eq:DN_state}, subject to the more general constraint
-\begin{eqnarray}\begin{aligned}
+\end{aligned}\end{equation}
+The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.
+
+We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
+\begin{equation}
+\label{eq:lattice}
+\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
+\end{equation}
+to rewrite the zero mode part as 
+\begin{equation}
+  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
+\end{equation}
+which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
+\begin{equation}
+\begin{aligned}
 \label{eq:S_1_constraint}
-\tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
-\end{aligned}\end{eqnarray}
-Thus we conclude that the conformal boundary state reads
-\begin{eqnarray}\begin{aligned}
+\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
+\end{aligned}
+\end{equation}
+and the conformal boundary state reads
+\begin{equation}\begin{aligned}
 g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}.
-The g-factor can only be determined by Cardy condition\cite{oshikawa_boundary_2010}.
+The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}.
 Since it is not important for what follows, we shall not repeat the calculation here.
-For the case of $S=S_2$, it is evident that the same calculation can be carried out, and one will arrive at the similar boundary state.
+Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in a similar parameter $\lambda$ and boundary state.
+We omit the expression here because the main text does not use it.
 
@@
 \label{app_sub:winding_contribution}
-In order to demonstrate that the winding mode will have no contribution to the leading order of $\beta$, we shall reconsider the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
-\begin{eqnarray}\begin{aligned}
+We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
+\begin{equation}\begin{aligned}
 Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
-\end{aligned}\end{eqnarray}
-For the winding mode contribution, we simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$). For the case of same boundary state $\lambda_1=\lambda_2$, we have the winding mode contribution as
-\begin{eqnarray}\begin{aligned}
+\end{aligned}\end{equation}
+To that end, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).
+
+For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
+\begin{equation}
+\begin{aligned}
 \label{eq:Z0}
 Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
-\end{aligned}\end{eqnarray}
+\end{aligned}
+\end{equation}
 In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy.
@@
 The same conclusion still holds in the limit $\beta\rightarrow\infty$.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-11 def_fidel_echo.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig_fidel.pdf}
+\includegraphics[width=0.8\textwidth]{fig_fidelity-DN-lambda-folding.pdf}
 \caption{Fidelity of connecting two CFTs.
@@
 
-\todo[inline]{echo diagram folding}
-
 The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
@@
 \end{equation}
-The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~{\color{red} TODO}.
+The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
 Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt is also the associated the free energy.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\textwidth]{fig_echo-DN-lambda-folding.pdf}
+\caption{\color{red} fill in caption of echo diagram}
+\label{fig:echo}
+\end{figure}
 
@@
 The tip of the slit is no longer a twist field with presence of the conformal interface.
-Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and {\color{red} TODO} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
+Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
 From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator.

### 2017-05-11 disc.tex
[draft] appendix done; analytic results done; discussion draft 1.

% relation between fidelity and echo

In all the computation we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will be mainly discuss the echo properties.

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the echo is always $\frac{1}{4} \ln t$, regardless of the theta angle. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two corresponds to the parts of the Lorentz group and can't be connected by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of $DD \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
\end{equation}
which gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation. This is very likely due to the ambiguity of the free boson zero mode, as moving slight way from the point remedy the situation. And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation. Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy. It would be interesting to have a CFT calculation to reproduce the better numerical result of
\begin{equation}
{\rm ND} + {\rm DN} \rightarrow \lambda + {\rm ND} 
\end{equation}

Nevertheless the special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this and the $DD \rightarrow {\rm P}$ one  $\frac{3}{8}- \frac{1}{4} = \frac{1}{16} $ is interpreted as the bcc operator dimension between D and N. The picture is complete in this full ${\rm DN}$ to $\lambda $ transition.

% connecting Luttinger liquid(quantum wire) using votage to control the boundary condition. X-ray edge singularity. examples include Taylor santo's topological phases. Hope to have experimental setup.

Aside from free lattice boson model for the numerical purposes, these set of boundary conditions can be realized in connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides. A X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-11 general_formulation.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
 
-\todo[inline]{Mao: I put $\partial_t$ on the top in my notes. The 'DN' 'ND' convention seems to be wrong here. I'll think about it.}
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:def_M}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
@@
 As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 M_1(\theta)=\pm
@@
 \end{bmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.
@@
 Hereafter we shall denote this combination as 'DN'.
-Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to DN, DD, NN respectively.
+Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to ND, DD, NN respectively.
 \item $\theta = \pm \frac{\pi}{4}$.
 In this case, $M(\theta)$ characterizes a perfectly transmitting defect.
-For example, there is effectively no defect in the case $M( \frac{\pi}{4})$.
+For example, there is effectively no defect in the case $M( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
 For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
@@
 We therefore establish the scattering relation
-\begin{eqnarray}\begin{aligned}
+\begin{equation}\begin{aligned}
 \label{eq:def_S}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 
-\todo[inline]{Tianci: Add in the right panel in Fig.~\ref{fig:cut-and-join} the field content?}
 and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
-\begin{eqnarray}\begin{aligned}
+
+\begin{equation}\begin{aligned}
 \label{eq:S1_S2}
@@
 \end{bmatrix}
-\end{aligned}\end{eqnarray}
+\end{aligned}\end{equation}
 \todo[inline]{Mao: please do not interchangably use defect or interface. We use interface throughout the text.}
@@
 
-We now work in the folding picture as shown in Fig.{\color{red} TODO}.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{fig_folding_pic.pdf}
+\caption{{\color{red} folding picture text}}
+\label{fig:folding_pic}
+\end{figure}
+
+We now work in the folding picture as shown in Fig.~\ref{fig:folding_pic}.
 The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary state.
 The folding sends $\phi^2(x)$ to $\phi^2(-x)$ and hence the gluing condition becomes
-\begin{eqnarray}\begin{aligned}
+\begin{equation}
+\begin{aligned}
 \partial_t(\cos\theta\phi^1-\sin\theta\phi^2)=0 \quad
 \partial_x(\sin\theta\phi^1+\cos\theta\phi^2)=0 
-\end{aligned}\end{eqnarray}
-for the case $M=M_1(\theta)$.
+\end{aligned}
+\end{equation}
+for the case $M = M_1(\theta)$.
 
@@
 We end up with a set of operator identities for each mode
-\begin{eqnarray}\begin{aligned}
+\begin{equation}
+\begin{aligned}
 \label{eq:rotation_a_basis}
@@
 \sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
-\end{aligned}\end{eqnarray}
+\end{aligned}
+\end{equation}
 which is valid on the following boundary state

### 2017-05-11 gnd_dn_lambda.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
-% flatex input: [gnd_dn_lambda.tex]
-
 \begin{figure}[h]
@@
 
-In this appendix, we would like to calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}.
-In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and linking boundary condition at $x = 0$.
+In this appendix, we calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}.
+In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and conformal interface $\lambda$ at $x = 0$.
 The general solutions can be written as
@@
 \end{equation}
-As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction reads
+As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction becomes
 \begin{eqnarray}\begin{aligned}
@@
 \end{equation}
-It is evident that the momentum $k$ is shifted from integer multiple of $2\pi/L$ due to the $\lambda$ boundary condition in the middle. 
-\begin{comment}
-Thus, the normalized eigenfunctions are
-\begin{equation}
-f_n(x) = \sqrt{\frac{2}{L}}
-\left\lbrace
-\begin{aligned}
-  \cos(kx +\frac{1}{2}kL ) &  \quad x < 0  \\
-  \pm \sin(kx - \frac{1}{2}kL ) & \quad x > 0   \\
-\end{aligned} \right. 
-\qquad 
-k = \frac{2\pi}{L}\left( n \pm  \frac{\theta}{\pi} \right)  \quad n \in \mathbb{Z} 
-\end{equation}
-Expand the field $\phi = \sum_n \phi_n f_n(x) $, the action and Hamiltonian becomes
-\begin{equation}
-  S = \frac{g}{2} \int dt \, \sum_{n \in \mathbb{Z} }\left(  \dot{\phi}^2_n + k^2 \phi_n^2 \right) \implies\quad   g \dot{\phi}_n  = \pi_n \quad \implies H =  
-\frac{1}{2g}\sum_{n \in \mathbb{Z} } \pi_n^2 + ( kg )^2  \phi_n^2 
-\end{equation}
-\end{comment}
+It is evident that the momentum $k$ is shifted from integer multiple of $\frac{2\pi}{L}$ due to the $\lambda$ boundary condition in the middle.
 
-It is clear that the normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in mode expansion.
-Following the same procedure in Ref.~\onlinecite{di_francesco_conformal_1997}, we have the Hamiltonian as
+The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in the mode expansion, we thus have the 
 \begin{equation}
@@
 
-The Casimir energy is the vacuum energy brought by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and define $x\equiv\theta/\pi$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
+The Casimir energy is the vacuum energy brought up by the finite size of the setup.
+From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and use $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
 \begin{equation}
@@
 \end{equation}
-where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy reads
+where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy in the large $\beta$ limit is
 \begin{equation}
@@
 which agrees with the boundary state calculation in Sec.~\ref{app:lambda_12}.
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-11 intro.tex
[draft] appendix done; analytic results done; discussion draft 1.

@@
 The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
-There are numerous impurity problem of this kind that has been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc.
+There are numerous impurity problem of this kind that has been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
 

### 2017-05-11 pf_of_id.tex
[draft] 1.add bibs, 2. geneneral formulation, free boson lattice done 3. Appendix of winding mode not done yet, I will add the caveat later
[draft] appendix done; analytic results done; discussion draft 1.

@@
-% flatex input: [pf_of_id.tex]
-
-In this appendix, we provide more details for calculating the amplitude $Z_{ab}$ in Sec.{\bf\color{red}where}. We started to prove the following identity for a real symmetric matrix $M$
+In this appendix, we provide more details for calculating the amplitude $Z_{ab}$ in Sec.~\ref{sec:analytic_numerics}. We start to prove the following identity for a real symmetric matrix $M$
 \begin{equation}
@@
 where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators.
-As emphasized in the {\bf\color{red}main text}, the matrix notation, for example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
+The matrix notation here should be understand as bilinear form.
+For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
 
@@
 \end{equation}
-where we understood $\vec{\bar{b}}^\dagger$ is a column vector and independent to $\vec{{b}}^\dagger$. Thus the whole expression can be written as
+where we understand $\vec{\bar{b}}^\dagger$ as a column vector independent to $\vec{{b}}^\dagger$. Thus the whole expression can be written as
 \begin{equation}

### 2017-05-16 codes/echo_fit.py
[code] echo_fit.py added, and the fits for DDDD, NNNN added

@@ -1,0 +1,97 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.optimize
+from random import randint
+
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+
+bc = 'NNNN'
+path = "/Users/MaoLin/Dropbox/Physics_Research/Quench/fermion_EE/bcft_paper/data/" + bc + "/"
+fig_path = "/Users/MaoLin/Dropbox/Physics_Research/Quench/fermion_EE/bcft_paper/images/"
+figname = fig_path + bc +"_fit.pdf"
+
+dataset = []
+for (dirpath, dirnames, filenames) in walk(path):
+    dataset.extend(filenames)
+
+# ----------------------------------------------------------------------           
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+filename=[]
+slope=[]
+error=[]
+for filename in dataset:
+    if filename[0]=='.':
+        continue
+    x = []
+    y = []
+    for line in open( path + filename ):
+        xx, yy = map(float,line.split() )
+        x.append( xx )
+        y.append( yy )
+    if filename==dataset[1]: # for inset
+        x_inset=x
+        y_inset=y
+    slope_array = []
+    f = lambda x, a, b: a * x ** b
+    for i in range(0,5): # fit five times
+        start = randint(0,5)
+        x_fit = x[len(x)-start-10 : len(x)-start]
+        y_fit = y[len(x)-start-10 : len(x)-start]
+        p , c = scipy.optimize.curve_fit( f, x_fit , y_fit )
+        slope_array.append( p[1] )
+    slope.append( np.mean( slope_array ) )
+    error.append( np.std( slope_array ) ) 
+# print slope    
+# print error    
+    
+# Print the slope and error bar into a file
+
+# ---------------------------------------------------------------------- 
[…]

### 2017-05-18 num_result.tex
[draft] num_result added, some figure environments are fixed, figure of DDDD, NNNN fixed

In order to check our analytic results, we reconsider the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice}. In particular, we calculate the Loschmidt echo and bipartite fidelity for various joining boundary conditions determined by $S_1(\theta)$ or $S_2(\theta)$. We refer the reader to App.~\ref{app:comp_fid_echo} for the technical details.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The slope of the free energy for Loschmidt echo in the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$ where $\theta\in(0,\frac{\pi}{2})$. We work with total system size $N=30k$ sites, with parameters $m=10^{-8}$,$k=1$. The lattice constant is set to unity. The blue dots are the numerical results and the red line is the analytical result. As predicted, the slopes are equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta=0.02\pi$ shown in log scale. The dashline denotes the power law with $t^{-0.25}$. The curve fitting method is described in the main text.}
\label{fig:DDDD}
\end{figure}

We start with the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$ and the numerical simulation is performed for $\theta=0.02n\pi$, $n=1,...,25$. The results for Loschmidt echo is shown in Fig.~\ref{fig:DDDD}, and numerical parameters are given in the caption. The green dots correspond to numerical results for the slope of free energy, and the solid line shows the analytical result for echo in Eq.~\eqref{eq:result_DDDD}. The inset shows the double logarithmic plot of Loschmidt echo versus time for the case $\theta=0.02\pi$. The dashline denotes the expected power law decay $\mathcal{L}(t)\sim t^{-0.25}$. For the curve fitting, we randomly pick a data point near $t=10$ and fit the lower half of the data. This is repeated five times and we calculate the mean and standard deviation for the exponents. With the data processing method described, the error bar in the main figure is invisible on the data points. We have performed the identical simulation for the process $\text{NN}+\text{NN}\rightarrow\lambda+\text{NN}$ and obtained identical result shown in Fig.~\ref{fig:DDDD} (the initial decay of Loschmidt is different but has the same exponent at larger time). We note one caveat for this case with Neumann boundary conditions on both sides of the chain. Because of the zero mode, it is expected (indeed we saw) that the numerical simulation may not be stable. The problem can be avoided by adding a small mass regulator $m=10^{-8}$. Similar numerical analysis can be applied to calculate the fidelity which matches the result in Eq.~\eqref{eq:result_DDDD}. We shall not show the result here.

Next we analyze the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ in which the joining boundary condition is determined by $S_1(\theta)$. There is one subtly which is that $S_1(0)$ corresponds to `DN' and the process reduces to $\text{DN}+\text{DN}\rightarrow\text{DN}+\text{DN}$. The zero mode will cause the numerical simulation unstable near $\theta=0$, and it turns out that the mass regulator cannot resolve this problem. Rather, we shall shift one of the `DN' slightly and consider the following process
\begin{eqnarray}\begin{aligned}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
\end{aligned}\end{eqnarray}
where we take $\delta\theta=0.003\pi$ and $\theta=0.02n\pi$, $n=1,...,25$. We shall discuss the introduction of extra bcc at $-\infty$ due to this shift in Sec.~\ref{sec:disc}. We show the numerical result for Loschmidt echo in Fig.~\ref{fig:DDNN}(a). The slope of the free energy follows a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. The deviation from the analytic result (without the shift) near $\theta=0$ has been greatly suppressed because of $\delta\theta$ introduced manually. The numerical results near $\theta=0.5\pi$ will match the analytical ones more precisely if we were to set $\delta\theta=0$.

Next we perform the numerical simulation for $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ with $\theta\in(0,\frac{\pi}{2})$.  We recall that

{\color{red}say why echo bad, say we shift it that is why dot below curve slightly near pi, say there is extra bcc, say why fidelity better, say to confirm we do fidelity as shown in Fig.~\ref{fig:DDNN}(b) and it is good, confirm our conjecture. }

We further consider the case $\text{P}+\text{P}\rightarrow\lambda+\text{P}$, and the numerical results for Loschmidt echo and fidelity are shown in Fig.~\ref{fig:PPPP}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DN_DN2tan.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=30k$ sites with the same parameters in Fig.~\ref{fig:DDDD}. The numerical value of slopes follow a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. For the deviation from the analytic results in (a), see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
    \todo[inline]{Tianci: make the plots have the same style?}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
    \caption{daf}
    \label{fig:PPPP}
    \todo[inline]{Mao: Put the PPPP for echo; Tianci: make the plots have the same style?}
\end{figure}

### 2017-05-19 num_result.tex
[draft] results for PP added for analytical result, and numerical result. New app for Scale invaraint interface added, PP_fit pdf added

@@
-In order to check our analytic results, we reconsider the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
-In particular, we calculate the Loschmidt echo and bipartite fidelity for various joining boundary conditions determined by $S_1(\theta)$ or $S_2(\theta)$.
-We refer the reader to App.~\ref{app:comp_fid_echo} for the technical details.
-
 \begin{figure}[h]
@@
 \caption{The slope of the free energy for Loschmidt echo in the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$ where $\theta\in(0,\frac{\pi}{2})$.
-We work with total system size $N=30k$ sites, with parameters $m=10^{-8}$,$k=1$.
+We work with total system size $N=30k$ sites, with parameters $m=10^{-8}$, $k=1$.
 The lattice constant is set to unity.
@@
 The dashline denotes the power law with $t^{-0.25}$.
+The finite size effect will set in after $t=10^{3}$.
 The curve fitting method is described in the main text.}
@@
 \end{figure}
+
+In order to check our analytic results, we reconsider the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
+In particular, we calculate the Loschmidt echo and bipartite fidelity for various joining boundary conditions determined by $S_1(\theta)$ or $S_2(\theta)$.
+Similar numerical evaluations exist in the literatures\cite{vasseur_universal_2014,stephan_local_2011},  however we shall follow a different approach, and the reader is referred to App.~\ref{app:comp_fid_echo} for the technical details.
 
@@
 The problem can be avoided by adding a small mass regulator $m=10^{-8}$.
-Similar numerical analysis can be applied to calculate the fidelity which matches the result in Eq.~\eqref{eq:result_DDDD}.
+We have performed similar numerical analysis to calculate the free energy for fidelity, and it matches the result in Eq.~\eqref{eq:result_DDDD}.
 We shall not show the result here.
@@
 \begin{eqnarray}\begin{aligned}
+\label{eq:approx_DNDN}
 S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
@@
 where we take $\delta\theta=0.003\pi$ and $\theta=0.02n\pi$, $n=1,...,25$.
-We shall discuss the introduction of extra bcc at $-\infty$ due to this shift in Sec.~\ref{sec:disc}.
+In the limit $\delta\theta=0$, Eq.~\eqref{eq:approx_DNDN} reduces to the process we would like to study.
+The issue of extra bcc at $-\infty$ due to $\delta\theta$ will be discussed in Sec.~\ref{sec:disc}.
 We show the numerical result for Loschmidt echo in Fig.~\ref{fig:DDNN}(a).
@@
 The deviation from the analytic result (without the shift) near $\theta=0$ has been greatly suppressed because of $\delta\theta$ introduced manually.
-The numerical results near $\theta=0.5\pi$ will match the analytical ones more precisely if we were to set $\delta\theta=0$.
+The cost is that the numerical results near $\theta=0.5\pi$ was shifted slightly, which will match more precisely if $\delta\theta=0$.
+We demonstrated the $\theta$-dependence of power law in the inset.
+To confirm that zero mode is responsible for the unexpected behavior near $\theta=0$, we numerically calculate the free energy for fidelity, which is immune to the zero mode.
+The simulation is performed in the same setup with  $\delta\theta=0.001\pi$.
+The result is shown in Fig.~\ref{fig:DDNN}(b), which shows perfect match between numerical and analytical results.
 
-Next we perform the numerical simulation for $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ with $\theta\in(0,\frac{\pi}{2})$.  We recall that
-
-{\color{red}say why echo bad, say we shift it that is why dot below curve slightly near pi, say there is extra bcc, say why fidelity better, say to confirm we do fidelity as shown in Fig.~\ref{fig:DDNN}(b) and it is good, confirm our conjecture.
-}
-
-We further consider the case $\text{P}+\text{P}\rightarrow\lambda+\text{P}$, and the numerical results for Loschmidt echo and fidelity are shown in Fig.~\ref{fig:PPPP}.
+Further we consider the case $\text{P}+\text{P}\rightarrow\lambda+\text{P}$, and the numerical results for Loschmidt echo and fidelity are shown in Fig.~\ref{fig:PPPP}(a).
+Since $S_2(\frac{\pi}{4})$ corresponds to periodic boundary condition, numerical instability will set in near $\theta=\frac{\pi}{4}$ due to the zero mode.
+We shift one of the periodic boundary condition slightly
+\begin{eqnarray}\begin{aligned}
+\label{eq:approx_DNDN}
+S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right)
+\end{aligned}\end{eqnarray}
+where we take $\delta\theta=0.003\pi$ and $\theta=0.02n\pi$, $n=1,...,25$. 
+\todo[inline]{Describe the result for PP}
+As a diagnostic tool, the result for fidelity is presented in Fig.~\ref{fig:PPPP}(b).
 
@@
     \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
-The total system size is $N=30k$ sites with the same parameters in Fig.~\ref{fig:DDDD}.
-The numerical value of slopes follow a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
+The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}.
+The numerical value of slopes follow a quadratic relation as predicted.
 For the deviation from the analytic results in (a), see the discussion in the main text.
 Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$.
+The finite size effect will set in after $t=10^{4}$.
 We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
@@
   \centering
+  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
     \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
-    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
-    \caption{daf}
+    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
+The parameters are the same as those in Fig.~\ref{fig:DDNN}.
+The plot is symmetric with respect to $\theta=0.25\pi$ as predicted.
+For the deviation from the analytic results in (a), see the discussion in the main text.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$.
+The finite size effect will set in after $t=10^{4}$.
+We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
     \label{fig:PPPP}

### 2017-05-19 def_fidel_echo.tex
[draft] num_result added, some figure environments are fixed, figure of DDDD, NNNN fixed

@@
 \end{equation}
-For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal defect.
+For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal interface.
 Both of them can be produced by the imaginary time evolution.
@@
 \begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{fig_fidelity-DN-lambda-folding.pdf}
+\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
 \caption{Fidelity of connecting two CFTs.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig_echo-DN-lambda-folding.pdf}
+\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
 \caption{\color{red} fill in caption of echo diagram}

### 2017-05-19 free_boson_lattice.tex

@@
 
-% Despite its simpleness, such discrete bosonic defect can be considered in more general quadratic bosonic\cite{PhysRevA.74.022329}, or fermionic\cite{PhysRevB.64.064412} systems.
-It also sheds light on the possible application of our CFT results in condensed matter experiments\cite{Rohringer2015,Trotzky2012}.
-
-\todo[inline]{I think the reference cited here are irrelevant.}
-
 We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
-\begin{eqnarray}\begin{aligned}
-H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
-\begin{bmatrix}
-1 + \Sigma_{11}  & \Sigma_{12} \\
-\Sigma_{21} &  1 + \Sigma_{22} \\
-\end{bmatrix}
+\begin{equation}
+H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\Sigma
 \begin{pmatrix}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
-where the matrix $\Sigma$ parameterize two-site interaction.
+\end{equation}
+%\begin{eqnarray}\begin{aligned}
+%H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+%\begin{bmatrix}
+%1 + \Sigma_{11}  & \Sigma_{12} \\
+%\Sigma_{21} &  1 + \Sigma_{22} \\
+%\end{bmatrix}
+%\begin{pmatrix}
+%\phi_0 \\
+%\phi_1 
+%\end{pmatrix}
+%\end{aligned}\end{eqnarray}
+where the $2\times2$ matrix $\Sigma$ parameterizes two-site interaction.
 In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.
-
-\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$.
-In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}
-
-To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
+We perform the scattering analysis in App.~\ref{app:interface_free_boson}, and the scale invariant S-matrix reads
 \begin{equation}
-\label{eq:ansatz}
-\phi_n
-= \left\lbrace
-  \begin{aligned}
-    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
-    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
-  \end{aligned} \right. 
- \quad 
-\end{equation}
-where $a$ is the lattice constant.
-The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless.
-The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
-Upon plugging ansatz and dispersion relation into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
-\begin{equation}
-\label{eq:discrete_S}
-\begin{pmatrix}
-A_{-} \\
-B_{+}\\
-\end{pmatrix}
-=-
-\begin{bmatrix}
-\Sigma_{11} + e^{-ika} & \Sigma_{12} \\
-\Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
-\end{bmatrix}^{-1}
-\begin{bmatrix}
-\Sigma_{11} +e^{ika} & \Sigma_{12}\\
-\Sigma_{21} & \Sigma_{22} + e^{ika}
-\end{bmatrix}
-\begin{pmatrix}
-A_{+}\\
-B_{-}\\
-\end{pmatrix}
-\end{equation}
-and the scattering matrix can be solved as
-\begin{equation}
-  S = \frac{-1}{ \det \Sigma  + e^{-ika} \text{tr} \Sigma   + e^{-2ika}}
-\begin{bmatrix}
-\det \Sigma+ \Sigma_{11} e^{-ika} + \Sigma_{22} e^{ika}+1  & -2i \sin ka \Sigma_{12}  \\
--2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
-\end{bmatrix}
-\end{equation}
-A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
-\begin{equation}
-\label{eq:Sigma_condition}
-\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
-\end{equation}
-Therefore, we have the scale invariant S-matrix as
-\begin{equation}
-S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
+S = \frac{1}{1 - e^{-2ika } } ( -2i \sin ka ) \Sigma
  = - e^{ika} \Sigma
 \end{equation}
-In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
+where $a$ is the lattice constant. In the continuum limit $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
 \begin{equation}
@@
 \end{equation}
-in accordance to Eq.~\eqref{eq:Sigma_condition}.
 
 {\bf\color{red}
-Say in the continuum limit, what happens
 

### 2017-05-19 general_formulation.tex
[draft] num_result added, some figure environments are fixed, figure of DDDD, NNNN fixed

@@
 \begin{equation}\begin{aligned}
+\label{eq:M1M2}
 M_1(\theta)=\pm
@@
 \item $\theta=0,\pm \frac{\pi}{2}$.
-In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the defect cannot transmit to the other side, so the interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
+In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the interface cannot transmit to the other side, so the interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
 For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition are imposed on the right and Neumann boundary condition on the left.
-Hereafter we shall denote this combination as 'DN'.
+Hereafter we shall denote this combination as `DN'.
 Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to ND, DD, NN respectively.
 \item $\theta = \pm \frac{\pi}{4}$.
-In this case, $M(\theta)$ characterizes a perfectly transmitting defect.
-For example, there is effectively no defect in the case $M( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
+In this case, $M(\theta)$ characterizes a perfectly transmitting interface.
+For example, there is effectively no interface in the case $M( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
 For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
@@
 \end{aligned}\end{equation}
-\todo[inline]{Mao: please do not interchangably use defect or interface. We use interface throughout the text.}
 For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices.
@@
 \centering
-\includegraphics[width=\textwidth]{fig_folding_pic.pdf}
+\includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
 \caption{{\color{red} folding picture text}}

### 2017-05-19 interface_free_boson.tex

In this section, we consider a lattice model with bosonic interface at the center\cite{peschel_exact_2012,calabrese_entanglement_2012}, which reduces to the one considered in Sec.~\ref{sec_sub:general_formulation} in the continuum limit\cite{sakai_entanglement_2008}. Therefore, it serves as a numerical tool to check our analytic results in Sec.~\ref{sec:analytic_numerics}.

We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
\begin{eqnarray}\begin{aligned}
H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
\begin{bmatrix}
1 + \Sigma_{11}  & \Sigma_{12} \\
\Sigma_{21} &  1 + \Sigma_{22} \\
\end{bmatrix}
\begin{pmatrix}
\phi_0 \\
\phi_1 
\end{pmatrix}
\end{aligned}\end{eqnarray}
where the matrix $\Sigma$ parameterize two-site interaction. In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.

\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$. In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}

To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
\begin{equation}
\label{eq:ansatz}
\phi_n
= \left\lbrace
  \begin{aligned}
    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
  \end{aligned} \right. 
 \quad 
\end{equation}
where $a$ is the lattice constant. The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless. The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}. Upon plugging ansatz and dispersion relation into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
\begin{equation}
\label{eq:discrete_S}
\begin{pmatrix}
A_{-} \\
B_{+}\\
\end{pmatrix}
=-
\begin{bmatrix}
\Sigma_{11} + e^{-ika} & \Sigma_{12} \\
\Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
\end{bmatrix}^{-1}
\begin{bmatrix}
\Sigma_{11} +e^{ika} & \Sigma_{12}\\
\Sigma_{21} & \Sigma_{22} + e^{ika}
\end{bmatrix}
\begin{pmatrix}
A_{+}\\
B_{-}\\
\end{pmatrix}
\end{equation}
and the scattering matrix can be solved as
\begin{equation}
  S = \frac{-1}{ \det \Sigma  + e^{-ika} \text{tr} \Sigma   + e^{-2ika}}
\begin{bmatrix}
\det \Sigma+ \Sigma_{11} e^{-ika} + \Sigma_{22} e^{ika}+1  & -2i \sin ka \Sigma_{12}  \\
-2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
\end{bmatrix}
\end{equation}
A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
\begin{equation}
\label{eq:Sigma_condition}
\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
\end{equation}
Therefore, we have the scale invariant S-matrix as
\begin{equation}
S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
 = - e^{ika} \Sigma
\end{equation}
In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
in accordance to Eq.~\eqref{eq:Sigma_condition}.

{\bf\color{red}
Say in the continuum limit, what happens

say in the long time, what happens?

say the special case in the boundary
}

This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-19 codes/fidel_fit.py
[data] 1. remove .txt extention (rm_txt.sh) 2. add fidelity DDNN data 3. create fidelity fit script

@@ -1,0 +1,114 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.optimize
+from random import randint
+
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+
+folder = 'DDNN_fidel'
+path = "../data/" + folder + "/"
+fig_path = "../images/"
+figname = fig_path + folder + "_fit.pdf"
+
+# get all the filenames in the subdirectory
+dataset = []
+for ( dirpath, dirnames, filenames ) in walk( path ):
+    dataset.extend( filenames )
+print( dataset )
+
+# ----------------------------------------------------------------------
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+def fit_data( x, y ):
+    slope_array = []
+
+    f = lambda x, a, b: a * x ** b
+    for i in range( 0, 5 ): # fit five times
+        start = randint( 0, 5 )
+        x_fit = x[len(x)-start-10 : len(x)-start]
+        y_fit = y[len(x)-start-10 : len(x)-start]
+        p , c = scipy.optimize.curve_fit( f, x_fit , y_fit )
+        slope_array.append( -p[1] )
+
+    slope = np.mean( slope_array )
+    error = np.std( slope_array )
+
+    return slope, error 
+
+slope = []
+error = []
+x = []
+
+for filename in dataset:
+    data = np.loadtxt( path + filename )
+    t = data[:,0]
+    echo = data[:,1]
+
+    # extract x = theta / pi from filename
+    x.append( float( filename ) )
+    
+    this_slope, this_error = fit_data( t, echo );
+    slope.append( this_slope )
+    error.append( this_error )
+
+inset_data = np.loadtxt( path + dataset[1] )
+t_inset = inset_data[:,0]
+echo_inset = inset_data[:,1]
+
[…]

### 2017-05-19 data/rm_txt.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+for file in *.txt; do
+	filename="${file%.*}"
+	mv $file $filename
+done

### 2017-05-19 num_result.tex
[draft] change in bCFT and numerical result, in case of conflict

@@
 The lattice constant is set to unity.
-The blue dots are the numerical results and the red line is the analytical result.
+The blue dots are the numerical results and the red line is the analytic result.
 As predicted, the slopes are equal for different values of $\theta$.
@@
 The results for Loschmidt echo is shown in Fig.~\ref{fig:DDDD}, and numerical parameters are given in the caption.
-The green dots correspond to numerical results for the slope of free energy, and the solid line shows the analytical result for echo in Eq.~\eqref{eq:result_DDDD}.
+The green dots correspond to numerical results for the slope of free energy, and the solid line shows the analytic result for echo in Eq.~\eqref{eq:result_DDDD}.
 The inset shows the double logarithmic plot of Loschmidt echo versus time for the case $\theta=0.02\pi$.
@@
 The simulation is performed in the same setup with  $\delta\theta=0.001\pi$.
-The result is shown in Fig.~\ref{fig:DDNN}(b), which shows perfect match between numerical and analytical results.
+The result is shown in Fig.~\ref{fig:DDNN}(b), which shows perfect match between numerical and analytic results.
 

### 2017-05-19 free_boson_lattice.tex
[draft] free boson lattice and its appendix done. No more commit today..

@@
 \begin{equation}
+\label{eq:lattice_H}
 H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
@@
 In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.
-We perform the scattering analysis in App.~\ref{app:interface_free_boson}, and the scale invariant S-matrix reads
+We perform the standard scattering analysis in App.~\ref{app:interface_free_boson}, and the scale invariant S-matrix reads
 \begin{equation}
@@
 \begin{equation}
+\label{eq:def_Sigma}
 \Sigma = -\lim_{a \rightarrow 0 } S = 
@@
 \end{equation}
-
-{\bf\color{red}
-
-say in the long time, what happens?
-
-say the special case in the boundary
-}
-
-This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.
+where $\lambda\in\mathbb{R}$. The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results.
 

### 2017-05-19 interface_free_boson.tex
[draft] free boson lattice and its appendix done. No more commit today..

@@
-In this section, we consider a lattice model with bosonic interface at the center\cite{peschel_exact_2012,calabrese_entanglement_2012}, which reduces to the one considered in Sec.~\ref{sec_sub:general_formulation} in the continuum limit\cite{sakai_entanglement_2008}.
-Therefore, it serves as a numerical tool to check our analytic results in Sec.~\ref{sec:analytic_numerics}.
-
-We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
-\begin{eqnarray}\begin{aligned}
-H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
-\begin{bmatrix}
-1 + \Sigma_{11}  & \Sigma_{12} \\
-\Sigma_{21} &  1 + \Sigma_{22} \\
-\end{bmatrix}
+\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$.
+In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}
+In this appendix, we demonstrate how to realize scale invariant S-matrix in a lattice regularization. Following Sec.~\ref{sec_sub:free_boson_lattice}, we consider the following harmonic chain 
+\begin{equation}
+H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\Sigma
 \begin{pmatrix}
@@
 \end{pmatrix}
-\end{aligned}\end{eqnarray}
-where the matrix $\Sigma$ parameterize two-site interaction.
-In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.
-
-\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$.
-In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}
-
-To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
+\end{equation}
+where the matrix $\Sigma$ parameterize two-site interaction between site 0 and 1.
+To find the scattering matrix, we set up the plane wave scattering problem across the interface with the following ansatz (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
 \begin{equation}
@@
 where $a$ is the lattice constant.
-The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless.
+Upon solving the equation of motion far away from the interface, it is found that the system is gapless with the dispersion relation $\omega = \left|2\sin\frac{k}{2}\right|$.
 The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
-Upon plugging ansatz and dispersion relation into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
+After some algebra, the incoming and outgoing amplitudes are related via
+\begin{widetext}
 \begin{equation}
@@
 \begin{pmatrix}
-A_{-} \\
-B_{+}\\
+A_{+} \\
+B_{-}\\
 \end{pmatrix}
@@
 \begin{bmatrix}
+\Sigma_{11} +e^{ika} & \Sigma_{12}\\
+\Sigma_{21} & \Sigma_{22} + e^{ika}
+\end{bmatrix}^{-1}
+\begin{bmatrix}
 \Sigma_{11} + e^{-ika} & \Sigma_{12} \\
 \Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
-\end{bmatrix}^{-1}
-\begin{bmatrix}
-\Sigma_{11} +e^{ika} & \Sigma_{12}\\
-\Sigma_{21} & \Sigma_{22} + e^{ika}
 \end{bmatrix}
 \begin{pmatrix}
-A_{+}\\
-B_{-}\\
+A_{-}\\
+B_{+}\\
 \end{pmatrix}
@@
 \end{equation}
-A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
+\end{widetext}
+The S matrix elements are reflection and transmission coefficients.
+In order to have a scale invariant interface, they need to be $k-$independent.
+Therefore the necessary condition is that the ratio $|S_{11}/S_{21}|$ is independent of $k$, which implies
 \begin{equation}
@@
 \begin{equation}
-S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
+S = \frac{1}{1 - e^{-2ika } } ( -2i \sin ka ) \Sigma
  = - e^{ika} \Sigma
 \end{equation}
-In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
+In the actual simulation, we evolved a large enough system for a long time, such that a field theoretic description can be applied.
+In this continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
 \begin{equation}
@@
 \end{equation}
-in accordance to Eq.~\eqref{eq:Sigma_condition}.
-
-{\bf\color{red}
-Say in the continuum limit, what happens
-
-say in the long time, what happens?
-
-say the special case in the boundary
-}
-
-This is the matrix we will use for the numerics. The results will be presented in Sec.~\ref{sec:analytic_numerics}.
+where $\lambda\in\mathbb{R}$ is the parameter for $S_1(\theta)$, as emphasized in Sec.~\ref{sec:notation}.
+This simple relation between $\Sigma$ and the S-matrix provides a tool to check our analytic results.
 

### 2017-05-20 disc.tex
[draft]numerical results revision 1

@@
 It is then reasonable to find an universal echo between them.
-The special value of $DD \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
+The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
 
@@
 Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation.
-This is very likely due to the ambiguity of the free boson zero mode, as moving slight way from the point remedy the situation.
+This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation.
 And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation.
@@
 \end{equation}
+
+\todo[inline]{insert the ND + DN figure. Compare it with the DN + DN figure}
 

### 2017-05-20 num_result.tex
[draft]numerical results revision 1

--- 2017-05-18 num_result.tex
@@
-In order to check our analytic results, we reconsider the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
-In particular, we calculate the Loschmidt echo and bipartite fidelity for various joining boundary conditions determined by $S_1(\theta)$ or $S_2(\theta)$.
-We refer the reader to App.~\ref{app:comp_fid_echo} for the technical details.
-
 \begin{figure}[h]
 \includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
-\caption{The slope of the free energy for Loschmidt echo in the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$ where $\theta\in(0,\frac{\pi}{2})$.
-We work with total system size $N=30k$ sites, with parameters $m=10^{-8}$,$k=1$.
+\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$.
+We work with total system size $N = 30k$ sites, and parameters $m = 10^{-8}$, $k = 1$.
 The lattice constant is set to unity.
-The blue dots are the numerical results and the red line is the analytical result.
-As predicted, the slopes are equal for different values of $\theta$.
-Inset: An example of Loschmidt echo with $\theta=0.02\pi$ shown in log scale.
-The dashline denotes the power law with $t^{-0.25}$.
-The curve fitting method is described in the main text.}
+The blue dots representing the numerical results lie on the red analytic line.
+As predicted, the echo exponents are equal for different values of $\theta$.
+Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale.
+The dashline denotes the expected power law of $t^{-0.25}$.
+The finite size effect do not emerge before $t=10^{3}$, which sets the right boundary of the range we fit.
+See main text for the curve fitting method.}
 \label{fig:DDDD}
@@
 
-We start with the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$ and the numerical simulation is performed for $\theta=0.02n\pi$, $n=1,...,25$.
-The results for Loschmidt echo is shown in Fig.~\ref{fig:DDDD}, and numerical parameters are given in the caption.
-The green dots correspond to numerical results for the slope of free energy, and the solid line shows the analytical result for echo in Eq.~\eqref{eq:result_DDDD}.
-The inset shows the double logarithmic plot of Loschmidt echo versus time for the case $\theta=0.02\pi$.
-The dashline denotes the expected power law decay $\mathcal{L}(t)\sim t^{-0.25}$.
-For the curve fitting, we randomly pick a data point near $t=10$ and fit the lower half of the data.
-This is repeated five times and we calculate the mean and standard deviation for the exponents.
-With the data processing method described, the error bar in the main figure is invisible on the data points.
-We have performed the identical simulation for the process $\text{NN}+\text{NN}\rightarrow\lambda+\text{NN}$ and obtained identical result shown in Fig.~\ref{fig:DDDD} (the initial decay of Loschmidt is different but has the same exponent at larger time).
-We note one caveat for this case with Neumann boundary conditions on both sides of the chain.
-Because of the zero mode, it is expected (indeed we saw) that the numerical simulation may not be stable.
-The problem can be avoided by adding a small mass regulator $m=10^{-8}$.
-Similar numerical analysis can be applied to calculate the fidelity which matches the result in Eq.~\eqref{eq:result_DDDD}.
-We shall not show the result here.
+We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results.
+Our numerical evaluations is based on Boson Bogoliubov transformation and explicit form of the groundstates.
+The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details.
+In all the figures, we present the coefficients of the logarithmic term $\mathcal{F} / \ln L$ and $\mathcal{F} / \ln t$ and call them fidelity and echo exponents respectively.
 
-Next we analyze the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ in which the joining boundary condition is determined by $S_1(\theta)$.
-There is one subtly which is that $S_1(0)$ corresponds to `DN' and the process reduces to $\text{DN}+\text{DN}\rightarrow\text{DN}+\text{DN}$.
-The zero mode will cause the numerical simulation unstable near $\theta=0$, and it turns out that the mass regulator cannot resolve this problem.
-Rather, we shall shift one of the `DN' slightly and consider the following process
+We start with the process
+\begin{equation}
+\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}
+\end{equation}
+and shows its Loschmidt echo in Fig.~\ref{fig:DDDD}.
+The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay.
+We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as a dashline for comparison.
+The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $.
+To avoid subjective choice of data points, we repeat 5 times to randomly pick {\color{red} 10 points} before the finite size revival surges to obtain the deviation.
+We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.
+
+We also calculate the companion process
+\begin{equation}
+ \text{NN}+\text{NN}\rightarrow\lambda+\text{NN}
+\end{equation}
+and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}.
+The avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
+While the short time decay pattern are different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity.
+We therefore do not present the result here.
+
+Next we analyze the more interesting $\theta$ dependent process
+\begin{equation}
+  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN}
+\end{equation}
+in which the joining boundary condition is determined by $S_1(\theta)$.
+A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
+We therefore turn to another regulator that shift the far end boundary condition DN to $\mathcal{S}_1( \delta \theta )$ and consider the following process
 \begin{eqnarray}\begin{aligned}
+\label{eq:approx_DNDN}
 S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
 \end{aligned}\end{eqnarray}
-where we take $\delta\theta=0.003\pi$ and $\theta=0.02n\pi$, $n=1,...,25$.
-We shall discuss the introduction of extra bcc at $-\infty$ due to this shift in Sec.~\ref{sec:disc}.
-We show the numerical result for Loschmidt echo in Fig.~\ref{fig:DDNN}(a).
-The slope of the free energy follows a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
-The deviation from the analytic result (without the shift) near $\theta=0$ has been greatly suppressed because of $\delta\theta$ introduced manually.
-The numerical results near $\theta=0.5\pi$ will match the analytical ones more precisely if we were to set $\delta\theta=0$.
-
-Next we perform the numerical simulation for $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$ with $\theta\in(0,\frac{\pi}{2})$.  We recall that
-
-{\color{red}say why echo bad, say we shift it that is why dot below curve slightly near pi, say there is extra bcc, say why fidelity better, say to confirm we do fidelity as shown in Fig.~\ref{fig:DDNN}(b) and it is good, confirm our conjecture.
-}
-
-We further consider the case $\text{P}+\text{P}\rightarrow\lambda+\text{P}$, and the numerical results for Loschmidt echo and fidelity are shown in Fig.~\ref{fig:PPPP}.
+Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process.
+This "shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}.
+The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
+We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.
 
@@
     \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
-The total system size is $N=30k$ sites with the same parameters in Fig.~\ref{fig:DDDD}.
-The numerical value of slopes follow a quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
-For the deviation from the analytic results in (a), see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$.
+The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}.
+The numerical value of exponents follow a quadratic relation as predicted.
+There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi, 0.24\pi$ and $0.48\pi$.
+The finite size effect do not emerge before $t=10^{4}$.
 We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
@@
 
+We finally consider the case
+\begin{equation}
+\text{P}+\text{P}\rightarrow\lambda+\text{P}
+\end{equation}
+in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occur at $\theta \frac{\pi}{4}$. We therefore apply the shift regulator there 
+\begin{equation}
+\begin{aligned}
+\label{eq:approx_DNDN}
+S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right)
+\end{aligned}
+\end{equation}
+where we take $\theta=0.003\pi$. The $\theta$ dependent exponents now is a shifted quadratic curve symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.
+
 \begin{figure}
   \centering
+  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
     \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
-    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
-    \caption{daf}
+    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
+The parameters are the same as those in Fig.~\ref{fig:DDNN}.
+The plot is symmetric with respect to $\theta=0.25\pi$ as predicted.
+The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$.
+The finite size effect do not emerge before $t=10^{4}$.
+We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
     \label{fig:PPPP}
@@
 \end{figure}
+
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-20 codes/fidel_fit.py

@@ -102,7 +102,6 @@ for tick in ax2.xaxis.get_major_ticks():
 for tick in ax2.yaxis.get_major_ticks():
     tick.label.set_fontsize( 8 )
 
-
 ax2.set_yscale( 'log' ) 
 ax2.set_xscale( 'log' )
 ax2.set_xlabel( r"$t$", fontsize = 8 )

### 2017-05-20 conclusion.tex
[draft] conclusion draft out; fidelity figure revised

In this paper, we analyze a class of boson conformal interfaces by computing the fidelity and Loschmidt echo.

We begin by classifying the boundary states by two types of $S$ matrices, where the conventional DD, NN boundary conditions belong to $S_1$ while DN and $P$ belongs to $S_2$. A harmonic chain model allows us to realize part of these boundary conditions, including the partially-transimitive ones on a concrete setting.

The study of the Loschmidt echo are a generalization of the conventional "cut-and-join" protocol. Its power law decay exponent is related to the bcc operator scaling dimension that now can depend on the tune-able transmission coefficient. Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices. While the exponent will depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$.

These two features are tested in three typical processes in the numerical calculation. After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error. Although irrelevant to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement, providing more confidence about the analytic results.

We proposed that the Loschmidt echo exponent in principle should be realizable in connecting two quantum wire with an X-ray type experiment.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-20 codes/DDNN_fidel_fit.py

@@ -116,8 +116,8 @@ for tick in ax2.yaxis.get_major_ticks():
 
 ax2.set_yscale( 'log' ) 
 ax2.set_xscale( 'log' )
-ax2.set_xlabel( r"$L$", fontsize = 8 )
-ax2.set_ylabel( r"Fidelity", fontsize = 8 )
+ax2.set_xlabel( r"$t$", fontsize = 8 )
+ax2.set_ylabel( r"$\mathcal{L}(t)$", fontsize = 8 )
  
 # plt.tight_layout()
 

### 2017-05-21 codes/DDDD_echo_fit.py
[code] fitting codes modified

@@ -1,0 +1,140 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+from math import pi, exp
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.stats
+from random import randint
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+colorL={6:"#ff2222", 8:'#ffa500', 10:'#4488ff', 12:"#0000aa", 14:'#66bb22'}
+
+bc = 'DDDD' 
+path = "../data/" + bc + "/"
+fig_path = "../images/"
+figname = fig_path + bc +"_fit.pdf"
+
+offset=0
+
+dataset = []
+for (dirpath, dirnames, filenames) in walk(path):
+    dataset.extend(filenames)
+# print dataset
+
+# ----------------------------------------------------------------------           
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+
+
+def fit_data( x, y ):
+
+    log_x = np.log( x ) / np.log( 10 )
+    log_y = np.log( y ) / np.log( 10 )
+
+    log_x = log_x[ x > 20 ]
+    log_y = log_y[ x > 20 ]
+
+    slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
+
+    log_x_mean = np.mean( log_x )
+    ssx = np.sum( np.square( log_x - log_x_mean ) )
+
+    error = np.sqrt( std_err / ssx )
+
+    return -slope, error 
+
+slope = []
+error = []
+x = []
+
+for filename in dataset:
+   if filename[0]=='.':
+       continue
+   data = np.loadtxt( path + filename )
+   t = data[:,0]
+   echo = data[:,1]
+
+   # extract x = theta / pi from filename
+   x.append( float( filename.split('_')[1] ) )
+   this_slope, this_error = fit_data( t, echo );
[…]

### 2017-05-21 codes/DDNN_echo_fit.py

@@ -1,0 +1,158 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+from math import pi, exp
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.stats
+from random import randint
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+colorL={6:"#ff2222", 8:'#ffa500', 10:'#4488ff', 12:"#0000aa", 14:'#66bb22'}
+
+bc = 'DDNN' 
+path = "../data/" + bc + "/"
+fig_path = "../images/"
+figname = fig_path + bc +"_fit.pdf"
+
+offset=0.15/25*pi/2/pi
+
+dataset = []
+for (dirpath, dirnames, filenames) in walk(path):
+    dataset.extend(filenames)
+# print dataset
+
+# ----------------------------------------------------------------------           
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+
+def fit_data( x, y, where ):
+
+    log_x = np.log( x ) / np.log( 10 )
+    log_y = np.log( y ) / np.log( 10 )
+
+    if where=='left':
+            # log_x = log_x[ (x>300)*(x<5000) ]
+            # log_y = log_y[ (x>300)*(x<5000) ]
+            # log_x = log_x[ (x>200)*(x<500) ]
+            # log_y = log_y[ (x>200)*(x<500) ]
+            log_x = log_x[ (x>200)*(x<4500) ]
+            log_y = log_y[ (x>200)*(x<4500) ]
+    elif where=='center':
+            log_x = log_x[ (x>30)*(x<400) ]
+            log_y = log_y[ (x>30)*(x<400) ]        
+    elif where=='right':
+            log_x = log_x[ (x>30)*(x<400) ]
+            log_y = log_y[ (x>30)*(x<400) ]
+
[…]

### 2017-05-21 codes/NNNN_echo_fit.py

@@ -1,0 +1,138 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+from math import pi, exp
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.stats
+from random import randint
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+colorL={6:"#ff2222", 8:'#ffa500', 10:'#4488ff', 12:"#0000aa", 14:'#66bb22'}
+
+bc = 'NNNN' 
+path = "../data/" + bc + "/"
+fig_path = "../images/"
+figname = fig_path + bc +"_fit.pdf"
+
+offset=0
+
+dataset = []
+for (dirpath, dirnames, filenames) in walk(path):
+    dataset.extend(filenames)
+# print dataset
+
+# ----------------------------------------------------------------------           
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+def fit_data( x, y ):
+
+    log_x = np.log( x ) / np.log( 10 )
+    log_y = np.log( y ) / np.log( 10 )
+
+    log_x = log_x[ x > 20 ]
+    log_y = log_y[ x > 20 ]
+
+    slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
+
+    log_x_mean = np.mean( log_x )
+    ssx = np.sum( np.square( log_x - log_x_mean ) )
+
+    error = np.sqrt( std_err / ssx )
+
+    return -slope, error 
+
+slope = []
+error = []
+x = []
+
+for filename in dataset:
+   if filename[0]=='.':
+       continue
+   data = np.loadtxt( path + filename )
+   t = data[:,0]
+   echo = data[:,1]
+
+   # extract x = theta / pi from filename
+   x.append( float( filename.split('_')[1] ) )
+   this_slope, this_error = fit_data( t, echo );
+   slope.append( this_slope )
[…]

### 2017-05-21 codes/PPPP_echo_fit.py

@@ -1,0 +1,156 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+from math import pi, exp
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.optimize
+from random import randint
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+colorL={6:"#ff2222", 8:'#ffa500', 10:'#4488ff', 12:"#0000aa", 14:'#66bb22'}
+
+bc = 'PP' 
+path = "../data/" + bc + "/"
+fig_path = "../images/"
+figname = fig_path + bc +"_fit.pdf"
+
+offset=0.15/25*pi/2/pi
+
+dataset = []
+for (dirpath, dirnames, filenames) in walk(path):
+    dataset.extend(filenames)
+# print dataset
+
+# ----------------------------------------------------------------------           
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+def fit_data( x, y ,where ):
+    slope_array = []
+
+    f = lambda x, a, b: a * x ** b
+    for i in range( 0, 5 ): # fit five times
+        start = randint( 0, 5 )
+        if where=='center':
+            x_fit = t[40-start-15 : 40-start]
+            y_fit = echo[40-start-15 : 40-start]
+        elif where=='others':
+            x_fit = t[25-start-20 : 25-start]
+            y_fit = echo[25-start-20 : 25-start]
+        p , c = scipy.optimize.curve_fit( f, x_fit , y_fit )
+        slope_array.append( -p[1] )
+
+    slope = np.mean( slope_array )
+    error = np.std( slope_array )
+
+    return slope, error 
+
+slope = []
+error = []
+x = []
+
+for filename in dataset:
+   if filename[0]=='.':
+       continue
[…]

### 2017-05-21 analy_eval.tex
[draft] add P case to the analytic result
[draft] num_result added, some figure environments are fixed, figure of DDDD, NNNN fixed
[draft] results for PP added for analytical result, and numerical result. New app for Scale invaraint interface added, PP_fit pdf added
[draft]numerical results revision 1
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 However, without regulators the conformal invariance can rescale both to $1$ by doing a dilation transformation, thus getting rid of their dependence.
-Therefore, regulators are necessary in keeping track of the scale dependence and also physically sensible considering the lattice realization of the systems.
+Therefore, regulators are necessary in keeping track of the scale dependence, and also physically sensible when considering the lattice realization of the systems.
 
-We thus add small semi-circles around the points where the boundary condition changing operator resides and then do a series of conformal mapping.
-
-For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map} 
+We thus add small semi-circles around the points where the bcc operators reside, followed a series of conformal mapping.
+For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}.
 \begin{figure}[h]
 \centering
-\includegraphics[width=\textwidth]{fig_fidel-map.pdf}
+\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
 \caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $.
@@
 \centering
-\includegraphics[width=\textwidth]{fig_H-tau_fold}
+\includegraphics[width=\columnwidth]{fig_H-tau_fold}
 \caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions.
@@
 \begin{equation}
+\label{eq:DDDD}
 {\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD}
@@
 \begin{equation}
+\label{eq:result_DDDD}
 \mathcal{F} = 
@@
 \begin{equation}
+\label{eq:DNDN}
 {\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
@@
 \begin{equation}
+\label{eq:result_DNDN}
 \mathcal{F} = 
@@
 
+We also use a less physical process
+\begin{equation}
+  \label{eq:PP}
+  {\rm P} + {\rm P} \rightarrow \lambda + {\rm P}
+\end{equation}
+to check the shift of the curve
+\begin{equation}
+\label{eq:periodic-case}
+\mathcal{F} = 
+\left\lbrace
+\begin{aligned}
+  \Big(|x-\frac{1}{4}| - (x-\frac{1}{4})^2 \Big)\ln L   &  \quad {\rm fidelity} \\
+  2\Big(|x-\frac{1}{4}| - (x-\frac{1}{4})^2 \Big) \ln t  & \quad \text{ Loschmidt echo} \\
+\end{aligned} \right. 
+\end{equation}
+
 %%% Local Variables:

### 2017-05-21 bd_notation.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface.
-The process $a + c \rightarrow b + c$ represents the change of boundary condition form the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench.
+The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench.
 Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
@@
 
-In the "cut-and-join" protocol we considered, $a$ should be one of 'DD', 'DN', 'ND', 'NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$.
-The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of the boundary condition.
+In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$.
+The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of boundary condition.
 For instance, the notation for the process presented in Fig.~\ref{fig:echo} is

### 2017-05-21 comp_fid_echo.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 \label{eq:preserve_commutator}
-J\equiv\begin{bmatrix}
+J&\equiv\begin{bmatrix}
 0 & \mathbb{I}\\
@@
 {\bf b} & {\bf b}^\dagger
-\end{pmatrix}]S
-=S^T JS.
+\end{pmatrix}]S \\
+&=S^T JS.
 \end{aligned}
@@
 \pi
-\end{pmatrix}
-=\frac{1}{2}
+\end{pmatrix} \\
+&=\frac{1}{2}
 \begin{pmatrix}
@@
 \begin{equation}\begin{aligned}
-|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{1}{|\text{det}(u_1)|} \Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2   = \frac{1}{|\text{det}(u_1)|}
+|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{\Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2}{|\text{det}(u_1)|} = \frac{1}{|\text{det}(u_1)|}
 \end{aligned}\end{equation}
@@
 \label{eq:BdG_transformation_echo}
-({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
-({\bf a} , {\bf a}^\dagger)e^{iHt}=({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
+&({\bf a}(t),{\bf a}^\dagger(t))=e^{-iHt}
+({\bf a} , {\bf a}^\dagger)e^{iHt} \\
+=&({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
 \end{aligned}\end{equation}
@@
 S&=C\mathcal{S}C^{-1}
-&=\begin{bmatrix}
+=\begin{bmatrix}
 O(D^{1/2}+D^{-1/2}) & O(D^{1/2}-D^{-1/2}) \\

### 2017-05-21 conclusion.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 
-We begin by classifying the boundary states by two types of $S$ matrices, where the conventional DD, NN boundary conditions belong to $S_1$ while DN and $P$ belongs to $S_2$.
-A harmonic chain model allows us to realize part of these boundary conditions, including the partially-transimitive ones on a concrete setting.
+We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ while `DN' and $P$ belongs to $S_2$.
+A harmonic chain model allows us to realize part of these boundary conditions, including the partially-transmitive ones, on a concrete setting.
 
-The study of the Loschmidt echo are a generalization of the conventional "cut-and-join" protocol.
-Its power law decay exponent is related to the bcc operator scaling dimension that now can depend on the tune-able transmission coefficient.
+The study of the Loschmidt echo are a generalization of the conventional ``cut-and-join" protocol.
+Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient.
 Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices.

### 2017-05-21 def_fidel_echo.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 \begin{equation}
-{\rm fidelity} = |\langle \psi_1 |\psi_2  \rangle |^2 
+{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 
 \end{equation}
-For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal interface.
+For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface.
 Both of them can be produced by the imaginary time evolution.
@@
 The horizontal axis the imaginary time.
-Evolution on the two infinitely extended side produces the groundstate of the disconnected and connected chain Hamiltonians.
-The right diagram is the result of folding the lower part of the diagram up, so that all the boundary are now boundary states.}
+Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians.
+The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states.
+The solid dot represents boundary changing operator.}
 \label{fig:fidel}
@@
 The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
-One of the them the groundstate of the disconnected chain and the other is groundstate evolved by the connected chain Hamiltonian
+One of the them is the groundstate of the disconnected chains and the other is groundstate evolved by the Hamiltonian of the connected chains
 \begin{equation}
-\mathcal{L} = |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
+\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
 \end{equation}
 The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
-Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt is also the associated the free energy.
+Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.
 
@@
 \includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
-\caption{\color{red} fill in caption of echo diagram}
+\caption{Loschmidt echo of connecting two CFTs.
+The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians.
+They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains.
+In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case).
+See the discussion in main text.}
 \label{fig:echo}
 \end{figure}
-
+\todo[inline]{Tianci: Change the single slit to double slit at the LHS, and add $\tau$ at the RHS?}
 If the interface is completely transparent, i.e.
@@
 According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
-One would expect the fidelity and echo to have power law decay patter with respective to these scales in the long wavelength limit.
-In fact, such kind of computation has been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration.
+One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit.
+In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration.
 If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
@@
 
-The tip of the slit is no longer a twist field with presence of the conformal interface.
+The tip of the slit is no longer a twist field with the presence of the conformal interface.
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
 From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator.
-These diagrams then becomes the one and two point functions of the bcc operators and the free energy logarithmic term extracts their scaling dimensions.
+These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
 

### 2017-05-21 general_formulation.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 There are however many successful attempts to construct a subset of those bosonic boundary states.
-One way to do is to impose current operator rather than Virasolo generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
-Other example utilizes the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.
+One way is to impose current operator rather than Virasoro generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+Other examples utilize the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.
 
-We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantize it give the boundary state.
+We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantizes it to give the boundary state.
 The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.
 
-Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the "gluing condition"
-
+Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
 \begin{equation}\begin{aligned}
@@
 
-Several special choice of $\theta$ need to be noted. 
+Several special choices of $\theta$ need to be noted. 
 \begin{enumerate}
 \item $\theta=0,\pm \frac{\pi}{2}$.
-In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the interface cannot transmit to the other side, so the interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
-For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition are imposed on the right and Neumann boundary condition on the left.
+In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other.
+The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
+For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left.
 Hereafter we shall denote this combination as `DN'.
-Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to ND, DD, NN respectively.
+Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to `ND', `DD', `NN' respectively.
 \item $\theta = \pm \frac{\pi}{4}$.
-In this case, $M(\theta)$ characterizes a perfectly transmitting interface.
-For example, there is effectively no interface in the case $M( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
+In this case, $M_1(\theta)$ characterizes a perfectly transmitting interface.
+For example, there is effectively no interface in the case $M_1( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
 For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
@@
 The physical significance of $\theta$ will be manifest in the scattering process described below.
-We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ derivative to extract the left and right going modes.
-For example, $\partial_{-} \phi^2$ will be a function $t - x$ only and hence represent a right going mode on the right half plane.
-It is then one of the scattering products that leave the interface.
+We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes.
+For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane.
+It is then one of the scattering products that leaves the interface.
 On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain.
@@
 \end{aligned}\end{equation}
-
 and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
-
 \begin{equation}\begin{aligned}
@@
 For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices.
-The fact of their wavelength independence is an indication of the interface's scale invariance.
+The fact of their wavelength independence is an indication of scale invariance of the interface.
 
@@
 \includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
-\caption{{\color{red} folding picture text}}
+\caption{Folding picture for penetrable interface.
+Left panel: World line of the penetrable interface.
+$\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domain.
+Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$.
+The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.}
 \label{fig:folding_pic}
@@
 
-If we quantize the Boson theory on the interface line $x = 0$, these gluing condition becomes an operator identity for the Boson creation and annihilation of the modes.
+If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes.
 We shall interpret these identities to be valid only when acting on the boundary states.
-The mode expansion of free Boson on $x = 0$\cite{di_francesco_conformal_1997} is
+The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
 \begin{equation}
@@
 
-\todo[inline]{say sth: connecting to what will follow etc? }
-
 %%% Local Variables:

### 2017-05-21 intro.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}.
-Operators close to the boundary are interpreted as boundary condition changing operator\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
+Operators close to the boundary are interpreted as boundary condition changing operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
 Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}.
-One example is the "Anderson orthogonality catastrophe", where the core hole creates a potential that act as an impurity to the conduction band.
+One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band.
 The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
-There are numerous impurity problem of this kind that has been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
+There are numerous impurity problems of this kind that have been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
 
@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-The "cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system.
-As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve.
+The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system.
+As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connects them at $t = 0$ and evolves.
 Various quantities are used to detect the information in the quench process.
 For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems.
-And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitation emitted at the joint.
-Ref.~\onlinecite{vasseur_universal_2014} take A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution.
-In this mode, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.
+And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint.
+Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution.
+In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\textwidth]{fig_cut_and_join.pdf}
+\begin{figure}[h]
+\includegraphics[width=1\columnwidth]{fig_cut_and_join.pdf}
 \caption{Cut-and-join quench protocol.
-Left panel: prepare the ground states of two separated chains and joined them at $t = 0$, then do the time evolution with whole chain Hamiltonian.
+Left panel: prepare the ground states of two separated chains and joine them at $t = 0$, then do the time evolution with whole chain Hamiltonian.
 Right panel: spacetime diagram of the cut and join protocol.
@@
 % All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
-In the path integral language, the "cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}.
+In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}.
 The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them.
-Before the quench, the slit before $t = 0$ represents the boundary that are completely reflective to the injecting particles.
+Before the quench, the slit represents boundaries that are completely reflective to the injecting particles.
 The joining turns on the transmission from one side to the other.
-In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of \onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.
+In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.
 
-It would therefore be interesting to consider to connect two different CFTs in the "cut-and-join" protocol.
+It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol.
 The interface produced will interpolate between the total reflective and complete transparent ones.
 It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}.
-There is also non-compact free boson/free fermion lattice realization, which was used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties.
+There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties.
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
 In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses.
-We expect it to be tunable in the a realistic experimental setting.
+We expect it to be tunable in a realistic experimental setting.
 
@@
 Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench.
-There is no dynamic information in fidelity, nevertheless its finite size effect also reveal the boundary critical exponent that maybe be diagnostic in Loschmidt echo computation.
+There is no dynamic information in fidelity, nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic in Loschmidt echo computation.
 The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$.

### 2017-05-21 num_result.tex
[draft] conclusion draft out; fidelity figure revised
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results.
-Our numerical evaluations is based on Boson Bogoliubov transformation and explicit form of the groundstates.
+Our numerical evaluations is based on boson Bogoliubov transformation and the explicit form of the groundstates.
 The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details.
@@
 \end{equation}
-and shows its Loschmidt echo in Fig.~\ref{fig:DDDD}.
+and show its Loschmidt echo in Fig.~\ref{fig:DDDD}.
 The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay.
@@
 The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $.
-To avoid subjective choice of data points, we repeat 5 times to randomly pick {\color{red} 10 points} before the finite size revival surges to obtain the deviation.
+To avoid subjective choice of data points, we repeat 5 times to randomly pick {\color{red} 10 points} before the finite size revival surges, followed by taking the mean and standard deviation.
 We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.
 
-We also calculate the companion process
+We also calculated the companion process
 \begin{equation}
@@
 and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}.
-The avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
-While the short time decay pattern are different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity.
+We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
+While the short time decay pattern is different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity.
 We therefore do not present the result here.
@@
 A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
-We therefore turn to another regulator that shift the far end boundary condition DN to $\mathcal{S}_1( \delta \theta )$ and consider the following process
+We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
 \begin{eqnarray}\begin{aligned}
@@
 Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process.
-This "shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}.
+This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}.
 The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
@@
 \includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
-\includegraphics[width=1\columnwidth]{DN_DN2tan.pdf}
+\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
     \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
@@
 \end{equation}
-in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occur at $\theta \frac{\pi}{4}$. We therefore apply the shift regulator there 
+in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
 \begin{equation}
@@
 \end{equation}
-where we take $\theta=0.003\pi$. The $\theta$ dependent exponents now is a shifted quadratic curve symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.
+where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are shifted quadratic curves symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.
 
@@
 The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi,0.24\pi$ and $0.48\pi$.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi,0.18\pi$ and $0.24\pi$.
 The finite size effect do not emerge before $t=10^{4}$.

### 2017-05-21 pf_of_id.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

@@
 \label{eq:first_id_app_pf_of_id}
-\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
+e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger} }  = e^{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger} } e^{- \vec{b}^{\dagger} M \vec{b} } 
+%\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
 \end{equation}
@@
 \begin{aligned}
-  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}  =  
-  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger  \Big\} \\
-& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
+  e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger }  =  
+  e^{- \vec{d}^{\dagger} \Lambda \vec{d} } e^{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger } = \prod_i  e^{- \lambda_i d_i^{\dagger} d_i } e^{  d_i^{\dagger} \bar{d}_i ^{\dagger} }
+%  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}  =  
+%  \exp\Big\{- \vec{d}^{\dagger} \Lambda \vec{d}  \Big\} \exp \Big\{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger  \Big\} \\
+%& = \prod_i  \exp\Big\{- \lambda_i d_i^{\dagger} d_i  \Big\} \exp \Big\{  d_i^{\dagger} \bar{d}_i ^{\dagger}  \Big\}
 \end{aligned}
@@
 \begin{aligned}
- \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}   &= \prod_i \exp \Big\{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
- & = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
+e^{- \vec{b}^{\dagger} M \vec{b} } e^{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger }   &= \prod_i e^{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i }  e^{-\lambda_i  d^{\dagger}_i d_i }  = e^{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger} e^{- \vec{b}^{\dagger} M \vec{b} }
+% \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}   &= \prod_i \exp \Big\{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
+ %& = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
 \end{aligned}
@@
 \label{eq:second_id_in_app_pf_of_id}
-Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
+Z_{ab} = \langle 0 | e^{ \vec{b} R_a^* \vec{\bar{b}} } e^{ - \vec{b}^{\dagger} M  \vec{b} } e^{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger} }  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
+%Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
 \end{equation}

### 2017-05-22 abstract.tex
[draft] abstract and structure of paper added

We study the quantum quench problem for a class of bosonic conformal interface by computing the fidelity and Loschmidt echo. The scattering matrix $S(\theta)$ associated with the permeable interfaces are classified into two sectors of $O(2)$ group. The fidelity and Loschmidt echo decay algebraically as $t^{-\alpha}$ after the quench. The exponent $\alpha$ is found to depend on the change of $\theta$ as a quadratic relation if the boundary conditions (before and after quench) are in the same sectors of $O(2)$, while remain $\frac{1}{4}$ if they belong to different sectors. We confirm our results by various numerical simulations. The winding modes of compact bosons will have no contribution at leading order. We expect such conformal interface can be realized in a wide range of experiments of one-dimensional bosonized electron gas.

%1. cut and joint two different CFT

%7 Experiment

### 2017-05-22 intro.tex
[draft] abstract and structure of paper added

@@
 
-% structure of the paper.
-\todo[inline]{structure of the paper}
+The rest of the paper is organized as follows.
+
+In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable interface and its lattice realization.
+
+In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison.
+We discuss our results and related experimental works in Sec.~\ref{sec:disc}.
+Finally we conclude in Sec.~\ref{sec:conclusion}.
+
+In App.~\ref{app:F_correction}, we point out two corrections to the free energy, namely boundary logarithmic term and Schwarzian term.
+We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}.
+The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}.
+In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation.
+We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}.
+The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}.
+Throughout this paper, we work exclusively with the oscillator modes of free bosons.
+In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} have contribution to the free energy at the leading order.
+Therefore the results presented in this paper remain valid in the more general case where two compactified bosons of different radii are connected by a conformal interface.
 

### 2017-05-22 interface_free_boson.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow
[data] PP figure python version out

@@
-\todo[inline]{Mao: I suggest to relocate this part to an appendix, and maybe more details can be filled in, especially scale invariance condition imposed on the $\Sigma$.
-In the main text, just cite the relation between $\Sigma$ and $S$ and proceed}
-In this appendix, we demonstrate how to realize scale invariant S-matrix in a lattice regularization. Following Sec.~\ref{sec_sub:free_boson_lattice}, we consider the following harmonic chain 
+In this appendix, we demonstrate how to realize conformal interface in a lattice harmonic chain defined in Sec.~\ref{sec_sub:free_boson_lattice},
+\todo[inline]{Mao: Your expression of the Hamiltonian is wrong! Please note the coefficients of the cross $\phi_1 \phi_0$ term. }
 \begin{equation}
-H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
-\Sigma
+\begin{aligned}
+H =& \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  \\
+ &+ \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\begin{bmatrix}
+1 + \Sigma_{11}  & \Sigma_{12} \\
+\Sigma_{21} &  1 + \Sigma_{22} \\
+\end{bmatrix}
 \begin{pmatrix}
@@
 \end{pmatrix}
+\end{aligned}
 \end{equation}
-where the matrix $\Sigma$ parameterize two-site interaction between site 0 and 1.
-To find the scattering matrix, we set up the plane wave scattering problem across the interface with the following ansatz (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
+where the matrix $\Sigma$ parameterizes the two-site interaction between site 0 and 1.
+We set up the plane wave scattering problem across the interface with the following ansatz (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
 \begin{equation}
@@
   \begin{aligned}
-    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
-    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
+	& A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
+	& B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
   \end{aligned} \right. 
@@
 where $a$ is the lattice constant.
-Upon solving the equation of motion far away from the interface, it is found that the system is gapless with the dispersion relation $\omega = \left|2\sin\frac{k}{2}\right|$.
-The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}.
-After some algebra, the incoming and outgoing amplitudes are related via
+The solution on both semi-infinite chains are gapless with the dispersion relation $\omega = \left|2\sin\frac{ka}{2}\right|$.
+The $S$ matrix connecting them can be found by relating the incoming and outgoing amplitudes
 \begin{widetext}
@@
 \end{equation}
-and the scattering matrix can be solved as
+and the explicit expression is
 \begin{equation}
@@
 \end{widetext}
-The S matrix elements are reflection and transmission coefficients.
-In order to have a scale invariant interface, they need to be $k-$independent.
-Therefore the necessary condition is that the ratio $|S_{11}/S_{21}|$ is independent of $k$, which implies
+
+The reflection and transmission coefficients associated with this interface contained in the $S$ matrix and both of them have to be $k-$independent to form a conformal interface\cite{peschel_exact_2012}.
+A necessary condition is that $|S_{12}|$ must be $k$-independent.
+If $\Sigma_{12} = \Sigma_{21} = 0 $, we have
+\begin{equation}
+  S_{11} = - \frac{\Sigma_{11} + e^{ika} }{\Sigma_{11} + e^{-ika}}
+\end{equation}
+which is not scale invariant. The only remaining possibility is
 \begin{equation}
@@
 \end{equation}
-Therefore, we have the scale invariant S-matrix as
+which leads to a scale invariant S-matrix 
 \begin{equation}
@@
 \end{equation}
-In the actual simulation, we evolved a large enough system for a long time, such that a field theoretic description can be applied.
 In this continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
@@
 \end{equation}
-where $\lambda\in\mathbb{R}$ is the parameter for $S_1(\theta)$, as emphasized in Sec.~\ref{sec:notation}.
-This simple relation between $\Sigma$ and the S-matrix provides a tool to check our analytic results.
+where $\lambda\in\mathbb{R}$ is the parameter for $S_1(\theta)$, as introduced in Sec.~\ref{sec:notation}.
+
+We use this series of two-site to model the $S_1(\theta)$ type conformal interface, as they give the same $S$ matrix in the continuum limit.
+Therefore, the large $t$ behavior of its Loschmidt echo should match with our field theoretic prediction.
 

### 2017-05-22 codes/PP_fidel_fit.py

@@ -16,8 +16,9 @@ rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
 rc( 'text', usetex = True )
 rcParams['legend.numpoints'] = 1
 rcParams['axes.linewidth'] = 0.5
+colorList={0:"#ff2222", 1:'#ffa500', 2:'#4488ff', 3:"#0000aa", 4:'#66bb22'}
 
-folder = 'DDNN_fidel'
+folder = 'PP_fidel'
 path = "../data/" + folder + "/"
 fig_path = "../images/"
 figname = fig_path + folder + "_fit.pdf"
@@ -36,8 +37,9 @@ def fit_data( x, y ):
     log_x = np.log( x ) / np.log( 10 )
     log_y = np.log( y ) / np.log( 10 )
 
-    log_x = log_x[ x > 2.5 ]
-    log_y = log_y[ x > 2.5 ]
+    data_range = np.logical_and( ( log_x > 2 ) , ( log_x < 5 ) )
+    log_x = log_x[ data_range ]
+    log_y = log_y[ data_range ]
 
     slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
 
@@ -54,13 +56,13 @@ x = []
 
 for filename in dataset:
     data = np.loadtxt( path + filename )
-    t = data[:,0]
-    echo = data[:,1]
+    L = data[:,0]
+    F = data[:,1]
 
     # extract x = theta / pi from filename
     x.append( float( filename ) )
     
-    this_slope, this_error = fit_data( t, echo );
+    this_slope, this_error = fit_data( L, F );
     slope.append( this_slope )
     error.append( this_error )
 
@@ -74,9 +76,13 @@ slope = slope[idx]
 error = error[idx]
 
 # inset data
-inset_data = np.loadtxt( path + dataset[1] )
-t_inset = inset_data[:,0]
-echo_inset = inset_data[:,1]
+inset_x = [1, 11, 16]
+L_inset = []
+F_inset = []
+for i in inset_x:
+    inset_data = np.loadtxt( path + dataset[i] )
+    L_inset.append( inset_data[:,0] )
+    F_inset.append( inset_data[:,1] )
 
 # ---------------------------------------------------------------------- 
 #                           plot and insets                            |
@@ -84,9 +90,10 @@ echo_inset = inset_data[:,1]
 
[…]

### 2017-05-23 compact_boson.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow
[draft] App. G done

@@
-\todo[inline]{Remember to mention in the main text, winding sectors have no contribution}
-
 In this appendix, we address the issue of winding modes of compact bosons.
-In the main text, we exclusively work with the oscillator modes of free bosons.
+In the main text, we have exclusively worked with the oscillator modes of free bosons.
 Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order.
@@
 Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, then mode expansion will have zero mode
+
+\begin{widetext}
 \begin{equation}
@@
 \begin{equation}
+\label{eq:zzbar}
 z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
@@
 \begin{aligned}
-\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
-&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
+\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n }
 \end{aligned}
 \end{equation}
+\end{widetext}
 We further identify 
@@
 \begin{equation}
+\begin{aligned}
 i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
+\end{aligned}
 \end{equation}
@@
 
-\todo[inline]{Say the caveat, where is the bounadry}
+Following the treatment of boundary CFT in Ref.~\onlinecite{di_francesco_conformal_1997}, we shall quantize the theory by imposing \emph{equal-time} commutator for $a_n$ and $\bar{a}_n$ in Eq.~\eqref{eq:boson-mode-exp}.
+The conformal boundary state will be defined on a constant time slice, say $t=0$.
+For the permeable wall connecting two compactified bosons, this results in folding $t\rightarrow-t$ rather than $x\rightarrow-x$ as in the main text.
+Since the two cases are {\bf T}-dual to each other, the results are not affected.
 
-We recall that the conformal boundary condition can be written as
+%Before we invoke the folding trick, we need to note one important caveat here.
+In the usual treatment of boundary CFT, for example in , the field is quantized on the real axis.
+As emphasized in Sec.~\ref{sec:bosonic_conformal_interface}, the gluing condition becomes an operator identity of creation and annihilation operators, which is valid \emph{only} when acting on the conformal boundary states.
+
+We recall that the gluing condition is written as
+\begin{equation}\begin{aligned}
+\label{eq:def_M}
+\begin{pmatrix}
+\partial_t\phi^1\\
+\partial_x\phi^1
+\end{pmatrix}_{t=0^-}
+=M\begin{pmatrix}
+\partial_t\phi^2\\
+\partial_x\phi^2
+\end{pmatrix}_{t=0^+}
+\end{aligned}\end{equation}
+where the derivatives are evaluated at the appropriate limit.
+In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$.
+Therefore we establish the scattering matrix as
 \begin{equation}
@@
 \end{equation}
-where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}. The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
+%The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
+%\begin{equation}
+%\begin{aligned}
+%\label{eq:def_S_in_app_2}
+%\begin{pmatrix}
+%\partial_+\phi^1\\
+%\partial_+\phi^2
+%\end{pmatrix}
+%=S(\theta)
+%\begin{pmatrix}
+%\partial_-\phi^1\\
+%\partial_-\phi^2
+%\end{pmatrix}
+%\end{aligned}
+%\end{equation}
+%Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
+%\begin{equation}
+%\begin{aligned}
+%\label{eq:def_S_in_app_2}
+%\sum_{n\in\mathbb{Z}}
+%\begin{pmatrix}
+%\bar{a}_n^1\bar{z}^{-n}\\
+%\bar{a}_n^2\bar{z}^{-n}
+%\end{pmatrix}
+%=S(\theta)
+%\sum_{n\in\mathbb{Z}}
+%\begin{pmatrix}
+%a_n^1{z}^{-n}\\
+%a_n^2{z}^{-n}
+%\end{pmatrix}
+%\end{aligned}
+%\end{equation}
+%As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
+%\begin{equation}\begin{aligned}
+%a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
+%\end{aligned}\end{equation}
+%The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}. 
+The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
 \begin{equation}
@@
 \bar{a}_n^1\bar{z}^{-n}\\
-\bar{a}_n^2\bar{z}^{-n}
+a_n^2z^{-n}
 \end{pmatrix}
-=S(\theta)
+=-S(\theta)
 \sum_{n\in\mathbb{Z}}
@@
 a_n^1{z}^{-n}\\
-a_n^2{z}^{-n}
+\bar{a}_n^2\bar{z}^{-n}
 \end{pmatrix}
@@
 \begin{equation}\begin{aligned}
-a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
+a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
 \end{aligned}\end{equation}
-The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.
+The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign.
+Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.
 
@@
 \begin{equation}\begin{aligned}
-Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
+Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
 \end{aligned}\end{equation}
-Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy.
+The integral is a constant, thus the winding mode will contribute at most a $\ln\beta$ term to the free energy.
 Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.

### 2017-05-23 compact_boson.tex
[draft] todo added to App.G

@@
 We recall that the gluing condition is written as
-\begin{equation}\begin{aligned}
-\label{eq:def_M}
-\begin{pmatrix}
-\partial_t\phi^1\\
-\partial_x\phi^1
-\end{pmatrix}_{t=0^-}
-=M\begin{pmatrix}
-\partial_t\phi^2\\
-\partial_x\phi^2
-\end{pmatrix}_{t=0^+}
-\end{aligned}\end{equation}
-where the derivatives are evaluated at the appropriate limit.
-In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$.
-Therefore we establish the scattering matrix as
 \begin{equation}
@@
 \end{equation}
-%The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
+The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
+\begin{equation}
+\begin{aligned}
+\label{eq:def_S_in_app_2}
+\begin{pmatrix}
+\partial_+\phi^1\\
+-\partial_+\phi^2
+\end{pmatrix}
+=S(\theta)
+\begin{pmatrix}
+\partial_-\phi^1\\
+-\partial_-\phi^2
+\end{pmatrix}
+\end{aligned}
+\end{equation}
+For convenience, we shift $\phi^2\rightarrow-\phi^2$ by a sign.
+This amounts to reparameterize the S-matrix and exchange the two sectors of $O(2)$ group.
+But this will not change our conclusion in the main text.
+\todo[inline]{Check the parameterization} 
+Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
+\begin{equation}
+\begin{aligned}
+\label{eq:def_S_in_app_2}
+\sum_{n\in\mathbb{Z}}
+\begin{pmatrix}
+\bar{a}_n^1\bar{z}^{-n}\\
+\bar{a}_n^2\bar{z}^{-n}
+\end{pmatrix}
+=S(\theta)
+\sum_{n\in\mathbb{Z}}
+\begin{pmatrix}
+a_n^1{z}^{-n}\\
+a_n^2{z}^{-n}
+\end{pmatrix}
+\end{aligned}
+\end{equation}
+As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
+\begin{equation}\begin{aligned}
+a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
+\end{aligned}\end{equation}
+The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.
+
+%We recall that the gluing condition can written as
+%\begin{equation}\begin{aligned}
+%\label{eq:def_M}
+%\begin{pmatrix}
+%\partial_t\phi^1\\
+%\partial_x\phi^1
+%\end{pmatrix}_{t=0^-}
+%=M\begin{pmatrix}
+%\partial_t\phi^2\\
+%\partial_x\phi^2
+%\end{pmatrix}_{t=0^+}
+%\end{aligned}\end{equation}
+%where the derivatives are evaluated at the appropriate limit.
+In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$.
+Therefore we establish the scattering matrix as
+%\begin{equation}
+%\begin{aligned}
+%\label{eq:def_S_in_app}
+%\begin{pmatrix}
+%\partial_+\phi^1\\
+%\partial_-\phi^2
+%\end{pmatrix}
+%=S(\theta)
+%\begin{pmatrix}
+%\partial_-\phi^1\\
+%\partial_+\phi^2
+%\end{pmatrix}
+%\end{aligned}
+%\end{equation}
+%
+%The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
 %\begin{equation}
@@
 %\end{equation}
-%Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
+%We note that the parameterization of S-matrix is \emph{different} from Eq.~\eqref{eq:def_S}, but this will not change our conclusions in the main text.
+Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
 %\begin{equation}
@@
 %\end{pmatrix}
-%=S(\theta)
+%=-S(\theta)
 %\sum_{n\in\mathbb{Z}}
@@
 %\end{equation}
+%\todo[inline]{Check the sign and parameterization of S}
 %As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
 %\begin{equation}\begin{aligned}
-%a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
+%a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
 %\end{aligned}\end{equation}
-%The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}. 
-The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
-\begin{equation}
-\begin{aligned}
-\label{eq:def_S_in_app_2}
-\begin{pmatrix}
-\partial_+\phi^1\\
-\partial_+\phi^2
-\end{pmatrix}
-=S(\theta)
-\begin{pmatrix}
-\partial_-\phi^1\\
-\partial_-\phi^2
-\end{pmatrix}
-\end{aligned}
-\end{equation}
-Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
-\begin{equation}
-\begin{aligned}
-\label{eq:def_S_in_app_2}
-\sum_{n\in\mathbb{Z}}
-\begin{pmatrix}
-\bar{a}_n^1\bar{z}^{-n}\\
-a_n^2z^{-n}
-\end{pmatrix}
-=-S(\theta)
-\sum_{n\in\mathbb{Z}}
-\begin{pmatrix}
-a_n^1{z}^{-n}\\
-\bar{a}_n^2\bar{z}^{-n}
-\end{pmatrix}
-\end{aligned}
-\end{equation}
-As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
-\begin{equation}\begin{aligned}
-a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
-\end{aligned}\end{equation}
-The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign.
+%The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign.
 Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.

### 2017-05-23 abstract.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
-We study the quantum quench problem for a class of bosonic conformal interface by computing the fidelity and Loschmidt echo.
-The scattering matrix $S(\theta)$ associated with the permeable interfaces are classified into two sectors of $O(2)$ group.
-The fidelity and Loschmidt echo decay algebraically as $t^{-\alpha}$ after the quench.
-The exponent $\alpha$ is found to depend on the change of $\theta$ as a quadratic relation if the boundary conditions (before and after quench) are in the same sectors of $O(2)$, while remain $\frac{1}{4}$ if they belong to different sectors.
-We confirm our results by various numerical simulations.
-The winding modes of compact bosons will have no contribution at leading order.
-We expect such conformal interface can be realized in a wide range of experiments of one-dimensional bosonized electron gas.
+We study the quantum quench problem for a class of bosonic conformal interface by computing the Loschmidt echo and the bipartite fidelity.
+These boson conformal interfaces can be viewed as the change of boundary conditions (quench) when connecting two one-dimensional critical systems.
+They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface.
+The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$.
+We perform analytic and numerical calculation of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
+Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.
 
-%1. cut and joint two different CFT
-
-%7 Experiment
+%%% Local Variables:
+%%% TeX-master: "bCFT_paper"
+%%% TeX-PDF-mode: t
+%%% End:

### 2017-05-23 analy_eval.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
-In this subsection, we relate the free energy to the amplitudes between boundary states and give analytic results.
+In this subsection, we relate the free energy to the amplitudes between boundary states and present the analytic results.
 
@@
 
-We thus add small semi-circles around the points where the bcc operators reside, followed a series of conformal mapping.
+We thus add small semi-circles around the points where the bcc operators reside, followed by a series of conformal mapping.
 For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}.
@@
 Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
-The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function
+The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function is
 \begin{equation}
@@
 Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
-In the $\xi$ plane, we end with the same diagram as fidelity.
+In the $\xi$ plane, we end up with the same diagram as fidelity.
 With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.
@@
 But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation.
-In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law increase of Loschmidt echo, which does not agree with the known results.
-One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence
+In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law surge of Loschmidt echo, which does not agree with the known results.
+One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
 \begin{equation}

### 2017-05-23 bCFT_paper.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)
[draft] discussion restored.
[draft] add boson bogoliubov transformation original tex file
1. Hamiltonian changed to A B notation 2. bmatrix, pmatrix used 3. \tilde{S} changed to \mathcal{S} 4. labeling changed
[draft] App. A draft finished.
[draft] 1. compact boson moved to appendix 2. added compact_boson but just started 3. general formulation nearly finis

--- 2017-04-17 bCFT_paper.tex
@@
-\documentclass[preprint, prb]{revtex4-1}
+\documentclass[reprint, prb]{revtex4-1}
 \usepackage{amsmath}
@@
 \usepackage{bm}
-\usepackage[font={footnotesize}]{caption}
+\usepackage[caption=false]{subfig}
 \usepackage{todonotes}
+\usepackage{comment}
+\graphicspath{{./}{./images/}}
 \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
@@
 \usepackage[all]{hypcap}
-
 \renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
@@
 \begin{abstract}
+\input{abstract}
 \end{abstract}
@@
 \section{Introduction}
-% the last one to be finished.
+\input{intro}
 
 \section{Bosonic Conformal Interface}
+\label{sec:bosonic_conformal_interface}
 \subsection{General Formulation}
-% M, S
-% special case
-\subsection{Physical Realization: Connecting Bosons of Different Compactification Radii}
-% free boson + compact
+\label{sec_sub:general_formulation}
+\input{general_formulation}
 \subsection{A Free Boson Lattice Model}
-% cite Calabrese, introduce the model
-% lattice model S matrix
+\label{sec_sub:free_boson_lattice}
+\input{free_boson_lattice}
 
 \section{Bipartite Fidelity and Loschmidt Echo}
+\label{sec:analytic_numerics}
 \subsection{Definition}
-% definition
-% general discussion
-
-\section{Analytic and Numerical Results}
-\subsection{Fidelity}
-% analytic: conformal transformation
-% numerical comparison 
-\subsection{Loschmidt Echo}
-% analytic: conformal transformation
-% numerical comparison
+\input{def_fidel_echo}
+\subsection{Notation of Boundary Conditions}
+\label{sec:notation}
+\input{bd_notation}
+\subsection{Analytic Evaluation}
+\label{sec_sub:analy_eval}
+\input{analy_eval}
+\subsection{Numerical Results and Comparison}
+\input{num_result}
 
 \section{Discussion}
+\label{sec:disc}
+\input{disc}
+
+\section{Conclusion}
+\label{sec:conclusion}
+\input{conclusion}
 
 \begin{acknowledgments}
-\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
+\todo[inline]{Mao: funding number?}
+We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Taylor Hughes and Romain Vasseur during the course of this research. 
 TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
-    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
-    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
-    Supercomputing Applications (NCSA) and which is supported by funds from the University of
-    Illinois at Urbana-Champaign.
+This work made use of the Illinois Campus Cluster, a computing resource that is operated by the Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for Supercomputing Applications (NCSA) and which is supported by funds from the University of Illinois at Urbana-Champaign.
 \end{acknowledgments}
@@
 % 2. contribution from the boundary: cite Cardy 
+\label{app:F_correction}
+\input{F_correction}
+
+\section{Conformal Interface in Free Bosonic Lattice}
+\label{app:interface_free_boson}
+\input{interface_free_boson}
 
@@
 % Peschel_EE.pdf
+\label{app:comp_fid_echo}
+\input{comp_fid_echo}
 
 \section{A Determinant Identity for the Boundary State Amplitude}
+\label{app:pf_of_id}
 % copy notes app. C
-
-\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
-% copy notes app. B
+\input{pf_of_id}
 
 \section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
+\label{app:gnd_dn_lambda}
 % copy notes app. A
+\input{gnd_dn_lambda}
+
+\section{General Boundary State Amplitude}
+\label{app:lambda_12}
+% copy notes app. B
+\input{lambda_1_lambda_2}
+
+\section{Winding Modes of Compact Bosons}
+% free boson + compact
+\label{app:compact_diff_boson}
+\input{compact_boson}
 

### 2017-05-23 bd_notation.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 We use chemical reaction style to represent the change of boundary conditions.
-Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents status on two ends of the chain before and after the quench.
+Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench.
 The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface.
@@
 Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$.
-To remove the bcc operator from $c$ to $a$ at infinity, we usually take $a = c$ in the numerical calculation.
+To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.
 
@@
 \end{equation}
-The scaling dimension of this bcc operator does indeed deviate from the completely transmitting case for certain choice of boundary conditions.
-
 Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e.

### 2017-05-23 compact_boson.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 
-\subsection{Gluing Condition for Winding Modes}
+\subsection{Gluing Condition for the Winding Modes}
 \label{app_sub:compact_gluing_boundary}
 
-Following the treatment of boundary CFT in Ref.~\onlinecite{di_francesco_conformal_1997}, we shall quantize the theory by imposing \emph{equal-time} commutator for $a_n$ and $\bar{a}_n$ in Eq.~\eqref{eq:boson-mode-exp}.
-The conformal boundary state will be defined on a constant time slice, say $t=0$.
-For the permeable wall connecting two compactified bosons, this results in folding $t\rightarrow-t$ rather than $x\rightarrow-x$ as in the main text.
-Since the two cases are {\bf T}-dual to each other, the results are not affected.
+Here we solve the boundary state on the $t = 0$ slice.
+Our actual boundary state used in the text corresponds to the $x = 0$ slice.
+There is a $x \rightarrow t$ exchange in the convention here.
+However, that amounts to the change of $\theta \rightarrow \frac{\pi}{2} - \theta$ in the $S$ matrix argument.
 
-%Before we invoke the folding trick, we need to note one important caveat here.
-In the usual treatment of boundary CFT, for example in , the field is quantized on the real axis.
-As emphasized in Sec.~\ref{sec:bosonic_conformal_interface}, the gluing condition becomes an operator identity of creation and annihilation operators, which is valid \emph{only} when acting on the conformal boundary states.
-
+\todo[inline]{Mao: this is not a T-dual transformation, it is DN -> ND. }
 We recall that the gluing condition is written as
@@
 \end{equation}
-The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
-\begin{equation}
-\begin{aligned}
-\label{eq:def_S_in_app_2}
-\begin{pmatrix}
-\partial_+\phi^1\\
--\partial_+\phi^2
-\end{pmatrix}
-=S(\theta)
-\begin{pmatrix}
-\partial_-\phi^1\\
--\partial_-\phi^2
-\end{pmatrix}
-\end{aligned}
-\end{equation}
-For convenience, we shift $\phi^2\rightarrow-\phi^2$ by a sign.
-This amounts to reparameterize the S-matrix and exchange the two sectors of $O(2)$ group.
-But this will not change our conclusion in the main text.
-\todo[inline]{Check the parameterization} 
+
 Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
@@
 \begin{equation}
-  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
+  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
 \end{equation}
@@
 \end{equation}
-and the conformal boundary state reads
+and the conformal boundary state
 \begin{equation}\begin{aligned}
+\label{eq:S1bd-state}
 g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
@@
 The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}.
-Since it is not important for what follows, we shall not repeat the calculation here.
-Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in a similar parameter $\lambda$ and boundary state.
-We omit the expression here because the main text does not use it.
+Since it is not important for what follows, we shall not include the calculation here.
+
+Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraints on the winding number
+\begin{equation}
+\vec{M} = \frac{\cot \theta}{g} 
+\begin{bmatrix}
+0 & -1\\
+1 & 0 \\                                
+\end{bmatrix}
+\vec{M}^*
+\end{equation}
 
@@
 \begin{equation}\begin{aligned}
-Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
+Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
 \end{aligned}\end{equation}
-To that end, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).
+With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).
 
@@
 \label{eq:Z0}
-Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
+Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
 \end{aligned}
 \end{equation}
+where the equality only is only taken when the two boundary states are identical.
+
 In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
 \begin{equation}\begin{aligned}
-Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
+Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
 \end{aligned}\end{equation}
-The integral is a constant, thus the winding mode will contribute at most a $\ln\beta$ term to the free energy.
-Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.
-
-For the case $\lambda_1\neq\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$.
-The same conclusion still holds in the limit $\beta\rightarrow\infty$.
+The winding mode thus can contribute at most a $\ln\beta$ term to the free energy.
+Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.
 

### 2017-05-23 conclusion.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
-In this paper, we analyze a class of boson conformal interfaces by computing the fidelity and Loschmidt echo.
+In this paper, we analyze a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.
 
-We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ while `DN' and $P$ belongs to $S_2$.
-A harmonic chain model allows us to realize part of these boundary conditions, including the partially-transmitive ones, on a concrete setting.
+We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$.
+A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions a concrete lattice setting.
 
-The study of the Loschmidt echo are a generalization of the conventional ``cut-and-join" protocol.
+The study of the Loschmidt echo is a generalization of the conventional ``cut-and-join" protocol.
 Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient.
-Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices.
-While the exponent will depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$.
+Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices and depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$s.
 
-These two features are tested in three typical processes in the numerical calculation.
+These two features are tested in three typical processes in the numerical calculation of the harmonic chains.
 After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error.
-Although irrelevant to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement, providing more confidence about the analytic results.
+Although tangential to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.
 
-We proposed that the Loschmidt echo exponent in principle should be realizable in connecting two quantum wire with an X-ray type experiment.
+We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on quantum wires systems.
 

### 2017-05-23 def_fidel_echo.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 \end{figure}
-\todo[inline]{Tianci: Change the single slit to double slit at the LHS, and add $\tau$ at the RHS?}
+\todo[inline]{Mao: double slits on the LHS, tau on the RHS, please confirm.}
+
 If the interface is completely transparent, i.e.
@@
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
-From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator.
+From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing (bcc) operator.
 These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-05-23 disc.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces.
-Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will be mainly discuss the echo properties.
+Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.
 
@@
 We find that if the conformal interfaces are of different types, i.e.
-$i \ne j$, the echo is always $\frac{1}{4} \ln t$, regardless of the theta angle.
+$i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles.
 The two types of conformal interface do not talk to each other because they impose on different fields.
-If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ one of them on the duel field of $\phi$.
-In the derivation of the $M$ matrix, these two corresponds to the parts of the Lorentz group and can't be connected by taking singular value of $\lambda$.
+If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$.
+In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$.
 It is then reasonable to find an universal echo between them.
-The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
+The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
 
@@
 \begin{equation}
-{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
+{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
 \end{equation}
-which gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT.
-Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation.
+The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT.
+Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used).
 This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation.
-And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation.
+The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one $\frac{1}{4}$ is interpreted as the bcc operator dimension $\frac{1}{16}$ between D and N.
+This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$.
+In a rational boson theory, the possible number of primary fields are finite.
+It requires further study to identify these bcc operators and explore their physical significance.
+
+Numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, {\it does change} the scaling dimensional in a way that is not captured by our analytic computation.
 Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy.
@@
 \begin{equation}
-{\rm ND} + {\rm DN} \rightarrow \lambda + {\rm ND} 
+{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
 \end{equation}
-
-\todo[inline]{insert the ND + DN figure. Compare it with the DN + DN figure}
-
-Nevertheless the special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this and the $DD \rightarrow {\rm P}$ one  $\frac{3}{8}- \frac{1}{4} = \frac{1}{16} $ is interpreted as the bcc operator dimension between D and N.
-The picture is complete in this full ${\rm DN}$ to $\lambda $ transition.
+shown in Fig.~\ref{fig:PDN_fit}.
 
@@
 
-Aside from free lattice boson model for the numerical purposes, these set of boundary conditions can be realized in connecting two compact bosons.
+These set of boundary conditions can be realized in connecting two compact bosons.
 There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
@@
 The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides.
-A X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible.
+An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.
 

### 2017-05-23 free_boson_lattice.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 \begin{equation}
+\begin{aligned}
 \label{eq:lattice_H}
-H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
-\Sigma
+H &= \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2 \\
+& + \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\begin{bmatrix}
+1 + \Sigma_{11}  & \Sigma_{12} \\
+\Sigma_{21} &  1 + \Sigma_{22} \\
+\end{bmatrix}
 \begin{pmatrix}
@@
 \end{pmatrix}
+\end{aligned}
 \end{equation}
-%\begin{eqnarray}\begin{aligned}
-%H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
-%\begin{bmatrix}
-%1 + \Sigma_{11}  & \Sigma_{12} \\
-%\Sigma_{21} &  1 + \Sigma_{22} \\
-%\end{bmatrix}
-%\begin{pmatrix}
-%\phi_0 \\
-%\phi_1 
-%\end{pmatrix}
-%\end{aligned}\end{eqnarray}
-where the $2\times2$ matrix $\Sigma$ parameterizes two-site interaction.
-In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there.
-We perform the standard scattering analysis in App.~\ref{app:interface_free_boson}, and the scale invariant S-matrix reads
+where the $2\times2$ matrix $\Sigma$ parameterizes the two-site interaction.
+We performed the standard scattering analysis in App.~\ref{app:interface_free_boson}.
+For mode with momentum $k$, the only possible scale invariant S-matrix is
 \begin{equation}
-S = \frac{1}{1 - e^{-2ika } } ( -2i \sin ka ) \Sigma
- = - e^{ika} \Sigma
+S = - e^{ika} \Sigma
 \end{equation}
@@
 \end{equation}
-where $\lambda\in\mathbb{R}$. The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results.
+where $\lambda\in\mathbb{R}$.
+
+The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both Loschmidt echo and fidelity.
 

### 2017-05-23 general_formulation.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other.
-The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends here.
+The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there.
 This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}.
@@
 The physical significance of $\theta$ will be manifest in the scattering process described below.
-We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes.
+We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes.
 For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane.
@@
 \begin{equation}
-\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^n - \bar{a}_{-n } \bar{z}^{-n}   \right)
+\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right)
 \end{equation}
-where take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
+where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
 \begin{equation}
-z= e^{ 2\pi ( i\tau - x ) / T } \quad \bar{z} = e^{ -2\pi ( i\tau + x ) / T }
+z= e^{ 2\pi i(x - t) / T } \quad \bar{z} = e^{ 2\pi i( x + t  ) / T }
 \end{equation}
@@
 \end{equation}
-where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.
-The calculation for the case $M=M_2(\theta)$ is completely analogous.
-Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.
+where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.
+
+The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.
 

### 2017-05-23 intro.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 % quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
-In (one-dimensional) quantum critical systems, the presence of physical boundary and isolated impurity weakly break the conformal symmetry.
-Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}.
-Operators close to the boundary are interpreted as boundary condition changing operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
-Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}.
+In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the system's conformal symmetry.
+Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}.
+Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
+Their correlation functions can exhibit different critical exponent from the bulk counterpart\cite{cardy_conformal_1984}.
 One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band.
 The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
-There are numerous impurity problems of this kind that have been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
+There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
 
@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system.
-As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connects them at $t = 0$ and evolves.
+The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system.
+As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve.
 Various quantities are used to detect the information in the quench process.
 For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems.
-And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint.
+The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint.
 Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution.
-In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.
+In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.
 
@@
 In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}.
-The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them.
+The separating ground states prepared before $t = 0$ are joined to form a new type of interface between them.
 Before the quench, the slit represents boundaries that are completely reflective to the injecting particles.
@@
 It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}.
-There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties.
+There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties.
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
@@
 
-In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable interface and its lattice realization.
+In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.
 
@@
 
-In App.~\ref{app:F_correction}, we point out two corrections to the free energy, namely boundary logarithmic term and Schwarzian term.
+This paper includes several appendices for technical details.
+In App.~\ref{app:F_correction}, we point out two corrections to the free energy, complementary to the argument made in the main text.
 We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}.
@@
 The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}.
-Throughout this paper, we work exclusively with the oscillator modes of free bosons.
-In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} have contribution to the free energy at the leading order.
-Therefore the results presented in this paper remain valid in the more general case where two compactified bosons of different radii are connected by a conformal interface.
+Up until this point, we work exclusively with the oscillator modes of free bosons.
+In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order.
+Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.
 

### 2017-05-23 num_result.tex
[data] PP figure python version out
[draft] App. G checked. PDN data added. Whole paper 1st pass.

@@
 We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results.
-Our numerical evaluations is based on boson Bogoliubov transformation and the explicit form of the groundstates.
+Our numerical evaluations is based on a boson Bogoliubov transformation and the explicit form of the groundstates.
 The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details.
-In all the figures, we present the coefficients of the logarithmic term $\mathcal{F} / \ln L$ and $\mathcal{F} / \ln t$ and call them fidelity and echo exponents respectively.
+In all the figures, we present the coefficients of the logarithmic term $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.
 
@@
 The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay.
-We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as a dashline for comparison.
+We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast.
 The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $.
-To avoid subjective choice of data points, we repeat 5 times to randomly pick {\color{red} 10 points} before the finite size revival surges, followed by taking the mean and standard deviation.
+The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution of the each point.
 We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.
@@
       \label{fig:DDNN}
-    \todo[inline]{Tianci: make the plots have the same style?}
 \end{figure}
@@
   \includegraphics[width=1\columnwidth]{PP_fit.pdf}
-    \includegraphics[width=1\columnwidth]{p_p2tan.pdf}
-    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
+    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
+    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
 The parameters are the same as those in Fig.~\ref{fig:DDNN}.
@@
     \label{fig:PPPP}
-    \todo[inline]{Mao: Put the PPPP for echo; Tianci: make the plots have the same style?}
+    \todo[inline]{Mao: Put the PP for echo;}
 \end{figure}
+
+Finally, we also provide the data for the process
+\begin{equation}
+{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}
+\end{equation}
+to evaluate the influence of the boundary condition $c$.
+It {\rm does} influence the scaling dimension, in a way that is not captured by our analytic calculation.
+Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
+\caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$.
+The boundary condition $c$ changes the scaling of the completely.
+The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$ and becomes smaller and approach zero for small $\theta$.
+}
+\label{fig:PDN_fit}
+\end{figure}
+
+\todo[inline]{May need to improve the figure quality.}
 

### 2017-05-23 codes/DDNN_fidel_fit.py

@@ -16,6 +16,7 @@ rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
 rc( 'text', usetex = True )
 rcParams['legend.numpoints'] = 1
 rcParams['axes.linewidth'] = 0.5
+colorList={0:"#ff2222", 1:'#ffa500', 2:'#4488ff', 3:"#0000aa", 4:'#66bb22'}
 
 folder = 'DDNN_fidel'
 path = "../data/" + folder + "/"
@@ -36,8 +37,9 @@ def fit_data( x, y ):
     log_x = np.log( x ) / np.log( 10 )
     log_y = np.log( y ) / np.log( 10 )
 
-    log_x = log_x[ x > 2.5 ]
-    log_y = log_y[ x > 2.5 ]
+    data_range = ( log_x < 4 )
+    log_x = log_x[ data_range ]
+    log_y = log_y[ data_range ]
 
     slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
 
@@ -54,13 +56,13 @@ x = []
 
 for filename in dataset:
     data = np.loadtxt( path + filename )
-    t = data[:,0]
-    echo = data[:,1]
+    L = data[:,0]
+    F = data[:,1]
 
     # extract x = theta / pi from filename
     x.append( float( filename ) )
     
-    this_slope, this_error = fit_data( t, echo );
+    this_slope, this_error = fit_data( L, F );
     slope.append( this_slope )
     error.append( this_error )
 
@@ -74,9 +76,13 @@ slope = slope[idx]
 error = error[idx]
 
 # inset data
-inset_data = np.loadtxt( path + dataset[1] )
-t_inset = inset_data[:,0]
-echo_inset = inset_data[:,1]
+inset_x = [1, 5, 40]
+L_inset = []
+F_inset = []
+for i in inset_x:
+    inset_data = np.loadtxt( path + dataset[i] )
+    L_inset.append( inset_data[:,0] )
+    F_inset.append( inset_data[:,1] )
 
 # ---------------------------------------------------------------------- 
 #                           plot and insets                            |
@@ -96,7 +102,9 @@ for cap in caps:
 # inset position
 left, bottom, width, height = [0.55, 0.27, 0.3, 0.25]
 ax2 = fig.add_axes( [left, bottom, width, height] )
[…]

### 2017-05-23 codes/PDN_fit.py

@@ -1,0 +1,116 @@
+#!/bin/env python3
+# ----------------------------------------------------------------------- 
+#                                header                                 |
+# ----------------------------------------------------------------------- 
+import glob
+from os import walk
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from matplotlib import rcParams
+import scipy.optimize
+import scipy.stats
+
+
+rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
+rc( 'text', usetex = True )
+rcParams['legend.numpoints'] = 1
+rcParams['axes.linewidth'] = 0.5
+colorList={0:"#ff2222", 1:'#ffa500', 2:'#4488ff', 3:"#0000aa", 4:'#66bb22'}
+
+folder = 'PDN'
+path = "../data/" + folder + "/"
+fig_path = "../images/"
+figname = fig_path + folder + "_fit.pdf"
+
+# get all the filenames in the subdirectory
+dataset = []
+for ( dirpath, dirnames, filenames ) in walk( path ):
+    dataset.extend( filenames )
+print( dataset )
+
+# ----------------------------------------------------------------------
+#                         error bar and slope                          |           
+# ----------------------------------------------------------------------
+def fit_data( x, y ):
+
+    log_x = np.log( x ) / np.log( 10 )
+    log_y = np.log( y ) / np.log( 10 )
+
+    data_range = np.logical_and( log_x > 1, log_x < 2.5 )
+    log_x = log_x[ data_range ]
+    log_y = log_y[ data_range ]
+
+    slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
+
+    log_x_mean = np.mean( log_x )
+    ssx = np.sum( np.square( log_x - log_x_mean ) )
+
+    error = np.sqrt( std_err / ssx )
+
+    return -slope, error 
+
+slope = []
+error = []
+x = []
+
+for filename in dataset:
+    data = np.loadtxt( path + filename )
+    t = data[:,0]
+    echo = data[:,1]
+
+    # extract x = theta / pi from filename
+    x.append( float( filename.split('_')[0] ) )
+    
+    this_slope, this_error = fit_data( t, echo );
+    slope.append( this_slope )
+    error.append( this_error )
+
+# sort index
+x = np.array( x )
+slope = np.array( slope )
[…]

### 2017-05-25 compact_boson.tex
[draft] App. G sign issue fixed.

@@
 Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.
+
 \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}
@@
 \subsection{Mode Expansion of Compact Boson}
-Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, then mode expansion will have zero mode
-
+Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
 \begin{widetext}
-\begin{equation}
-\begin{aligned}
-\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\  
-&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  +  \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\ 
-\end{aligned}
-\end{equation}
-where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. In the holomorphic coordinates
-\begin{equation}
-\label{eq:zzbar}
-z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
-\end{equation}
-the mode expansion becomes
 \begin{equation}
@@
 \end{aligned}
+\end{equation}\end{widetext}
+where $n,m$ are momentum and winding modes quantum numbers.
+
+In Ref.\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space.
+The boundary state we need here however lives on $x = 0$ -- a equal-space slice.
+We therefore exchange compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
+\begin{equation}
+\label{eq:zzbar}
+z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
 \end{equation}
-\end{widetext}
+This corresponds to exchange the $x$ and $t$ in Ref.\onlinecite{di_francesco_conformal_1997}.
+
 We further identify
@@
 \end{equation}
-and then 
+to obtain the expression uniform for all the modes
 \begin{equation}
@@
 
-Here we solve the boundary state on the $t = 0$ slice.
-Our actual boundary state used in the text corresponds to the $x = 0$ slice.
-There is a $x \rightarrow t$ exchange in the convention here.
-However, that amounts to the change of $\theta \rightarrow \frac{\pi}{2} - \theta$ in the $S$ matrix argument.
-
-\todo[inline]{Mao: this is not a T-dual transformation, it is DN -> ND. }
 We recall that the gluing condition is written as
@@
 \end{equation}
-
-Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
+Upon folding $\phi^2$ to the negative axis, its $\partial_x$ derivative becomes $-\partial_x$, so 
+\begin{equation}
+\begin{bmatrix}
+\partial_{+} \phi^1 \\
+\partial_{+} \phi^2 \\
+\end{bmatrix}
+ = S
+\begin{bmatrix}
+\partial_{-} \phi^1 \\
+\partial_{-} \phi^2 \\
+\end{bmatrix}
+\end{equation}
+In terms of the holomorphic coordinates defined in Eq.~\eqref{eq:zzbar}, 
+\begin{equation}
+\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z}
+\end{equation}
+the $S$ matrix establish a relation between the modes
 \begin{equation}
@@
 \end{pmatrix}
-=S(\theta)
+= -S(\theta)
 \sum_{n\in\mathbb{Z}}
@@
 \end{equation}
-As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
-\begin{equation}\begin{aligned}
-a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
-\end{aligned}\end{equation}
+At the boundary $x = 0$ $\bar{z}=z^{-1}$, therefore we have
+\begin{equation}
+\begin{aligned}
+a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0
+\end{aligned}
+\end{equation}
 The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.
-
-%We recall that the gluing condition can written as
-%\begin{equation}\begin{aligned}
-%\label{eq:def_M}
-%\begin{pmatrix}
-%\partial_t\phi^1\\
-%\partial_x\phi^1
-%\end{pmatrix}_{t=0^-}
-%=M\begin{pmatrix}
-%\partial_t\phi^2\\
-%\partial_x\phi^2
-%\end{pmatrix}_{t=0^+}
-%\end{aligned}\end{equation}
-%where the derivatives are evaluated at the appropriate limit.
-In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$.
-Therefore we establish the scattering matrix as
-%\begin{equation}
-%\begin{aligned}
-%\label{eq:def_S_in_app}
-%\begin{pmatrix}
-%\partial_+\phi^1\\
-%\partial_-\phi^2
-%\end{pmatrix}
-%=S(\theta)
-%\begin{pmatrix}
-%\partial_-\phi^1\\
-%\partial_+\phi^2
-%\end{pmatrix}
-%\end{aligned}
-%\end{equation}
-%
-%The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
-%\begin{equation}
-%\begin{aligned}
-%\label{eq:def_S_in_app_2}
-%\begin{pmatrix}
-%\partial_+\phi^1\\
-%\partial_+\phi^2
-%\end{pmatrix}
-%=S(\theta)
-%\begin{pmatrix}
-%\partial_-\phi^1\\
-%\partial_-\phi^2
-%\end{pmatrix}
-%\end{aligned}
-%\end{equation}
-%We note that the parameterization of S-matrix is \emph{different} from Eq.~\eqref{eq:def_S}, but this will not change our conclusions in the main text.
-Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
-%\begin{equation}
-%\begin{aligned}
-%\label{eq:def_S_in_app_2}
-%\sum_{n\in\mathbb{Z}}
-%\begin{pmatrix}
-%\bar{a}_n^1\bar{z}^{-n}\\
-%\bar{a}_n^2\bar{z}^{-n}
-%\end{pmatrix}
-%=-S(\theta)
-%\sum_{n\in\mathbb{Z}}
-%\begin{pmatrix}
-%a_n^1{z}^{-n}\\
-%a_n^2{z}^{-n}
-%\end{pmatrix}
-%\end{aligned}
-%\end{equation}
-%\todo[inline]{Check the sign and parameterization of S}
-%As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
-%\begin{equation}\begin{aligned}
-%a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
-%\end{aligned}\end{equation}
-%The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign.
-Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.
 

### 2017-05-26 abstract.tex
[draft] revision suggested by Mike.

@@
-We study the quantum quench problem for a class of bosonic conformal interface by computing the Loschmidt echo and the bipartite fidelity.
-These boson conformal interfaces can be viewed as the change of boundary conditions (quench) when connecting two one-dimensional critical systems.
+We study the quantum quench problem for a class of bosonic conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.
+The quench can be viewed as a sudden change of boundary conditions parameterized by $\theta$ when connecting two one-dimensional critical systems.
 They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface.

### 2017-05-26 bCFT_paper.tex
[draft] App. G sign issue fixed.
[draft] revision suggested by Mike.

@@
 \todo[inline]{Mao: funding number?}
-We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Taylor Hughes and Romain Vasseur during the course of this research. 
+We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Michael Stone, Taylor Hughes and Romain Vasseur during the course of this research. 
 TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
@@
 \section{Corrections to the Free Energy}
-% two corrections:
-% 1. staircase geometry
-% 2. contribution from the boundary: cite Cardy 
 \label{app:F_correction}
@@
 \section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
-% basis transformation, Bogoliubov state, overlap(master theorem)
-% Peschel_EE.pdf
 \label{app:comp_fid_echo}
@@
 \label{app:pf_of_id}
-% copy notes app. C
 \input{pf_of_id}
@@
 \label{app:gnd_dn_lambda}
-% copy notes app. A
 \input{gnd_dn_lambda}
@@
 \label{app:lambda_12}
-% copy notes app. B
 \input{lambda_1_lambda_2}
@@
 \section{Winding Modes of Compact Bosons}
-% free boson + compact
 \label{app:compact_diff_boson}

### 2017-05-26 conclusion.tex
[draft] revision suggested by Mike.

@@
 
-We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$.
+We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$.
 A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions a concrete lattice setting.

### 2017-05-26 disc.tex
[draft] revision suggested by Mike.

@@
 
-In all the computation we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$.
+In the computations we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$.
 The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips.
@@
 % x dependence, DN -> ND agrees with existing result;
-More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
+More interesting is when the boundary conditions are of the same type, in which case we verified the quadratic angle dependence numerically for this process 
 \begin{equation}
@@
 Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used).
-This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation.
-The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one $\frac{1}{4}$ is interpreted as the bcc operator dimension $\frac{1}{16}$ between D and N.
+This is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation.
+The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as the twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
 This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$.
-In a rational boson theory, the possible number of primary fields are finite.
+In a rational boson theory, the number of primary fields is finite.
 It requires further study to identify these bcc operators and explore their physical significance.
 
-Numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, {\it does change} the scaling dimensional in a way that is not captured by our analytic computation.
-Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy.
-It would be interesting to have a CFT calculation to reproduce the better numerical result of
+\todo[inline]{verify the 1/16 statement in reference. }
+
+Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation.
+This is because the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
+It would be interesting to have a CFT calculation that reproduces the better numerical result of
 \begin{equation}
@@
 
-These set of boundary conditions can be realized in connecting two compact bosons.
-There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
+This set of boundary conditions can be realized by connecting two compact bosons.
+There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
 For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions.

### 2017-05-26 intro.tex
[draft] revision suggested by Mike.

@@
 \caption{Cut-and-join quench protocol.
-Left panel: prepare the ground states of two separated chains and joine them at $t = 0$, then do the time evolution with whole chain Hamiltonian.
+Left panel: prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian.
 Right panel: spacetime diagram of the cut and join protocol.
@@
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses.
+In the compact Boson case, it is controlled by the ratio of the compactification radii, and in the free lattice Boson case by the ratio of masses.
 We expect it to be tunable in a realistic experimental setting.

### 2017-05-26 codes/DDDD_echo_fit.py

@@ -79,8 +79,8 @@ slope = slope[idx]
 error = error[idx]
 
 # print x
-print slope    
-print error
+# print slope    
+# print error
 
 inset_data = np.loadtxt( path + dataset[1] )
 t_inset = inset_data[:,0]
@@ -102,8 +102,8 @@ for cap in caps:
 
 left, bottom, width, height = [0.25, 0.2, 0.60, 0.4]
 ax2 = fig.add_axes([left, bottom, width, height])
-ax2.plot( t_inset, echo_inset , 'o' , markersize = 1 )    
-ax2.loglog( t_inset[40:-1], [y*(0.2)**(0.25) for y in echo_inset[40:-1]], 'k--', lw=1 , label = "asf" )
+ax2.loglog( t_inset, echo_inset , 'o' , markersize = 1 )
+ax2.loglog( t_inset[40:-1], [y*(0.2)**(0.25) for y in echo_inset[40:-1]], 'k--', lw = 0.5 )
 # ax2.annotate("$t^{-0.25}$", xy=(0.5, 0.3), xycoords='axes fraction' ,horizontalalignment='left', verticalalignment='bottom' )
 ax2.annotate("$t^{-0.25}$", xy=(0.1,0.1), xytext=(1.5, 0.2) ,horizontalalignment='left', verticalalignment='bottom' )
 
@@ -128,7 +128,7 @@ for tick in ax2.yaxis.get_major_ticks():
 ax2.set_yscale('log')
 ax2.set_xscale('log')
 ax2.set_xlabel( r"$t$" , fontsize=8 )
-ax2.set_ylabel( r"$\mathcal{L}(t)$" , fontsize=8 )
+ax2.set_ylabel( r"Loschmidt Echo" , fontsize = 8 )
 
 ax2.set_xlim( ( 0.01 , 1000 ) )
 # ax2.xaxis.set_ticks(np.linspace( 0.01 , 1000 , 2 ))

### 2017-05-26 num_result.tex
[figure] update py scripts and replot.

@@
 There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi, 0.24\pi$ and $0.48\pi$.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$.
 The finite size effect do not emerge before $t=10^{4}$.
@@
 The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi,0.18\pi$ and $0.24\pi$.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi $ and $0.18\pi$.
 The finite size effect do not emerge before $t=10^{4}$.

### 2017-05-26 codes/DDDD_echo_fit.py

@@ -77,12 +77,14 @@ idx = np.argsort( x )
 x = x[idx]
 slope = slope[idx]
 error = error[idx]
+print( idx )
+
 
 # print x
-# print slope    
+# print slope
 # print error
 
-inset_data = np.loadtxt( path + dataset[1] )
+inset_data = np.loadtxt( path + dataset[idx[0]] )
 t_inset = inset_data[:,0]
 echo_inset = inset_data[:,1] 
 
@@ -102,8 +104,8 @@ for cap in caps:
 
 left, bottom, width, height = [0.25, 0.2, 0.60, 0.4]
 ax2 = fig.add_axes([left, bottom, width, height])
-ax2.loglog( t_inset, echo_inset , 'o' , markersize = 1 )
-ax2.loglog( t_inset[40:-1], [y*(0.2)**(0.25) for y in echo_inset[40:-1]], 'k--', lw = 0.5 )
+ax2.loglog( t_inset, echo_inset , 'o' , markersize = 1, color = 'blue' )
+ax2.loglog( t_inset[20:-1], (t_inset[20:-1])**(-0.25) / 2, 'k--', lw = 0.25, dashes = (5, 5) )
 # ax2.annotate("$t^{-0.25}$", xy=(0.5, 0.3), xycoords='axes fraction' ,horizontalalignment='left', verticalalignment='bottom' )
 ax2.annotate("$t^{-0.25}$", xy=(0.1,0.1), xytext=(1.5, 0.2) ,horizontalalignment='left', verticalalignment='bottom' )
 

### 2017-05-26 codes/PP_echo_fit.py

@@ -9,7 +9,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc
 from matplotlib import rcParams
-import scipy.stats
+import scipy.optimize
 from random import randint
 
 rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
@@ -18,7 +18,7 @@ rcParams['legend.numpoints'] = 1
 rcParams['axes.linewidth'] = 0.5
 colorL={6:"#ff2222", 8:'#ffa500', 10:'#4488ff', 12:"#0000aa", 14:'#66bb22'}
 
-bc = 'DDNN' 
+bc = 'PP' 
 path = "../data/" + bc + "/"
 fig_path = "../images/"
 figname = fig_path + bc +"_fit.pdf"
@@ -33,34 +33,25 @@ for (dirpath, dirnames, filenames) in walk(path):
 # ----------------------------------------------------------------------           
 #                         error bar and slope                          |           
 # ----------------------------------------------------------------------
+def fit_data( x, y ,where ):
+    slope_array = []
 
-def fit_data( x, y, where ):
+    f = lambda x, a, b: a * x ** b
+    for i in range( 0, 5 ): # fit five times
+        start = randint( 0, 5 )
+        if where=='center':
+            x_fit = t[40-start-15 : 40-start]
+            y_fit = echo[40-start-15 : 40-start]
+        elif where=='others':
+            x_fit = t[25-start-20 : 25-start]
+            y_fit = echo[25-start-20 : 25-start]
+        p , c = scipy.optimize.curve_fit( f, x_fit , y_fit )
+        slope_array.append( -p[1] )
 
-    log_x = np.log( x ) / np.log( 10 )
-    log_y = np.log( y ) / np.log( 10 )
+    slope = np.mean( slope_array )
+    error = np.std( slope_array )
 
-    if where=='left':
-            # log_x = log_x[ (x>300)*(x<5000) ]
-            # log_y = log_y[ (x>300)*(x<5000) ]
-            # log_x = log_x[ (x>200)*(x<500) ]
-            # log_y = log_y[ (x>200)*(x<500) ]
-            log_x = log_x[ (x>200)*(x<4500) ]
-            log_y = log_y[ (x>200)*(x<4500) ]
[…]

### 2017-05-26 codes/DDDD_echo_fit.py
[figure] std_err is already the error of the slope!

@@ -42,13 +42,11 @@ def fit_data( x, y ):
 
     log_x = log_x[ x > 20 ]
     log_y = log_y[ x > 20 ]
-
+    
+    # std_err is already the error of the slope!
     slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
 
-    log_x_mean = np.mean( log_x )
-    ssx = np.sum( np.square( log_x - log_x_mean ) )
-
-    error = np.sqrt( std_err / ssx )
+    error = std_err
 
     return -slope, error 
 

### 2017-05-26 codes/DDNN_echo_fit.py

@@ -54,10 +54,8 @@ def fit_data( x, y, where ):
             log_y = log_y[ (x>30)*(x<400) ]
 
     slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
-    log_x_mean = np.mean( log_x )
-    ssx = np.sum( np.square( log_x - log_x_mean ) )
 
-    error = np.sqrt( std_err / ssx )
+    error = std_err
 
     return -slope, error 
 

### 2017-05-26 codes/DDNN_fidel_fit.py

@@ -43,10 +43,7 @@ def fit_data( x, y ):
 
     slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
 
-    log_x_mean = np.mean( log_x )
-    ssx = np.sum( np.square( log_x - log_x_mean ) )
-
-    error = np.sqrt( std_err / ssx )
+    error = std_err
 
     return -slope, error 
 

### 2017-05-29 bCFT_paper.tex
[draft] ML grant number added.

@@
 \begin{acknowledgments}
-\todo[inline]{Mao: funding number?}
 We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Michael Stone, Taylor Hughes and Romain Vasseur during the course of this research. 
 TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
+M.L. is supported by US NSF under grant DMR 1351895-CAR and US NSF Emerging Frontiers in Research and Innovation grant EFMA-1627184
 This work made use of the Illinois Campus Cluster, a computing resource that is operated by the Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for Supercomputing Applications (NCSA) and which is supported by funds from the University of Illinois at Urbana-Champaign.

### 2017-05-30 codes/DDDD_echo_fit.py
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,

@@ -28,7 +28,11 @@ offset=0
 dataset = []
 for (dirpath, dirnames, filenames) in walk(path):
     dataset.extend(filenames)
-# print dataset
+
+for filename in dataset:
+    if filename[0]=='.':
+        dataset.remove( filename )
+# print( dataset )   
 
 # ----------------------------------------------------------------------           
 #                         error bar and slope                          |           
@@ -55,8 +59,6 @@ error = []
 x = []
 
 for filename in dataset:
-   if filename[0]=='.':
-       continue
    data = np.loadtxt( path + filename )
    t = data[:,0]
    echo = data[:,1]
@@ -78,11 +80,11 @@ error = error[idx]
 print( idx )
 
 
-# print x
-# print slope
+print (x)
+print ( slope )
 # print error
 
-inset_data = np.loadtxt( path + dataset[idx[0]] )
+inset_data = np.loadtxt( path + dataset[idx[1]] )
 t_inset = inset_data[:,0]
 echo_inset = inset_data[:,1] 
 

### 2017-05-30 codes/PP_echo_fit.py

@@ -9,7 +9,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc
 from matplotlib import rcParams
-import scipy.optimize
+import scipy.stats
 from random import randint
 
 rc( 'font', **{'family': 'serif', 'serif': ['Computer Modern'], 'size' : 10} )
@@ -28,30 +28,36 @@ offset=0.15/25*pi/2/pi
 dataset = []
 for (dirpath, dirnames, filenames) in walk(path):
     dataset.extend(filenames)
-# print dataset
+
+for filename in dataset:
+    if filename[0]=='.':
+        dataset.remove( filename )
+# print( dataset ) 
 
 # ----------------------------------------------------------------------           
 #                         error bar and slope                          |           
 # ----------------------------------------------------------------------
 def fit_data( x, y ,where ):
-    slope_array = []
+    
+    log_x = np.log( x ) / np.log( 10 )
+    log_y = np.log( y ) / np.log( 10 )
 
-    f = lambda x, a, b: a * x ** b
-    for i in range( 0, 5 ): # fit five times
-        start = randint( 0, 5 )
-        if where=='center':
-            x_fit = t[40-start-15 : 40-start]
-            y_fit = echo[40-start-15 : 40-start]
-        elif where=='others':
-            x_fit = t[25-start-20 : 25-start]
-            y_fit = echo[25-start-20 : 25-start]
-        p , c = scipy.optimize.curve_fit( f, x_fit , y_fit )
-        slope_array.append( -p[1] )
+    if where=='left_center':
+        print( x )
+        log_x = log_x[ (x>1000)*(x<4000) ]
+        log_y = log_y[ (x>1000)*(x<4000) ]        
+    elif where=='right_center':
+        print( x )
+        log_x = log_x[ (x>500)*(x<3000) ]
+        log_y = log_y[ (x>500)*(x<3000) ] 
+    else:
+        log_x = log_x[ (x>100)*(x<1000) ]
+        log_y = log_y[ (x>100)*(x<1000) ]
+    slope, _, _, _, std_err = scipy.stats.linregress( log_x, log_y )
 
-    slope = np.mean( slope_array )
-    error = np.std( slope_array )
[…]

### 2017-06-05 codes/PDN_fit.py
[data] PDN data updated.

@@ -37,7 +37,7 @@ def fit_data( x, y ):
     log_x = np.log( x ) / np.log( 10 )
     log_y = np.log( y ) / np.log( 10 )
 
-    data_range = np.logical_and( log_x > 1, log_x < 2.5 )
+    data_range = np.logical_and( log_x > 0, log_x < 2 )
     log_x = log_x[ data_range ]
     log_y = log_y[ data_range ]
 

### 2017-06-14 def_fidel_echo.tex
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,
[draft] typo fixes

@@
 \caption{Fidelity of connecting two CFTs.
-The horizontal axis the imaginary time.
+The horizontal axis is the imaginary time.
 Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians.
@@
 \end{figure}
-\todo[inline]{Mao: double slits on the LHS, tau on the RHS, please confirm.}
 
@@
 One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit.
-In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration.
+In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration.
 If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}

### 2017-06-19 codes/DDDD_echo_fit.py
[draft] Pictures modified. PP finished. PP, DN can be further improved maybe. The styles are the same now. The fonts are enlarged

@@ -116,9 +116,9 @@ ax2.annotate("$t^{-0.25}$", xy=(0.1,0.1), xytext=(1.5, 0.2) ,horizontalalignment
 
 ax.set_xlim( ( 0, 0.5 ) )
 ax.set_ylim( ( 0 , 0.3 ) )
-ax.set_xlabel( r"$\frac{\theta}{\pi}$" )
+ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15 )
 ax.set_ylabel( r"Echo Exponent" )
-ax.legend( loc = 'upper left', frameon = False, prop = {'size':6}, ncol = 1, handlelength = 3 )
+ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 2, handlelength = 3 )
 
 
 # smaller font for inset

### 2017-06-19 codes/DDNN_echo_fit.py

@@ -134,11 +134,11 @@ ax.plot( x_analy , y_analy , c = 'red' , label = r"analytical $2\left(\frac{\the
 for cap in caps:
   cap.set_markeredgewidth( 1 )
 # These are in unitless percentages of the figure size. (0,0 is bottom left)
-left, bottom, width, height = [0.53, 0.17, 0.35, 0.35]
+left, bottom, width, height = [0.55, 0.27, 0.3, 0.25]
 ax2 = fig.add_axes([left, bottom, width, height])
-ax2.plot( t_inset, echo_inset , 'o' , markersize = 1.5 , markeredgecolor='k', markeredgewidth=0.5 , c = colorL[6] , label = r"$\theta=0.02\pi$" )    
-ax2.plot( t_inset_2, echo_inset_2 , 'o' , markersize = 1.5 , markeredgecolor='k', markeredgewidth=0.5 , c = colorL[8] , label = r"$\theta=0.12\pi$" )
-ax2.plot( t_inset_3, echo_inset_3 , 'o' , markersize = 1.5 , markeredgecolor='k', markeredgewidth=0.5 , c = colorL[10] , label = r"$\theta=0.24\pi$" )
+ax2.plot( t_inset, echo_inset , 'o' , markersize = 1.5 ,  c = colorL[6] , label = r"$\theta=0.02\pi$" )    
+ax2.plot( t_inset_2, echo_inset_2 , 'o' , markersize = 1.5 ,  c = colorL[8] , label = r"$\theta=0.12\pi$" )
+ax2.plot( t_inset_3, echo_inset_3 , 'o' , markersize = 1.5 ,  c = colorL[10] , label = r"$\theta=0.24\pi$" )
 # plt.text(0.05, 0.9,'(a)', ha='center', va='center', transform=ax.transAxes)
 
 # ----------------------------------------------------------------------           
@@ -147,10 +147,10 @@ ax2.plot( t_inset_3, echo_inset_3 , 'o' , markersize = 1.5 , markeredgecolor='k'
 
 ax.set_xlim( ( 0, 0.5 ) )
 ax.set_ylim( ( 0 , 0.6 ) )
-ax.set_xlabel( r"$\frac{\theta}{\pi}$" )
+ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Echo Exponent" )
 
[…]

### 2017-06-19 codes/DDNN_fidel_fit.py

@@ -109,9 +109,9 @@ for i in range( 0, len( inset_x ) ):
 
 ax.set_xlim( ( 0, 0.5 ) )
 ax.set_ylim( ( 0, 0.3 ) )
-ax.set_xlabel( r"$\frac{\theta}{\pi}$" )
+ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Fidelity Exponent" )
-ax.legend( loc = 'upper left', frameon = False, prop = {'size':6}, ncol = 1, handlelength = 3 )
+ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 1, handlelength = 3 )
 
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():

### 2017-06-19 codes/PDN_fit.py

@@ -104,9 +104,9 @@ for cap in caps:
 
 ax.set_xlim( ( 0, 0.5 ) )
 ax.set_ylim( ( 0, 0.6 ) )
-ax.set_xlabel( r"$\frac{\theta}{\pi}$" )
+ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15 )
 ax.set_ylabel( r"Echo Exponent" )
-ax.legend( loc = 'upper left', frameon = False, prop = {'size':6}, ncol = 1, handlelength = 3 )
+ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 1, handlelength = 3 )
 
 # plt.tight_layout()
 

### 2017-06-19 codes/PP_echo_fit.py

@@ -44,12 +44,18 @@ def fit_data( x, y ,where ):
 
     if where=='left_center':
         print( x )
-        log_x = log_x[ (x>1000)*(x<4000) ]
-        log_y = log_y[ (x>1000)*(x<4000) ]        
+        print( 'left_center' )
+        log_x = log_x[ (x>1000)*(x<2000) ]
+        log_y = log_y[ (x>1000)*(x<2000) ]        
     elif where=='right_center':
         print( x )
-        log_x = log_x[ (x>500)*(x<3000) ]
-        log_y = log_y[ (x>500)*(x<3000) ] 
+        print( 'right_center' )
+        log_x = log_x[ (x>400)*(x<2000) ]
+        log_y = log_y[ (x>400)*(x<2000) ] 
+    elif where=='right':
+        # print( 'right' )
+        log_x = log_x[ (x>100)*(x<300) ]
+        log_y = log_y[ (x>100)*(x<300) ]
     else:
         log_x = log_x[ (x>100)*(x<1000) ]
         log_y = log_y[ (x>100)*(x<1000) ]
@@ -87,10 +93,12 @@ for filename in dataset:
    data = np.loadtxt( path + filename )
    t = data[:,0]
    echo = data[:,1]
-   if filename in dataset[9:11]:
+   if filename in dataset[18:24]:
         where='left_center'
-   elif filename in dataset[11:13]:
+   elif filename in dataset[28:33]:
         where='right_center'
+   elif filename in dataset[37:51]:
+        where='right'
    else:
         where='others'
    print( filename )
@@ -99,16 +107,15 @@ for filename in dataset:
    error.append( this_error )
 
 
-inset_data = np.loadtxt( path + dataset[1] )
+inset_data = np.loadtxt( path + dataset[4] )
 t_inset = inset_data[:,0]
 echo_inset = inset_data[:,1]
-inset_data = np.loadtxt( path + dataset[4] )
+inset_data = np.loadtxt( path + dataset[8] )
 t_inset_2 = inset_data[:,0]
 echo_inset_2 = inset_data[:,1]
-inset_data = np.loadtxt( path + dataset[9] )
+inset_data = np.loadtxt( path + dataset[18] )
 t_inset_3 = inset_data[:,0]
[…]

### 2017-06-19 codes/PP_fidel_fit.py

@@ -98,7 +98,7 @@ for cap in caps:
     cap.set_markeredgewidth( 1 )
 
 # inset position
-left, bottom, width, height = [0.4, 0.5, 0.3, 0.25]
+left, bottom, width, height = [0.4, 0.43, 0.3, 0.25]
 ax2 = fig.add_axes( [left, bottom, width, height] )
 for i in range( 0, len( inset_x ) ):
     ax2.plot( L_inset[i], F_inset[i] , 'o' , markersize = 1.5, c = colorList[i] )
@@ -109,9 +109,9 @@ for i in range( 0, len( inset_x ) ):
 
 ax.set_xlim( ( 0, 0.5 ) )
 ax.set_ylim( ( 0, 0.3 ) )
-ax.set_xlabel( r"$\frac{\theta}{\pi}$" )
+ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Fidelity Exponent" )
-ax.legend( loc = 'upper left', frameon = False, prop = {'size':6}, ncol = 1, handlelength = 3 )
+ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 1, handlelength = 3 )
 
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():
@@ -123,7 +123,7 @@ ax2.set_yscale( 'log' )
 ax2.set_xscale( 'log' )
 ax2.set_xlabel( r"$L$", fontsize = 8 )
 ax2.set_ylabel( r"Fidelity", fontsize = 8 )
-ax2.yaxis.set_ticks( np.linspace( 0.01, 1, 2 ) )
+ax2.yaxis.set_ticks( np.linspace( 0.01, 0.1, 2 ) )
 ax2.yaxis.set_label_coords( -0.1, 0.5 )
  
 # plt.tight_layout()

### 2017-06-19 comp_fid_echo.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 \label{eq:bosonic_McMahon}
-\langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY)
+\langle0|\exp\left\{\frac{1}{2}b_iX_{ij}b_j\right\}\exp\left\{\frac{1}{2}b^\dagger_iY_{ij}b^\dagger_j\right\}|0\rangle=\text{det}^{-\frac{1}{2}}(1-XY),
 \end{equation}
-for symmetric matrix $X$ and $Y$ and set of independent Bosonic creation operators $b_i^{\dagger}$.
+for symmetric matrix $X$ and $Y$ and set of independent bosonic creation operators $b_i^{\dagger}$.
 One can prove it for (simultaneously) diagonalizable matrices and then claim its legitimacy for its combinatorial nature.
@@
 B & -A^* \\
-\end{bmatrix}
+\end{bmatrix},
 \end{aligned}
@@
 \end{pmatrix}]S \\
-&=S^T JS.
+&=S^T JS,
 \end{aligned}
@@
 \begin{eqnarray}
-  u^\dagger u-v^\dagger v&=\mathbb{I}\label{eq:constraint_1}\\
-  u^T u-v^T v&=0\label{eq:constraint_2}  
+  u^\dagger u-v^\dagger v&=\mathbb{I},\label{eq:constraint_1}\\
+  u^T u-v^T v&=0\label{eq:constraint_2}.  
 \end{eqnarray}
@@
 \pi
-\end{pmatrix}
+\end{pmatrix},
 \end{aligned}\end{equation}
@@
 \pi
-\end{pmatrix}
+\end{pmatrix}.
 \end{aligned}\end{equation}
@@
 \end{bmatrix}
-\mathcal{S}^T
+\mathcal{S}^T,
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-One can show that
+One can show that,
 \begin{equation*}\begin{aligned}
@@
 \label{eq:boson_BCS_gnd}
-|0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b}\\
+|0\rangle_{{\bf a}}&=\text{det}^{\frac{1}{4}}(1-T^\dagger T)\exp\left\{-\frac{1}{2}b_j^\dagger T_{jk}b_k^\dagger\right\}|0\rangle_{\bf b},\\
 \end{aligned}\end{equation}
@@
 \begin{equation}
-\text{det}^{\frac{1}{4}}(1-T^\dagger T) =|\text{det}(u)|^{-\frac{1}{2}}
+\text{det}^{\frac{1}{4}}(1-T^\dagger T) =|\text{det}(u)|^{-\frac{1}{2}}.
 \end{equation}
@@
 \label{eq:two_BdG}
-({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger)\quad
-({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger)
+({\bf b} , {\bf b}^\dagger)S_0=({\bf a} , {\bf a}^\dagger),\quad
+({\bf b} , {\bf b}^\dagger)S_1=({\bf c} , {\bf c}^\dagger),
 \end{aligned}\end{equation}
@@
 \label{eq:S0invS}
-({\bf a} , {\bf a}^\dagger)=({\bf c} , {\bf c}^\dagger)\left(S_0^{-1}S_1\right)^{-1}
+({\bf a} , {\bf a}^\dagger)=({\bf c} , {\bf c}^\dagger)\left(S_0^{-1}S_1\right)^{-1}.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{\Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2}{|\text{det}(u_1)|} = \frac{1}{|\text{det}(u_1)|}
+|{}_{\bf a}\langle0|0\rangle_{\bf c}|^2=\frac{\Big|{}_{\bf a}\langle 0 | \exp( -\frac{1}{2} a_j^{\dagger} T^{jk} a_k^{\dagger} )|0   \rangle_{\bf a} \Big|^2}{|\text{det}(u_1)|} = \frac{1}{|\text{det}(u_1)|}.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-|0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a}
+|0\rangle_{{\bf a}(t)}\equiv e^{-i\hat{H}_1t}|0\rangle_{\bf a},
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t}
+a_i(t)&=e^{-i\hat{H}_1t}a_ie^{i\hat{H}_1t},
 \end{aligned}\end{equation}
@@
 ({\bf a} , {\bf a}^\dagger)e^{iHt} \\
-=&({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0
+=&({\bf a},{\bf a}^\dagger)S_0^{-1}S_1\text{diag}(e^{iEt},e^{-iEt})S_1^{-1}S_0.
 \end{aligned}\end{equation}
@@
 \label{eq:echo_t}
-\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}
+\mathcal{L}(t)=|_{\bf a}\langle0|0\rangle_{{\bf a}(t)}|^2=|\text{det}(u_1^\dagger e^{iEt}u_1-v_1^\dagger e^{-iEt}v_1)|^{-1}.
 \end{aligned}\end{equation}
@@
 
-The matrix $\mathcal{S}$ that diagonalize $\mathcal{M}$
+The matrix $\mathcal{S}$ that diagonalize $\mathcal{M}$,
 \begin{equation}
@@
 & \mathcal{O}D^{-1/2}
-\end{bmatrix}
+\end{bmatrix}.
 \end{aligned}\end{equation}
@@
 \end{bmatrix}
-S
+S,
 \end{aligned}\end{equation}
@@
 O(D^{1/2}-D^{-1/2}) & O(D^{1/2}+D^{-1/2}) 
-\end{bmatrix}
+\end{bmatrix}.
 \end{aligned}\end{equation}

### 2017-06-19 compact_boson.tex
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 
-\todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}
-
-Our derivation follows the general multi-component Boson constraints in Ref.~\onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}.
+Our derivation follows the general multi-component boson constraints in Ref.~\onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}.
 A review of the detailed parameterization of the states can be found in Ref.~\onlinecite{sakai_entanglement_2008}.
@@
 \begin{aligned}
-\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n }
+\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } ,
 \end{aligned}
@@
 \label{eq:zzbar}
-z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
+z = \exp( 2 \pi i \frac{t - x}{L}), \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L}).
 \end{equation}
@@
 \begin{aligned}
-  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right) \\
-   \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)
+  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right), \\
+   \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right),
   \end{aligned}
@@
 \begin{aligned}
-i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
+i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} .
 \end{aligned}
@@
 \partial_+\phi^2
-\end{pmatrix}
+\end{pmatrix}.
 \end{aligned}
@@
 \partial_{-} \phi^2 \\
-\end{bmatrix}
+\end{bmatrix}.
 \end{equation}
@@
 \begin{equation}
-\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z}
+\partial_{+} = \frac{4\pi i }{T} \bar{z} \partial_{\bar{z}} ,\qquad \partial_{-} = -\frac{4\pi i }{T} z\partial_{z},
 \end{equation}
@@
 a_n^2{z}^{-n}
-\end{pmatrix}
+\end{pmatrix}.
 \end{aligned}
@@
 \begin{aligned}
-a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0
+a^i_n + (S^{-1}_{ij})\bar{a}^j_{-n}=0.
 \end{aligned}
@@
 \label{eq:lattice}
-\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
+\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top,
 \end{equation}
@@
 \begin{equation}
-  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
+  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
 \end{equation}
@@
 \label{eq:S_1_constraint}
-\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
+\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2},
 \end{aligned}
@@
 \label{eq:S1bd-state}
-g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
+g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle,
 \end{aligned}\end{equation}
@@
 \end{bmatrix}
-\vec{M}^*
+\vec{M}^*.
 \end{equation}
@@
 \begin{equation}\begin{aligned}
-Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
+Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle,\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0).
 \end{aligned}\end{equation}
@@
 \label{eq:Z0}
-Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
+Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\},
 \end{aligned}
@@
 \begin{equation}\begin{aligned}
-Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
+Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}.
 \end{aligned}\end{equation}

### 2017-06-19 disc.tex
[draft] remove the 1/16 scaling dimension todo; it is clear in notes Eq. (124) why there is a factor of 2
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 \begin{equation}
- S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
+ S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
 \end{equation}
@@
 
-\todo[inline]{verify the 1/16 statement in reference. }
-
 Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation.
@@
 This set of boundary conditions can be realized by connecting two compact bosons.
-There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
+There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
 For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions.
-The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides.
+The interface studied in this paper is a generalization which (in the folding picture) twist the two independent bosons (two left modes plus two right modes) on the two sides.
 An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.

### 2017-06-19 general_formulation.tex
[draft] App. G sign issue fixed.
1. figure font enlarged. 2. name accent fixed in bib 3. captions need to be checked later.
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}.
-In the Boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.
+In the boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.
 
@@
 
-Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
+Assume two free bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
 \begin{equation}\begin{aligned}
@@
 \partial_x\phi^2
-\end{pmatrix}
+\end{pmatrix},
 \end{aligned}\end{equation}
@@
 0 & \lambda
-\end{bmatrix}\quad
+\end{bmatrix},\quad
 M_2(\theta)=\pm
@@
 \lambda^{-1} & 0 
-\end{bmatrix}
+\end{bmatrix},
 \end{aligned}\end{equation}
@@
 \partial_+\phi^2
-\end{pmatrix}
+\end{pmatrix},
 \end{aligned}\end{equation}
@@
 \sin 2\theta & -\cos 2\theta
-\end{bmatrix}\quad
+\end{bmatrix},\
 S_2(\theta)=\begin{bmatrix}
@@
 -\sin 2\theta & -\cos 2\theta
-\end{bmatrix}
+\end{bmatrix}.
 \end{aligned}\end{equation}
@@
 The fact of their wavelength independence is an indication of scale invariance of the interface.
-
 \begin{figure}[h]
 \centering
-\includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
+\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
 \caption{Folding picture for penetrable interface.
@@
 \begin{aligned}
-\partial_t(\cos\theta\phi^1-\sin\theta\phi^2)=0 \quad
-\partial_x(\sin\theta\phi^1+\cos\theta\phi^2)=0 
+\partial_t(\sin\theta\phi^1-\cos\theta\phi^2)=0, \quad
+\partial_x(\cos\theta\phi^1+\sin\theta\phi^2)=0, 
 \end{aligned}
@@
 
-If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes.
+If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes.
 We shall interpret these identities to be valid only when acting on the boundary states.
 The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
-\begin{equation}
-\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right)
-\end{equation}
+\begin{eqnarray}\begin{aligned}
+\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
+ \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
+\end{aligned}\end{eqnarray}
 where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
 \begin{equation}
-z= e^{ 2\pi i(x - t) / T } \quad \bar{z} = e^{ 2\pi i( x + t  ) / T }
+z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} }.
 \end{equation}
@@
 \label{eq:rotation_a_basis}
-\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
-\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
+\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
+\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
 \end{aligned}
@@
 | B \rangle 
-& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
+& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
 \begin{pmatrix}
@@
 \bar{a}_{-n}^1  \bar{a}_{-n}^2
-\end{pmatrix} \Big\} |0\rangle
+\end{pmatrix} \Big\} |0\rangle,
 \end{aligned}

### 2017-06-19 gnd_dn_lambda.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 \centering
-\includegraphics{fig_gnd_dn_lambda.pdf}
+\includegraphics[width=\columnwidth]{fig_gnd_dn_lambda.pdf}
 \caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions.
@@
   A_1 e^{i kt} \cos\left(kx +\frac{1}{2}kL \right) &  \quad x < 0  \\
-  A_2 e^{ikt}  \sin\left(kx - \frac{1}{2}kL \right) & \quad x > 0   \\
+  A_2 e^{ikt}  \sin\left(kx - \frac{1}{2}kL \right) & \quad x > 0 .  \\
 \end{aligned} \right. 
@@
 \begin{eqnarray}\begin{aligned}
-\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2}, \quad \theta \in \left[0,\frac{\pi}{2} \right]
+\frac{\partial_x \phi_1}{ \partial_t \phi_1} = \lambda^2 \frac{\partial_x \phi_2}{ \partial_t \phi_2} = \tan^2 \theta\frac{\partial_x \phi_2}{ \partial_t \phi_2}, \quad \theta \in \left[0,\frac{\pi}{2} \right]  ,
 \end{aligned}\end{eqnarray}
@@
 \label{eq:momentum_gnd_dn_lambda}
-k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right),  \quad n\in\mathbb{Z}
+k = \frac{2\pi}{L}\left( n \pm \frac{\theta}{\pi} \right),  \quad n\in\mathbb{Z}.
 \end{equation}
@@
 \label{eq:H_in_gnd_dn_lambda}
-H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right)
+H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right) ,
 \end{equation}
@@
 \begin{aligned}
-a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) \\
-a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) \\
+a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) ,\\
+a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) .\\
 \end{aligned}
@@
 &= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
-&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right)
+&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
 \end{aligned}
@@
 \begin{equation}
-F = \beta E_c = - \frac{\beta}{2} B_2( x) 
+F = \beta E_c = - \frac{\beta}{2} B_2( x) ,
 \end{equation}

### 2017-06-19 num_result.tex
[draft] PP_echo, DDDD_echo .py changed, new data for DDDD and PPPP added,
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 \begin{equation}
-\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}
+\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
 \end{equation}
@@
 \begin{equation}
- \text{NN}+\text{NN}\rightarrow\lambda+\text{NN}
+ \text{NN}+\text{NN}\rightarrow\lambda+\text{NN},
 \end{equation}
@@
 \begin{equation}
-  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN}
+  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
 \end{equation}
@@
 \label{eq:approx_DNDN}
-S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta)
+S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
 \end{aligned}\end{eqnarray}
@@
 \begin{equation}
-\text{P}+\text{P}\rightarrow\lambda+\text{P}
+\text{P}+\text{P}\rightarrow\lambda+\text{P},
 \end{equation}
@@
 \label{eq:approx_DNDN}
-S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right)
+S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
 \end{aligned}
@@
 The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi $ and $0.18\pi$.
+Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$.
 The finite size effect do not emerge before $t=10^{4}$.
@@
     \label{fig:PPPP}
-    \todo[inline]{Mao: Put the PP for echo;}
 \end{figure}
@@
 \begin{equation}
-{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}
+{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
 \end{equation}
@@
 
-\todo[inline]{May need to improve the figure quality.}
-
 %%% Local Variables:

### 2017-06-19 pf_of_id.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .

@@
 \label{eq:first_id_app_pf_of_id}
-e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger} }  = e^{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger} } e^{- \vec{b}^{\dagger} M \vec{b} } 
+e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger} }  = e^{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger} } e^{- \vec{b}^{\dagger} M \vec{b} } ,
 %\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\}
@@
 \begin{equation}
-  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^\dagger = O^T \vec{\bar{b}}^\dagger
+  \vec{b}^{\dagger}  M \vec{b} = \vec{d}^{\dagger} \Lambda \vec{d}  \quad \vec{d} = O \vec{b} \quad \vec{\bar{d}}^\dagger = O^T \vec{\bar{b}}^\dagger,
 \end{equation}
@@
   e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger }  =  
-  e^{- \vec{d}^{\dagger} \Lambda \vec{d} } e^{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger } = \prod_i  e^{- \lambda_i d_i^{\dagger} d_i } e^{  d_i^{\dagger} \bar{d}_i ^{\dagger} }
+  e^{- \vec{d}^{\dagger} \Lambda \vec{d} } e^{   \vec{d}^{\dagger} \bar{\vec{d}}^\dagger } = \prod_i  e^{- \lambda_i d_i^{\dagger} d_i } e^{  d_i^{\dagger} \bar{d}_i ^{\dagger} }.
 %  \exp&\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}  =  
@@
 \begin{equation}
-  e^X e^{Y} = e^{\exp (s ) Y} e^{X}
+  e^X e^{Y} = e^{\exp (s ) Y} e^{X},
 \end{equation}
@@
 \label{eq:lambda_commutator}
-[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} 
+[- \lambda_i d_i^{\dagger} d_i, d_i ^{\dagger} \bar{d}_i^{\dagger}] =  - \lambda_i  d_i ^{\dagger} \bar{d}_i^{\dagger} ,
 \end{equation}
@@
 \begin{aligned}
-e^{- \vec{b}^{\dagger} M \vec{b} } e^{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger }   &= \prod_i e^{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i }  e^{-\lambda_i  d^{\dagger}_i d_i }  = e^{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger} e^{- \vec{b}^{\dagger} M \vec{b} }
+e^{- \vec{b}^{\dagger} M \vec{b} } e^{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger }   &= \prod_i e^{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i }  e^{-\lambda_i  d^{\dagger}_i d_i }  = e^{ \vec{b}^{\dagger} e^{-M}  \bar{\vec{b}}^\dagger} e^{- \vec{b}^{\dagger} M \vec{b} }.
 % \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{  \vec{b}^{\dagger} \bar{\vec{b}}^\dagger  \Big\}   &= \prod_i \exp \Big\{ e^{- \lambda_i }  d^{\dagger}_i \bar{d}^{\dagger}_i  \Big\}  \exp \Big\{-\lambda_i  d^{\dagger}_i d_i  \Big\} \\
@@
 \label{eq:second_id_in_app_pf_of_id}
-Z_{ab} = \langle 0 | e^{ \vec{b} R_a^* \vec{\bar{b}} } e^{ - \vec{b}^{\dagger} M  \vec{b} } e^{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger} }  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
+Z_{ab} = \langle 0 | e^{ \vec{b} R_a^* \vec{\bar{b}} } e^{ - \vec{b}^{\dagger} M  \vec{b} } e^{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger} }  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} ,
 %Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )}
 \end{equation}
-where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$. Using the identity we have just proved, 
+where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$. Using the identity we have just proved
 \begin{equation}
-Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle 
+Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle ,
 \end{equation}
-A direct application of the MacMahon master theorem
+a direct application of the MacMahon master theorem
 \begin{equation}

### 2017-06-19 intro.tex
[bib] More marginally relevant refs added at the 2nd para of intro.

@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system.
+\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,kibble-zurek_2017,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system.
 As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve.
@@
 The interface produced will interpolate between the total reflective and complete transparent ones.
-It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}.
+It can be realized as interface of two free compact boson theories with different compactification radii\cite{bachas_permeable_2002}.
 There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties.
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the compact Boson case, it is controlled by the ratio of the compactification radii, and in the free lattice Boson case by the ratio of masses.
+In the compact boson case, it is controlled by the ratio of the compactification radii, and in the free lattice boson case by the ratio of masses.
 We expect it to be tunable in a realistic experimental setting.
@@
 The rest of the paper is organized as follows.
-
 In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.
-
 In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison.

### 2017-06-20 analy_eval.tex
[draft] typo fixes
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[draft] caption revised.

@@
 \caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $.
-The two black dots represent possible insertion of bcc operators.
-The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries.
-The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
+The two black dots represent possible locations of boundary condition changing (bcc) operators.
+The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of the point connecting $a$ and $b$ boundaries.
+The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
 To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
@@
 \begin{equation}
-\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
+\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
 \end{equation}
@@
 \begin{equation}
-  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
+  Z_{ab} = \langle a | e^{-\pi H } |b \rangle .
 \end{equation}
 
-The Loschmidt echo can be evaluated the same way.
+The Loschmidt echo can be evaluated in the same way.
 Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
@@
 \includegraphics[width=\columnwidth]{fig_H-tau_fold}
-\caption{Left: diagram of the partition function of Loschimidt echo, where time is the horizontal direction, the dashed(solid) lines are open(gluing) boundary conditions.
+\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions.
 Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
-The blue semi-circles are UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow(equal time slice).
-Middle: image of the map $\xi = \frac{z}{\tau - z}$.
-Right: image of $w = \ln \xi$.
-It is a cylinder by identifying the blue lines and standard radial quantization can be applied.
+The blue semi-circles are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
+Middle: Image of the map $\xi = \frac{z}{\tau - z}$.
+Right: Image of $w = \ln \xi$.
+It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied.
 }
@@
 \begin{equation}
-\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta 
+\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
 \end{equation}
@@
 \begin{equation}
-S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
+S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) ,
 \end{equation}
@@
   &\frac{1}{2}(|x| - x^2 )\beta  \quad &i = j \\
-  &\frac{1}{16}\beta   \quad &i \ne j   \\
-\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} 
+  &\frac{1}{16}\beta   \quad &i \ne j ,  \\
+\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} .
 \end{equation}
@@
 \label{eq:DDDD}
-{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD}
+{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
 \end{equation}
@@
 \frac{1}{8}\ln L  &\quad\text{fidelity}  \\
-\frac{1}{4}\ln t   &\quad \text{echo}   \\
+\frac{1}{4}\ln t   &\quad \text{echo} ,  \\
 \end{aligned} \right.  
@@
 \label{eq:DNDN}
-{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
+{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
 \end{equation}
@@
  (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
- 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} \\
+ 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
 \end{aligned} \right. 
@@
   \label{eq:PP}
-  {\rm P} + {\rm P} \rightarrow \lambda + {\rm P}
+  {\rm P} + {\rm P} \rightarrow \lambda + {\rm P},
 \end{equation}
@@
   \Big(|x-\frac{1}{4}| - (x-\frac{1}{4})^2 \Big)\ln L   &  \quad {\rm fidelity} \\
-  2\Big(|x-\frac{1}{4}| - (x-\frac{1}{4})^2 \Big) \ln t  & \quad \text{ Loschmidt echo} \\
+  2\Big(|x-\frac{1}{4}| - (x-\frac{1}{4})^2 \Big) \ln t  & \quad \text{ Loschmidt echo} .\\
 \end{aligned} \right. 

### 2017-06-20 def_fidel_echo.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[draft] caption revised.

@@
 In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams.
-It will then be evident that these quantities are just the free energy of Boson with conformal interfaces (or boundaries).
+It will then be evident that these quantities are just the free energy of boson with conformal interfaces (or boundaries).
 
@@
 \begin{equation}
-{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 
+{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 ,
 \end{equation}
@@
 \begin{equation}
-\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z
+\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z,
 \end{equation}
@@
 The horizontal axis is the imaginary time.
-Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians.
+Evolution along the two semi-infinite stripes produces the groundstates of the disconnected and connected chain Hamiltonians.
 The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states.
-The solid dot represents boundary changing operator.}
+The solid dot represents boundary changing operator.
+Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$ are possible choices of boundary conditions.)}
 \label{fig:fidel}
@@
 \begin{equation}
-\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
+\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2,
 \end{equation}
@@
 \caption{Loschmidt echo of connecting two CFTs.
-The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians.
-They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains.
-In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case).
+Evolution along the two infinitely extended sides produces the groundstate of the disconnected chain Hamiltonians.
+They sandwich the evolution of the connected chains.
+In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).
 See the discussion in main text.}
@@
 \label{eq:full-pass}
-\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
+\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
 \end{equation}

### 2017-06-20 general_formulation.tex
[draft] caption revised.

@@
 \includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
-\caption{Folding picture for penetrable interface.
+\caption{Folding picture for the penetrable interface.
 Left panel: World line of the penetrable interface.
-$\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domain.
+$\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains.
 Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$.
-The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.}
+The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.
+The arrow represents the incoming and outgoing particle scattered by the interface.}
 \label{fig:folding_pic}

### 2017-06-20 num_result.tex
[draft] caption revised.

@@
 \caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$.
-We work with total system size $N = 30k$ sites, and parameters $m = 10^{-8}$, $k = 1$.
+We work with the total system size $N = 30$k sites, and parameters $m = 10^{-8}$, $k = 1$.
 The lattice constant is set to unity.
 The blue dots representing the numerical results lie on the red analytic line.
-As predicted, the echo exponents are equal for different values of $\theta$.
+As predicted, the echo exponents are all equal for different values of $\theta$.
 Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale.
 The dashline denotes the expected power law of $t^{-0.25}$.
-The finite size effect do not emerge before $t=10^{3}$, which sets the right boundary of the range we fit.
+Finite size effect does not emerge before $t=10^{3}$, which sets the right boundary of the range we fit.
 See main text for the curve fitting method.}
@@
     \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
-The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}.
+The total system size is $N=35$k sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.
-There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text.
+There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text.
 Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$.
-The finite size effect do not emerge before $t=10^{4}$.
+Finite size effect does not emerge before $t=10^{4}$.
 We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
@@
     \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
-    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
+    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
 The parameters are the same as those in Fig.~\ref{fig:DDNN}.
@@
 The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$.
-The finite size effect do not emerge before $t=10^{4}$.
+Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$.
+Finite size effect does not emerge before $t=10^{4}$.
 We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
@@
 \caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$.
-The boundary condition $c$ changes the scaling of the completely.
-The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$ and becomes smaller and approach zero for small $\theta$.
+The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
+The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.
 }

### 2017-06-27 abstract.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$.
-We perform analytic and numerical calculation of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
+We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
 Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

### 2017-06-27 analy_eval.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 These are the characteristic size of the corner at the tip of the slit.
-However, without regulators the conformal invariance can rescale both to $1$ by doing a dilation transformation, thus getting rid of their dependence.
-Therefore, regulators are necessary in keeping track of the scale dependence, and also physically sensible when considering the lattice realization of the systems.
+If there is no regulator, however, a dilation transformation can rescale both to $1$ and get rid of their dependence.
+Therefore, regulators are necessary in keeping track of the scale dependence, and physically sensible when considering the lattice realization of the systems.
 
@@
 Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
-The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function is
+The dashed line and solid line can then be regarded as two boundary states, and the diagram corresponds to the following partition function
 \begin{equation}
@@
 In the $\xi$ plane, we end up with the same diagram as fidelity.
-With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.
+With one more conformal mapping, it becomes the cylinder partition function between the two boundary states.
 
@@
 \frac{1}{8}\ln L  &\quad\text{fidelity}  \\
-\frac{1}{4}\ln t   &\quad \text{echo} ,  \\
+\frac{1}{4}\ln t   &\quad \text{echo} .  \\
 \end{aligned} \right.  
 \end{equation}
-where same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
+The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
 Another process

### 2017-06-27 bd_notation.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface.
-The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench.
+The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench.
 Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
 \begin{equation}
-S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) 
+S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
 \end{equation}
@@
 In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$.
-The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of boundary condition.
+The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition.
 For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
 \begin{equation}
-{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} 
+{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .
 \end{equation}
@@
 $S_2( \frac{\pi}{4} )$.
-This corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.
+This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.
 

### 2017-06-27 conclusion.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
-In this paper, we analyze a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.
+In this paper, we analyzed a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.
 
 We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$.
-A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions a concrete lattice setting.
+A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.
 
@@
 
-These two features are tested in three typical processes in the numerical calculation of the harmonic chains.
-After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error.
-Although tangential to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.
+These two features were tested in three typical processes in the numerical calculation of the harmonic chains.
+After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error.
+Although tangential to the non-equilibrium dynamics, the fidelity calculation was used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.
 

### 2017-06-27 def_fidel_echo.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 \begin{equation}
-{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 ,
+{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
 \end{equation}
@@
 \begin{equation}
-\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z,
+\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z.
 \end{equation}
@@
 The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
-One of the them is the groundstate of the disconnected chains and the other is groundstate evolved by the Hamiltonian of the connected chains
+One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
 \begin{equation}
-\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2,
+\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
 \end{equation}
@@
 According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
-One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit.
+One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
 In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration.
@@
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
-From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing (bcc) operator.
-These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
+From the boundary CFT point of view, the change of boundary condition can be regarded as insertion of primary field which is the (bcc) operator.
+These diagrams then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
 

### 2017-06-27 disc.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 
-In the computations we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$.
+In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$.
 The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips.
@@
 If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$.
-In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$.
+In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$.
 It is then reasonable to find an universal echo between them.
@@
 % x dependence, DN -> ND agrees with existing result;
-More interesting is when the boundary conditions are of the same type, in which case we verified the quadratic angle dependence numerically for this process 
+
+For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for this process 
 \begin{equation}
@@
 Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used).
-This is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation.
-The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as the twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
+Such discrepancy is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation.
+The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
 This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$.
@@
 Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation.
-This is because the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
+The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
 It would be interesting to have a CFT calculation that reproduces the better numerical result of
@@
 This set of boundary conditions can be realized by connecting two compact bosons.
-There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
+There are already numerous theoretical and experimental works on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
 For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions.
-The interface studied in this paper is a generalization which (in the folding picture) twist the two independent bosons (two left modes plus two right modes) on the two sides.
-An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.
+The interface studied in this paper is a generalization which (in the folding picture) twists the two independent bosons (two left modes plus two right modes) on the two sides.
+An X-ray edge singularity experiment in a quantum wire system, which uses ions to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.
 

### 2017-06-27 general_formulation.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous.
-An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other.
-The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there.
+An equivalent perspective (and will be used later) is to fold one of the theories on top of the other.
+The interface located on the boundary of the tensor theory becomes impenetrable, and momentum flow vanishes there.
 This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}.
-In the boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.
+In the boson theory we are interested in, the tensor theory has $c = 2$.
 
-There are however many successful attempts to construct a subset of those bosonic boundary states.
-One way is to impose current operator rather than Virasoro generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
-Other examples utilize the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.
+Despite the general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are however many successful attempts to construct a subset of those bosonic boundary states.
+Rather than Virasoro generator, one may use current operator which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989}.
+This idea has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+Further, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
 
-We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantizes it to give the boundary state.
-The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.
+We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which begins with a classical boundary condition and the boundary state follows from the quantization.
+The interface obtained is actually the same as the one from using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but the scattering process derived here is more intuitive and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} is more transparent.
 
-Assume two free bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
+Assume two free boson fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. The interface located at $x = 0$ is characterized by the ``gluing condition"
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
-As argued, the momentum component of stress tensor is continuous across the interface.
+where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
+As argued, the momentum components of the stress tensor are continuous across the interface.
 As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
@@
 In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other.
-The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
+The interface reduces to individual boundary conditions for the boson on the left and right half planes: They are combination of Dirichlet and Neumann boundary conditions.
 For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left.
@@
 In this case, $M_1(\theta)$ characterizes a perfectly transmitting interface.
-For example, there is effectively no interface in the case $M_1( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P.
+For example, there is effectively no interface in the case of $M_1( \frac{\pi}{4})$.
+We will denote it as ``P'' as it corresponds to the traditional periodic boundary condition.
 For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
@@
 
-The physical significance of $\theta$ will be manifest in the scattering process described below.
-We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes.
-For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane.
-It is then one of the scattering products that leaves the interface.
-On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain.
+The physical significance of $\theta$ will be clear in the scattering process described below.
+We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes.
+For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane.
+This mode is one of the scattering modes that leave the interface.
+On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain.
 We therefore establish the scattering relation
@@
 For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices.
-The fact of their wavelength independence is an indication of scale invariance of the interface.
+We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant.
 \begin{figure}[h]
@@
 
-If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes.
+If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an identity for the boson creation and annihilation operators.
 We shall interpret these identities to be valid only when acting on the boundary states.
@@
 \end{aligned}\end{eqnarray}
-where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
+where we take the following choice of the holomorphic and anti-holomorphic coordinates
 \begin{equation}
-z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} }.
+z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} },
 \end{equation}
-We end up with a set of operator identities for each mode
+with $T$ being the time period. We end up with a set of operator identities for each mode
 \begin{equation}
@@
 \end{equation}
-which is valid on the following boundary state
+which is valid for the following boundary state
 \begin{equation}

### 2017-06-27 intro.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

--- 2017-05-26 intro.tex
@@
 % quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
-In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the system's conformal symmetry.
-Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}.
+In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry of the system.
+Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}.
 Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
-Their correlation functions can exhibit different critical exponent from the bulk counterpart\cite{cardy_conformal_1984}.
+Their correlation functions can exhibit different critical exponents from the bulk counterparts\cite{cardy_conformal_1984}.
 One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band.
@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system.
-As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve.
-Various quantities are used to detect the information in the quench process.
+\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,kibble-zurek_2017,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
+As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states.
+They will be joined at $t = 0$ and evolve.
+Various quantities can be used to detect the information in the quench process.
 For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems.
-The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint.
-Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution.
-In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.
+The authors ascribe such increase to the proliferation and propagation of quasi-particle excitations emitted at the joint.
+Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase.
+In this model, the Majorana zero mode acts as a bcc and its conformal dimension appears in the exponent of the power law decay for the Loschmidt echo.
 
@@
 \caption{Cut-and-join quench protocol.
-Left panel: prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian.
-Right panel: spacetime diagram of the cut and join protocol.
+Left panel: Prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian.
+Right panel: Spacetime diagram of the cut and join protocol.
 The solid line represents the boundaries of the two disconnected chains.
@@
 % All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
-In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}.
+In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in the right panel of Fig.~\ref{fig:cut-and-join}.
 The separating ground states prepared before $t = 0$ are joined to form a new type of interface between them.
@@
 
-It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol.
+In this paper, we generalize these ideas and consider connecting two different CFTs in the ``cut-and-join" protocol.
 The interface produced will interpolate between the total reflective and complete transparent ones.
-It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}.
-There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties.
+As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface can be realized as a domain wall between two free compact boson theories with different compactification radii.
+Entanglement properties for non-compact free boson/free fermion lattices have been numerically and analytically studied\cite{peschel_exact_2012,sakai_entanglement_2008}.
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the compact Boson case, it is controlled by the ratio of the compactification radii, and in the free lattice Boson case by the ratio of masses.
+In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, whereas it is controlled by the ratio of masses in the case of free lattice boson.
 We expect it to be tunable in a realistic experimental setting.
@@
 Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process.
-Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench.
-There is no dynamic information in fidelity, nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic in Loschmidt echo computation.
-The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$.
+Fidelity is the (square of) the overlap of the ground state wavefunctions of the Hamiltonians before and after the quench.
+There is no dynamic information in fidelity; nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic for the Loschmidt echo computation.
+The Loschmidt echo is (square of) the overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
 The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit.
-Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFT in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
-What we do in this paper is to extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
+Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
+In this paper we extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
 
 The rest of the paper is organized as follows.
-
 In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.
-
 In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison.
@@
 This paper includes several appendices for technical details.
-In App.~\ref{app:F_correction}, we point out two corrections to the free energy, complementary to the argument made in the main text.
+In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text.
 We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}.
@@
 The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}.
-Up until this point, we work exclusively with the oscillator modes of free bosons.
+Up until this point, we work exclusively with the oscillator modes of the free bosons.
 In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order.

### 2017-06-27 num_result.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

@@
 We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast.
-The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.02n \pi$, $n = 1,...,25 $.
-The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution of the each point.
+The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $.
+The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution for each point.
 We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.
@@
 in which the joining boundary condition is determined by $S_1(\theta)$.
-A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
+A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction.
 We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
@@
 to evaluate the influence of the boundary condition $c$.
-It {\rm does} influence the scaling dimension, in a way that is not captured by our analytic calculation.
+It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation.
 Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$.

### 2017-06-27 conclusion.tex
[draft] iid expanded; 3rd paragraph of section conclusion section modified.

@@
 
-We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$.
+We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface.
+The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$.
+Generic value of $\theta$ then interpolates those conventional boundary conditions.
 A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.
 
-The study of the Loschmidt echo is a generalization of the conventional ``cut-and-join" protocol.
-Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient.
-Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices and depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$s.
+The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface, which we denote as
+\begin{equation}
+S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
+\end{equation}
+Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces.
+Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$.
+On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).
 

### 2017-06-27 num_result.tex
[draft] iid expanded; 3rd paragraph of section conclusion section modified.

@@
 The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $.
-The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution for each point.
+The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point.
 We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

### 2017-06-28 intro.tex
[draft] intro

@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,kibble-zurek_2017,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
+\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
 As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states.

### 2017-06-28 disc.tex
[draft] wording changes for descritive text.

@@
 
-In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$.
+In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the replacement recipe $ \ln L \rightarrow 2 \ln \tau$.
 The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips.

### 2017-06-28 general_formulation.tex
[draft] wording changes for descritive text.

@@
 
-Despite the general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are however many successful attempts to construct a subset of those bosonic boundary states.
-Rather than Virasoro generator, one may use current operator which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989}.
-This idea has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
-Further, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
+Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states.
+For example, one may use the current operator rather than the Virasoro generator to solve the zero momentum flow condition.
+This idea dates back to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
 
-We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which begins with a classical boundary condition and the boundary state follows from the quantization.
-The interface obtained is actually the same as the one from using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but the scattering process derived here is more intuitive and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} is more transparent.
+We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state.
+The interface obtained is actually the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.
 
@@
 
-The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.
+The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in the fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.
 

### 2017-06-28 intro.tex
[draft] wording changes for descritive text.

@@
 % fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
-Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process.
-Fidelity is the (square of) the overlap of the ground state wavefunctions of the Hamiltonians before and after the quench.
-There is no dynamic information in fidelity; nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic for the Loschmidt echo computation.
-The Loschmidt echo is (square of) the overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
-The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit.
-Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
-In this paper we extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
+We compute the Loschmidt echo to extract information in the dynamics of the quench process.
+The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
+It decays with a power law $t^{- \alpha}$for the lack of length scale in the $t \rightarrow \infty$ limit.
+The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
+We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
+We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transition coefficients.
+Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
+The finite size fidelity calculation further supports these results.
 

### 2017-06-28 analy_eval.tex
[draft] anal, def. num changed.

@@
 These are the characteristic size of the corner at the tip of the slit.
-If there is no regulator, however, a dilation transformation can rescale both to $1$ and get rid of their dependence.
-Therefore, regulators are necessary in keeping track of the scale dependence, and physically sensible when considering the lattice realization of the systems.
+Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence.
+The introduction of regulators is also physically sensible when considering the lattice realization of the systems.
 
@@
 The Loschmidt echo can be evaluated in the same way.
-Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
+Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
 In the $\xi$ plane, we end up with the same diagram as fidelity.
-With one more conformal mapping, it becomes the cylinder partition function between the two boundary states.
+With one more conformal mapping, the diagram becomes the cylinder partition function between the two boundary states.
 
@@
 The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$.
-But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation.
-In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law surge of Loschmidt echo, which does not agree with the known results.
+But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation.
+In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results.
 One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
@@
 where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$.
-A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.
+A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to come from the Schwartzian and outer circle regulator.
 

### 2017-06-28 def_fidel_echo.tex
[draft] wording changes for descritive text.
[draft] anal, def. num changed.

@@
 In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams.
-It will then be evident that these quantities are just the free energy of boson with conformal interfaces (or boundaries).
+We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries).
 
@@
 Both of them can be produced by the imaginary time evolution.
-Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
+Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
 The logarithmic fidelity is then (twice) the free energy of this diagram
@@
 at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities.
-According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
 One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
@@
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
-From the boundary CFT point of view, the change of boundary condition can be regarded as insertion of primary field which is the (bcc) operator.
-These diagrams then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
+From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator.
+The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
 

### 2017-06-28 num_result.tex
[draft] anal, def. num changed.

@@
 \end{equation}
-where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are shifted quadratic curves symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.
+where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.
 

### 2017-06-28 arxiv_sub.sh
[submit] submission tools ready

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+# remove the tex file extention except for the master file bCFT.tex
+# then compress to tar gz that can be uploaded to arxiv
+tar --transform='flags=r;s|.tex||' --transform='flags=r;s|^bCFT$|bCFT.tex|' -cvzf bCFT.tar.gz *.tex *.bbl images

### 2017-06-28 prb_sub.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+./flatex -v bCFT.tex
+tar --transform='flags=r;s|.flt|.tex|' -cvzf bCFT.tar.gz bCFT.flt images *.bbl

### 2017-06-28 arxiv_sub.sh
[submit] tar pacakge ready

@@ -1,5 +1,5 @@
 #!/bin/bash
 
-# remove the tex file extention except for the master file bCFT.tex
+# remove the tex file extention except for the master file bCFT_paper.tex
 # then compress to tar gz that can be uploaded to arxiv
-tar --transform='flags=r;s|.tex||' --transform='flags=r;s|^bCFT$|bCFT.tex|' -cvzf bCFT.tar.gz *.tex *.bbl images
+tar --transform='flags=r;s|.tex||' --transform='flags=r;s|^bCFT_paper$|bCFT_paper.tex|' -cvzf bCFT_paper.tar.gz *.tex *.bbl images

### 2017-06-28 prb_sub.sh

@@ -1,4 +1,4 @@
 #!/bin/bash
 
-./flatex -v bCFT.tex
-tar --transform='flags=r;s|.flt|.tex|' -cvzf bCFT.tar.gz bCFT.flt images *.bbl
+./flatex -v bCFT_paper.tex
+tar --transform='flags=r;s|.flt|.tex|' -cvzf bCFT_paper.tar.gz bCFT_paper.flt images *.bbl

### 2017-06-28 intro.tex
[draft] reference order updated

@@
 % non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
-Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity.
-\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
+Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}.
+The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
 As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states.

### 2017-09-20 F_correction.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[referee] Q1 fixed.

@@
-In the course of derivation the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable.
-However, free energy is not invariant under the conformal transformation, because the boundaries partially break the conformal symmetry.
-In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term -- to get the correct exponent of the fidelity and Loschmidt echo.
+In the course of deriving the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state calculation in App.~\ref{app:lambda_12} (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable.
+However, free energy is not invariant under the conformal transformation since the boundaries partially break the conformal symmetry.
+In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term to get the correct exponent of the fidelity and Loschmidt echo.
 
 % outer boundary correction
-It is discussed in Cardy and Peschel's pioneering work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy.
-The original of these term comes from the nonzero geodesic curvature of the boundary, which when adding back the bulk curvature term constitutes the trace anomaly.
-Here we demonstrate this principle using the disk free energy example in Ref.~\onlinecite{cardy_finite-size_1988}.
+It is discussed in Cardy and Peschel's pioneering work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
+\begin{equation}
+F = - \frac{c}{6} \left( \int_M  K(x) d^2x + \int_{\partial M} k_g ds \right)  \ln L 
+\end{equation}
+where $M$ is a 2d smooth manifold, $K(x)$ is the Gaussian curvature, $k_g$ is the geodesic curvature of on the boundary of the manifold and $L$ is the system's characteristic length.
+
+The boundary term was not previous noticed in the literature, but is actually important even in the simplest example of the disk free energy.
 Consider an annulus on flat space with inner radius $r_1$ and outer radius $r_2$.
@@
 \begin{equation}
-F({\rm annulus}) = -  \frac{c}{6} \ln \frac{r_2}{r_1} 
+F({\rm annulus}) = -  \frac{c}{6} \ln \frac{r_2}{r_1} .
 \end{equation}
@@
 \begin{equation}
-  F( {\rm disk} ) = - \frac{c}{6} \ln \frac{r_2}{a}
+  F( {\rm disk} ) = - \frac{c}{6} \ln \frac{r_2}{a},
 \end{equation}
@@
 The disk free energy is completely contributed by its outer boundary with other parts being conformal invariant.
-One can then interpret the annulus free energy as an additive contribution from its outer and inner surfaces as (which is also consistent with the geodesic curvature integral calculation),
+In fact, $K = 0, k_g = \frac{1}{r}$ for disk, and so
 \begin{equation}
-F( {\rm annulus} ) = -  \frac{c}{6} \ln \frac{r_2}{a} +  \frac{c}{6} \ln \frac{r_1}{a} = - \frac{c}{6} \ln \frac{r_2}{r_1}
+F( {\rm disk}  ) = - \frac{c}{6}  \left( \int_{\partial M} k_g ds \right)  \ln \frac{r_2}{a}  = - \frac{c}{6}  \ln \frac{r_2}{a}
 \end{equation}
-An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface, because $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible compared to the other term.
+where $a$ is the short distance cut-off.
 
-A similar outer surface logarithmic term also appears in the conformation transformation from the slit diagram to the annulus in Fig.~\ref{fig:H-tau_fold}.
+One can then interpret the annulus free energy as an additive contribution from its outer and inner surfaces as
+\begin{equation}
+F( {\rm annulus} ) = -  \frac{c}{6} \ln \frac{r_2}{a} +  \frac{c}{6} \ln \frac{r_1}{a} = - \frac{c}{6} \ln \frac{r_2}{r_1}.
+\end{equation}
+An annulus becomes a disk when its inner radius is of order $a$, and we can see that the contribution from the inner surface $\frac{c}{6} \ln \frac{r_1}{a}$ becomes negligible compared to the one from the outer surface.
+
+A similar outer surface logarithmic term also appears in the conformal transformation from the slit diagram to the annulus in Fig.~\ref{fig:H-tau_fold}.
 In the slit diagram, the regulators all have radii that are at the order of the short distance cut-off.
 They will have negligible contributions to the free energy.
-However, after doing the conformal transformation, the outer surface will contribute $-\frac{c}{6} \ln \frac{r_2}{r_1}$ which should not be there.
-Using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
+However, after doing the conformal transformation, the outer surface radus is much larger than {\it the new short distance regulator} in the $\xi$ plane, which will contribute a $-\frac{c}{6} \ln \frac{r_2}{r_1}$ term that should not be there.
+Therefore using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
 \begin{equation}
-F_{\xi } = F_{z} + \frac{c}{6} \beta 
+F_{z} = F_{\xi} + \frac{c}{6} \beta .
 \end{equation}
@@
 % staircase geometry correction
-The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its angular time evolution.
+The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction .
 The traditional radial quantization however has radial direction to be the time.
@@
 \begin{equation}
-H_{w} = H_{\xi} - \frac{c}{24\pi} \beta 
+H_{\xi} = H_{w} - \frac{c}{24\pi} \beta .
 \end{equation}
@@
 \begin{equation}
-F_w = F_{\xi} - \frac{c}{12} \beta 
+F_{\xi} = F_{w} - \frac{c}{12} \beta .
 \end{equation}
@@
 \begin{equation}
-F_{w} = F_z + \frac{c}{12}\beta
+F_{z} = F_w + \frac{c}{12}\beta.
 \end{equation}

### 2017-09-21 gnd_dn_lambda.tex
[review] Forgot to commit just now. Fig. 3, 4, 5, 11 changed. Appendices are rearranged such that analytical ones are before the numerical ones.

@@
 In this appendix, we calculate the amplitude for the setup shown in Fig.~\ref{fig:Fig_gnd_dn_lambda}.
-In particular, the unfolded configuration has D/N boundary conditions at $x = \pm \frac{L}{2}$ and conformal interface $\lambda$ at $x = 0$.
+In particular, the unfolded configuration has D/N boundary conditions at $y = \pm \frac{L}{2}$ and conformal interface $\lambda$ at $y = 0$.
 The general solutions can be written as
@@
 \label{eq:normalized_f}
-f(k, x) = 
+f(k, y) = 
 \left\lbrace
 \begin{aligned}
-  A_1 e^{i kt} \cos\left(kx +\frac{1}{2}kL \right) &  \quad x < 0  \\
-  A_2 e^{ikt}  \sin\left(kx - \frac{1}{2}kL \right) & \quad x > 0 .  \\
+  A_1 e^{i kt} \cos\left(ky +\frac{1}{2}kL \right) &  \quad y < 0  \\
+  A_2 e^{ikt}  \sin\left(ky - \frac{1}{2}kL \right) & \quad y > 0 .  \\
 \end{aligned} \right. 
 \end{equation}
-As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,x<0)\equiv\phi_1$ and $f(k,x>0)\equiv\phi_2$, the boundary condition at the junction becomes
+As demonstrated in Sec.~\ref{sec_sub:general_formulation}, if we denote $f(k,y<0)\equiv\phi_1$ and $f(k,y>0)\equiv\phi_2$, the boundary condition at the junction becomes
 \begin{eqnarray}\begin{aligned}

### 2017-09-21 num_result.tex
[review] Forgot to commit just now. Fig. 3, 4, 5, 11 changed. Appendices are rearranged such that analytical ones are before the numerical ones.

@@
 \caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$.
-We work with the total system size $N = 30$k sites, and parameters $m = 10^{-8}$, $k = 1$.
+We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$.
 The lattice constant is set to unity.
@@
     \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
-The total system size is $N=35$k sites with the same parameters as in Fig.~\ref{fig:DDDD}.
+The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.

### 2017-09-22 analy_eval.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

@@
 Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
-The blue semi-circles are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
+The blue semi-circles {\color{red} of radii $\epsilon$} are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
 Middle: Image of the map $\xi = \frac{z}{\tau - z}$.
-Right: Image of $w = \ln \xi$.
+{\color{red}The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.}  Right: Image of $w = \ln \xi$.
 It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied.
@@
 \begin{equation}
+\label{eq:S_i_S_j}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) ,
@@
 The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
-Another process
-\begin{equation}
-\label{eq:DNDN}
-{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
-\end{equation}
+Another process {\color{red} in Eq.~\eqref{eq:DNDN}}
+%\begin{equation}
+%\label{eq:DNDN}
+%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
+%\end{equation}
 is used to verify

### 2017-09-22 conclusion.tex
[draft] wording changes for descritive text.
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

@@
 The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$.
-Generic value of $\theta$ then interpolates those conventional boundary conditions.
+Generic value of $\theta$ then interpolates between those conventional boundary conditions.
 A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.
 
-The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface, which we denote as
-\begin{equation}
-S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
-\end{equation}
+The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
+%, which we denote as
+%\begin{equation}
+%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
+%\end{equation}
 Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces.

### 2017-09-22 disc.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

@@
 % analytic results type 1 -> type 2, c/4; 
-In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
-\begin{equation}
- S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
-\end{equation}
+In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process {\color{red}described in Eq.~\eqref{eq:S_i_S_j}} (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$).
+%\begin{equation}
+% S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
+%\end{equation}
 We find that if the conformal interfaces are of different types, i.e.
@@
 
-For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for this process 
-\begin{equation}
-{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
-\end{equation}
+For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for {\color{red}the process in Eq.~\eqref{eq:DNDN}.}
+%this process 
+%\begin{equation}
+%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
+%\end{equation}
 The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT.
@@
 The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
-It would be interesting to have a CFT calculation that reproduces the better numerical result of
-\begin{equation}
-{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
-\end{equation}
+It would be interesting to have a CFT calculation that reproduces the better numerical result {\color{red}for the process in Eq.~\eqref{eq:DNP_rand()}, as}
+%of
+%\begin{equation}
+%{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
+%\end{equation}
 shown in Fig.~\ref{fig:PDN_fit}.

### 2017-09-22 num_result.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

@@
 \includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
-\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$.
+\caption{The Loschmidt echo decay exponent of the process in {\color{red}Eq.~\eqref{eq:DDDD}}, with gluing condition $S_1(\theta)$.
 We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$.
@@
 
-We start with the process
-\begin{equation}
-\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
-\end{equation}
+We start with the process in {\color{red}Eq.~\eqref{eq:DDDD}}, 
+%\begin{equation}
+%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
+%\end{equation}
 and show its Loschmidt echo in Fig.~\ref{fig:DDDD}.
@@
 
-Next we analyze the more interesting $\theta$ dependent process
-\begin{equation}
-  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
-\end{equation}
+Next we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
+%\begin{equation}
+%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
+%\end{equation}
 in which the joining boundary condition is determined by $S_1(\theta)$.
@@
 \includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
-    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$.
-The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
+    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.}The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.
@@
 
-We finally consider the case
-\begin{equation}
-\text{P}+\text{P}\rightarrow\lambda+\text{P},
-\end{equation}
+We finally consider the {\color{red}process in Eq.~\eqref{eq:PP}}
+%\begin{equation}
+%\text{P}+\text{P}\rightarrow\lambda+\text{P},
+%\end{equation}
 in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
@@
     \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
-    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$.
+    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process {\color{red}in Eq.~\eqref{eq:PP}}.
 The parameters are the same as those in Fig.~\ref{fig:DDNN}.
@@
 \begin{equation}
+\label{eq:DNP_rand()}
 {\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
@@
 \includegraphics[width=1\columnwidth]{PDN_fit.pdf}
-\caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$.
-The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
+\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
 The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.

### 2017-09-22 codes/DDNN_echo_fit.py

@@ -130,7 +130,7 @@ x_analy = [this_x_analy-offset  for this_x_analy in x_analy]
 y_analy = (-1)*2 * ( np.square(x_analy) - x_analy )
 ax.plot( x_analy , y_analy , c = 'red' , label = r"analytical $2\left(\frac{\theta}{\pi} - \left(\frac{\theta}{\pi}\right)^2\right)$" )
 # ax.plot( x , [-this_slope for this_slope in slope] , 'o', markersize = 2, c = 'black', markeredgewidth=0.0 , label = "numerical" )
-(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2 , label = "numerical" ) 
+(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2.5, elinewidth=1 , label = "numerical" ) 
 for cap in caps:
   cap.set_markeredgewidth( 1 )
 # These are in unitless percentages of the figure size. (0,0 is bottom left)
@@ -151,7 +151,7 @@ ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Echo Exponent" )
 
 ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol=1, handlelength=3 )
-
+ax.annotate('(a)', xy=(0.05, 0.55), xytext=(0.01, 0.56))
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():
     tick.label.set_fontsize( 8 )

### 2017-09-22 codes/DDNN_fidel_fit.py

@@ -92,7 +92,7 @@ y_analy = ( -np.square( x_analy ) + x_analy )
 ax.plot( x_analy, y_analy, color = 'red' , label = r"analytical $\frac{\theta}{\pi} - \left(\frac{\theta}{\pi}\right)^2$" )
 
 # numerical results
-(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2, label = "numerical" ) 
+(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2.5, elinewidth=1 , label = "numerical" ) 
 for cap in caps:
     cap.set_markeredgewidth( 1 )
 
@@ -112,7 +112,7 @@ ax.set_ylim( ( 0, 0.3 ) )
 ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Fidelity Exponent" )
 ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 1, handlelength = 3 )
-
+ax.annotate('(b)', xy=(0.05, 0.25), xytext=(0.01, 0.28))
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():
     tick.label.set_fontsize( 8 )

### 2017-09-22 codes/PDN_fit.py

@@ -93,9 +93,9 @@ ax.plot( x_analy, y_analy, color = 'red' , label = r"analytical $\frac{\theta}{\
 ax.plot( x_analy, y_analy-1.0/8, color = 'green' , label = r"$\frac{\theta}{\pi} - \left(\frac{\theta}{\pi}\right)^2-\frac{1}{8}$" )
 
 # numerical results
-(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 1, label = "numerical" ) 
+(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2.5, elinewidth=1 , label = "numerical" ) 
 for cap in caps:
-    cap.set_markeredgewidth( 0.5 )
+    cap.set_markeredgewidth( 1 )
 
 
 # ----------------------------------------------------------------------           

### 2017-09-22 codes/PP_echo_fit.py

@@ -134,7 +134,7 @@ ax.plot( x_analy , y_analy , c = 'red' , label = r"analytical $2\left(\left|\fra
 # ax.plot( x , [-this_slope for this_slope in slope] , 'o', markersize = 2, c = 'black', markeredgewidth=0.0 , label = "numerical" )
 
 # numerical results
-(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2, label = "numerical" ) 
+(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2.5, elinewidth=1 , label = "numerical" ) 
 for cap in caps:
     cap.set_markeredgewidth( 1 )
 
@@ -158,7 +158,7 @@ ax.set_ylabel( r"Echo Exponent" )
 # ax.errorbar( x , slope , yerr=error , fmt='k.')
   
 ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol=1, handlelength=3 )
-
+ax.annotate('(a)', xy=(0.05, 0.55), xytext=(0.01, 0.56))
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():
     tick.label.set_fontsize( 8 )

### 2017-09-22 codes/PP_fidel_fit.py

@@ -93,7 +93,7 @@ y_analy = ( -np.square( x_analy - 0.25 ) + np.abs( x_analy - 0.25 ) )
 ax.plot( x_analy, y_analy, color = 'red' , label = r"analytical $\left|\frac{\theta}{\pi} - \frac{1}{4}\right| - \left(\frac{\theta}{\pi} - \frac{1}{4} \right)^2$" )
 
 # numerical results
-(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2, label = "numerical" ) 
+(_, caps, _) = ax.errorbar( x, slope, yerr = error, fmt='o', color = 'black', capsize = 1, markersize = 2.5, elinewidth=1 , label = "numerical" ) 
 for cap in caps:
     cap.set_markeredgewidth( 1 )
 
@@ -112,7 +112,7 @@ ax.set_ylim( ( 0, 0.3 ) )
 ax.set_xlabel( r"$\frac{\theta}{\pi}$" , fontsize=15)
 ax.set_ylabel( r"Fidelity Exponent" )
 ax.legend( loc = 'upper left', frameon = False, prop = {'size':10}, ncol = 1, handlelength = 3 )
-
+ax.annotate('(b)', xy=(0.05, 0.25), xytext=(0.01, 0.28))
 # smaller font for inset
 for tick in ax2.xaxis.get_major_ticks():
     tick.label.set_fontsize( 8 )

### 2017-09-28 bd_notation.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added
[review] Some texts changed

@@
 \end{equation}
-Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$.
+{\color{red} Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$.
 To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.
+Probably changed to: To remove the bcc operator from c to a at infinity, the analytic and numerical calculations are performed by taking $a=c$ and $L\gg\tau$.}
 
@@
 \begin{equation}
+\label{eq:DNDN}
 {\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .

### 2017-09-28 general_formulation.tex
[review] Some texts changed

@@
 \end{aligned}\end{equation}
-For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices.
+For generic values of $\theta$, the interface is partially-transmitting, 
+{\color{red}whose transmission coefficient
+%and reflection coefficients 
+can be read off from the scattering matrices
+\begin{eqnarray}\begin{aligned}
+t = \sin2\theta.
+\end{aligned}\end{eqnarray}
+}
 We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 

### 2017-09-28 num_result.tex
[review] Some texts changed

@@
 It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation.
-Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$.
+{\color{red}Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$.
+Probably change to: We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at larger value of $\theta$.
+The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.}
 \begin{figure}[htb]

### 2017-10-02 abstract.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface.
-The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$.
+The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartite fidelity as $L^{-\frac{\alpha}{2}}$.
 We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
-Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.
+Possible physical realizations of these interfaces include for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.
 

### 2017-10-02 analy_eval.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 The Loschmidt echo can be evaluated in the same way.
-Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
+Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
 In the $\xi$ plane, we end up with the same diagram as fidelity.
@@
 The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$.
-But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation.
+But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformations.
 In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results.

### 2017-10-02 def_fidel_echo.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries).
+{\color{red}We would like to emphasize that all the path-integral spacetime diagrams are in the Euclidean space, and the analytic continuation will be performed only for the final results.}
 
@@
 at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities.
-According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity {\color{red}($L$ is the finite size of the system)} and $\ln \tau$ in Loschmidt echo {\color{red}($\tau$ is the imaginary time)}.
 One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
@@
 \end{equation}
+where $\tau$ is the imaginary time.
 
-The tip of the slit is no longer a twist field with the presence of the conformal interface.
+The tip of the slit is no longer a {\color{red}corner singularity\cite{cardy_finite-size_1988}} with the presence of the conformal interface.
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.

### 2017-10-02 general_formulation.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states.
-For example, one may use the current operator rather than the Virasoro generator to solve the zero momentum flow condition.
-This idea dates back to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+For example, one may use the current operator rather than the Virasoro generator to solve the zero-momentum flow condition.
+This idea dates to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
 Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
@@
 We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state.
-The interface obtained is actually the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.
+The interface obtained is the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.
 
@@
 where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
-As argued, the momentum components of the stress tensor are continuous across the interface.
+As argued, the momentum components of the stress tensor is continuous across the interface.
 As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
@@
 This mode is one of the scattering modes that leave the interface.
-On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain.
+On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain.
 We therefore establish the scattering relation

### 2017-10-02 intro.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 We discuss our results and related experimental works in Sec.~\ref{sec:disc}.
-Finally we conclude in Sec.~\ref{sec:conclusion}.
+Finally, we conclude in Sec.~\ref{sec:conclusion}.
 
 This paper includes several appendices for technical details.
+In App.~\ref{app:lambda_12}, we present the detailed calculation of the free energy for the above-mentioned interfaces.
+In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example.
 In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text.
+Up to this point, we work exclusively with the oscillator modes of the free bosons.
+In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order.
+Therefore, the results remain valid in the physical situation of connecting two compactified bosons of different radii.
+In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation.
 We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}.
-The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}.
-In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation.
-We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}.
-The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}.
-Up until this point, we work exclusively with the oscillator modes of the free bosons.
-In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order.
-Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.
+The details of numerical simulation are presented in App.~\ref{app:comp_fid_echo}.
 

### 2017-10-02 num_result.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)

@@
 
-We start with the process in {\color{red}Eq.~\eqref{eq:DDDD}}, 
+{\color{red}We first consider the process in Eq.~\eqref{eq:DDDD} for a lattice with $3000$ sites}, 
 %\begin{equation}
@@
 We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
-While the short time decay pattern is different from the DD case, the long time behavior and exponents remain the same for both echo and fidelity.
+While the short time decay pattern is different from the DD case, the long-time behavior and exponents remain the same for both echo and fidelity.
 We therefore do not present the result here.
 
-Next we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
+Next, we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
 %\begin{equation}
@@
 in which the joining boundary condition is determined by $S_1(\theta)$.
-A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction.
+{\color{red}We worked with a system containing $35000$ sites.} A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction.
 We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
@@
 \includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
-    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.}The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
+    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.} The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.

### 2017-10-04 reply_to_referee.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{{./}}

\newcommand{\cf}{\textit{cf.} }
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }

\newcommand{\up}{\mathord{\uparrow}}
\newcommand{\dn}{\mathord{\downarrow}}
\newcommand{\I}{\mathbb{I}}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\qed}[0]{$\blacksquare$}

\newcommand{\reply}[1]{{\color{black}#1}}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

% \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
% \usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}

\begin{document}
\large

{\bf Reply to the First Referee -- BF13677/Zhou}

\color{blue}

The authors investigate a quench problem where two critical bosonic chains are initially separated and then coupled by a conformal defect. This generalizes earlier treatments, where the chains were simply connected. They determine the fidelity (the negative logarithm of the overlap of the initial and the final ground state for chain lengths L) and the Loschmidt echo (the negative logarithmic overlap of the evolved state after some time t with the initial ground state). Since these overlaps decay as power laws, the logarithms vary as lnL and lnt, respectively. For a simple connection of the chains, the prefactors are known to be 1/8 and 1/4, respectively. For a defect, the authors find, that they can vary continuously with the defect transmission, depending on the boundary conditions at the chain ends and at the defect. This is derived analytically via a path- integral picture of the two quantities and conformal mappings. It is also verified by numerical calculations on oscillator chains, based on explicit expressions of the ground states in terms of boson operators from which the overlaps can be obtained as determinants.

Given that such varying exponents have a long history and were found also for the entanglement entropy in chains with defects, this is an interesting topic and the results are worth publishing. However, there are a couple of points to be clarified or changed.

\reply{We first acknowledge the effort of this respectful referee to read our manuscript thoroughly and provide constructive comments. We will address the issues below.}

(1) In order to obtain the correct result for the known case, the authors have to add a constant beta/12 in (21). However, the derivation in Appendix A is not right. The relation (A5) between the Hamiltonians in the staircase and in the strip differs by a sign from the one given in Ref. [32]. I think that the argument must be different. Usually, the universal terms in free energies are determined via appropriate non-conformal transformations which bring in the energy- momentum tensor. In this context one wonders about additional constants coming from the starting states in the path integral representation.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{/images/fig_H-tau_fold.pdf}
\caption{Conformal transformation from the slit to cylinder.}
\label{fig:H-tau_fold}
\end{figure}

\reply{
We thank the referee for pointing out this sign error, in fact we used the $w \rightarrow \xi \rightarrow z$ order in the calculation as opposed to the $z \rightarrow \xi \rightarrow w$ order of the conformal transformation in the figure. We have fixed them.

Nevertheless we hold our opinion of using these two corrections to account for the missing $\frac{1}{12}\beta$. Let us reiterate our arguments.

The first correction comes from mapping the slit diagram to the annulus. Before doing this conformal transformation, the short distance regulator is small on the $z$ plane. Hence the contribution of the free energy coming from introducing the two blue lines are small. However, after the transformation, we implicitly choose another regulator which is small on the $\xi$ plane. But by the change of this short distance cutoff, the $\xi$ plane erroneously contribute a $- \frac{c}{6} \ln \frac{r_2}{r_1}$ term from the outer surface. The compensation $+\frac{c}{6} \ln \frac{r_2}{r_1} = \frac{c}{6}\beta$ is the correction we are talking about.

The is the lesson we learned from the Cardy-Peschel paper, where there are two explicit examples of computing the free energies of a corner and a cone. Both objects should be regarded as infinitely extended without boundaries at certain radii. The authors computed the correct results by conformally mapping the geometry to whole plane (or upper half plane) and contrasted with the calculation of the truncated corner and cone with both short and long distance regulators. They found that the discrepancies of the truncated cone and corner w.r.t. to the correct results come from the outer boundary contribution. By subtracting this otherwise nonexistent contribution using their proposed geodesic curvature formula, they are able to recover the correct result. We believe that the mapping from the $z$ to $\xi$ plane result in the same situation here.

The staircase geometry Hamiltonian and the plane Hamiltonian is differed by the Schwartzian term in the transformation rule of the stress tensor, which gives $-\frac{c}{12} \beta $ correction. By gathering the two terms, we do get the desired $\frac{c}{12}\beta$ correction.

We request the referee to reconsider the presented arguments.
}

(2) I also find the whole presentation of the mapping unsatisfactory. In part, this has to with the fact that no lengths are indicated in the figures.

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $z = 1$. To evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R$. This should avoid the problem the referee was worried about.

(By the way, we add the semi-circle manually in the center of Fig. 5, which is in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (and maybe the worry the referee previously had), we notice the following fact
\begin{itemize}
\item the non-conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be doing by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis. 
\end{itemize}
since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

This line of argument is also included in the main text below Fig. 6. 
}

For the Loschmidt echo, the starting point is again a strip of width L, as shown in Fig. 4. However, in the left part of Fig. 6 this width no longer appears. There is only a small remark in the text that L >> tau. But L is of significance, for finite L the ratio t/L enters, and in Ref. [25] this case could actually be treated.

\reply{We declared in the text (above Fig. 4) that we will take $L \gg \tau$ in all the echo computation. This keeps the problem with only one length scale.

  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel mappings, as demonstrated in Ref.[25]. But the conformal interface, the dashed line, will be inside the upper half plane and we don;t know how to calculate its OPE with the stress tensor. So in this paper, we only aim to understand the leading order behavior and its relation to the transmission coefficient. }

In the center part, there are two half-circles around the origin, which supposedly are the images of those on the left. But their radii (which determine the parameter beta) are not given anywhere.

\reply{The radii for the left and center parts are indicated in the caption, and also discussed in the main text.}

Finally, the identification of the two semi-circles is physically quite strange. One wonders if it is really necessary for the calculations or the reasoning.

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line shouldn’t matter. We therefore take the simplest periodic boundary condition for the ease of computation. }

(3) The calculation of the vacuum energy in equ.(E6) is not quite clear. Since the original expression diverges, a word about regularization would be in order. In the conversion of the sums into zeta functions (what does the index H mean ?) it seems to me that the n=0 terms are not handled correctly. The second function must be zeta(-1,-x). One could also imagine just giving a reference.

\reply{
A clarification is indeed necessary. We here use the Hurwitz zeta function regularization and so H stands for Hurwitz.

The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s)}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!

We labeled several minus signs to be red to remind future readers to be cautious. }

I also think that Appendix E ("Alternative approach...") should come after the "actual" approach which is presented in Appendix F. There is also a typo in equ.(F9).

\reply{We have rearranged the order of appendixes as request and fix the typo in Eq.(A9), where the $\frac{1}{6}$ should be $-\frac{1}{6}$}

(4) The main result, namely the variation of the exponents in Equ. (27) and Figs. 8-10 as functions of the parameter theta is not discussed. The increase with theta must have some kind of physical interpretation and also the particular values at theta=0 and theta=pi/2.

\reply{We add two paragraphs in the discussion section about the main results.

We first deal the three special points $\theta = 0, \frac{\pi}{4}, \frac{\pi}{2}$ and their special relations to the bcc operator ${\rm D} \rightarrow {\rm N}$, and then present an hand wave argument that the quadratic relation should come from the dimension of the vertex operators.

In another paragraph, we use the free lattice boson model to argue why the exponent increase for larger $\theta$. 
}

(5) In all examples except the very last one in Fig.10, the outer boundaries of the chains remain the same and only the inner ones change. Therefore the notation for the change of boundary conditions introduced in (17) is unnecessary complicated. The formulation in (22) would be sufficient and much simpler.

(6) A number of equations expressing these changes of boundary conditions appear several times in identical form: (22),(37),(40); (24),(30) and Fig.7; (18),(26),(32),(38) and Fig.8; (28),(34) and Fig.9; (36),(39) and Fig.10. This is a redundancy which should be reduced.

\reply{Question (5) and (6) are about the notations of boundary conditions.

We remove the redundant boundary condition c in the some of the equations as long as it is equal to a. The simplified notation like $\text{DN} \rightarrow \lambda$ is better to be perceived as a single boundary condition changing process and the associated bcc operator.

Since the notation is shortened, we don’t let them occupy a single equation and instead put them inside a sentence. We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase “in Eq.(XX)”, and the time it saves to look up. }

(7) All References appear twice with different numbers! This must also be the reason, why the numbering in the text starts at 48. I am astonished that the authors did not notice that.

\reply{This is really embarrassing. We had 47 citations in our local version of manuscripts but 94 on the submitted. We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.

But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }

(8) At no point could I see a remark on the analytical continuation from imaginary to real time. Instead, the notation changes back and forth between t and tau.

\reply{This point should be clarified in the introduction of the path-integral formalism(Sec. III. A.). All the path-integral spacetime diagrams are in the imaginary time. We only do analytic continuation to the final results of the imaginary time diagram.

We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq. (17). Thereafter we uniformly use $t$ towards the end of the main text.}

(9) As the parameter theta determines the transmission through the defect, it would be useful to give the transmission coefficient below Equ.(4) explicitly.

\reply{We have added the transmission coefficients and add a short paragraph discussing the parameter lambda in different physical realizations.}

(10) As to the figures:

- If one wants to show the folding in Figs. 3 and 4, one should not move and rescale the strip on the right hand sides but leave it in place. Then the meaning of the length L is also clearer. Incidentally, L appears here for the first time in the paper, which should also be changed.

- In Fig. 5, the boundary conditions should also be indicated on the right side.

\reply{We have modified Fig. 3 and 4 according to the suggestions.

We also define L to be the length for immediately after the definition of fidelity and above Fig. 4 for echo.

We have dramatically change Fig. 5. 
}

- The legends in Figs. 7-10 are strange in that the analytical results are represented by a horizontal symbol (line), but the numerical ones by a vertical one.

\reply{The numerical results are represented by dots and error bar. The error bar is small and not clearly visible in these diagrams. We have modified the legend for Fig. 7-10 to make the vertical error bar clearer.}

- There is no (a) and (b) in Figs. 8 and 9, but in the caption these are referred to.

\reply{We have modified Fig. 8 and 9 accordingly.}

- The system sizes in the numerics given in the captions are unclear to me. What does 30k or 35k mean? In Fig. 7, it says k=1 immediately after that. Is this the same k? If not, what is it? As with L, I think that such numbers should also appear in the text. If one is talking about 35.000 sites, one wonders why such a large number was taken.

\reply{The k in the math mode font is the spring constant, while the $k$ after 30 and 35 means 1000. We didn't realize the conflict. We have changed 30k to 30000 and 35k to 35000. We take 35000 sites for reducing the finite size effect in Fig. 8 which is important for the theta value near zero.

- Fig. 11 corresponds to the right piece of Fig. 6, but is rotated by 90°. This is confusing, in particular since the corresponding Fig. 12 is not rotated. The lambda line on the left has to be dotted. Also confusing is the use of x and L in (E1) below.

We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{pi}$. }

(11) In a number of places the English has to be corrected (missing articles or endings, missing or incorrect words).

\reply{We have proofread the paper before the resubmission and (hopefully) corrected those grammatical/spelling errors.}

{\bf \color{black} Report of the Second Referee -- BF13677/Zhou}

In the manuscript "Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface" the authors report on results concerning the finite volume decay exponent of the fidelity and long time exponent of the Loschmidt echo after joining two bosonic boundary CFTs. As they point out such exponents could potentially be observed in certain quantum wire experiments. The results appear to be correct and they are supported by independent numerical calculations coming from a harmonic lattice model.

I think the paper is interesting enough and sufficiently well written to be published in Physical Review B, but before acceptance I would like the authors to consider my remarks below and make the necessary modifications.

\reply{We thank the referee for the positive review and reply to the comments below.}

1) The introduction overestimates the results that are actually presented in the main text. In the fourth paragraph it is claimed that the paper studies joining two different CFTs, when in fact only a very special case is treated: joining two identical massless free boson theories, with arbitrary (but identical) boundary conditions though. It should be clarified in the introduction that we will only see results for this special case. In fact, paragraph 4 is not at all clear, it should be rewritten.

\reply{We agree that this paper only deals with 2d bosonic CFTs. However these CFTs can be different, e.g. having different compactification radii. The relation between lambda and the the different compactification radii are nevertheless hidden in the last appendix of the paper, which makes it hardly accessible to the readers. We also didn't explicitly point out the derivation (and physical interpretation) of this relation in one of the references we cited.

On the other hand, the boundary conditions on the sites that later connected are different. For example, the notation DN means that one end of the chain has Dirichlet and the other end that connects to it has Neumann boundary conditions, see Fig. 3.

After connection, normally one should assume it's a periodic boundary condition (after folding) which gives transmission coefficient 1. However, in the text we consider more general conformal interface that can have arbitrary transmission coefficient between 0 and 1. Such interface can indeed be realized by connecting two boson theories with different compactification radii.

To clarify this issue, we have rewritten paragraph 4 in the introduction that made the following changes 
\begin{itemize}
\item We rephrase what we did as ``generalization to interface that is partially transmissive''.
\item We list the examples we talked about in this paper: the harmonic chain example(non-compact boson), the two different 1+1 bosonic CFT with different radii.
\item We also explicitly mention the the dependence of lambda w.r.t. the different compactification at the end of Sec. II. A
\end{itemize}
}

2) In this 4th paragraph of the introduction (also recurring in some places later) it is mentioned that the parameter lambda is controlled by the ratio of compactification radii. Is this so? This point is never discussed in the main text (or the appendices). Doesn't lambda describe the interface after joining the two CFTs and the compactification radii are the same in the two theories? At least in the case considered in the main text.

\reply{It is our fault that the relation of lambda and ratio of the compactification radii are not pointed out explicitly in the main text. 
We have made changes in paragraph 4 accordingly and also some texts in the end of Sec.II.A to discuss the generalization to compact bosons (with different radii)}

3) In section 3 after Eq. (16) twist fields are mentioned but these were never introduced before, therefore the statement "The tip of the slit is no longer a twist field..." doesn't seem to be self-contained.

\reply{We avoid the use the phrase ``twist field'' and change it to corner singularity and cite Cardy1988 for its treatment.}

4) After Eq. (17) it is stated that the boundary condition "c" is neglected. Isn't it taken to be "a" instead?

\reply{This statement is incorrect. It is taken to be a and changing it will influence the result even in the large L limit. So we didn’t neglect ‘c’ but taking it to be ‘a’. We also take a simpler notation for this case after Eq. (17) }

5) Now we come to the main result of the paper, Eq. (23), that will yield all the exponents which will then be numerically verified. Despite this equation being the main results, its derivation is hidden away in an appendix. In fact all the calculations in this paper are demoted to be part of one of the numerous Appendix sections. I believe, that at least the main result should be given some space in the main text. I don't think this would compromise readability or accessibility of the results, in fact it think it would improve on it.

\reply{The derivation of Eq.(23) is contained in the original App. F, which is mainly the evaluation of partition function using a determinant identity with no physical arguments. In fact we believe moving App. F back to the main text will still make it isolated to the surrounding physical discussion.  However, in order to improve readability, we have rearranged the appendices and make explicit references in the main text for the derivation.

App. A is the calculation for the main analytic results. The reader shall only need this appendix to reproduce Eq.(23).

App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details. We have also mentioned these structural changes in the end of the introduction.}

6) The last sentence before Sec. 4 states that the analytical (incorrect) and numerical curves "merge" at theta=0. In fact, these two curves are quite different and clearly the analytical curve cannot reproduce the numerics at all, as expected. To me it seems like that the green curve coincides with the dots in Fig. 10 only by chance. I'm not sure what the relevance of this curve is or mentioning that at theta=0 the numerics and the (incorrect) analytics "merge." This merging is simply because theta=0 is the no-quench point, when the pre- and post-quench setup is the same.

\reply{We have remove the sentence of ``merging'' at theta = 0. That is as the referee said only a calibrating point. But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence. The difference ⅛ is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c). We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

7) The references appear in duplicate.

8) Additionally, there are typos throughout the text that should be corrected (e.g. like "the this"), I suggest the manuscript to be proofread carefully before resubmission.

\end{document}
%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

### 2017-10-04 F_correction.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 % outer boundary correction
-It is discussed in Cardy and Peschel's pioneering work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
+It is discussed in Cardy and Peschel's work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
 \begin{equation}
@@
 \end{equation}
-where $M$ is a 2d smooth manifold, $K(x)$ is the Gaussian curvature, $k_g$ is the geodesic curvature of on the boundary of the manifold and $L$ is the system's characteristic length.
+where $M$ is a 2d smooth manifold, $K(x)$ is the Gaussian curvature, $k_g$ is the geodesic curvature of the boundary of the manifold and $L$ is the system's characteristic length.
 
@@
 
-A similar outer surface logarithmic term also appears in the conformal transformation from the slit diagram to the annulus in Fig.~\ref{fig:H-tau_fold}.
-In the slit diagram, the regulators all have radii that are at the order of the short distance cut-off.
+A similar outer surface logarithmic term also appears in the middle panel of Fig.~\ref{fig:fidel-map}.
+The conformal map from the $z$ plane to $\xi$ plane bring the strip (with the small blue semi-circle) to the upper half plane with the semi-circle around $z = 1$ extracted.
+This is in close analogy with the truncated corner calculation in Ref.~\onlinecite{cardy_finite-size_1988}.
+In order to evaluate this diagram, we manually add the large blue semi-circle as IR cut-off, at the price of introducing an additional contribution  $-\frac{c}{6} \ln \frac{r_2}{a}$ of free energy which should not be there.
+
+The same thing happened in Fig.~\ref{fig:H-tau_fold} with a slightly different mechanism.
+In the slit diagram (left panel in Fig.~\ref{fig:H-tau_fold}), the regulators all have radii that are at the order of the short distance cut-off.
 They will have negligible contributions to the free energy.
-However, after doing the conformal transformation, the outer surface radus is much larger than {\it the new short distance regulator} in the $\xi$ plane, which will contribute a $-\frac{c}{6} \ln \frac{r_2}{r_1}$ term that should not be there.
+However, in the new $\xi$ plane, we implicitly switch to a {\it new short distance regulator} such that only the blue semi-circle around $0$ contribute negligibly.
+The outer surface radius, despite being the image of a small semi-circle on $z$ plane, will contribute a $-\frac{c}{6} \ln \frac{r_2}{a}$ term on the $\xi$ plane that should not be there.
+
 Therefore using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
@@
 \end{equation}
+for both the fidelity and Loschmidt echo.
 

### 2017-10-04 analy_eval.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 
-We thus add small semi-circles around the points where the bcc operators reside, followed by a series of conformal mapping.
-For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}.
+We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mapping.
+
+For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
 \begin{figure}[h]
@@
 \includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
-\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $.
+\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $.
 The two black dots represent possible locations of boundary condition changing (bcc) operators.
@@
 The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
-To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
+To evaluate the diagram, we add the outer blue semi-circle centered at $z = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(z - 1)$}
 \label{fig:fidel-map}
 \end{figure}
-We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
+We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$.
+Then both of $z = 0$ and $1$ can host bcc operators.
+We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $z = 1$.
+In order to evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( z- 1)$.
+Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
+\begin{equation}
+Z_{ab} = \langle a | e^{-\pi H } |b \rangle
+\end{equation}
+
+The height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
 \begin{equation}
@@
 \end{equation}
-The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $.
-Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order.
-The dashed line and solid line can then be regarded as two boundary states, and the diagram corresponds to the following partition function
+The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$. So the width of the cylinder is 
 \begin{equation}
-  Z_{ab} = \langle a | e^{-\pi H } |b \rangle .
+\label{eq:fidel_cyd_width}
+\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant} 
 \end{equation}
@@
 Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
-In the $\xi$ plane, we end up with the same diagram as fidelity.
-With one more conformal mapping, the diagram becomes the cylinder partition function between the two boundary states.
+From $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case.
+With one more conformal mapping $w = \ln \xi$, the diagram becomes the cylinder partition function between the two boundary states.
+
+The height of the cylinder is still $\pi$ because of folding.
+In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \pm \epsilon} \sim \frac{\pm \epsilon}{ \tau }$.
+The end points of the larger semi-circle are at $\pm \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\pm \tau}{\epsilon}$.
+Hence the width of the cylinder is
+\begin{equation}
+\label{eq:echo_cyd_width}
+\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant} 
+\end{equation}
 
@@
 \includegraphics[width=\columnwidth]{fig_H-tau_fold}
-\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions.
+\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions.
 Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
-The blue semi-circles {\color{red} of radii $\epsilon$} are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
+The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
 Middle: Image of the map $\xi = \frac{z}{\tau - z}$.
@@
 
-The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$.
-But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformations.
-In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results.
-One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
+One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric.
+This can be resolved by the following observation.
+There exists conformal mappings from the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane.
+Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$.
+In fact, the width of the cylinder is a conformal invariant and only depend on the cross ratio of the half annulus.
+The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
+\begin{equation}
+\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
+\end{equation}
+Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$.
+Since conformal transformation preserves the cross ratio, this is also the result if just plug in the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
+The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder.
+The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.
+
+Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
+
+In App.~\ref{app:lambda_12}, we performed the calculation of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy to the leading order of cylinder width $\beta$.
+A na\"ive application of the result however will lead to an apparent contradiction.
+One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface.
+Physically this corresponds to the situation that the boundary condition does not change after joining the two chains.
+Hence the Loschmidt echo will stay at $1$ and the free energy is $0$.
+This motivates a shift to the free energy
 \begin{equation}
@@
 where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$.
-A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to come from the Schwartzian and outer circle regulator.
+A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.
 
-For the process ($c$ is assumed to be the same as $a$)
+After incorporating this shift, for the process ($c$ is assumed to be the same as $a$)
 \begin{equation}
@@
 \end{equation}
-We can then read off the fidelity and Loschmidt echo power law decay exponent with the identification $\beta = 2 \ln L$ and $ 4 \ln \tau$.
+We can then set $\beta = 2 \ln L$ and $ 4 \ln t$ (after analytic continuing to real time) to get the fidelity and echo exponent.
 
 As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND.
-In the region accessible to the numerical calculation in the lattice model, we choose the process
-\begin{equation}
-\label{eq:DDDD}
-{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
-\end{equation}
-to verify
+In the region accessible to the numerical calculation in the lattice model, we choose the process ${\rm DD} \rightarrow  \lambda$ to verify
 \begin{equation}
@@
 The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
-Another process {\color{red} in Eq.~\eqref{eq:DNDN}}
-%\begin{equation}
-%\label{eq:DNDN}
-%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
-%\end{equation}
-is used to verify
+Another process \rev{$\rm{DN} \rightarrow \lambda$} {\iffalse \color{red} in Eq.~\eqref{eq:DNDN}\fi} is used to verify
 \begin{equation}
@@
 
-We also use a less physical process
-\begin{equation}
-  \label{eq:PP}
-  {\rm P} + {\rm P} \rightarrow \lambda + {\rm P},
-\end{equation}
-to check the shift of the curve
+We also use a more artificial process ${\rm P} \rightarrow \lambda$ to check the shift of the curve
 \begin{equation}

### 2017-10-04 bd_notation.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

--- 2017-06-27 bd_notation.tex
@@
 \end{equation}
-Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$.
-To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.
+\rev{In most cases of the following, we will consider taking $a = c$ to remove the bcc operator from $a$ to $c$ at infinity. And we will use the shorthand notation
+\begin{equation}
+S_a( \theta_a ) \rightarrow S_b( \theta_b )
+\end{equation}
+to remind ourselves that we are isolating the boundary condition change only on joint of the two chains. 
+}
 
@@
 \begin{equation}
-{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .
+\label{eq:DNDN}
+ {\rm DN} \rightarrow \lambda.
 \end{equation}

### 2017-10-04 comp_fid_echo.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 Our strategy takes advantage of the symplectic structure of the bosonic Bogoliubov transformation and explicitly construct the "BCS" like ground state.
-With slight modification\cite{blaizot_quantum_1986}, one can work out its fermionic version and apply to quadratic fermion models for example in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011}.
+With slight modification\cite{blaizot_quantum_1986}, one can work out its fermionic version and apply to quadratic fermion models in Ref.~\onlinecite{vasseur_universal_2014,stephan_local_2011}.
 
@@
 
-The general solution diagonalization problem is hard\cite{arnold_mathematical_2010}, however the positive definite $\mathcal{M}$ (and hence $M$) can be solved by Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006}, which states the existence, uniqueness (up to reordering of eigenvalues) and explicit construction of the matrix $\mathcal{S}\in {\rm Sp}(2n \mathbb{R}) $ such that
+The general solution of the diagonalization problem is hard\cite{arnold_mathematical_2010}, however the positive definite $\mathcal{M}$ (and hence $M$) case can be solved by Williamson's theorem\cite{arnold_mathematical_2010,xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006}, which states the existence, uniqueness (up to reordering of eigenvalues) and explicit construction of the matrix $\mathcal{S}\in {\rm Sp}(2n \mathbb{R}) $ such that
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where the normalization is given by the McMahon Master theorem Eq.~\ref{eq:bosonic_McMahon}.
+where the normalization is given by the McMahon Master theorem Eq.~\eqref{eq:bosonic_McMahon}.
 Apply constraint in Eq.~\eqref{eq:constraint_1}, it simplifies to the top left corner of the symplectic matrix

### 2017-10-04 compact_boson.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 \subsection{Mode Expansion of Compact Boson}
-Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
+Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.~\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
 \begin{widetext}
@@
 
-In Ref.\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space.
+In Ref.~\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space.
 The boundary state we need here however lives on $x = 0$ -- a equal-space slice.
-We therefore exchange compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
+We therefore compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
 \begin{equation}
@@
 \end{equation}
-This corresponds to exchange the $x$ and $t$ in Ref.\onlinecite{di_francesco_conformal_1997}.
+This corresponds to exchange the $x$ and $t$ in Ref.~\onlinecite{di_francesco_conformal_1997}.
 
@@
 \end{equation}
-At the boundary $x = 0$ $\bar{z}=z^{-1}$, therefore we have
+At the boundary $x = 0$, $\bar{z}=z^{-1}$, therefore we have
 \begin{equation}
@@
 where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}.
-The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}.
+The g-factor can only be determined by the Cardy condition\cite{cardy_boundary_2004}.
 Since it is not important for what follows, we shall not include the calculation here.
@@
 The winding mode thus can contribute at most a $\ln\beta$ term to the free energy.
-Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.
+Compared to the result in App.~\ref{app:lambda_12}-\ref{app:gnd_dn_lambda}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.
 

### 2017-10-04 def_fidel_echo.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

--- 2017-06-28 def_fidel_echo.tex
@@
-In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams.
-We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries).
+In this section, we define the fidelity and Loschmidt echo and present their corresponding imaginary time path integral diagrams.
+We will see that these path integrals are just the free energy of boson with conformal interfaces (or boundaries).
 
@@
 \end{equation}
-For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface.
-Both of them can be produced by the imaginary time evolution.
-Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
+For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length $L$, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface.
+Both of them can be produced by an imaginary time evolution.
+Taking the horizontal axis as imaginary time direction, the fidelity can be diagrammatically represented in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
 The logarithmic fidelity is then (twice) the free energy of this diagram
 \begin{equation}
-\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z.
+\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln |Z|.
 \end{equation}
@@
 The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states.
-The solid dot represents boundary changing operator.
+The solid dot represents boundary condition changing (bcc) operator.
 Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$ are possible choices of boundary conditions.)}
@@
 \begin{equation}
-\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
+\mathcal{L}( t )  \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
 \end{equation}
-The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
+\rev{The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition} similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
 Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.
+\rev{After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence.
+For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}).
+The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).}
 
@@
 If the interface is completely transparent, i.e.
-at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities.
-According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
+at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
 One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
-In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration.
+In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or integration of the Ward identity.
 If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
@@
 \label{eq:full-pass}
-\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
+\begin{aligned}
+  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L \\
+ \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
+\end{aligned}
 \end{equation}
+\rev{where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo}.
 
-The tip of the slit is no longer a twist field with the presence of the conformal interface.
+With the presence of the conformal interface, the tip of the slit is no longer a {\color{red}corner singularity\cite{cardy_finite-size_1988}} .
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.

### 2017-10-04 disc.tex
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 % analytic results type 1 -> type 2, c/4; 
-In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process {\color{red}described in Eq.~\eqref{eq:S_i_S_j}} (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$).
-%\begin{equation}
-% S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
-%\end{equation}
+In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process $S_i( \theta_1 ) \rightarrow S_j( \theta_2 )$ {\iffalse {\color{red}described in Eq.~\eqref{eq:S_i_S_j}}\fi} (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$).
+
 We find that if the conformal interfaces are of different types, i.e.
@@
 In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$.
-It is then reasonable to find an universal echo between them.
+It is then reasonable to find a universal echo between them.
 The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
@@
 
-For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for {\color{red}the process in Eq.~\eqref{eq:DNDN}.}
-%this process 
-%\begin{equation}
-%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
-%\end{equation}
-The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT.
-Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used).
-Such discrepancy is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation.
-The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
-This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$.
+For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}.
+We can first understand the values of several special points on this curve.
+\begin{itemize}
+\item $\theta = 0$: This is where the boundary condition does change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
+\item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$.
+The chain is still disconnected after the change of the boundary condition.
+We can thus view the problem of changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D.
+The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimension is $\Delta = \frac{1}{16}$.
+From this we can get the exponent to be $\frac{1}{2}$
+\begin{equation}
+\begin{aligned}
+  \quad \mathcal{L}(\tau) &\sim |\langle \phi_{{\rm D N}}(0) \phi_{{\rm ND}}(\tau)   \rangle |^2 
+|\langle \phi_{{\rm ND}}(0)  \phi_{{\rm DN}}(\tau)   \rangle| ^2\\
+& \sim \frac{1}{|\tau|^{8\Delta}} = \frac{1}{|\tau|^{\frac{1}{2}}},
+\end{aligned}
+\end{equation}
+which agrees with our results. 
+\item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$.
+The exponent $\frac{3}{8}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
+\end{itemize}
+In general, the result gives the full spectrum of operator dimensions in the ${\rm DN}$ to $\lambda $ transition.
+In the bosonic theory we consider, the primary fields are vertex operators, which is exponential of the field $\exp( \nu \phi )$.
+Depending on the convention, the dimension of the vertex operator is a numerical constant times $\frac{\nu^2}{8\pi}$.
+So if $\nu$ linearly depend on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points we work out above.
 In a rational boson theory, the number of primary fields is finite.
-It requires further study to identify these bcc operators and explore their physical significance.
+It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.
+
+On the other hand, in our lattice boson model, $\theta$ parameterizes the bond interaction between the boundary sites of the chains.
+Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means the $\Sigma$ matrix is closer to the original, thus a smaller perturbation and vise versa.
+Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) of the result.
 
@@
 The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
-It would be interesting to have a CFT calculation that reproduces the better numerical result {\color{red}for the process in Eq.~\eqref{eq:DNP_rand()}, as}
-%of
-%\begin{equation}
-%{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
-%\end{equation}
-shown in Fig.~\ref{fig:PDN_fit}.
+It would be interesting to have a CFT calculation that reproduces the better numerical result in Fig.~\ref{fig:PDN_fit} {\color{red}for the process in Eq.~\eqref{eq:DNP_rand()}}
+% \begin{equation}
+% {\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
+% \end{equation}
 

### 2017-10-04 general_formulation.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 \end{aligned}\end{equation}
-For generic values of $\theta$, the interface is partially-transmitting, 
-{\color{red}whose transmission coefficient
-%and reflection coefficients 
-can be read off from the scattering matrices
-\begin{eqnarray}\begin{aligned}
-t = \sin2\theta.
-\end{aligned}\end{eqnarray}
-}
-We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
+For generic values of $\theta$, the interface is partially-transmitting, {\color{red}whose transmission coefficient is $\pm \sin 2 \theta$.}
+
+We note that the $S$-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
 \begin{figure}[h]
@@
 
+So far the deviation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''.
+For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$.
+Because the winding mode lives on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$.
+App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$.
+For example, the $S_1(\theta)$ interface should satisfy
+\begin{equation}
+\lambda = \tan \theta = \frac{n_2 R_1}{n_1 R_2}
+\end{equation}
+for coprime integer $n_1$ and $n_2$. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the CFTs on both sides.
+
+The winding modes however do not contribute to the fidelity and echo exponent to the leader order, as shown in App.~\ref{app:compact_diff_boson}.
+So the derivations with the non-compact boson boundary state in Eq.~\eqref{eq:bd_state} holds true for the compact bosons.
+
 %%% Local Variables:

### 2017-10-04 interface_free_boson.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 In this appendix, we demonstrate how to realize conformal interface in a lattice harmonic chain defined in Sec.~\ref{sec_sub:free_boson_lattice},
-\todo[inline]{Mao: Your expression of the Hamiltonian is wrong! Please note the coefficients of the cross $\phi_1 \phi_0$ term. }
 \begin{equation}
@@
   \phi_1 
-\end{pmatrix}
+\end{pmatrix},
 \end{aligned}
@@
 	& A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
-	& B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
+	& B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 ,\\
   \end{aligned} \right. 
@@
 B_{+}\\
-\end{pmatrix}
+\end{pmatrix},
 \end{equation}
@@
 -2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
-\end{bmatrix}
+\end{bmatrix}.
 \end{equation}
@@
 \begin{equation}
-  S_{11} = - \frac{\Sigma_{11} + e^{ika} }{\Sigma_{11} + e^{-ika}}
+  S_{11} = - \frac{\Sigma_{11} + e^{ika} }{\Sigma_{11} + e^{-ika}},
 \end{equation}
@@
 \label{eq:Sigma_condition}
-\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
+\det \Sigma = -1, \, \, \text{tr} \Sigma = 0,
 \end{equation}
@@
 S = \frac{1}{1 - e^{-2ika } } ( -2i \sin ka ) \Sigma
- = - e^{ika} \Sigma
+ = - e^{ika} \Sigma.
 \end{equation}
@@
 \frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
-\end{bmatrix}
+\end{bmatrix},
 \end{equation}
@@
 
-We use this series of two-site to model the $S_1(\theta)$ type conformal interface, as they give the same $S$ matrix in the continuum limit.
+We use this two-site interaction to model the $S_1(\theta)$ type conformal interface, as they give the same $S$ matrix in the continuum limit.
 Therefore, the large $t$ behavior of its Loschmidt echo should match with our field theoretic prediction.

### 2017-10-04 intro.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 % quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
-In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry of the system.
-Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}.
+In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry.
+Simply put, the interface scatters the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}.
 Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT).
-Their correlation functions can exhibit different critical exponents from the bulk counterparts\cite{cardy_conformal_1984}.
+Their correlation functions can exhibit different critical exponents from their bulk counterparts\cite{cardy_conformal_1984}.
 One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band.
-The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
+The X-ray absorption rate will then have a power singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
 There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
@@
 Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}.
-The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system.
+The ``cut-and-join" quench protocol is a popular framework for investigating the spreading of the influence from the localized impurity (or boundary) across the system.
 As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states.
@@
 Various quantities can be used to detect the information in the quench process.
-For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems.
+For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem A, when both A and B are identical critical systems.
 The authors ascribe such increase to the proliferation and propagation of quasi-particle excitations emitted at the joint.
 Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase.
-In this model, the Majorana zero mode acts as a bcc and its conformal dimension appears in the exponent of the power law decay for the Loschmidt echo.
+In this model, the Majorana zero mode acts as a bcc operator and its conformal dimension appears in the exponent of the power law decay of the Loschmidt echo.
 
@@
 Before the quench, the slit represents boundaries that are completely reflective to the injecting particles.
-The joining turns on the transmission from one side to the other.
+During the quench, the joining turns on the transmission from one side to the other.
 In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.
 
-In this paper, we generalize these ideas and consider connecting two different CFTs in the ``cut-and-join" protocol.
-The interface produced will interpolate between the total reflective and complete transparent ones.
-As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface can be realized as a domain wall between two free compact boson theories with different compactification radii.
-Entanglement properties for non-compact free boson/free fermion lattices have been numerically and analytically studied\cite{peschel_exact_2012,sakai_entanglement_2008}.
+In this paper, we generalize these ideas to an interface that interpolate between the total reflective and complete transparent ones.
+This kind of interface can have many realizations.
+They can be produced by connecting two different bosonic CFTs in the ``cut-and-join" protocol.
+As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface is a domain wall between two free compact boson theories with different compactification radii.
+It can also be implemented by non-compact free boson/free fermion on the lattice with a finely tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies).
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, whereas it is controlled by the ratio of masses in the case of free lattice boson.
+In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, while for free lattice boson it is controlled by the ratio of masses.
 We expect it to be tunable in a realistic experimental setting.
@@
 % fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
-We compute the Loschmidt echo to extract information in the dynamics of the quench process.
+We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models.
 The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
-It decays with a power law $t^{- \alpha}$for the lack of length scale in the $t \rightarrow \infty$ limit.
+It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit.
 The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
@@
 The rest of the paper is organized as follows.
-In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.
+In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable bosonic conformal interface and its lattice realization.
 In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison.
@@
 This paper includes several appendices for technical details.
-In App.~\ref{app:lambda_12}, we present the detailed calculation of the free energy for the above-mentioned interfaces.
+In App.~\ref{app:lambda_12}, we present the leading order analytical calculation of the free energy for the above-mentioned interfaces.
 In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example.

### 2017-10-04 num_result.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 \includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
-\caption{The Loschmidt echo decay exponent of the process in {\color{red}Eq.~\eqref{eq:DDDD}}, with gluing condition $S_1(\theta)$.
+\caption{The Loschmidt echo decay exponent of the process in \rev{$\text{DD}\rightarrow \lambda$}{\iffalse \color{red}Eq.~\eqref{eq:DDDD}\fi}, with gluing condition $S_1(\theta)$.
 We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$.
@@
 
-{\color{red}We first consider the process in Eq.~\eqref{eq:DDDD} for a lattice with $3000$ sites}, 
+We first consider the process ${\rm DD} \rightarrow \lambda$
+%in Eq.~\eqref{eq:DDDD}
 %\begin{equation}
@@
 %\end{equation}
-and show its Loschmidt echo in Fig.~\ref{fig:DDDD}.
-The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay.
+and show its Loschmidt echo of \rev{system size 30000 sites} in Fig.~\ref{fig:DDDD}.
+The inset is a typical Loschmidt echo diagram, whose linearly decreasing behavior in the log-log scale indicates the expected power law decay.
 We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast.
@@
 
-We also calculated the companion process
-\begin{equation}
- \text{NN}+\text{NN}\rightarrow\lambda+\text{NN},
-\end{equation}
-and obtain identical exponents as shown in Fig.~\ref{fig:DDDD}.
+We also calculated the companion process \rev{${\rm NN} \rightarrow \lambda$} and obtain identical exponents as in Fig.~\ref{fig:DDDD}.
 We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
@@
 
-Next, we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
+Next, we analyze the more interesting $\theta$ dependent process {\color{red}${\rm DN} \rightarrow \lambda$}
+%in Eq.~\eqref{eq:DNDN}
 %\begin{equation}
@@
 in which the joining boundary condition is determined by $S_1(\theta)$.
-{\color{red}We worked with a system containing $35000$ sites.} A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction.
+{\color{red}We worked with a system containing $35000$ sites.} A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
 We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
@@
 The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
-We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.
+%We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.
 
@@
 \includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
-    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.} The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
+    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{DN} \rightarrow \lambda$ {\iffalse in Eq.~\eqref{eq:DNDN}\fi}.
+The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.
@@
 
-We finally consider the {\color{red}process in Eq.~\eqref{eq:PP}}
+We finally consider the process {\color{red}$\text{P} \rightarrow \lambda$}
+% in Eq.~\eqref{eq:PP}
 %\begin{equation}
@@
 \begin{aligned}
-\label{eq:approx_DNDN}
+\label{eq:approx_PPPP}
 S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
@@
 \end{equation}
-where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.
+where $\delta\theta=0.003\pi$. The $\theta$ dependent exponents are now symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.
 
@@
     \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
-    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process {\color{red}in Eq.~\eqref{eq:PP}}.
+    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{P} \rightarrow \lambda${\iffalse in Eq.~\eqref{eq:PP}\fi}.
 The parameters are the same as those in Fig.~\ref{fig:DDNN}.
@@
 It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation.
-{\color{red}Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$.
-Probably change to: We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at larger value of $\theta$.
+{\color{red}We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$.
 The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.}

### 2017-10-04 pf_of_id.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

@@
 where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators.
-The matrix notation here should be understand as bilinear form.
+The matrix notation here should be understand as a bilinear expression.
 For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
@@
 \end{equation}
-where we understand $\vec{\bar{b}}^\dagger$ as a column vector independent to $\vec{{b}}^\dagger$. Thus the whole expression can be written as
+where we understand $\vec{\bar{b}}^\dagger$ as a column vector independent of $\vec{{b}}^\dagger$. Thus the whole expression can be written as
 \begin{equation}

### 2017-10-04 reply_Mao.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article

\documentclass{article}
%\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,slashed,amstext,array,blkarray,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{svg}
%\usepackage{multicol} % only for \documentclass{article}
%\usepackage{mathabx} % only for \documentclass{article}
%\usepackage{mathtools, cuted}  % only for \documentclass{article}
%\usepackage{svg} % only for \documentclass{article}
\usepackage{enumitem}
\usepackage[toc,page]{appendix}
\usepackage{bm,bbold}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\usepackage{comment}
\usepackage{changepage}
%\usepackage{epsfig,subcaption,float,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{tkz-euclide}

\graphicspath{{./}{./Figs/}}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\cf}{\textit{cf.} } 
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in
% document begins

\begin{document}
%\maketitle
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{/images/fig_fidel-map.pdf}
\caption{?}
\label{fig:Conformal_transformation}
\end{figure}

We would like to consider the following conformal transformation in Fig.~\ref{fig:Conformal_transformation}. We first map the stripe on the $\omega$-plane to a semicirlce on the $z$-plane, and then map it to two concentric circles on $z'$-plane, and finally maps it to a cylinder on the $\xi$-plane.

The UV regulator on the $z$-plane was spanned across $\exp\pm\pi\frac{\epsilon}{L}$ while the IR regulator was spanned across $\pm \exp\pi\frac{W}{L}$ where $W$ is the IR regulator on the $\omega$-plane.

We want to map it to two concentric circles on $z'$-plane, to the first order of $\epsilon$. First we want to illustrate that the following map
\begin{eqnarray}\begin{aligned}
z'(z)&=\frac{z-a}{az-1}
\end{aligned}\end{eqnarray}
does not work. First $z'(1)=-1$, thus $a$ and $b$, which roughly are $a\pm\epsilon$ should be around $-1$ rather than around the origin. Indeed, we can simply expand
\begin{eqnarray}\begin{aligned}
\frac{1\pm\epsilon-a}{a(1\pm\epsilon)-1} = \frac{1-a\pm\epsilon}{a-1}\left(1\mp\frac{a}{a-1}\epsilon\right) = -1\pm\frac{1+a}{a-1}\epsilon
\end{aligned}\end{eqnarray}
as it should be.

The map we may want is 
\begin{eqnarray}\begin{aligned}
z'(z) = \frac{1}{z-1}
\end{aligned}\end{eqnarray}
which intuitively makes sense. Let's check
\begin{eqnarray}\begin{aligned}
z'(\exp\pm\pi\frac{\epsilon}{L}) &= \pm\frac{L}{\pi\epsilon} \\
z'(\pm\exp\pi\frac{W}{L}) &= \pm\exp\pi\frac{-W}{L} \\
\end{aligned}\end{eqnarray}
Thus the IR and UV regulator exchange places in the $z'$-plane, and they are concentric. We note also that the relative position of the solid and dash line does not change.

And finally the map from $z'$ to $\xi$ would be $\xi = \ln z'$ such that it is mapped from circle to stripe. Thus The complete map is 
\begin{eqnarray}\begin{aligned}
\xi(\omega) = \ln\frac{1}{\exp\frac{\pi\omega}{L}-1}
\end{aligned}\end{eqnarray}
Let's check. The boundary condition of a is $(-\infty,-\epsilon)$ and $b$ is $(\epsilon,W)$ and $c$ is $(-\infty+iL,W+iL)$, they are mapped to
\begin{eqnarray}\begin{aligned}
a&: (-i\pi,-\ln\frac{\pi\epsilon}{L}-i\pi) \\
b&: (-\ln\frac{\pi\epsilon}{L},-\frac{\pi W}{L}) \\
c&: (-i\pi,-\frac{\pi W}{L}-i\pi) \\
\end{aligned}\end{eqnarray}
which is a cylinder with width $\pi$ and length $-\ln\frac{\pi\epsilon}{L}+\frac{\pi W}{L}$. The length go to infinity with $\epsilon\rightarrow0$ and $W\rightarrow\infty$.

It is clear from the map $\xi(\omega)$ that the minus sign in front of the log-function is irrelevant, namely the map $z'(z)$ can really be taken as $z'(z)=z-1$ rather than $z'(z)=\frac{1}{z-1}$, as we did here.

%\end{comment}

\end{document}

### 2017-10-10 reply_to_referee.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 \newcommand{\etc}{\textit{etc.} }
+\newcommand{\rev}[1]{{\color{red}#1}}
 
@@
 5 and Fig.
-6 are strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$.
+6 are \rev{not} strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$.
 To resolve this problem, (and maybe the worry the referee previously had), we notice the following fact
@@
 \item the non-conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be doing by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
-\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis. 
+\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
 \end{itemize}
@@
 6 this width no longer appears.
-There is only a small remark in the text that L >> tau.
+There is only a small remark in the text that $L \gg \tau$.
 But L is of significance, for finite L the ratio t/L enters, and in Ref.
@@
 
-As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line shouldn’t matter.
+As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line shouldn‚Äôt matter.
 We therefore take the simplest periodic boundary condition for the ease of computation.
-}
+\rev{Do we want to mention this somewhere in the text?}}
 
@@
 
-We labeled several minus signs to be red to remind future readers to be cautious. }
+We labeled several minus signs to be red to remind future readers to be cautious. \rev{Do we want to keep these highlights?}}
 
@@
 
-Since the notation is shortened, we don’t let them occupy a single equation and instead put them inside a sentence.
-We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase “in Eq.(XX)”, and the time it saves to look up.
+Since the notation is shortened, we don'Äôt let them occupy a single equation and instead put them inside a sentence.
+We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase in Eq.(XX)Äù, and the time it saves to look up.
 }
@@
 
-We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq. (17). Thereafter we uniformly use $t$ towards the end of the main text.}
+We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq.
+(17).
+Thereafter we uniformly use $t$ towards the end of the main text.
+\rev{This seems not to be the case..
+Do we want to change that?}}
 
@@
 8 which is important for the theta value near zero.
+}
 
@@
 11 corresponds to the right piece of Fig.
-6, but is rotated by 90°.
+6, but is rotated by 90¬∞.
 This is confusing, in particular since the corresponding Fig.
@@
 
-We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{pi}$. }
+\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{pi}$. }
 
@@
 It is taken to be a and changing it will influence the result even in the large L limit.
-So we didn’t neglect ‘c’ but taking it to be ‘a’.
+So we did noÄôt neglect cÄ but taking it to be aÄô.
 We also take a simpler notation for this case after Eq.
@@
 But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence.
-The difference ⅛ is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c).
+The difference $1/8$õ is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c).
 We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

### 2017-10-10 analy_eval.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 
+\rev{Tian ci: Proofread this part for the conformal map}
+
 For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
@@
 The two black dots represent possible locations of boundary condition changing (bcc) operators.
-The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of the point connecting $a$ and $b$ boundaries.
-The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
-To evaluate the diagram, we add the outer blue semi-circle centered at $z = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(z - 1)$}
+The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries.
+The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
+To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
 \label{fig:fidel-map}
@@
 We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$.
-Then both of $z = 0$ and $1$ can host bcc operators.
-We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $z = 1$.
-In order to evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( z- 1)$.
+Then both of $\xi = 0$ and $1$ can host bcc operators.
+We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $\xi = 1$.
+In order to evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$.
 Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
 \begin{equation}
-Z_{ab} = \langle a | e^{-\pi H } |b \rangle
+Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
 \end{equation}
@@
 \label{eq:fidel_cyd_width}
-\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant} 
+\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
 \end{equation}
@@
 The height of the cylinder is still $\pi$ because of folding.
-In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \pm \epsilon} \sim \frac{\pm \epsilon}{ \tau }$.
-The end points of the larger semi-circle are at $\pm \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\pm \tau}{\epsilon}$.
+In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$.
+The end points of the larger semi-circle are at $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$.
 Hence the width of the cylinder is
@@
 \label{eq:echo_cyd_width}
-\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant} 
+\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
 \end{equation}
@@
 Middle: Image of the map $\xi = \frac{z}{\tau - z}$.
-{\color{red}The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.}  Right: Image of $w = \ln \xi$.
+The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.
+Right: Image of $w = \ln \xi$.
 It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied.
@@
 This can be resolved by the following observation.
-There exists conformal mappings from the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane.
+There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}.
 Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$.
-In fact, the width of the cylinder is a conformal invariant and only depend on the cross ratio of the half annulus.
+In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus.
 The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
@@
 Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$.
-Since conformal transformation preserves the cross ratio, this is also the result if just plug in the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
+Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
 The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder.
@@
 The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
-Another process \rev{$\rm{DN} \rightarrow \lambda$} {\iffalse \color{red} in Eq.~\eqref{eq:DNDN}\fi} is used to verify
+Another process $\rm{DN} \rightarrow \lambda$ {\iffalse \color{red} in Eq.~\eqref{eq:DNDN}\fi} is used to verify
 \begin{equation}

### 2017-10-10 conclusion.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface.
-The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$.
+The conventional `DD', `NN' boundary conditions belong to the special choice of $\theta$ in $S_1$, and `DN' and P are among the special choices of $S_2$.
 Generic value of $\theta$ then interpolates between those conventional boundary conditions.
@@
 
-The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
+The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in Eq.~\eqref{eq:S_i_S_j}.
 %, which we denote as

### 2017-10-10 def_fidel_echo.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 \end{equation}
-\rev{The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition} similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
+The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}.
 Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.
-\rev{After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence.
+After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence.
 For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}).
-The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).}
+The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).
 
@@
 \begin{aligned}
-  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L \\
+  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L, \\
  \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
@@
 \end{equation}
-\rev{where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo}.
+where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo.
 
-With the presence of the conformal interface, the tip of the slit is no longer a {\color{red}corner singularity\cite{cardy_finite-size_1988}} .
+With the presence of the conformal interface, the tip of the slit is no longer a corner singularity\cite{cardy_finite-size_1988} .
 Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.

### 2017-10-10 disc.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 \begin{itemize}
-\item $\theta = 0$: This is where the boundary condition does change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
+\item $\theta = 0$: This is where the boundary condition does not change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
 \item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$.
@@
 The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy.
-It would be interesting to have a CFT calculation that reproduces the better numerical result in Fig.~\ref{fig:PDN_fit} {\color{red}for the process in Eq.~\eqref{eq:DNP_rand()}}
+It would be interesting to have a CFT calculation that reproduces the better numerical result in Fig.~\ref{fig:PDN_fit} for the process in Eq.~\eqref{eq:DNP_rand()}.
 % \begin{equation}

### 2017-10-10 general_formulation.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 \end{aligned}\end{equation}
-For generic values of $\theta$, the interface is partially-transmitting, {\color{red}whose transmission coefficient is $\pm \sin 2 \theta$.}
+For generic values of $\theta$, the interface is partially-transmitting, whose transmission coefficient is $\pm \sin 2 \theta$.
 

### 2017-10-10 num_result.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

@@
 \includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
-\caption{The Loschmidt echo decay exponent of the process in \rev{$\text{DD}\rightarrow \lambda$}{\iffalse \color{red}Eq.~\eqref{eq:DDDD}\fi}, with gluing condition $S_1(\theta)$.
+\caption{The Loschmidt echo decay exponent of the process in $\text{DD}\rightarrow \lambda$ {\iffalse \color{red}Eq.~\eqref{eq:DDDD}\fi}, with gluing condition $S_1(\theta)$.
 We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$.
@@
 %\end{equation}
-and show its Loschmidt echo of \rev{system size 30000 sites} in Fig.~\ref{fig:DDDD}.
+and show its Loschmidt echo of system size 30000 sites in Fig.~\ref{fig:DDDD}.
 The inset is a typical Loschmidt echo diagram, whose linearly decreasing behavior in the log-log scale indicates the expected power law decay.
@@
 
-We also calculated the companion process \rev{${\rm NN} \rightarrow \lambda$} and obtain identical exponents as in Fig.~\ref{fig:DDDD}.
+We also calculated the companion process ${\rm NN} \rightarrow \lambda$ and obtain identical exponents as in Fig.~\ref{fig:DDDD}.
 We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
@@
 
-Next, we analyze the more interesting $\theta$ dependent process {\color{red}${\rm DN} \rightarrow \lambda$}
+Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
 %in Eq.~\eqref{eq:DNDN}
@@
 in which the joining boundary condition is determined by $S_1(\theta)$.
-{\color{red}We worked with a system containing $35000$ sites.} A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
+We worked with a system containing $35000$ sites.
+A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
 We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
@@
 \end{aligned}\end{eqnarray}
+\rev{ where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}. }
 Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process.
@@
 
-We finally consider the process {\color{red}$\text{P} \rightarrow \lambda$}
+We finally consider the process $\text{P} \rightarrow \lambda$
 % in Eq.~\eqref{eq:PP}
@@
 It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation.
-{\color{red}We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$.
-The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.}
+We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$.
+The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.
 \begin{figure}[htb]

### 2017-10-11 reply_to_referee.tex
[referee] 2nd round pass

@@
 
-The first correction comes from mapping the slit diagram to the annulus.
+The first correction comes from mapping the slit diagram to the annulus (in Fig.
+6).
 Before doing this conformal transformation, the short distance regulator is small on the $z$ plane.
@@
 
+We also change Fig 5, where in the left panel there is no vertical line IR regulator.
+So after doing the $\exp$ conformal transformation, the center diagram should be the upper half plane minus the small circle around $\xi = 1$.
+This is also an extended object, much the same way as the cone and corner in the Cardy-Peschel paper.
+To evaluate this extended diagram, we manually add another big semi-circle centered at $\xi = 1$ with radius $R_{\xi } \gg 1$.
+This will introduce a $-\frac{c}{6} \beta $ term that should not be there.
+
+Then we move on to the $\xi$ to $w$ plane transformation.
 The staircase geometry Hamiltonian and the plane Hamiltonian is differed by the Schwartzian term in the transformation rule of the stress tensor, which gives $-\frac{c}{12} \beta $ correction.
@@
 
-We request the referee to reconsider the presented arguments.
+The content of this reply is supplemented in App. C. We request the referee to reconsider the presented arguments.
 }
@@
 
-(By the way, we add the semi-circle manually in the center of Fig.
-5, which is in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper.
+(We add the semi-circle manually in the center of Fig.
+5, which is incidentally in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper.
 So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App.
@@
 5 and Fig.
-6 are \rev{not} strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$.
-To resolve this problem, (and maybe the worry the referee previously had), we notice the following fact
+6 are not strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$.
+To resolve this problem, (which the referee maybe worried about), we notice the following fact
 \begin{itemize}
-\item the non-conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be doing by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
+\item the conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
 \item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
@@
   We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel mappings, as demonstrated in Ref.[25].
-But the conformal interface, the dashed line, will be inside the upper half plane and we don;t know how to calculate its OPE with the stress tensor.
+But the conformal interface, the dashed line, will be inside the upper half plane and we don't know how to calculate its OPE with the stress tensor.
 So in this paper, we only aim to understand the leading order behavior and its relation to the transmission coefficient.
@@
 
-As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line shouldn‚Äôt matter.
-We therefore take the simplest periodic boundary condition for the ease of computation.
-\rev{Do we want to mention this somewhere in the text?}}
+As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line should not matter.
+We therefore take the simplest periodic boundary condition for the ease of computation.}
 
@@
 
-The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s)}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!
-
-We labeled several minus signs to be red to remind future readers to be cautious. \rev{Do we want to keep these highlights?}}
+The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!}
 
@@
 (17).
-Thereafter we uniformly use $t$ towards the end of the main text.
-\rev{This seems not to be the case..
-Do we want to change that?}}
+When referring to the imaginary path integral diagram, we use $\tau$ because that's the scale on Fig.
+5 and Fig.
+6.
+When representing the final result for Loschmidt echo, we do analytic continuation as Eq.
+(17).
+}
 
@@
 
-\reply{The derivation of Eq.(23) is contained in the original App.
-F, which is mainly the evaluation of partition function using a determinant identity with no physical arguments.
-In fact we believe moving App.
-F back to the main text will still make it isolated to the surrounding physical discussion.
-However, in order to improve readability, we have rearranged the appendices and make explicit references in the main text for the derivation.
+\reply{The derivation of Eq.(23) is contained in the original App. F, which is mainly the evaluation of partition function using a determinant identity with no physical arguments.
+
+In order to improve readability, we first setup the calculation in the main text by explicitly spelling out the boundary states and the Hamiltonian in terms of the bosonic operators.
+We end up with an vacuum amplitude with three exponential of bilinears of bosonic operators in between.
+Such an expression can be evaluated using the determinant identity in the appendix.
+And we defer the detailed technical calculation in App.
+A.
+
+In fact, we have rearranged the orders of the appendices for better accessibility.
 
@@
 
+\reply{This is really embarrassing.
+We had 47 citations in our local version of manuscripts but 94 on the submitted.
+We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.
+
+But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }
+
 8) Additionally, there are typos throughout the text that should be corrected (e.g. like "the this"), I suggest the manuscript to be proofread carefully before resubmission.
+
+\reply{We have proofread the paper before the resubmission and (hopefully) corrected those grammatical/spelling errors.}
 

### 2017-10-11 analy_eval.tex
[referee] 2nd round pass

@@
 We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mapping.
-
-\rev{Tian ci: Proofread this part for the conformal map}
 
@@
 We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$.
-Then both of $\xi = 0$ and $1$ can host bcc operators.
-We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $\xi = 1$.
-In order to evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$.
+Then both $\xi = 0$ and $1$ can host bcc operators.
+We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle around $\xi = 1$.
+In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$.
 Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
 \begin{equation}
+\label{eq:partition_fun}
 Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
@@
 
-In App.~\ref{app:lambda_12}, we performed the calculation of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy to the leading order of cylinder width $\beta$.
+The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order.
+Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
+\begin{equation}
+Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
+\end{equation}
+Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
+\begin{equation}
+\begin{aligned}
+F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
+&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
+\end{aligned}
+\end{equation}
+where $E_c$ is the groundstate energy of $H_{ab}$.
+We see that different choice of the boundary conditions only change the term independent of $\beta$.
+Thus in the leading order we can choose any boundary condition.
+The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.
+
+Here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
+We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
+\begin{equation}
+\begin{aligned}
+b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
+\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
+\end{aligned}
+\end{equation}
+for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
+\begin{equation}
+\begin{aligned}
+\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^T, \quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^T\\
+\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^T, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^T .
+\end{aligned}
+\end{equation}
+The boundary state in Eq.~\eqref{eq:bd_state} is then 
+\begin{equation}
+\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
+\begin{pmatrix}
+  \vec{\bar{b}}_1^{\dagger}\\
+  \vec{\bar{b}}_2^{\dagger}
+\end{pmatrix}\Big\}  |0  \rangle ,
+\end{equation}
+where $R_a( \theta ) = -S_a \times \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )$, we have
+\begin{equation}
+|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
+\end{equation}
+
+The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
+\begin{equation}
+\begin{aligned}
+  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
+  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
+  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
+\begin{pmatrix}
+  \vec{{b}_1}\\
+  \vec{{b}_2}
+\end{pmatrix}\\
+ &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
+\end{aligned}
+\end{equation}
+where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
+\begin{equation}
+M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
+\end{equation}
+The partition function is
+\begin{equation}
+\label{eq:Zab-bd}
+\begin{aligned}
+Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
+=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
+&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
+\end{aligned}
+\end{equation}
+
+In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}.
 A na\"ive application of the result however will lead to an apparent contradiction.

### 2017-10-11 num_result.tex
[referee] 2nd round pass

@@
 \end{aligned}\end{eqnarray}
-\rev{ where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}. }
+where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}.
 Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process.
@@
 \includegraphics[width=1\columnwidth]{PDN_fit.pdf}
-\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
+\caption{The decay exponent of Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}.
+The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
 The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.

### 2017-10-13 reply_to_referee.tex
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.

@@
 We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle.
-After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $z = 1$.
-To evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R$.
+After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $\xi = 1$.
+To evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_\xi$.
 This should avoid the problem the referee was worried about.
@@
 \item the conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
-\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
+\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis. 
 \end{itemize}
-since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles.
+Since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles.
 The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct.
@@
 As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line should not matter.
-We therefore take the simplest periodic boundary condition for the ease of computation.}
+We therefore take the simplest periodic boundary condition for the ease of computation.
+
+This line of argument is also included in the main text below Fig. 6. }
 
@@
 
-\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{pi}$. }
+\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{\pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{\pi}$. }
 

### 2017-10-13 analy_eval.tex
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.

@@
 We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo.
-These are the characteristic size of the corner at the tip of the slit.
+These are the characteristic size of the corners at the tip of the slits.
 Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence.
@@
 The two black dots represent possible locations of boundary condition changing (bcc) operators.
-The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries.
-The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
+The dot inside the blue semi-circle has coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries.
+The other dot $\xi = 0$ corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
 To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
@@
 Then both $\xi = 0$ and $1$ can host bcc operators.
-We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle around $\xi = 1$.
+We assume $a = c$ such that the only bcc operator on the real axis is the one enclosed by the blue semi-circle around $\xi = 1$.
 In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$.
@@
 \end{equation}
-
-The height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
+where the height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
 \begin{equation}
@@
 \end{equation}
-The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$. So the width of the cylinder is 
+The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ such that the width of the cylinder is 
 \begin{equation}
@@
 The height of the cylinder is still $\pi$ because of folding.
-In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$.
-The end points of the larger semi-circle are at $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$.
+In the $\xi$ plane, the coordinates of the two end points of the small semi-circle are $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$, while those of the larger semi-circle are $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$.
 Hence the width of the cylinder is
@@
 \includegraphics[width=\columnwidth]{fig_H-tau_fold}
-\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions.
+\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are gluing (open) boundary conditions.
 Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
@@
 Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$.
-In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus.
+In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus.
 The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
@@
 Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
-The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder.
+The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders.
 The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.
 
-Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
+\rev{Check this and the following paragraph} For the rest of this section, we should denote the width of the cylinder as $\beta$.
+After obtaining the partition function for the cylinder, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.
 
-The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order.
-Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
+The actual boundary conditions on the blue lines, which are the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, are not important in the leading order.
+Taking Fig.~\ref{fig:fidel-map} for example, rather than using Eq.~\eqref{eq:partition_fun}, we can alternatively view the right panel as the amplitude between the two blue boundary states $|1\rangle$ and $|2\rangle$
 \begin{equation}
-Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
+Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  , 
 \end{equation}
-Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
+where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$.
+Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontally in this case) to project out only the groundstate $|0_{ab}\rangle $.
+Hence the free energy reads
 \begin{equation}
@@
 where $E_c$ is the groundstate energy of $H_{ab}$.
+We see that different choice of the boundary conditions only change the term independent of $\beta$.
+Thus in the leading order we can choose any boundary condition.
+The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.
+
+%Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
+
+%The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order.
+Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
+%\begin{equation}
+%Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
+%\end{equation}
+%Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
+%\begin{equation}
+%\begin{aligned}
+%F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
+%&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
+%\end{aligned}
+%\end{equation}
+%where $E_c$ is the groundstate energy of $H_{ab}$.
 We see that different choice of the boundary conditions only change the term independent of $\beta$.
@@
 \end{equation}
-The partition function is
+The partition function in Eq.~\eqref{eq:partition_fun} becomes
 \begin{equation}

### 2017-10-13 general_formulation.tex
[referee] 2nd round pass
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.

@@
 The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
-\begin{eqnarray}\begin{aligned}
+\begin{equation}
+\label{eq:di_mode_expansion}
+\begin{aligned}
 \phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
  \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
-\end{aligned}\end{eqnarray}
+\end{aligned}
+\end{equation}
 where we take the following choice of the holomorphic and anti-holomorphic coordinates
@@
 
-So far the deviation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''.
+So far the derivation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''.
 For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$.
-Because the winding mode lives on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$.
+Because the winding modes live on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$.
 App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$.

### 2017-10-13 reply_to_referee.tex
[referee] revise reply letter

--- 2017-10-11 reply_to_referee.tex
@@
 This will introduce a $-\frac{c}{6} \beta $ term that should not be there.
+So in both cases we should compensate $+\frac{c}{6}\beta$.
 
@@
 We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle.
-After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $z = 1$.
-To evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R$.
-This should avoid the problem the referee was worried about.
+After doing the conformal mapping to the center diagram, we end up with a corner centered at $\xi = 1$ with round tip.
+To evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$.
+This should avoid the problem the referee was worrying about.
 
 (We add the semi-circle manually in the center of Fig.
-5, which is incidentally in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper.
+5, which is incidentally in close analogy to the treatment of the truncated cone and corner in the Cardy-Peschel paper.
 So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App.
@@
 \begin{itemize}
-\item the conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
-\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
+\item the conformal map from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map.
+\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the horizontal axis.
 \end{itemize}
@@
 
-\reply{We declared in the text (above Fig. 4) that we will take $L \gg \tau$ in all the echo computation. This keeps the problem with only one length scale.
+\reply{We declare in the text (after Eq. (16)) that we will take $L \gg t$ in all the echo computation. This keeps the problem with only one length scale.
 
-  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel mappings, as demonstrated in Ref.[25].
+  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel maps, as demonstrated in Ref.[25].
 But the conformal interface, the dashed line, will be inside the upper half plane and we don't know how to calculate its OPE with the stress tensor.
@@
 
-In the center part, there are two half-circles around the origin, which supposedly are the images of those on the left. But their radii (which determine the parameter beta) are not given anywhere.
+In the center part, there are two half-circles around the origin, which supposedly are the images of those on the left. But their radii (which determine the parameter $\beta$) are not given anywhere.
 
@@
 
-As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line should not matter.
+As far as the leading order (in $\beta$) is concerned, the boundary conditions imposed on the blue line should not matter.
 We therefore take the simplest periodic boundary condition for the ease of computation.}
@@
 
-\reply{We have rearranged the order of appendixes as request and fix the typo in Eq.(A9), where the $\frac{1}{6}$ should be $-\frac{1}{6}$}
+\reply{We have rearranged the order of appendixes as request.
+Now App.
+A is the calculation for the main analytic results.
+App.
+B/C are supplements to analytic results.
+Other appendices are for the numerical models and calculational details.
+
+We also fix the typo in Eq.(A9), where the $\frac{1}{6}$ should be $-\frac{1}{6}$.}
 
@@
 
-We first deal the three special points $\theta = 0, \frac{\pi}{4}, \frac{\pi}{2}$ and their special relations to the bcc operator ${\rm D} \rightarrow {\rm N}$, and then present an hand wave argument that the quadratic relation should come from the dimension of the vertex operators.
+We first deal the three special points $\theta = 0, \frac{\pi}{4}, \frac{\pi}{2}$ and their special relations to the bcc operator ${\rm D} \rightarrow {\rm N}$, and then present a hand-waving argument that the quadratic relation should come from the dimension of the vertex operators.
 
@@
 
-Since the notation is shortened, we don'Äôt let them occupy a single equation and instead put them inside a sentence.
-We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase in Eq.(XX)Äù, and the time it saves to look up.
+Since the notation is shortened, we don't let them occupy a single equation and instead put them inside a sentence.
+We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase ``in Eq.(XX)'', and the time it saves to look up.
 }
@@
 \reply{This is really embarrassing.
-We had 47 citations in our local version of manuscripts but 94 on the submitted.
+We had 47 citations in our local version of manuscripts but 94 on the submission.
 We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.
@@
 11 corresponds to the right piece of Fig.
-6, but is rotated by 90¬∞.
+6, but is rotated by 90Â°.
 This is confusing, in particular since the corresponding Fig.
@@
 It is taken to be a and changing it will influence the result even in the large L limit.
-So we did noÄôt neglect cÄ but taking it to be aÄô.
+So we did no€™t neglect c€ but taking it to be a€™.
 We also take a simpler notation for this case after Eq.
@@
 But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence.
-The difference $1/8$õ is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c).
+The difference $1/8$› is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c).
 We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

### 2017-10-13 analy_eval.tex
[referee] revise reply letter

--- 2017-10-11 analy_eval.tex
@@
 This can be resolved by the following observation.
-There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}.
+There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}.
 Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$.
@@
 Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$.
-Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
-The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder.
+Since conformal transformation preserves the cross ratio, the same expression can be used on the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, provided we use the intersection points there to calculate the cross ratio.
+The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently uses the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder.
 The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.
 
-Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
+Since the fidelity and Loschmidt echo are both square of the amplitudes, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
 
@@
 \end{equation}
-Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
+Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution will project out only the groundstate $|0_{ab}\rangle $. Hence the free energy is
 \begin{equation}
@@
 where $E_c$ is the groundstate energy of $H_{ab}$.
-We see that different choice of the boundary conditions only change the term independent of $\beta$.
+We see that different choices of the boundary conditions only change the term independent of $\beta$.
 Thus in the leading order we can choose any boundary condition.
@@
 
-Here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
+With these in mind, here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
 We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
@@
 \begin{aligned}
-\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^T, \quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^T\\
-\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^T, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^T .
+\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^\top, \qquad \,\,\quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^\top\\
+\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^\top, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^\top.
 \end{aligned}
@@
 \end{equation}
-where $R_a( \theta ) = -S_a \times \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )$, we have
+where $R_a( \theta ) = -S_a \otimes \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )^\top$, we have
 \begin{equation}
@@
 In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}.
+This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions.
 A na\"ive application of the result however will lead to an apparent contradiction.

### 2017-10-13 disc.tex
[referee] revise reply letter

@@
 \item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$.
-The chain is still disconnected after the change of the boundary condition.
-We can thus view the problem of changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D.
+The chain is still disconnected after the change of the boundary conditions.
+We can thus view the problem as changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D.
 The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimension is $\Delta = \frac{1}{16}$.
-From this we can get the exponent to be $\frac{1}{2}$
+From this we can get the exponent to be $\frac{1}{2}$,
 \begin{equation}
@@
 Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means the $\Sigma$ matrix is closer to the original, thus a smaller perturbation and vise versa.
-Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) of the result.
+Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) in the figures.
 

### 2017-10-13 reply_to_referee.tex

@@
 \end{itemize}
-since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles.
+Since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles.
 The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct.

### 2017-10-13 analy_eval.tex

--- 2017-10-13 analy_eval.tex
@@
 where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$.
-Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontally in this case) to project out only the groundstate $|0_{ab}\rangle $.
-Hence the free energy reads
+Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontal in this case) to project out only the groundstate $|0_{ab}\rangle $.
+Hence the free energy is
 \begin{equation}
@@
 
-%Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.
-
-%The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order.
-Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
-%\begin{equation}
-%Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
-%\end{equation}
-%Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
-%\begin{equation}
-%\begin{aligned}
-%F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
-%&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
-%\end{aligned}
-%\end{equation}
-%where $E_c$ is the groundstate energy of $H_{ab}$.
-We see that different choice of the boundary conditions only change the term independent of $\beta$.
-Thus in the leading order we can choose any boundary condition.
-The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.
-
-Here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
+With these in mind, here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
 We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through

### 2017-10-13 intro.tex

@@
 
-In this paper, we generalize these ideas to an interface that interpolate between the total reflective and complete transparent ones.
+In this paper, we generalize these ideas to an interface that interpolates between the total reflective and complete transparent ones.
 This kind of interface can have many realizations.
-They can be produced by connecting two different bosonic CFTs in the ``cut-and-join" protocol.
+As discussed in Ref.~\onlinecite{bachas_permeable_2002}, one can connect two different bosonic CFTs in the ``cut-and-join" protocol, and the interface is a domain wall between two free compact boson theories with different compactification radii.
+Such permeable interface can also be implemented by non-compact free boson/free fermion on a lattice with a fine-tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies).
+%They can be produced by connecting two different bosonic CFTs in the ``cut-and-join" protocol.
 As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface is a domain wall between two free compact boson theories with different compactification radii.

### 2017-10-14 F_correction.tex
[review] Some minor changes. The only major changes are highlighted, which is around Eq.26.
[referee] version resubmitted to prb.

@@
 \begin{equation}
-F = - \frac{c}{6} \left( \int_M  K(x) d^2x + \int_{\partial M} k_g ds \right)  \ln L 
+F = - \frac{c}{6} \left( \int_M  K(x) d^2x + \int_{\partial M} k_g ds \right)  \ln L , 
 \end{equation}
@@
 \begin{equation}
-F( {\rm disk}  ) = - \frac{c}{6}  \left( \int_{\partial M} k_g ds \right)  \ln \frac{r_2}{a}  = - \frac{c}{6}  \ln \frac{r_2}{a}
+F( {\rm disk}  ) = - \frac{c}{6}  \left( \int_{\partial M} k_g ds \right)  \ln \frac{r_2}{a}  = - \frac{c}{6}  \ln \frac{r_2}{a} , 
 \end{equation}
@@
 
-One can then interpret the annulus free energy as an additive contribution from its outer and inner surfaces as
+One can then interpret the annulus free energy as additive contributions from its outer and inner surfaces
 \begin{equation}
@@
 
-Therefore using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
+Therefore in both cases we should compensate $\frac{c}{6} \ln \frac{r_2}{a}$. Using the cylinder parameters in App.~\ref{app:lambda_12}, the $\xi$ plane and $z$ plane free energy are related through
 \begin{equation}
@@
 % staircase geometry correction
-The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction .
+The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction.
 The traditional radial quantization however has radial direction to be the time.
-One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988}
+One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988} of the conformal transform
 \begin{equation}

### 2017-10-14 analy_eval.tex
[referee] version resubmitted to prb.

@@
 These are the characteristic size of the corners at the tip of the slits.
-Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence.
+Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and drop those scales.
 The introduction of regulators is also physically sensible when considering the lattice realization of the systems.
 
-We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mapping.
+We thus add small semi-circles around the points where the bcc operators reside, and then apply a series of conformal mappings.
 
-For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
+For the fidelity case, the regulators as well as the conformal maps are depicted in Fig.~\ref{fig:fidel-map}. 
 \begin{figure}[h]
@@
 The other dot $\xi = 0$ corresponds to the connection between $a$ and $c$ boundaries at $- \infty$.
-To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
+To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
 \label{fig:fidel-map}
@@
 We assume $a = c$ such that the only bcc operator on the real axis is the one enclosed by the blue semi-circle around $\xi = 1$.
-In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$.
-Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
+In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to a cylinder of height $\pi$ on the right by $w = \ln ( \xi- 1)$.
+Finally the cylinder diagram can be viewed as an imaginary time path integral amplitude between the boundary states $b$ and $a$
 \begin{equation}
@@
 \end{equation}
-where the height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
+The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
 \begin{equation}
@@
 \end{equation}
-The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ such that the width of the cylinder is 
+The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$ and so the width of the cylinder is 
 \begin{equation}
@@
 From $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case.
-With one more conformal mapping $w = \ln \xi$, the diagram becomes the cylinder partition function between the two boundary states.
+With one more conformal mapping $w = \ln \xi$, the diagram again becomes the cylinder partition function between the two boundary states.
 
-The height of the cylinder is still $\pi$ because of folding.
+The height of the cylinder is still $\pi$.
 In the $\xi$ plane, the coordinates of the two end points of the small semi-circle are $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$, while those of the larger semi-circle are $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$.
@@
 \includegraphics[width=\columnwidth]{fig_H-tau_fold}
-\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are gluing (open) boundary conditions.
+\caption{The dashed (solid) lines are gluing (completely reflective) boundary conditions.
 Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state.
+Left: Diagram of the Loschmidt echo that reduces to a partition function with imaginary time in the horizontal direction.
 The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice).
@@
 Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}.
-The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders.
-The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.
+The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently use the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders.
+The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, so will not affect the fidelity and echo exponents.
 
-\rev{Check this and the following paragraph} For the rest of this section, we should denote the width of the cylinder as $\beta$.
-After obtaining the partition function for the cylinder, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.
+For the rest of this section, we should denote the width of the cylinder as $\beta$.
+After obtaining the partition function on it, we should set $\beta = 2 \ln L$ or $ 4 \ln \tau$ because the fidelity and Loschmidt echo are both square of the amplitudes.
 
@@
 where $H_{ab}$ is the Hamiltonian with boundary condition $a$ and $b$.
-Since $\beta$ is taken to be large, we expect that the imaginary time evolution (which is horizontal in this case) to project out only the groundstate $|0_{ab}\rangle $.
+Since $\beta$ is taken to be large, we expect the imaginary time evolution (which is horizontal in this case) to project out only the groundstate $|0_{ab}\rangle $.
 Hence the free energy is
@@
 \end{equation}
-where $E_c$ is the groundstate energy of $H_{ab}$.
+where $E_c$ is the groundstate/Casimir energy of $H_{ab}$.
 We see that different choices of the boundary conditions only change the term independent of $\beta$.
-Thus in the leading order we can choose any boundary condition.
+Thus in the leading order we can choose any boundary conditions.
 The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.
 
-With these in mind, here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}.
+With these simplifications, we now set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$.
 We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
@@
 \begin{equation}
+\label{eq:bd_state_matrix}
 |a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
 \end{equation}
+The matrix notation here should be understood as a bilinear expression.
+For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ actually means $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
 
@@
   H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
-  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
+  &= \frac{4\pi}{\beta}\sum_{\substack{n > 0\\ i=1,2} }  n (b^i_n)^{\dagger} b^i_n \\
   &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
@@
 where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$.
-A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.
+A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.
 

### 2017-10-14 bd_notation.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.
[referee] version resubmitted to prb.

@@
 We use chemical reaction style to represent the change of boundary conditions.
-Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench.
-The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface.
+Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status of the two ends of the chain before and after the quench.
+The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on $ab$ interface.
 The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench.
@@
 \begin{equation}
+\label{eq:Full_notation_rand()}
 S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
 \end{equation}
-\rev{In most cases of the following, we will consider taking $a = c$ to remove the bcc operator from $a$ to $c$ at infinity. And we will use the shorthand notation
+In most cases of the following, we will consider taking $a = c$ to remove the bcc operator from $a$ to $c$ at infinity. And we will use the shorthand notation
 \begin{equation}
@@
 \end{equation}
-to remind ourselves that we are isolating the boundary condition change only on joint of the two chains. 
-}
+to remind ourselves that we are isolating the boundary condition change only on the joint of the two chains.
 
@@
 \end{equation}
-Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e.
+Another interesting case is to take $a$ or $c$ to be a completely transmitting interface, i.e.
 $S_2( \frac{\pi}{4} )$.
-This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.
+This $S$-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.
 

### 2017-10-14 compact_boson.tex
[referee] version resubmitted to prb.

@@
 \end{equation}
-At the boundary $x = 0$, $\bar{z}=z^{-1}$, therefore we have
+At the boundary $x = 0$, $\bar{z}=z^{-1}$, we have
 \begin{equation}
@@
 \begin{equation}
-  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
+  a_0^i + S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* ),
 \end{equation}
@@
 \end{aligned}\end{equation}
-With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).
+For boundary states, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).
 

### 2017-10-14 conclusion.tex
[referee] version resubmitted to prb.

--- 2017-09-22 conclusion.tex
@@
 We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface.
-The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$.
+The conventional `DD', `NN' boundary conditions are among the special choices of $\theta$ in $S_1$, and `DN' and P are among the special choices of $S_2$.
 Generic value of $\theta$ then interpolates between those conventional boundary conditions.
@@
 
-The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
+The dynamical behavior of the Loschmidt echo reflects the change of the conformal interfaces during the process described in Eq.~\eqref{eq:S_i_S_j}.
 %, which we denote as
@@
 %\end{equation}
-Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces.
-Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$.
-On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).
+Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates the interfaces.
+Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary conditions is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$.
+On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same type of $S$ matrices ($i = j$).
 
-These two features were tested in three typical processes in the numerical calculation of the harmonic chains.
+These two features are tested in three typical processes in the numerical calculation of the harmonic chains.
 After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error.
@@
 
-We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on quantum wires systems.
+We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on the quantum wire systems.
 

### 2017-10-14 def_fidel_echo.tex
[referee] version resubmitted to prb.

@@
 
-Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
+Fidelity is the square of the overlap of the groundstates of the two Hamiltonians, 
 \begin{equation}
@@
 The solid dot represents boundary condition changing (bcc) operator.
-Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$ are possible choices of boundary conditions.)}
+Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$) are possible choices of boundary conditions.}
 \label{fig:fidel}
@@
 The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
-One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
+One of them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
 \begin{equation}
@@
 Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.
-After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence.
-For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}).
-The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).
+After obtaining the free energy in imaginary time, we can analytically continue back to real time to get the $t$ dependence.
+For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scale in the echo calculation (Fig.~\ref{fig:H-tau_fold}).
+The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see the treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).
 
@@
 They sandwich the evolution of the connected chains.
-In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).
-See the discussion in main text.}
+In the folding picture at the right, $a,b,c$ represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).}
 \label{fig:echo}
@@
 at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity.
-According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in the fidelity and $\ln \tau$ in the Loschmidt echo.
 One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
-In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or integration of the Ward identity.
+In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or the integration version of the Ward identity.
 If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
@@
 With the presence of the conformal interface, the tip of the slit is no longer a corner singularity\cite{cardy_finite-size_1988} .
-Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram.
-From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator.
-The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
+Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both the fidelity and echo diagrams.
+From the boundary CFT point of view, the change of boundary conditions can be regarded as inserting a bcc operator.
+The diagrams for the fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy's leading logarithmic term extracts their scaling dimensions.
 

### 2017-10-14 disc.tex
[referee] version resubmitted to prb.

@@
 
-In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the replacement recipe $ \ln L \rightarrow 2 \ln \tau$.
-The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips.
+In the computations we have done, the results of the fidelity can be converted to that of the Loschmidt echo by the replacement recipe $ \ln L \rightarrow 2 \ln \tau$.
+The numerical factor of $2$ comes from the fact that the Loschmidt echo has two slit tips.
 Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces.
-Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.
+The computation of the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.
 
 % analytic results type 1 -> type 2, c/4; 
-In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process $S_i( \theta_1 ) \rightarrow S_j( \theta_2 )$ {\iffalse {\color{red}described in Eq.~\eqref{eq:S_i_S_j}}\fi} (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$).
+In Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process $S_i( \theta_1 ) \rightarrow S_j( \theta_2 )$ {\iffalse {\color{red}described in Eq.~\eqref{eq:S_i_S_j}}\fi} (assuming the far end boundary condition $c$ is the same as prior-quench condition $a$).
 
@@
 $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles.
-The two types of conformal interface do not talk to each other because they impose on different fields.
-If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$.
-In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$.
+The two types of conformal interface do not talk to each other because they are imposed on different fields.
+If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$.
+In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group that can not be connected even by taking singular values of $\lambda$.
 It is then reasonable to find a universal echo between them.
-The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
+The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of the completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.
 
@@
 The chain is still disconnected after the change of the boundary conditions.
-We can thus view the problem as changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D.
-The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimension is $\Delta = \frac{1}{16}$.
-From this we can get the exponent to be $\frac{1}{2}$,
+We can thus view the problem as changing the boundary conditions for two independent chains in the left panel of Fig.~\ref{fig:echo}, one from D to N and the other from N to D.
+The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimensions are both $\Delta = \frac{1}{16}$.
+From this,
 \begin{equation}
@@
 \end{equation}
-which agrees with our results. 
+we can get the exponent to be $\frac{1}{2}$, which agrees with Fig.~\ref{fig:DDNN}. 
 \item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$.
-The exponent $\frac{3}{8}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
+The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
 \end{itemize}
-In general, the result gives the full spectrum of operator dimensions in the ${\rm DN}$ to $\lambda $ transition.
-In the bosonic theory we consider, the primary fields are vertex operators, which is exponential of the field $\exp( \nu \phi )$.
-Depending on the convention, the dimension of the vertex operator is a numerical constant times $\frac{\nu^2}{8\pi}$.
-So if $\nu$ linearly depend on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points we work out above.
-In a rational boson theory, the number of primary fields is finite.
+In general, the result gives the full spectrum of operator dimensions in the ${\rm DN} \rightarrow \lambda $ transition.
+In the bosonic CFT we consider, the primary fields are the vertex operators $\exp( \nu \phi )$.
+Depending on the convention, its dimension is a numerical constant times $\frac{\nu^2}{8\pi}$.
+So if $\nu$ depends linearly on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points above.
+In a rational CFT theory, the number of primary fields is finite.
 It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.
@@
 On the other hand, in our lattice boson model, $\theta$ parameterizes the bond interaction between the boundary sites of the chains.
-Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means the $\Sigma$ matrix is closer to the original, thus a smaller perturbation and vise versa.
+Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means smaller change of the bond interaction matrix $\Sigma$ thus a smaller perturbation and vise versa.
 Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) in the figures.
@@
 
-This set of boundary conditions can be realized by connecting two compact bosons.
+This set of the boundary conditions can be realized by connecting two compact bosons.
 There are already numerous theoretical and experimental works on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}.
 For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions.
-The interface studied in this paper is a generalization which (in the folding picture) twists the two independent bosons (two left modes plus two right modes) on the two sides.
-An X-ray edge singularity experiment in a quantum wire system, which uses ions to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.
+The interface studied in this paper is a generalization which (in the folding picture) twists the two independent bosons (two left modes plus two right modes) on their connecting ends.
+An X-ray edge singularity experiment in a quantum wire system, which uses ions to switch on and off the boson interfaces should be plausible to detect the exponents found in this paper.
 

### 2017-10-14 free_boson_lattice.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article
[referee] version resubmitted to prb.

@@
 
-We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
+We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ at lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
 \begin{equation}
@@
 H &= \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2 \\
-& + \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
+\quad & + \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
 \begin{bmatrix}
@@
 \phi_1 
-\end{pmatrix}
+\end{pmatrix},
 \end{aligned}
@@
 We performed the standard scattering analysis in App.~\ref{app:interface_free_boson}.
-For mode with momentum $k$, the only possible scale invariant S-matrix is
+For mode with momentum $k$, the only possible scale invariant $S$-matrix is
 \begin{equation}
-S = - e^{ika} \Sigma
+S = - e^{ika} \Sigma,
 \end{equation}
@@
 
-The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both Loschmidt echo and fidelity.
+The lattice model in Eq.~\eqref{eq:lattice_H} with bond interaction defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both the Loschmidt echo and the fidelity.
 

### 2017-10-14 general_formulation.tex
[referee] version resubmitted to prb.

@@
-The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous.
-An equivalent perspective (and will be used later) is to fold one of the theories on top of the other.
-The interface located on the boundary of the tensor theory becomes impenetrable, and momentum flow vanishes there.
-This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}.
-In the boson theory we are interested in, the tensor theory has $c = 2$.
+The general constraint on an interface is the continuity of the momentum flow across it.
+If we fold one side of the system on top of the other, then the resulting interface located on the boundary of the tensor theory (the crease of the folding) becomes impenetrable and the momentum flow should vanish there.
+This interface is naturally a conformal invariant boundary state\cite{cardy_boundary_2004,cardy_conformal_1984}.
+The interfaces in this paper are boundary states living in the $c = 2$ boundary CFT.
 
-Although general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states.
+Although the general classification of the boundary states is still an open question\cite{affleck_quantum_2001}, there are many successful attempts to construct a subset of those bosonic boundary states.
 For example, one may use the current operator rather than the Virasoro generator to solve the zero-momentum flow condition.
 This idea dates to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
-Additionally, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
+Additionally, the fusion algebra has also been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
 
@@
 
-Assume two free boson fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. The interface located at $x = 0$ is characterized by the ``gluing condition"
+Assuming two free boson fields $\phi^1$ and $\phi^2$ living on the left and right half planes respectively, the interface located at $x = 0$ is characterized by the ``gluing condition"
 \begin{equation}\begin{aligned}
@@
 \partial_x\phi^2
-\end{pmatrix},
+\end{pmatrix}.
 \end{aligned}\end{equation}
-where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
-As argued, the momentum components of the stress tensor is continuous across the interface.
+The derivatives here should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$.
+As argued before, the momentum components of the stress tensor is continuous across the interface.
 As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
@@
 \item $\theta=0,\pm \frac{\pi}{2}$.
-In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other.
-The interface reduces to individual boundary conditions for the boson on the left and right half planes: They are combination of Dirichlet and Neumann boundary conditions.
+In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot penetrate.
+The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
 For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left.
@@
 This mode is one of the scattering modes that leave the interface.
-On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain.
-We therefore establish the scattering relation
+On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domains.
+We can therefore establish the scattering relation
 \begin{equation}\begin{aligned}
@@
 \partial_+\phi^2
-\end{pmatrix},
+\end{pmatrix}.
 \end{aligned}\end{equation}
@@
 The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.
-The arrow represents the incoming and outgoing particle scattered by the interface.}
+The arrow represents the incoming and outgoing particles scattered by the interface.}
 \label{fig:folding_pic}
@@
 We now work in the folding picture as shown in Fig.~\ref{fig:folding_pic}.
-The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal boundary state.
+The boundary at $x=0$ becomes impenetrable for the folded system, and the resulting tensor theory admits a conformal invariant boundary state.
 The folding sends $\phi^2(x)$ to $\phi^2(-x)$ and hence the gluing condition becomes
@@
 \end{equation}
-where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.
+where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}.
+The calculation for the case $M=M_2(\theta)$ is completely analogous and we just have a replacement of $S_1( \theta ) $ by $S_2( \theta )$ in Eq.~\eqref{eq:def_S}.
 
@@
 
-So far the derivation is only for the non-compact bosons, where the interface is imposed by ``gluing conditions''.
+So far the derivation is only for the non-compact bosons, where the interface is determined by the ``gluing conditions''.
 For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$.
@@
 \end{equation}
-for coprime integer $n_1$ and $n_2$. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the CFTs on both sides.
+for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on two sides.
+This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by universal parameters of the CFTs on both sides.
 

### 2017-10-14 gnd_dn_lambda.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article
[referee] 2nd round pass
[referee] version resubmitted to prb.

@@
 \caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions.
-The width of the strip is $\pi$ due to folding.
-We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle.
+We unfold the cylinder and the new stripe have N and D boundary conditions on the top and bottom plus a $\lambda$ junction in the middle.
+The length $L$ here is the height of the unfolded cylinder $2\pi$.
 }
@@
 
-The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in the mode expansion, we thus have the 
+The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as an orthonormal basis in the mode expansion, we thus have
 \begin{equation}
@@
 The Casimir energy is the vacuum energy brought up by the finite size of the setup.
-From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and use $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
+From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and using $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
 \begin{equation}
@@
 E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\
-&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
-&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
+&= \frac{\pi}{2L} \Bigg( \sum_{n\ge 0 }  ( n + x ) + \sum_{n< 0 }  ( -n - x )  \\
+&\quad \quad + \sum_{n \le 0}  (- n + x ) + \sum_{n > 0} ( n- x )  \Bigg) \\
+&= \frac{\pi}{2L} \left( 2\sum_{n\ge 0 }  ( n + x ) + 2\sum_{n > 0} ( n- x )  \right).
+\end{aligned}
+\end{equation}
+We use Hurwitz zeta function
+\begin{equation}
+\zeta_{\rm H}(s,x) = \sum_{n=0}^\infty\frac{1}{(n+x)^s}
+\end{equation}
+to regularize the sum, 
+\begin{equation}
+\begin{aligned}
+E_c &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  -  (-x)^{-s} \Big]\Big|_{s = -1} \\
+&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, -x ) +  x \right] \\
 &= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
@@
 \end{equation}
-where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy in the large $\beta$ limit is
+where in the last line we use $L = 2\pi$ for the unfolded geometry.
+
+Thus the free energy in the large $\beta$ limit is
 \begin{equation}

### 2017-10-14 intro.tex
[referee] version resubmitted to prb.

--- 2017-10-04 intro.tex
@@
 The X-ray absorption rate will then have a power singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
-There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
+There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in the spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
 
@@
 Various quantities can be used to detect the information in the quench process.
-For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem A, when both A and B are identical critical systems.
-The authors ascribe such increase to the proliferation and propagation of quasi-particle excitations emitted at the joint.
+For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of the entanglement entropy in subsystem A, when both A and B are identical critical systems.
+The authors ascribe such increase to the proliferation and propagation of the quasi-particle excitations emitted at the joint.
 Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase.
@@
 
-In this paper, we generalize these ideas to an interface that interpolate between the total reflective and complete transparent ones.
+In this paper, we generalize these ideas to an interface that interpolates between the totally reflective and complete transparent ones.
 This kind of interface can have many realizations.
-They can be produced by connecting two different bosonic CFTs in the ``cut-and-join" protocol.
-As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface is a domain wall between two free compact boson theories with different compactification radii.
-It can also be implemented by non-compact free boson/free fermion on the lattice with a finely tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies).
+As discussed in Ref.~\onlinecite{bachas_permeable_2002}, one can connect two different bosonic CFTs in the ``cut-and-join" protocol, and the interface is a domain wall between two free compact boson theories with different compactification radii.
+Such permeable interface can also be implemented by non-compact free boson/fermion on a lattice with a fine-tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies).
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, while for free lattice boson it is controlled by the ratio of masses.
+In the case of compact boson, $\lambda$ is controlled by the ratio of the compactification radii, while for the free lattice boson it is controlled by the ratio of masses.
 We expect it to be tunable in a realistic experimental setting.
@@
 We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
-We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transition coefficients.
+We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transmission coefficients.
 Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
@@
 This paper includes several appendices for technical details.
-In App.~\ref{app:lambda_12}, we present the leading order analytical calculation of the free energy for the above-mentioned interfaces.
+In App.~\ref{app:lambda_12}, we present the leading order analytical calculation of the free energy for the setups in Sec.~\ref{sec_sub:analy_eval}.
 In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example.
@@
 Up to this point, we work exclusively with the oscillator modes of the free bosons.
-In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order.
+In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of the compactified bosons will \emph{not} contribute to the free energy at the leading order.
 Therefore, the results remain valid in the physical situation of connecting two compactified bosons of different radii.

### 2017-10-14 num_result.tex
[referee] version resubmitted to prb.

@@
 We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results.
-Our numerical evaluations is based on a boson Bogoliubov transformation and the explicit form of the groundstates.
+Our numerical calculations are based on a boson Bogoliubov transformation and the explicit form of the groundstates.
 The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details.
@@
 %\end{equation}
-in which the joining boundary condition is determined by $S_1(\theta)$.
+in which the boundary condition after joining is determined by $S_1(\theta)$.
 We worked with a system containing $35000$ sites.
 A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
-We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
+We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process (see the full notation in Eq.~\eqref{eq:Full_notation_rand()})
 \begin{eqnarray}\begin{aligned}
 \label{eq:approx_DNDN}
-S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
+S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta).
 \end{aligned}\end{eqnarray}
-where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}.
 Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process.
 This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}.
-The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
+The inset shows the $\theta$-dependence of the power law decay, and the corresponding exponents follow the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}.
 %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.
@@
 \includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
-    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{DN} \rightarrow \lambda$ {\iffalse in Eq.~\eqref{eq:DNDN}\fi}.
-The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
+    \caption{The slope of the free energy for (a) the Loschmidt echo and (b) the bipartite fidelity of the process $\text{DN} \rightarrow \lambda$.
+{\iffalse in Eq.~\eqref{eq:DNDN}\fi} The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}.
 The numerical value of exponents follow a quadratic relation as predicted.
 There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text.
-Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$.
+Inset in (a): From the top to bottom, we show the power law decay of the Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$.
 Finite size effect does not emerge before $t=10^{4}$.
-We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
+We use the same curve fitting method as described in Fig.~\ref{fig:DDDD}.}
       \label{fig:DDNN}
@@
 \end{equation}
-where $\delta\theta=0.003\pi$. The $\theta$ dependent exponents are now symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.
+where $\delta\theta=0.003\pi$. The $\theta$ dependent exponents are now symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance with Eq.~\eqref{eq:periodic-case}.
 
@@
     \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
-    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{P} \rightarrow \lambda${\iffalse in Eq.~\eqref{eq:PP}\fi}.
-The parameters are the same as those in Fig.~\ref{fig:DDNN}.
+    \caption{The decay exponent of (a) the Loschmidt echo and (b) the bipartite fidelity of the process $\text{P} \rightarrow \lambda$.{\iffalse in Eq.~\eqref{eq:PP}\fi} The parameters are the same as those in Fig.~\ref{fig:DDNN}.
 The plot is symmetric with respect to $\theta=0.25\pi$ as predicted.
@@
 \includegraphics[width=1\columnwidth]{PDN_fit.pdf}
-\caption{The decay exponent of Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}.
+\caption{The decay exponent of the Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}.
 The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve.
-The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.
-}
+The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.}
 \label{fig:PDN_fit}

### 2017-10-14 pf_of_id.tex
[referee] version resubmitted to prb.

@@
 \end{equation}
-where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators.
-The matrix notation here should be understand as a bilinear expression.
-For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.
+where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators. The matrix notation here should be understood as a bilinear expression as explained below Eq.~\eqref{eq:bd_state_matrix}.
 
@@
 \end{equation}
-where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$. Using the identity we have just proved
+where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$.
+
+One can use the identity in Eq.~\eqref{eq:first_id_app_pf_of_id} to reduce $Z_{ab}$ to 
 \begin{equation}
-Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle ,
+Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle, 
 \end{equation}
-a direct application of the MacMahon master theorem
+then a direct application of the MacMahon master theorem
 \begin{equation}

### 2017-10-14 reply_1.tex
[referee] version resubmitted to prb.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{{./}}

\newcommand{\cf}{\textit{cf.} }
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }
\newcommand{\rev}[1]{{\color{red}#1}}

\newcommand{\up}{\mathord{\uparrow}}
\newcommand{\dn}{\mathord{\downarrow}}
\newcommand{\I}{\mathbb{I}}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\qed}[0]{$\blacksquare$}

\newcommand{\reply}[1]{{\color{black}#1}}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

% \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
% \usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}

\begin{document}
\large

{\bf Reply to the First Referee -- BF13677/Zhou}

\color{blue}

The authors investigate a quench problem where two critical bosonic chains are initially separated and then coupled by a conformal defect. This generalizes earlier treatments, where the chains were simply connected. They determine the fidelity (the negative logarithm of the overlap of the initial and the final ground state for chain lengths L) and the Loschmidt echo (the negative logarithmic overlap of the evolved state after some time t with the initial ground state). Since these overlaps decay as power laws, the logarithms vary as lnL and lnt, respectively. For a simple connection of the chains, the prefactors are known to be 1/8 and 1/4, respectively. For a defect, the authors find, that they can vary continuously with the defect transmission, depending on the boundary conditions at the chain ends and at the defect. This is derived analytically via a path- integral picture of the two quantities and conformal mappings. It is also verified by numerical calculations on oscillator chains, based on explicit expressions of the ground states in terms of boson operators from which the overlaps can be obtained as determinants.

Given that such varying exponents have a long history and were found also for the entanglement entropy in chains with defects, this is an interesting topic and the results are worth publishing. However, there are a couple of points to be clarified or changed.

\reply{We first acknowledge the effort of this respectful referee to read our manuscript thoroughly and provide constructive comments. We will address the issues below.}

(1) In order to obtain the correct result for the known case, the authors have to add a constant beta/12 in (21). However, the derivation in Appendix A is not right. The relation (A5) between the Hamiltonians in the staircase and in the strip differs by a sign from the one given in Ref. [32]. I think that the argument must be different. Usually, the universal terms in free energies are determined via appropriate non-conformal transformations which bring in the energy- momentum tensor. In this context one wonders about additional constants coming from the starting states in the path integral representation.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{/images/fig_H-tau_fold.pdf}
\caption{Conformal transformation from the slit to cylinder.}
\label{fig:H-tau_fold}
\end{figure}

\reply{
We thank the referee for pointing out this sign error, in fact we used the $w \rightarrow \xi \rightarrow z$ order in the calculation as opposed to the $z \rightarrow \xi \rightarrow w$ order of the conformal transformation in the figure. We have fixed them.

Nevertheless we hold our opinion of using these two corrections to account for the missing $\frac{1}{12}\beta$. Let us reiterate our arguments.

The first correction comes from mapping the slit diagram to the annulus (in Fig. 6).  Before doing this conformal transformation, the short distance regulator is small on the $z$ plane. Hence the contribution of the free energy coming from introducing the two blue lines are small. However, after the transformation, we implicitly choose another regulator which is small on the $\xi$ plane. But by the change of this short distance cutoff, the $\xi$ plane erroneously contribute a $- \frac{c}{6} \ln \frac{r_2}{r_1}$ term from the outer surface. The compensation $+\frac{c}{6} \ln \frac{r_2}{r_1} = \frac{c}{6}\beta$ is the correction we are talking about.

The is the lesson we learned from the Cardy-Peschel paper, where there are two explicit examples of computing the free energies of a corner and a cone. Both objects should be regarded as infinitely extended without boundaries at certain radii. The authors computed the correct results by conformally mapping the geometry to whole plane (or upper half plane) and contrasted with the calculation of the truncated corner and cone with both short and long distance regulators. They found that the discrepancies of the truncated cone and corner w.r.t. to the correct results come from the outer boundary contribution. By subtracting this otherwise nonexistent contribution using their proposed geodesic curvature formula, they are able to recover the correct result. We believe that the mapping from the $z$ to $\xi$ plane result in the same situation here.

We also change Fig 5, where in the left panel there is no vertical line IR regulator. So after doing the $\exp$ conformal transformation, the center diagram should be the upper half plane minus the small circle around $\xi = 1$. This is also an extended object, much the same way as the cone and corner in the Cardy-Peschel paper. To evaluate this extended diagram, we manually add another big semi-circle centered at $\xi = 1$ with radius $R_{\xi } \gg 1$. This will introduce a $-\frac{c}{6} \beta $ term that should not be there. So in both cases we should compensate $+\frac{c}{6}\beta$.

Then we move on to the $\xi$ to $w$ plane transformation. The staircase geometry Hamiltonian and the plane Hamiltonian is differed by the Schwartzian term in the transformation rule of the stress tensor, which gives $-\frac{c}{12} \beta $ correction. By gathering the two terms, we do get the desired $\frac{c}{12}\beta$ correction.

The content of this reply is supplemented in App. C. We request the referee to reconsider the presented arguments.
}

(2) I also find the whole presentation of the mapping unsatisfactory. In part, this has to with the fact that no lengths are indicated in the figures.

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a corner centered at $\xi = 1$ with round tip. To evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$. This should avoid the problem the referee was worrying about.

(We add the semi-circle manually in the center of Fig. 5, which is incidentally in close analogy to the treatment of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are not strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (which the referee maybe worried about), we notice the following fact
\begin{itemize}
\item the conformal map from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the horizontal axis.
\end{itemize}
Since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

This line of argument is also included in the main text below Fig. 6. 
}

For the Loschmidt echo, the starting point is again a strip of width L, as shown in Fig. 4. However, in the left part of Fig. 6 this width no longer appears. There is only a small remark in the text that $L \gg \tau$. But L is of significance, for finite L the ratio t/L enters, and in Ref. [25] this case could actually be treated.

\reply{We declare in the text (after Eq. (16)) that we will take $L \gg t$ in all the echo computation. This keeps the problem with only one length scale.

  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel maps, as demonstrated in Ref.[25]. But the conformal interface, the dashed line, will be inside the upper half plane and we don't know how to calculate its OPE with the stress tensor. So in this paper, we only aim to understand the leading order behavior and its relation to the transmission coefficient. }

In the center part, there are two half-circles around the origin, which supposedly are the images of those on the left. But their radii (which determine the parameter $\beta$) are not given anywhere.

\reply{The radii for the left and center parts are indicated in the caption, and also discussed in the main text.}

Finally, the identification of the two semi-circles is physically quite strange. One wonders if it is really necessary for the calculations or the reasoning.

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in $\beta$) is concerned, the boundary conditions imposed on the blue line should not matter. We therefore take the simplest periodic boundary condition for the ease of computation.}

(3) The calculation of the vacuum energy in equ.(E6) is not quite clear. Since the original expression diverges, a word about regularization would be in order. In the conversion of the sums into zeta functions (what does the index H mean ?) it seems to me that the n=0 terms are not handled correctly. The second function must be zeta(-1,-x). One could also imagine just giving a reference.

\reply{
A clarification is indeed necessary. We here use the Hurwitz zeta function regularization and so H stands for Hurwitz.

The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!}

I also think that Appendix E ("Alternative approach...") should come after the "actual" approach which is presented in Appendix F. There is also a typo in equ.(F9).

\reply{We have rearranged the order of appendixes as request. Now App. A is the calculation for the main analytic results. App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details.

We also fix the typo in Eq.(A9), where the $\frac{1}{6}$ should be $-\frac{1}{6}$.}

(4) The main result, namely the variation of the exponents in Equ. (27) and Figs. 8-10 as functions of the parameter theta is not discussed. The increase with theta must have some kind of physical interpretation and also the particular values at theta=0 and theta=pi/2.

\reply{We add two paragraphs in the discussion section about the main results.

We first deal with the three special points $\theta = 0, \frac{\pi}{4}, \frac{\pi}{2}$ and their special relations to the bcc operator ${\rm D} \rightarrow {\rm N}$, and then present a hand-waving argument that the quadratic relation should come from the dimension of the vertex operators.

In another paragraph, we use the free lattice boson model to argue why the exponent increase for larger $\theta$. 
}

(5) In all examples except the very last one in Fig.10, the outer boundaries of the chains remain the same and only the inner ones change. Therefore the notation for the change of boundary conditions introduced in (17) is unnecessary complicated. The formulation in (22) would be sufficient and much simpler.

(6) A number of equations expressing these changes of boundary conditions appear several times in identical form: (22),(37),(40); (24),(30) and Fig.7; (18),(26),(32),(38) and Fig.8; (28),(34) and Fig.9; (36),(39) and Fig.10. This is a redundancy which should be reduced.

\reply{Question (5) and (6) are about the notations of boundary conditions.

We remove the redundant boundary condition c in the some of the equations as long as it is equal to a. The simplified notation like $\text{DN} \rightarrow \lambda$ is better to be perceived as a single boundary condition changing process and the associated bcc operator.

Since the notation is shortened, we don't let them occupy a single equation and instead put them inside a sentence. We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase ``in Eq.(XX)'', and the time it saves to look up. }

(7) All References appear twice with different numbers! This must also be the reason, why the numbering in the text starts at 48. I am astonished that the authors did not notice that.

\reply{This is really embarrassing. We had 47 citations in our local version of manuscripts but 94 on the submission. We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.

But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }

(8) At no point could I see a remark on the analytical continuation from imaginary to real time. Instead, the notation changes back and forth between t and tau.

\reply{This point should be clarified in the introduction of the path-integral formalism(Sec. III. A.). All the path-integral spacetime diagrams are in the imaginary time. We only do analytic continuation to the final results of the imaginary time diagram.

We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq. (17). When referring to the imaginary path integral diagram, we use $\tau$ because that's the scale on Fig. 5 and Fig. 6. When representing the final result for Loschmidt echo, we do analytic continuation as Eq. (17). }

(9) As the parameter theta determines the transmission through the defect, it would be useful to give the transmission coefficient below Equ.(4) explicitly.

\reply{We have added the transmission coefficients and add a short paragraph discussing the parameter lambda around Eq. (10).}

(10) As to the figures:

- If one wants to show the folding in Figs. 3 and 4, one should not move and rescale the strip on the right hand sides but leave it in place. Then the meaning of the length L is also clearer. Incidentally, L appears here for the first time in the paper, which should also be changed.

- In Fig. 5, the boundary conditions should also be indicated on the right side.

\reply{We have modified Fig. 3 and 4 according to the suggestions.

We also define L to be the length immediately after the definition of fidelity and above Fig. 4 for echo.

We have dramatically change Fig. 5. 
}

- The legends in Figs. 7-10 are strange in that the analytical results are represented by a horizontal symbol (line), but the numerical ones by a vertical one.

\reply{The numerical results are represented by dots and error bar. The error bar is small and not clearly visible in these diagrams. We have modified the legend for Fig. 7-10 to make the vertical error bar clearer.}

- There is no (a) and (b) in Figs. 8 and 9, but in the caption these are referred to.

\reply{We have modified Fig. 8 and 9 accordingly.}

- The system sizes in the numerics given in the captions are unclear to me. What does 30k or 35k mean? In Fig. 7, it says k=1 immediately after that. Is this the same k? If not, what is it? As with L, I think that such numbers should also appear in the text. If one is talking about 35.000 sites, one wonders why such a large number was taken.

\reply{The k in the math mode font is the spring constant, while the $k$ after 30 and 35 means 1000. We didn't realize the conflict. We have changed 30k to 30000 and 35k to 35000. We take 35000 sites for reducing the finite size effect in Fig. 8 which is important for the theta value near zero. }

- Fig. 11 corresponds to the right piece of Fig. 6, but is rotated by 90°. This is confusing, in particular since the corresponding Fig. 12 is not rotated. The lambda line on the left has to be dotted. Also confusing is the use of x and L in (E1) below.

\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{\pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{\pi}$. }

(11) In a number of places the English has to be corrected (missing articles or endings, missing or incorrect words).

\reply{We have proofread the paper before the resubmission and (hopefully) corrected those grammatical/spelling errors.}

\end{document}
%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

### 2017-10-14 reply_2.tex
[referee] version resubmitted to prb.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\usepackage[autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{{./}}

\newcommand{\cf}{\textit{cf.} }
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }
\newcommand{\rev}[1]{{\color{red}#1}}

\newcommand{\up}{\mathord{\uparrow}}
\newcommand{\dn}{\mathord{\downarrow}}
\newcommand{\I}{\mathbb{I}}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\qed}[0]{$\blacksquare$}

\newcommand{\reply}[1]{{\color{black}#1}}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

% \definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
% \usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}

\begin{document}
\large
\color{blue}
{\bf \color{black} Report of the Second Referee -- BF13677/Zhou}

In the manuscript "Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface" the authors report on results concerning the finite volume decay exponent of the fidelity and long time exponent of the Loschmidt echo after joining two bosonic boundary CFTs. As they point out such exponents could potentially be observed in certain quantum wire experiments. The results appear to be correct and they are supported by independent numerical calculations coming from a harmonic lattice model.

I think the paper is interesting enough and sufficiently well written to be published in Physical Review B, but before acceptance I would like the authors to consider my remarks below and make the necessary modifications.

\reply{We thank the referee for the positive review and reply to the comments below.}

1) The introduction overestimates the results that are actually presented in the main text. In the fourth paragraph it is claimed that the paper studies joining two different CFTs, when in fact only a very special case is treated: joining two identical massless free boson theories, with arbitrary (but identical) boundary conditions though. It should be clarified in the introduction that we will only see results for this special case. In fact, paragraph 4 is not at all clear, it should be rewritten.

\reply{We agree that this paper only deals with 2d bosonic CFTs. However these CFTs can be different, e.g. having different compactification radii. The relation between lambda and the the different compactification radii are nevertheless hidden in the last appendix of the paper, which makes it hardly accessible to the readers. We also didn't explicitly point out the derivation (and physical interpretation) of this relation in one of the references we cited.

On the other hand, the boundary conditions on the sites that later connected are different. For example, the notation DN means that one end of the chain has Dirichlet and the other end that connects to it has Neumann boundary conditions, see Fig. 3.

After connection, normally one should assume it's a periodic boundary condition (after folding) which gives transmission coefficient 1. However, in the text we consider more general conformal interface that can have arbitrary transmission coefficient between 0 and 1. Such interface can indeed be realized by connecting two boson theories with different compactification radii.

To clarify this issue, we have rewritten paragraph 4 in the introduction that made the following changes 
\begin{itemize}
\item We rephrase what we did as ``generalization to interface that is partially transmissive''.
\item We list the examples we talked about in this paper: the harmonic chain example(non-compact boson), the two different 1+1 bosonic CFT with different radii.
\item We also explicitly mention the the dependence of lambda w.r.t. the different compactification at the end of Sec. II. A
\end{itemize}
}

2) In this 4th paragraph of the introduction (also recurring in some places later) it is mentioned that the parameter lambda is controlled by the ratio of compactification radii. Is this so? This point is never discussed in the main text (or the appendices). Doesn't lambda describe the interface after joining the two CFTs and the compactification radii are the same in the two theories? At least in the case considered in the main text.

\reply{It is our fault that the relation of lambda and ratio of the compactification radii are not pointed out explicitly in the main text. 
We have made changes in paragraph 4 accordingly and also some texts in the end of Sec.II.A to discuss the generalization to compact bosons (with different radii)}

3) In section 3 after Eq. (16) twist fields are mentioned but these were never introduced before, therefore the statement "The tip of the slit is no longer a twist field..." doesn't seem to be self-contained.

\reply{We avoid the use the phrase ``twist field'' and change it to corner singularity and cite Cardy1988 for its treatment.}

4) After Eq. (17) it is stated that the boundary condition "c" is neglected. Isn't it taken to be "a" instead?

\reply{Our statement is incorrect. It is taken to be a and changing it will influence the result even in the large L limit. So we did no€™t neglect c€ but taking it to be a€™. We also take a simpler notation for this case after Eq. (17) }

5) Now we come to the main result of the paper, Eq. (23), that will yield all the exponents which will then be numerically verified. Despite this equation being the main results, its derivation is hidden away in an appendix. In fact all the calculations in this paper are demoted to be part of one of the numerous Appendix sections. I believe, that at least the main result should be given some space in the main text. I don't think this would compromise readability or accessibility of the results, in fact it think it would improve on it.

\reply{The derivation of Eq.(23) is contained in the original App. F, which is mainly the evaluation of partition function using a determinant identity with no physical arguments.

In order to improve readability, we first setup the calculation in the main text by explicitly spelling out the boundary states and the Hamiltonian in terms of the bosonic operators. We end up with an vacuum amplitude with three exponentials of bilinears bosonic operators in between. Such an expression can be evaluated using the determinant identity in the appendix. And we defer the detailed technical calculation in App. A.

In fact, we have rearranged the orders of the appendices for better accessibility.

App. A is the calculation for the main analytic results. The reader shall only need this appendix to reproduce Eq.(23).

App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details. We have also mentioned these structural changes in the end of the introduction.}

6) The last sentence before Sec. 4 states that the analytical (incorrect) and numerical curves "merge" at theta=0. In fact, these two curves are quite different and clearly the analytical curve cannot reproduce the numerics at all, as expected. To me it seems like that the green curve coincides with the dots in Fig. 10 only by chance. I'm not sure what the relevance of this curve is or mentioning that at theta=0 the numerics and the (incorrect) analytics "merge." This merging is simply because theta=0 is the no-quench point, when the pre- and post-quench setup is the same.

\reply{We have remove the sentence of ``merging'' at theta = 0. That is as the referee said only a calibrating point. But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence. The difference $1/8$› is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c). We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

7) The references appear in duplicate.

\reply{This is really embarrassing. We had 47 citations in our local version of manuscripts but 94 on the submitted. We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.

But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }

8) Additionally, there are typos throughout the text that should be corrected (e.g. like "the this"), I suggest the manuscript to be proofread carefully before resubmission.

\reply{We have proofread the paper before the resubmission and (hopefully) corrected those grammatical/spelling errors.}

\end{document}
%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

### 2017-10-14 prb_sub.sh

@@ -1,4 +1,4 @@
 #!/bin/bash
 
-./flatex -v bCFT_paper.tex
+./flatex -v -b bCFT_paper.tex
 tar --transform='flags=r;s|.flt|.tex|' -cvzf bCFT_paper.tar.gz bCFT_paper.flt images *.bbl

### 2017-11-30 F_correction.tex
[paper] referee's suggestions done.

@@
 In the course of deriving the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state calculation in App.~\ref{app:lambda_12} (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable.
-However, free energy is not invariant under the conformal transformation since the boundaries partially break the conformal symmetry.
+However, the free energy is not invariant under the conformal transformation since the boundaries partially break the conformal symmetry.
 In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term to get the correct exponent of the fidelity and Loschmidt echo.
@@
 % staircase geometry correction
-The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction.
+The annulus on the $\xi$ plane is called the staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction.
 The traditional radial quantization however has radial direction to be the time.

### 2017-11-30 analy_eval.tex
[paper] referee's suggestions done.

@@
 This can be resolved by the following observation.
-There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}.
+There exists a conformal map $\zeta(\xi)$ that maps the non-concentric circles to the two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}.
 Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$.
@@
 where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$.
-A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.
+A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformal transformation of the stress tensor from annulus to cylinder.
 

### 2017-11-30 compact_boson.tex
[paper] referee's suggestions done.

@@
-In this appendix, we address the issue of winding modes of compact bosons.
-In the main text, we have exclusively worked with the oscillator modes of free bosons.
-Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order.
+In this appendix, we address the issue of the winding modes of the compact bosons.
+In the main text, we have exclusively worked with the oscillator modes of the free bosons.
+Here, we shall show that winding modes for the compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order.
 Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.
@@
 \end{equation}\end{widetext}
-where $n,m$ are momentum and winding modes quantum numbers.
+where $n,m$ are the momentum and winding modes quantum numbers.
 
@@
 The boundary state we need here however lives on $x = 0$ -- a equal-space slice.
-We therefore compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
+We therefore compact the theory in the time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
 \begin{equation}

### 2017-11-30 disc.tex
[paper] referee's suggestions done.

@@
 The two types of conformal interface do not talk to each other because they are imposed on different fields.
-If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$.
+If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the dual field of $\phi$.
 In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group that can not be connected even by taking singular values of $\lambda$.
@@
 
-For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}.
+For the more interesting case where the boundary conditions are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}.
 We can first understand the values of several special points on this curve.
@@
 \end{equation}
-we can get the exponent to be $\frac{1}{2}$, which agrees with Fig.~\ref{fig:DDNN}. 
+we get the exponent to be $\frac{1}{2}$, which agrees with Fig.~\ref{fig:DDNN}. 
 \item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$.
-The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
+The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice of the dimension of the bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
 \end{itemize}

### 2017-11-30 general_formulation.tex
[paper] referee's suggestions done.

@@
 \end{aligned}\end{equation}
-For generic values of $\theta$, the interface is partially-transmitting, whose transmission coefficient is $\pm \sin 2 \theta$.
+For generic values of $\theta$, the interface is partially-transmitting, whose transmission coefficient is $\sin^2 2 \theta$.
 
@@
 for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on two sides.
-This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by universal parameters of the CFTs on both sides.
+This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the universal parameters of the CFTs on both sides.
 
-The winding modes however do not contribute to the fidelity and echo exponent to the leader order, as shown in App.~\ref{app:compact_diff_boson}.
+The winding modes however do not contribute to the fidelity and echo exponent to the leading order, as shown in App.~\ref{app:compact_diff_boson}.
 So the derivations with the non-compact boson boundary state in Eq.~\eqref{eq:bd_state} holds true for the compact bosons.

### 2017-11-30 gnd_dn_lambda.tex
[paper] referee's suggestions done.

@@
 \end{equation}
-where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators defined as usual
+where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators are defined as usual
 \begin{equation}
@@
 \end{equation}
-We use Hurwitz zeta function
+We use the Hurwitz zeta function
 \begin{equation}

### 2017-12-01 analy_eval.tex
[paper] Proofread very quickly...

@@
-In this subsection, we relate the free energy to the amplitudes between boundary states and present the analytic results.
+In this subsection, we relate the free energy to the amplitudes between boundary states, and present the analytic results.
 
@@
 The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently use the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders.
-The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, so will not affect the fidelity and echo exponents.
+The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, which will not affect the fidelity and echo exponents.
 

### 2017-12-01 def_fidel_echo.tex
[paper] referee's suggestions done.
[paper] Proofread very quickly...

@@
 Taking the horizontal axis as imaginary time direction, the fidelity can be diagrammatically represented in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
-The logarithmic fidelity is then (twice) the free energy of this diagram
+The logarithmic fidelity is then (twice of) the free energy of this diagram
 \begin{equation}
@@
 
-The Loschmidt echo is also the (square of the) overlap of two wavefunctions.
+The Loschmidt echo is also (square of) the overlap of the two wavefunctions.
 One of them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
@@
 at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity.
-According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in the fidelity and $\ln \tau$ in the Loschmidt echo.
+According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in the fidelity and $\ln \tau$ in the Loschmidt echo.
 One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit.
-In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or the integration version of the Ward identity.
+In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or the integral version of the Ward identity.
 If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}

### 2017-12-01 free_boson_lattice.tex
[paper] Proofread very quickly...

@@
 
-We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ at lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
+We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ at the lattice site $i$.
+The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
 \begin{equation}
@@
 We performed the standard scattering analysis in App.~\ref{app:interface_free_boson}.
-For mode with momentum $k$, the only possible scale invariant $S$-matrix is
+For modes with momentum $k$, the only possible scale invariant $S$-matrix is
 \begin{equation}

### 2017-12-01 analy_eval.tex
[paper] 2nd resubmission

@@
-In this subsection, we relate the free energy to the amplitudes between boundary states, and present the analytic results.
+In this subsection, we relate the free energy to the amplitudes between the boundary states, and present the analytic results.
 
@@
 Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and drop those scales.
-The introduction of regulators is also physically sensible when considering the lattice realization of the systems.
+The introduction of the regulators is also physically sensible when considering the lattice realization of the systems.
 
@@
 \caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $.
-The two black dots represent possible locations of boundary condition changing (bcc) operators.
+The two black dots represent possible locations of the boundary condition changing (bcc) operators.
 The dot inside the blue semi-circle has coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries.

### 2017-12-01 bCFT_paper.tex
[data] PDN data updated.
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[draft] wording changes for descritive text.
[draft] reference order updated
[review] Forgot to commit just now. Fig. 3, 4, 5, 11 changed. Appendices are rearranged such that analytical ones are before the numerical ones.
[review] various changes in the text, and discussion of the conformal transformation  added (called reply_reviewee)
[referee] 1. answer all the referee questions. 2. make major changes in

@@
 \renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
+\newcommand{\rev}[1]{{\color{red}#1}}
 
@@
 
-\title{Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface}
+\title{Bipartite Fidelity and Loschmidt Echo of the Bosonic Conformal Interface}
 
@@
 \label{sec:bosonic_conformal_interface}
+
 \subsection{General Formulation}
@@
 \input{general_formulation}
+
 \subsection{A Free Boson Lattice Model}
@@
 \label{sec:analytic_numerics}
+
 \subsection{Definition}
 \input{def_fidel_echo}
+
 \subsection{Notation of Boundary Conditions}
@@
 \input{bd_notation}
+
 \subsection{Analytic Evaluation}
@@
 \input{analy_eval}
+
 \subsection{Numerical Results and Comparison}
@@
 We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Michael Stone, Taylor Hughes and Romain Vasseur during the course of this research.
+We would like to thank Shinsei Ryu, Michael Stone, Taylor Hughes for reading the manuscripts.
+We also acknowledge the valuable questions and comments from the referees.
 TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
@@
 \appendix
+
+\section{General Boundary State Amplitude}
+\label{app:lambda_12}
+\input{lambda_1_lambda_2}
+
+\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
+\label{app:gnd_dn_lambda}
+\input{gnd_dn_lambda}
+
 \section{Corrections to the Free Energy}
@@
 \input{F_correction}
+
+\section{Winding Modes of Compact Bosons}
+\label{app:compact_diff_boson}
+\input{compact_boson}
 
@@
 
+\section{A Determinant Identity for the Boundary State Amplitude}
+\label{app:pf_of_id}
+\input{pf_of_id}
+
 \section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
@@
 
-\section{A Determinant Identity for the Boundary State Amplitude}
-\label{app:pf_of_id}
-\input{pf_of_id}
-
-\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
-\label{app:gnd_dn_lambda}
-\input{gnd_dn_lambda}
-
-\section{General Boundary State Amplitude}
-\label{app:lambda_12}
-\input{lambda_1_lambda_2}
-
-\section{Winding Modes of Compact Bosons}
-\label{app:compact_diff_boson}
-\input{compact_boson}
-
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{bCFT}

### 2017-12-01 bd_notation.tex
[paper] 2nd resubmission

@@
 Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status of the two ends of the chain before and after the quench.
-The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on $ab$ interface.
+The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the $ab$ interface.
 The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench.
@@
 In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$.
-The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition.
+The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of the boundary condition.
 For instance, the notation for the process presented in Fig.~\ref{fig:echo} is

### 2017-12-01 conclusion.tex
[paper] 2nd resubmission

@@
 These two features are tested in three typical processes in the numerical calculation of the harmonic chains.
-After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error.
-Although tangential to the non-equilibrium dynamics, the fidelity calculation was used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.
+After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error.
+Although tangential to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.
 

### 2017-12-01 def_fidel_echo.tex
[paper] 2nd resubmission

@@
 They sandwich the evolution of the connected chains.
-In the folding picture at the right, $a,b,c$ represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).}
+In the folding picture on the right, $a,b,c$ represent the most general boundary conditions of the chains (for example, $a$ and $c$ are DN according to the left figure).}
 \label{fig:echo}

### 2017-12-01 disc.tex
[paper] 2nd resubmission

@@
 The two types of conformal interface do not talk to each other because they are imposed on different fields.
-If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the dual field of $\phi$.
+If we treat $S_1$ as a combination of the Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the dual field of $\phi$.
 In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group that can not be connected even by taking singular values of $\lambda$.

### 2017-12-01 general_formulation.tex
[paper] 2nd resubmission

@@
 For example, one may use the current operator rather than the Virasoro generator to solve the zero-momentum flow condition.
-This idea dates to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
+This idea dates back to the discovery of the Ishibashi state\cite{ishibashi_boundary_1989} and has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}.
 Additionally, the fusion algebra has also been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.
@@
 In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot penetrate.
-The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions.
+The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of the Dirichlet and Neumann boundary conditions.
 For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left.
@@
 We shall interpret these identities to be valid only when acting on the boundary states.
-The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
+The mode expansion of free boson at $x = 0$\cite{di_francesco_conformal_1997} is
 \begin{equation}
@@
 \end{equation}
-for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on two sides.
-This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the universal parameters of the CFTs on both sides.
+for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on the two sides.
+This also suggests that connecting two different CFTs will generate an interface whose transmission coefficient are determined by the universal parameters of the CFTs on both sides.
 

### 2017-12-01 intro.tex
[paper] 2nd resubmission

@@
 One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band.
-The X-ray absorption rate will then have a power singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
+The X-ray absorption rate will then have a power law singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency.
 There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in the spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc
@@
 % non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
-Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}.
+Recently, more attention has been paid to the non-equilibrium dynamics of quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}.
 The ``cut-and-join" quench protocol is a popular framework for investigating the spreading of the influence from the localized impurity (or boundary) across the system.
@@
 Various quantities can be used to detect the information in the quench process.
-For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of the entanglement entropy in subsystem A, when both A and B are identical critical systems.
+For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem A, when both A and B are identical critical systems.
 The authors ascribe such increase to the proliferation and propagation of the quasi-particle excitations emitted at the joint.
@@
 \caption{Cut-and-join quench protocol.
-Left panel: Prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian.
+Left panel: Prepare the ground states of the two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian.
 Right panel: Spacetime diagram of the cut and join protocol.
@@
 In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient.
-In the case of compact boson, $\lambda$ is controlled by the ratio of the compactification radii, while for the free lattice boson it is controlled by the ratio of masses.
+In the case of the compact boson, $\lambda$ is controlled by the ratio of the compactification radii, while for the free lattice boson it is controlled by the ratio of masses.
 We expect it to be tunable in a realistic experimental setting.
@@
 We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models.
-The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
+The Loschmidt echo is the (square of the) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$.
 It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit.
-The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
+The decay exponent $\alpha$ has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}.
 We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
@@
 In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation.
-We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}.
-The details of numerical simulation are presented in App.~\ref{app:comp_fid_echo}.
+We derive the scale invariant interface for the free bosonic lattice in App.~\ref{app:interface_free_boson}.
+The details of the numerical simulation are presented in App.~\ref{app:comp_fid_echo}.
 

### 2017-12-01 num_result.tex
[paper] 2nd resubmission

@@
 The inset is a typical Loschmidt echo diagram, whose linearly decreasing behavior in the log-log scale indicates the expected power law decay.
-We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast.
+We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD} as contrast).
 The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $.
@@
 The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text.
-Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$.
+Inset in (a): From top to bottom, we show the power law decay of the Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$.
 Finite size effect does not emerge before $t=10^{4}$.

### 2017-12-13 F_correction.tex
[prb] version accepted by prb.

@@
 % outer boundary correction
-It is discussed in Cardy and Peschel's work\cite{cardy_finite-size_1988} that boundary will contribute a logarithmic term in the free energy,
+It is discussed in Cardy and Peschel's work\cite{cardy_finite-size_1988} that the boundary will contribute logarithmic term in the free energy,
 \begin{equation}
@@
 They will have negligible contributions to the free energy.
-However, in the new $\xi$ plane, we implicitly switch to a {\it new short distance regulator} such that only the blue semi-circle around $0$ contribute negligibly.
-The outer surface radius, despite being the image of a small semi-circle on $z$ plane, will contribute a $-\frac{c}{6} \ln \frac{r_2}{a}$ term on the $\xi$ plane that should not be there.
+However, in the new $\xi$ plane, we implicitly switch to a {\it new short distance regulator} such that only the blue semi-circle around $0$ contributes negligibly.
+The outer surface radius, despite being the image of a small semi-circle on the $z$ plane, will contribute a $-\frac{c}{6} \ln \frac{r_2}{a}$ term on the $\xi$ plane that should not be there.
 

### 2017-12-13 abstract.tex
[prb] version accepted by prb.

@@
 The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartite fidelity as $L^{-\frac{\alpha}{2}}$.
-We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
-Possible physical realizations of these interfaces include for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.
+We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are of the same type of $S$, while remaining $\frac{1}{4}$ otherwise.
+Possible physical realizations of these interfaces include, for instance, connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states, \etc and the exponent can be detected in a X-ray edge singularity type experiment.
 

### 2017-12-13 analy_eval.tex
[prb] version accepted by prb.

@@
 Again, we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}.
-From $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case.
+From the $z$ plane to the $\xi$ plane, we use $\xi = \frac{z}{\tau - z}$ to map the two slits to half of an annulus, which is the same as the fidelity case.
 With one more conformal mapping $w = \ln \xi$, the diagram again becomes the cylinder partition function between the two boundary states.
@@
 In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus.
-The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
+The four intersection points of two standard concentric circles on the $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
 \begin{equation}
@@
 
-As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND.
+As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, and $S_1( \theta )$ interpolates between DN and ND.
 In the region accessible to the numerical calculation in the lattice model, we choose the process ${\rm DD} \rightarrow  \lambda$ to verify

### 2017-12-13 bd_notation.tex
[prb] version accepted by prb.

@@
 The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the $ab$ interface.
-The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench.
+The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior to the quench to $b$/$c$ after the quench.
 Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as

### 2017-12-13 comp_fid_echo.tex
[referee] version resubmitted to prb.
[prb] version accepted by prb.

@@
 
-During the course of derivation in this and other appendices, we will repeatedly use the combinatorial identity called McMahon Master theorem
+During the course of derivation in this and other appendices, we will repeatedly use the combinatorial identity called the McMahon master theorem
 \begin{equation}
@@
 where ${\bf b}\equiv(b_{1},...,b_{n})^T$ is a vector of bosonic annihilation operators.
-The matrix $M$ consists of a $n\times n$ Hermitian block $A$ which plays the role of single particle Hamiltonian in the fermionic case and symmetric block $B$ of the pairing interaction.
+The matrix $M$ consists of a $n\times n$ Hermitian block $A$ which plays the role of a single particle Hamiltonian in the fermionic case and symmetric block $B$ of the pairing interaction.
 
@@
 \end{aligned}\end{equation}
-in which the Hamiltonian reads
+in which the Hamiltonian is
 \begin{equation}\begin{aligned}
@@
 
-We will not elaborate on Williamson's theorem and its proof (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in entanglement entropy context\cite{coser_contour_2017}).
-Instead we will show in App.~\ref{app_sub:harmonic_chain} that for the problem of harmonic chain we are interested in, the diagonalization can be easily done without using the general recipe in the Williamson theorem.
+We will not elaborate on Williamson's theorem and its proof (see proofs in Ref.~\onlinecite{xiao_theory_2009,pirandola_correlation_2009,gosson_symplectic_2006} and also a recent application in the entanglement entropy context\cite{coser_contour_2017}).
+Instead we will show in App.~\ref{app_sub:harmonic_chain} that for the problem of the harmonic chain we are interested in, the diagonalization can be easily done without using the general recipe in the Williamson theorem.
 
@@
 
-Suppose we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and in $b$ basis it satisfies
+Suppose we have obtained the required matrix $S$, the ground state will be the vacuum of the annihilation operators defined in Eq.~\eqref{eq:def_a} and in the $b$ basis it satisfies
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where the normalization is given by the McMahon Master theorem Eq.~\eqref{eq:bosonic_McMahon}.
+where the normalization is given by the McMahon master theorem Eq.~\eqref{eq:bosonic_McMahon}.
 Apply constraint in Eq.~\eqref{eq:constraint_1}, it simplifies to the top left corner of the symplectic matrix
@@
 
-We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in ${\bf b}$ basis, as in Eq.~\eqref{eq:quadratic_boson_H}.
-From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in ${\bf a}$ basis for positive definite $M$.
-At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in ${\bf b}$ basis, but is diagonalized in a new basis ${\bf c}$.
+We start with a quadratic bosonic Hamiltonian $\hat{H}_0$ in the ${\bf b}$ basis, as in Eq.~\eqref{eq:quadratic_boson_H}.
+From the discussion in App.~\ref{app_sub:boson_BdG}, we are able to diagonalize it in the ${\bf a}$ basis for positive definite $M$.
+At $t=0$, the Hamiltonian becomes $\hat{H}_1$, which is still written in the ${\bf b}$ basis, but is diagonalized in a new basis ${\bf c}$.
 The corresponding Bogoliubov transformations read
@@
 
-In this subsection, we explicitly construct the matrix $\mathcal{S}$ for the case of harmonic chain introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
-In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain reads
+In this subsection, we explicitly construct the matrix $\mathcal{S}$ for the case of the harmonic chain introduced in Sec.~\ref{sec_sub:free_boson_lattice}.
+In the basis defined in Eq.~\eqref{eq:real_basis}, the Hamiltonian for 1D harmonic chain is
 \begin{equation}\begin{aligned}
@@
 
-The matrix $\mathcal{S}$ that diagonalize $\mathcal{M}$,
+The matrix $\mathcal{S}$ that diagonalizes $\mathcal{M}$
 \begin{equation}

### 2017-12-13 compact_boson.tex
[prb] version accepted by prb.

@@
 In Ref.~\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space.
-The boundary state we need here however lives on $x = 0$ -- a equal-space slice.
+The boundary state we need here however lives on $x = 0$ -- an equal-space slice.
 We therefore compact the theory in the time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as
@@
 \end{equation}
-the $S$ matrix establish a relation between the modes
+the $S$ matrix establishes a relation between the modes
 \begin{equation}
@@
 where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}.
-The g-factor can only be determined by the Cardy condition\cite{cardy_boundary_2004}.
+The $g$-factor can only be determined by the Cardy condition\cite{cardy_boundary_2004}.
 Since it is not important for what follows, we shall not include the calculation here.
 
-Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraints on the winding number
+Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraint on the winding number
 \begin{equation}
@@
 The winding mode thus can contribute at most a $\ln\beta$ term to the free energy.
-Compared to the result in App.~\ref{app:lambda_12}-\ref{app:gnd_dn_lambda}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.
+Compared to the result in App.~\ref{app:lambda_12}-\ref{app:gnd_dn_lambda}, we conclude that the winding mode contribution will not present in the leading order of the large $\beta$ limit.
 

### 2017-12-13 conclusion.tex
[prb] version accepted by prb.

@@
 
-We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on the quantum wire systems.
+We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singularity type experiment on the quantum wire systems.
 

### 2017-12-13 def_fidel_echo.tex
[prb] version accepted by prb.

@@
 \end{equation}
-For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length $L$, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface.
+For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length $L$, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with the conformal interface.
 Both of them can be produced by an imaginary time evolution.
 Taking the horizontal axis as imaginary time direction, the fidelity can be diagrammatically represented in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$.
-The logarithmic fidelity is then (twice of) the free energy of this diagram
+The logarithmic fidelity is then (twice) the free energy of this diagram
 \begin{equation}
@@
 The solid dot represents boundary condition changing (bcc) operator.
-Here D(Dirichlet), N(Neumman), $\lambda$(permeable interface parameterized by $\lambda$) are possible choices of boundary conditions.}
+Here D(Dirichlet), N(Neumman) and $\lambda$(permeable interface parameterized by $\lambda$) are possible choices of boundary conditions.}
 \label{fig:fidel}
@@
 \end{equation}
-where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo.
+where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for the echo.
 

### 2017-12-13 disc.tex
[prb] version accepted by prb.

@@
 \item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$.
-The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice of the dimension of the bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
+The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of the bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
 \end{itemize}

### 2017-12-13 free_boson_lattice.tex
[prb] version accepted by prb.

@@
 
-The lattice model in Eq.~\eqref{eq:lattice_H} with bond interaction defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both the Loschmidt echo and the fidelity.
+The lattice model in Eq.~\eqref{eq:lattice_H} with the bond interaction defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both the Loschmidt echo and the fidelity.
 

### 2017-12-13 general_formulation.tex
[prb] version accepted by prb.

@@
 
-We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state.
+We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which imposes the conformal invariant boundary condition on the classical scalar fields and then quantize it to obtain the boundary state.
 The interface obtained is the same as the one by using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but this viewpoint gives a more intuitive scattering picture and has more transparent relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice}.
@@
 In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot penetrate.
-The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of the Dirichlet and Neumann boundary conditions.
-For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left.
+The interface reduces to individual boundary conditions for the boson on the left and right half planes: They are a combination of the Dirichlet and Neumann boundary conditions.
+For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that the Dirichlet boundary condition is imposed on the right and the Neumann boundary condition on the left.
 Hereafter we shall denote this combination as `DN'.
@@
 We will denote it as ``P'' as it corresponds to the traditional periodic boundary condition.
-For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface.
+For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted across the interface.
 \end{enumerate}
@@
 \partial_+\phi^2
-\end{pmatrix}.
+\end{pmatrix},
 \end{aligned}\end{equation}

### 2017-12-13 gnd_dn_lambda.tex
[prb] version accepted by prb.

@@
 \caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions.
-We unfold the cylinder and the new stripe have N and D boundary conditions on the top and bottom plus a $\lambda$ junction in the middle.
+We unfold the cylinder and the new stripe has N and D boundary conditions on the top and bottom plus a $\lambda$ junction in the middle.
 The length $L$ here is the height of the unfolded cylinder $2\pi$.
@@
 \end{equation}
-It is evident that the momentum $k$ is shifted from integer multiple of $\frac{2\pi}{L}$ due to the $\lambda$ boundary condition in the middle.
+It is evident that the momentum $k$ is shifted from an integer multiple of $\frac{2\pi}{L}$ due to the $\lambda$ boundary condition in the middle.
 

### 2017-12-13 intro.tex
[prb] version accepted by prb.

@@
 We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transmission coefficients.
-Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise.
+Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remaining $\frac{1}{4}$ otherwise.
 The finite size fidelity calculation further supports these results.
@@
 The rest of the paper is organized as follows.
-In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable bosonic conformal interface and its lattice realization.
-In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison.
+In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for the permeable bosonic conformal interface and its lattice realization.
+In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with the fidelity and Loschmidt echo, and present the numerical results for comparison.
 We discuss our results and related experimental works in Sec.~\ref{sec:disc}.

### 2017-12-13 num_result.tex
[prb] version accepted by prb.

@@
 The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details.
-In all the figures, we present the coefficients of the logarithmic term $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.
+In all the figures, we present the coefficients of the logarithmic terms $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.
 
@@
 We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD} as contrast).
-The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $.
+The exponent (negative of the slope of the line in the log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $.
 The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point.
@@
 We also calculated the companion process ${\rm NN} \rightarrow \lambda$ and obtain identical exponents as in Fig.~\ref{fig:DDDD}.
-We avoid the technical subtlety of zero mode by adding a small mass regulator $m=10^{-8}$.
+We avoid the technical subtlety of the zero mode by adding a small mass regulator $m=10^{-8}$.
 While the short time decay pattern is different from the DD case, the long-time behavior and exponents remain the same for both echo and fidelity.
@@
 We worked with a system containing $35000$ sites.
-A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
+A direct calculation with the mass regulator does not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction.
 We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process (see the full notation in Eq.~\eqref{eq:Full_notation_rand()})
